### 2019-06-28 abstract/abstract.tex
TIFS one pass done

%!TEX root = ../article.tex

% Abstract
\begin{abstract}

Nowadays, users' sensitive data in edge computing devices (desktops, laptops, and tablets, etc.) is at high risk because they run applications on potentially compromised or malicious systems. To address this problem, hardware manufacturers such as Intel released a new processor feature called Software Guard eXtension (SGX), and provisions shielded executions (i.e., enclaves) for security-sensitive computations. Regrettably, Intel SGX's design objectives omit trusted I/O paths. Without such guarantees, it is unlikely for an enclave to fulfill its security and privacy purposes because the source or sink of data may have been corrupted.

To this end, we propose a novel architecture called \textsc{Aurora} to provide trusted I/O paths for enclave programs even in the presence of untrusted system software.
Specifically, \textsc{Aurora} exploits two commercial-off-the-shelf x86 platform features (System Management Mode, SMM and SGX) and establishes a secure channel between an enclave program and target device.
Furthermore, we design and implement trusted paths for HID keyboard, serial port printer, hardware clocks, and USB mass storage, respectively. Leveraging these trusted paths, we protect real-world applications including OpenSSH client, OpenSSL server/client and SQLite database.
Security evaluations show that \textsc{Aurora} mitigates several kinds of I/O related attacks. Performance evaluations demonstrate that \textsc{Aurora} introduces acceptable overheads.

\end{abstract}

### 2019-06-28 sections/main.tex
TIFS one pass done

%!TEX root = ../article.tex

% Entry point for sections:
%
% This file specifies the sections and  its respective order in which they must
% be included.

% Article Sections

\section{Introduction}
%% 从定义出发 “可信计算” 的定义出发，可信计算包含五个组件。%% 云环境下安全问题众多（引用云攻击综述）；用户安全与隐私问题受人关注，IntelSGX应运而生，已有不少工作，例如针对原装二进制、数据分析、网络中间件等一系列工作横空出世，都很好地利用SGX自身的特点，那就是内存对外不可见。但是缺乏对安全IO的保证。
Trusted computing~\cite{DBLP:journals/ieeesp/Felten03} encompasses six key technologies including: 1) endorsement key, 2) protected execution, 3) sealed storage, 4) secure input and output, 5) remote attestation, and 6) trusted third party. To this end, Intel provisions Software Guard eXtensions (SGX) \cite{DBLP:conf/isca/McKeenABRSSS13} to establish trusted execution environment that protects the integrity and confidentiality of desired computation. %This technology can be treated as "protected execution" in these six requirements.
%% 比较可惜的是，这项技术本身并没有为数据的通道做任何加固。一个只计算不交互的应用几乎是不存在的，比如上面提到的工作，都对IO的吞吐做了评测。也就是说，SGX 不保护数据的安全进出，只保护计算过程本身。对于不可靠的数据，我们认为计算是没有价值的，例如时间。此外，我们认为，已有的SGX 网络工作更多保护了应用层数据，对底层的包数据没有很好的加固。这些都和SGX技术自身设计的出发点有关，那就是归根结底要依赖不可信的OS。
Intel SGX enforces strong isolation in memory for security-sensitive compartments in a user-level application, called \textit{enclaves}, from untrusted privileged systems. Many SGX-based protection architectures~\cite{DBLP:journals/tocs/BaumannPH15,DBLP:conf/osdi/HuntZXPW16,DBLP:conf/osdi/ArnautovTGKMPLM16,DBLP:conf/icdcs/NguyenG17,7545819,DBLP:conf/sp/SchusterCFGPMR15,WangSET18} have already been proposed to secure data and code on untrusted servers.

Unfortunately, Intel SGX enclaves have no direct access to any hardware resources because Intel SGX by design does not support any secure input/output mechanisms according to its Software Developer's Manual~\cite{Corporation2016Intel}. Concerning I/O requests, an enclave has to rely upon the untrusted compartments through system call interfaces. This unreliable dependency is susceptible to attacks such as memory-based Iago attacks~\cite{DBLP:conf/asplos/CheckowayS13} and I/O-based traffic analysis~\cite{DBLP:conf/ccs/MittalKJCB11}.

A trusted path between an enclave program and a target I/O device is a protected channel that assures the secrecy and authenticity of transferred data. It is extremely critical to user's privacy such as health information, financial account, personal documents, etc on personal computers. The private data can be protected inside an enclave during runtime, but it is impossible to protecte it at the time of being printed since typically printer devices only understand plaintext data and the corresponding drivers are under the control of the untrusted kernel. Similarly, the textual input from users such as keystrokes can be recorded on a compromised computer, which is a very serious problem when it comes to password security~\cite{DBLP:conf/uss/SilverJBCJ14}. Previous research like SafeKeeper \cite{DBLP:conf/www/KrawieckaKPMA18} only protects the password on the server side, but cannot protect the user's password from keylogging threats on the client side.

%% 以时间为例，LibOS的shield模块对系统毫无检验的能力；一些必须依赖正确时间的区块链程序只好去远程取绝对时间；Intel虽然在17 年从AMT/ME给出了可信时间服务，但依旧没有妥善解决这个问题，那就是高频时间戳请求下的精度问题。结果就是，来Intel自家的OpenSSL库都要用系统ftime接口，得到毫秒精度时间戳。
Intel SGX enclaves also suffer from the loss of a high-precision trusted clock.
State-of-the-art library OSes such as Haven~\cite{DBLP:journals/tocs/BaumannPH15}, Graphene-SGX~\cite{DBLP:conf/usenix/TsaiPV17} and Panoply \cite{shinde_panoply:_2017} relay the clock value from  untrusted systems. As a result, these systems are vulnerable to time deception attacks. Blockchain systems like Town Crier~\cite{DBLP:conf/ccs/ZhangCCJS16} depend on a remote server for a trusted time; however, this clock latency is high (usually hundreds of milliseconds) and uncertain. Intel Management Engine (ME) offers a trusted clock service for SGX enclaves, but the time value is coarse-grained (second-resolution) and not absolute at all \cite{intel_psw}. It is not satisfactory for those enclaves that request the timestamp information at a high frequency, (e.g., tens or hundreds of times per second). Hence, to achieve millisecond-resolution time, Intel SGX SSL~\cite{intel_sgx_ssl} has to use \textit{ftime}, offered by the OS, which contradicts original SGX threat model. Cryptographic libraries such as TaLos~\cite{TaLoS}, mbedTLS-SGX~\cite{mbedtls}, WolfSSL-SGX~\cite{wolfSSL} encounter the same problem as well. Additionaly, another trusted service named Intel monotonic counters are slow and the used NVRAM will wear out after a limited times of writes.

%% 我们不禁要反诘：如今的方案真的能保护好Enclave吗？尤其是那些会和不可信OS 交互的enclave？如果不行，我们继续问：那么到底怎样才能做好呢？所以，本文就是要探索一种方法，给SGX程序强有力的IO安全保护，本质还是为了保护enclave。当然，我们的场景设在云上，没有变。
%As for some enclave programs that require human interactions like keyboard/mice input and display on the screen,
Today's SGX ecosystem has not yet come up with an off-the-shelf solution to trusted I/O paths. Enclaves themselves cannot authenticate whether they are communicating with trusted devices or not. 
%Therefore, we make a bold judgment that: without trusted I/O paths, SGX enclaves themselves cannot fully accomplish their security purposes. 
It is significantly important to solve the problem on \textbf{\emph{how to establish trusted I/O paths for enclaves on untrusted systems}}, as almost all SGX-based projects exclude the underlying OS from the trusted computing base (TCB) while awkwardly depending on it for I/O requests. %In this paper, we concentrate on providing TIOS for enclaves, e.g. \textbf{device-to-enclave secure network, high-resolution absolute clock, and isolated keyboard input}, which are essentially significant yet rarely discussed in current SGX ecosystems.

%% 所以，我们有了Aurora，专门提供可信IO服务的Aurora，它负责为enclave提供一条直达IO设备的可信路径。这个方法引入了一个可以执行特权指令、访问IO 设备的特殊“enclave”，即系统管理模式RAM。它是现有X86架构下的一块高特权飞地，同一模式下的飞地外代码、其他模式都无法访问和修改它。我们在SMRAM 和enclave间构建本地的可信路径，就能很好地给enclave提供绕过不可信区域的IO可信路径！
On Intel x86 platforms, we observe that 1) all peripheral I/O devices are connected with south-bridge to I/O Advanced Programmable Interrupt Controller (I/O APIC), 2) I/O interrupts can be rerouted to System Management Interrupt (SMI) via configuring I/O APIC and 3) the SMI handler is initialized by Unified Extensible Firmware Interface (UEFI) which contains kinds of device drivers; thus, we hold the insight that \textit{the SMI handler} is a perfect candidate to provide trusted I/O paths for security-critical applications.

In this paper, we present \textsc{Aurora}, a novel architecture that safeguards I/O paths for SGX enclaves. To directly communicate with hardware devices without depending on the untrusted software, \textsc{Aurora} introduces System Management RAM (SMRAM) as a special enclave. SMRAM is a tamper-proof memory region used only in System Management Mode (SMM), much like the enclave region with SGX protection in user mode. \textsc{Aurora} delegates I/O requests from enclaves to the SMI handler protected inside SMRAM. We call this particular SMI handler \textit{SMVisor}. In hardware, SMVisor is safe from any corruptions by other privileged software (including OS, hypervisor/HV). Therefore, Intel SGX enclaves can safely use I/O devices while remaining  \textit{transparent} to the underlying OS. %of small code size and

%% 我们的贡献点有：Aurora是个全新的系统服务框架；三款全新的服务；实际的应用评估证明其可用性。
To summarize, this paper makes these contributions:
\begin{enumerate}[]
\item The notion of two types of trusted I/O paths (\autoref{types}) for security-sensitive applications (enclave programs) on untrusted commodity X86 systems.
\item A novel architecture named \textsc{Aurora} (\autoref{arch}) leveraging two hardware features of Intel processors (SMM and SGX) to provide enclaves trusted paths transparent to untrusted OSes/HVs with a minimal trusted computing base (\autoref{codebase}).
\item Design and implementation of four types of trusted I/O paths (\autoref{tpaths}): keyboard, printer, clock, and storage, based on \textsc{Aurora}.  To the best of our knowledge, we are the first to provide these \emph{realistic} trusted I/O paths for SGX enclaves on the client side.
\item Three case studies: OpenSSH client, OpenSSL client, and SQLite database using trusted I/O paths provided by \textsc{Aurora} (\autoref{casestudy}). Experimental results show that \textsc{Aurora} can protect them from typical I/O related attacks (\autoref{security}) with acceptable performance overhead (\autoref{performance}).
\end{enumerate}

\section{Background and Problem Definition}
In this section, we first describe two architecture features of Intel's CPU, and then propose two types of trusted I/O paths based on the characteristics of devices. Finally, we describe the threat model and assumptions.

\subsection{Software Guard eXtension}
%% SGX基本概念。不可见性
Intel SGX \cite{DBLP:conf/isca/McKeenABRSSS13} provides trusted execution environments called enclaves in user level. Enclaves' code and data reside in a hardware-protected memory named enclave page cache (EPC), which is inaccessible to any software including OS/HV or SMI handler. Enclave code can access the memory outside the enclave. As enclave code is only allowed to be executed in user mode, any interaction with devices must execute outside of the enclave and through untrusted system calls. SGX enables a threat model where users only trust the Intel CPUs and the code running inside the enclaves.

Intel SGX SDK provides a function call mechanism for enclaves via ECALL and OCALL.  Thus, an application can invoke an enclave's code via an ECALL and get the return values. The enclave can invoke an OCALL to execute a function in the untrusted portion of the application and receive a return value. With SGX's remote attestation ability \cite{Anati2013InnovativeTF}, one can gain confidence that the target application is securely running within an enclave. Local attestation allows an enclave to prove to one another that it is running on the same processor. %An enclave proves its identity to another target enclave via the EREPORT instruction. This instruction produces an attestation report that cryptographically binds a message supplied by the enclave with the enclave's measurement-based and certificate-based identities. Moreover, a particular enclave, called Quoting Enclave, is used for remote attestation. With the help of Quoting Enclave, an enclave can produce a secure assertion that identifies the hardware environment and itself. The enclave owner can use Intel Attestation Service to assess the trustworthiness of the assertion. Thereafter, the owner can establish a secure channel and provide sensitive data to the enclave.

\subsection{System Management Mode}
%% SMM模式的基本工作原理；对OS不可见；
System Management Mode (SMM) is the most privileged mode for handling system-wide functions like power management, hardware control, etc. Upon a System Management Interrupt (SMI), the CPU saves the system states and switches to SMM, and then executes a predefined logic (SMI handler) inside system management memory (SMRAM). SMRAM is fully transparent to the OS/HV since they are essentially suspended. An \textit{RSM} (resume) instruction is executed at the end of the SMI handler to switch back to the protected mode.  SMRAM is fully isolated by the hardware, any code outside SMRAM cannot access or modify it. We deem SMRAM as a special \textit{enclave} in SMM. %The CPU can enter SMM from any privilege mode upon a system management interrupt (SMI).

%% SMI中断不可屏蔽。
The SMI handler is initialized by UEFI, and  SMRAM can be locked by configuring D\_OPEN and D\_LCK bits in SMRAM control register. Therefore, the SMI handler is safe from corruption after booting. Moreover, the SMI handler can access all CPU registers, I/O devices, and physical memory (except for SGX EPCs), and thus we expand the SMI Handler to design \textsc{Aurora}'s SMM Supervisor in \autoref{arch}.

\subsection{Trusted I/O Paths}\label{types}
%% 传统的UNIX系统将设备分为字符设备、块设备和网络设备。每种设备都有自己的I/O端口号、IRQ中断号以及对应的物理内存。字符设备是最为原生的设备，这些设备包括鼠标、键盘、实时时钟、串口等。这些设备要么产生电平数据作为CPU的输入，要么得到CPU的输出作为指示。我们将此类设备归类为“生产/消费设备”。块设备和网络设备负责数据的持久化保存和在计算节点间传输，他们自身不产生也不消耗带有信息的数据，我们根据其功能将其命名为“存储/传输设备”。我们观察并认为所有的设备都可以归结为这两类，并为这两类设备与程序间构建可信路径。由于分类的不同，可信路径的工作原理也不同。参考Zhou，我们依旧将可信路径的组成分成三个组件：设备端、程序端和通信路径。“生产/消费设备”模型下可信路径要求设备的数据/指令必须通过通信路径传输。这是因为，这些设备参与了数据的产生或使用，而硬件自身并不支持加密协议来保证数据的隐私，这种情况下，我们需要在设备端引入新的TCB对数据做密码学处理。相比之下，“存储/传输设备”只是被动地接收或发送已有的数据，保护隐私的加密运算可以单独放在程序端完成。类型的不同导致了设计的不同，甚至实现代价也不同。我们会在后文中说明。
%% 面向“生产/消费设备”考虑隐私数据的保护，而面向“存储/传输设备”的可信路径用于对攻击检测、预期行为验证等。
We define the term \emph{trusted I/O paths} in trusted execution environments (TEEs, e.g. SGX) as follows. Given a trusted application (e.g. an SGX enclave) and a trusted peripheral device, a trusted I/O path is a secure channel of data transfers between them, even in the face of software adversaries such as host kernel, hypervisor, guest VM and kernel drivers. We classify trusted I/O paths into two categories based on their characteristics: %1) \textit{trusted I/O paths for data-provider/-consumer devices}, e.g., keyboard, mouse, printer, and clock; and 2)  \textit{trusted I/O paths for data-storage/-transmitter devices}, e.g. disk, network adapter.  Both of them co-exist with the commodity OS and can isolate critical components from the untrusted OS and other manipulated devices.

\begin{enumerate}

\item \textbf{Trusted I/O paths for data-provider/-consumer devices.}
Although SGX provides user-space strong isolation for program end-points (i.e. enclaves), most of the devices provide and/or consume plaintext messages. Cases vary from human input data (e.g., keyboard scan code) to outputted data (e.g., a stream of bits to printer/display), which cannot guarantee the confidentiality and integrity in an untrusted or compromised system. Therefore, for trusted paths of this kind, \textsc{Aurora} encrypts/decrypts in SMRAM the data from/to devices for enclaves to protect the data from the untrusted system.

\item \textbf{Trusted I/O paths for data-storage/-transmitter devices.} Storage disks and network adapters are typical storage/transmitter devices, and they don't require the stored/transmitted data in plaintext. Instead, both kinds of devices can deal with encrypted data without learning the semantics of the data. However, both devices need a pile of software stacks (e.g., file system, network protocol) to work correctly and remain compatible. Building trusted paths for them is very challenging. One possible approach is to decompose existing software stack and port them into the trusted applications, which will greatly swell the TCB and attack vectors. As an alternative, \textsc{Aurora} leverages a forward-and-verify method and reuses existing software stacks in a \emph{secure} manner.

\end{enumerate}

\subsection{Threat Model}
We consider an adversary that is able to compromise the target system. He can directly attack enclave interfaces visible to the OS, and actively reconfigure any devices (e.g., modify a device’s MMIO region, or change the operating mode of a device)
and perform arbitrary operations (e.g., trigger interrupts, issue DMA write requests) using any I/O commands. %Logical attacks, e.g., unauthorized memory access by privileged software, are \textsc{Aurora}'s major concern.

\textsc{Aurora} requires a modern Intel platform with SGX and TPM support. We assume the hardware and SMRAM firmware (the microkernel we implement) of the host machine is trusted. We do not trust the UEFI drivers but verify whether they operate following their specifications, or perform unintended operations: e.g., intercept bus traffic, or write to an address that is not specified in DMA commands. Our assumptions significantly reduce the TCB on the target host as modern commodity system contains a large system software (UEFI, possibly hypervisor, kernel and other applications) when dealing with I/O devices.  %As SGX's threat model, we don't consider denial-of-service (e.g. disabled SMI) and side channel attacks.
Even though we do not consider physical attacks on devices, side-channel attacks, or denial-of-service attacks, we adopt side-channel free cryptographic algorithms and apply an oblivious packet transferring method.

\begin{figure*}[t]
	\centering
	\includegraphics[height=0.2\textheight]{figures/arch.pdf}
	\caption{\textsc{Aurora}'s architecture. The gray areas denote untrusted parts, and the white ones represent \textsc{Aurora}'s trusted computing base.}
	\label{fig:architecture}
\end{figure*}

\section{Design}
%% 再说一次，我们用的是SMM和SGX两种CPU特性组成的“可靠、可信”系统服务。Aurora命名缘由。
To provide trusted I/O paths, we employ the combination of SGX and SMM, both of which are processor enforced protection features. As they are offered at the opposite ends of Intel privilege-level model, we name our framework after \textsc{Aurora}\footnote{Aurora takes place in the polar regions, i.e. south and north of the earth.}.

%% SMM call，代理+模拟 模式。Enclave的请求最终在SSV处得到响应，和syscall、vmcall是一个道理。
Establishing a trusted path in \textsc{Aurora} consists of the following three steps. First, \textsc{Aurora} builds a secure session between SMM Supervisor (SMVisor) and an enclave that performs an I/O request. Second, SMVisor receives the request via the secure session without leaking knowledge to the untrusted system. Third, SMVisor interacts with the target device on behalf of the enclave, and performs the desired I/O operations to respond to the request. The procedure is conceptually similar to a \textit{syscall} or \textit{vmcall}. We name it an \textit{smcall} for convenience.

\subsection{Architecture}\label{arch}

To take a bird's eye view, \textsc{Aurora} is composed of three components: SMVisor, libaurora and a secure session established between SMVisor and libaurora, as shown in Figure \ref{fig:architecture}.

%% SMVisor 负责判断中断源/设备，调用驱动，以此提供服务。SSV对驱动模型有限制。
%% libaurora 把SGX缺少的IO相关接口补上，方便移植
%% SSV和libaurora之间有信道连接
\begin{enumerate}%[(1)]
\item SMVisor takes charge of the target devices from the untrusted kernel. It dispatches device interrupts to either kernel or enclaves. SMVisor uses an forward-and-verify mechanism to securely invoke SMM drivers outside SMRAM.
\item Libaurora consists of two parts. The trusted part (Tlibaurora) complements unsupported I/O APIs in Intel SGX SDK library, helping developers secure enclave's I/O paths. The untrusted part (Ulibaurora) is responsible for forwarding \textit{smcalls} to SMVisor.  %; an ENCLAVEID can be obtained using \textit{EREPORT} instruction
\item The secure session exchanges encrypted messages between SMVisor and enclaves via a shared memory provided by a kernel module named ashmd.  \textsc{Aurora} leverages a 5-tuple for each message: \textit{(ENCLID, DEVID, OPTYPE, PAYLOAD, MAC)}. The first two arguments indicate the program endpoint and device endpoint respectively.  The third stands for the I/O operation type. The fourth carries the message data and the last one is the message authentication code used for integrity protection. All the arguments are marshaled and encrypted.

\end{enumerate}

%% 和LibOS一样，我们也是要减小对不可信OS的依赖，我们甚至没有和OS交互的数据流接口，只有中断对其是不透明的。
%% 但又和LibOS不一样，我们连驱动都不用不可信OS的，以此保证数据来源的可靠性和流出的不受干扰。
Like library OSes~\cite{DBLP:journals/tocs/BaumannPH15, DBLP:conf/usenix/TsaiPV17, shinde_panoply:_2017}, \textsc{Aurora} has few interfaces with the untrusted OS. %Only interrupts are forwarded by the OS to SMVisor.
The data plane of an enclave is protected by advanced encryption schemes accelerated by the processor (e.g. AES-GCM with AES-NI support), and the data flows between the enclave and SMVisor are completely invisible to the OS. Unlike library OSes, which delegate I/O operations to the untrusted OS, \textsc{Aurora} ships security-sensitive parts of these operations into SMVisor, thus eliminating the reliance on untrusted OS.

\subsection{Workflow}\label{workflow}
To help understand the workflow of a trusted path in \textsc{Aurora}, we break down the process of output path and input path respectively into sequential-logic phases, as illustrated in left and right part respectively of \autoref{fig:workflow}.

An output request is triggered by an enclave as a synchronous exception, as depicted as follows:\\
%\par
~~\textcircled{\footnotesize{1}} The user logic in the enclave issues an output request by invoking  Tlibaurora's APIs;\\
~~\textcircled{\footnotesize{2}} Tlibaurora marshals and encrypts the request's arguments, and invokes Ulibaurora outside the enclave to relay the request;\\ %sends the request via the secure session, via an OCALL
~~\textcircled{\footnotesize{3}} Ulibaurora ioctls the ashmd module to trigger an \textit{smcall};\\
~~\textcircled{\footnotesize{4}} SMVisor is notified and obtains the encrypted requests from the secure session;\\
~~\textcircled{\footnotesize{5}} SMVisor decrypts the request and invokes the corresponding  driver;\\
~~\textcircled{\footnotesize{6}} The driver operates the raw output data in PCI space or MMIO buffer;\\
~~\textcircled{\footnotesize{7}} The driver returns a result code to SMVisor. Finally, SMVisor  executes \textit{RSM} to return to protected mode. \\

\par
An input request from an enclave results in a device interrupt, as depicted as follows:\\
%\par
~~\textcircled{\footnotesize{1}} The target device triggers an interrupt, and the control is routed to SMVisor which is the interrupt handler;\\
~~\textcircled{\footnotesize{2}} SMVisor invokes the device driver to handle the input request;\\
~~\textcircled{\footnotesize{3}} The driver gets the raw input data and sends it to SMVisor;\\
~~\textcircled{\footnotesize{4}} SMVisor encrypts the data inside SMRAM, and sends it to the target enclave via the secure session;\\
~~\textcircled{\footnotesize{5}} The system switches back to protected mode and the ashmd module uses a signal to notify Ulibaurora;\\
~~\textcircled{\footnotesize{6}} Ulibaurora invokes Tlibaurora via an ECALL to receive encrypted data;\\
~~\textcircled{\footnotesize{7}} The enclave decrypts the encrypted data and finally obtains the raw input data. % from the secure session.

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{figures/workflow.pdf} %height=0.25\textheight,
	\caption{The work-flow of a trusted I/O path. }%The white areas denote the TCB.
	\label{fig:workflow}
\end{figure}

\subsection{SMVisor}\label{ssv}

SMVisor is the core component in \textsc{Aurora}.  It may take charge of multiple devices simultaneously, so it needs to determine which device is requested and then invokes the matching driver.

%% 数据来的时候首先被SSV拦下，判断好了再转发，避免OS污染隐私数据
%It protects the device ends from any other logical attacks. When SMVisor receives a request, it takes control of the target device interrupts to prevent the untrusted system from interrupt spoofing attacks.
\textbf{Interrupt Handler.} To deal with a device interrupt, SMVisor reroutes the interrupt to SMI. Specifically, SMVisor intercepts device events by configuring the \textit{Redirection Table} defined in I/O APIC and modifying the destination of the device event to SMI. SMVisor distinguishes the interrupt source and thus notifies the untrusted system or a certain enclave. In order to forward the interrupt to upper software layer (i.e. ashmd), it launches an inter-processor interrupt (IPI) by writing the interrupt command request (ICR) register in the local APIC.

%% SSV不用管OS要地址，自己能找到设备对应PCI内存区；当然，要是OS重新初始化了这个设备，把PCI空间移到被的地方，我是没有办法的|##|
%\emph{Device Manipulation.} 
To correctly perform I/O operations, a driver needs to know the exact I/O ports of the target device. At the time of system boot, SMVisor collects devices information and configures them. It also records their memory mapped I/O (MMIO) base addresses into a \textsf{PCI BAR table}, thereafter the corresponding drivers are able to manipulate the mapped PCI configuration space according to the \textsf{PCI BAR table}.

%% 为了防止传给driver的数据有问题，每次请求的参数都会被SSV检查；同时也限制driver的内存访问，防止隐私泄漏
%To avoid possible data leakage, SMVisor checks the memory access of the driver and clears the allocated RAM for the driver.
\textbf{Sanitization Module.}\label{shield}
SMVisor verifies the validity of parameters passed to the drivers (e.g. a PCI structure pointer should point to one of the entries in the \textsf{PCI BAR table} within SMRAM) and checks the return values according to the device specifications (e.g. each driver function has a specific range of error codes) as well as its correctness. When the parameters or return values are invalid, SMVisor notifies the enclave that a potential attack from OS may occur, and rejects the subsequent requests. Moreover, SMVisor checks the memory boundary (i.e. starting address and region range) that the driver tries to access to ensure that it can not write data outside of SMRAM. %leak information

%% 没有说是dlmalloc还是tcmalloc，这些分配器代码量大，我们是简单的，但做访问检查
%\textbf{Runtime Manager.}\label{secure_heap} 
Furthermore, a driver may require more memory space during run-time (e.g. for DMA with devices), therefore SMVisor maintains a dynamic heap with a sanity-checking feature \cite{DBLP:conf/ccs/SilvestroLCLL17}. To avoid possible memory leaks, the manager frees all allocated memory for the driver before returning to the protected mode.

\subsection{SMM Drivers}\label{driver}
In this section, we describe how SMVisor can safely reuse existing drivers. %{\color{red}what kind of APIs the drivers are supposed to export for SMVisor} and explain
%% 内核驱动不该用！移植量不大（见实现），述说移植的简单可行之处
%\textbf{forward.}\label{forward}
OS drivers are coupled with the kernel in modern monolithic systems. These drivers lack of effective isolation during runtime from the rest of the untrusted systems, therefore we do not use them. %There are two options that we can choose from.

%The other is to exclude drivers from the TCB and leave them outside the SMRAM. We prefer this choice because of the following three advantages:
Instead, since existing open-source UEFI firmware, such as Coreboot\footnote{https://www.coreboot.org/} and Project Mu\footnote{https://microsoft.github.io/mu/}, contain various drivers in their Driver eXecution Environment (DXE), and the code of these drivers are significantly scrutinized compared to the proprietary code, we reuse these drivers and forward the device interrupt for them to handle. This OS-neutral design allows \textsc{Aurora} to support different kinds of OS, e.g., Linux, Windows, or MacOS.

%\textbf{Verification.}
%Because the drivers are not protected inside SMRAM and may be tampered with by untrusted privileged software, we cannot simply forward without any verification. Instead, 
Moreover, we reuse UEFI drivers in a secure manner. At the booting stage, SMVisor calculates the hash checksum of each driver and stores its integrity signature inside SMRAM. When receiving an I/O request, SMVisor verifies the integrity of the corresponding driver to ensure that it is not tampered with. %, then it invokes the drivers to response the requests.
When executing a driver, SMVisor puts its data, heap, stack segments  inside SMRAM, and thus ensures them inaccessible to OS/HV. Furthermore, SMVisor uses its sanitization module to validate the behavior of the driver, as described in \autoref{shield}.

%% 驱动有个统一框架，方便未来扩展。probe判断设备可用性；读写操作，读写有个约束
%\textbf{Uniform Interfaces.}
%In order to accomplish TIOS in a safe manner, the drivers should provide three exported APIs for SMVisor: \textit{probe()} makes sure the device is available, \textit{write()} and \textit{read()} are used to process data flow from/to the devices. Using these APIs, we design and implement network, clock and keyboard input TIOSes. It illustrates that Aurora's uniform interfaces are sufficient. % We do not expose more interfaces to enclaves because these \textit{IOCTLs} may be abused by a malicious enclave to interfere the normal operations of the system.

\subsection{Secure Session}\label{secure_session}

We design a secure session that protects the message exchange between SMVisor and enclaves. We first describe \textsc{Aurora}'s kernel module that provides the shared memory for message exchange. Then we state the lifecycle of a secure session and optimization techniques upon it.

\subsubsection{ashmd Kernel Module}
%% Enclave可以在内部操作不可信内存区数据，从而避免退出；Iago会导致DoS，不会泄漏数据
SGX memory model is asymmetric: the processor prohibits code outside of enclave to access the enclave, whereas the enclave code can access addresses outside the enclave. \textsc{Aurora} leverages shared memory to bridge SMVisor and enclaves. For instance, we use a kernel module \emph{ashmd} to allocate contiguous physical memory as shared memory. For an enclave program, Ulibaurora opens and mmaps this device into its  address space. As a result, Tlibaurora can directly operate on this memory in enclave mode. If the kernel launches memory-based Iago attacks~\cite{DBLP:conf/asplos/CheckowayS13} such as mapping to an illegal location, Tlibaurora will verify whether the whole mmaped memory is outside of the enclave, otherwise the secure channel will not be established.

In order to distinguish interrupts to enclaves from others, ashmd module allocates an IRQ from the system. When ashmd receives an IPI from  SMVisor, it knows this is a response to an enclave.
Moreover, to prevent OS from modifying I/O redirection table, ashmd module spawns a kernel thread which holds a copy of  I/O APIC table and continually check the status of I/O APIC  table. Once it detects a modification by OS, it tries to restore it with the reserved one. If the attempt fails, ashmd  immediately notifies the target enclave with an error code.  We treat the denial of ashmd thread scheduling as a kind of DoS attack, which is beyond the scope of the paper.

%% 初始必须双发交换密钥，只要Intel服务器在机器启动时验证SSV，enclave加载时验证enclave，然后利用各自得到信道交换密钥就可以。虽然代价大，但只是初始化慢而已。
\subsubsection{Secure Session Life-cycle}
The initial stage of the secure session is to ensure whether both parties are trusted or not. On one hand, the untrusted privileged system may launch SMI-specific fuzzing attacks on  SMVisor. On the other hand, the privileged system may fake the identity as  SMVisor since it can emulate an SMI and try to \textit{handshake} with an enclave. To mitigate such a man-in-the-middle attack, we introduce \textit{mutual attestation}. When each of both parties trusts the other, they can exchange a symmetric secret key using \textit{key agreement}, as depicted in \autoref{fig:mutual}. %both parties are acknowledged

\begin{figure}[t]
\centering
\includegraphics[width=0.3\textwidth]{figures/mutual.pdf}%height=0.2\textheight,
\caption{Mutual attestation and key agreement between SMM Supervisor and an application enclave. The single line arrows denote the attestation direction, the double line arrow denotes the following key agreement.}
\label{fig:mutual}
\end{figure}

\textbf{Mutual Attestation.}
During a measured boot, Intel boot guard~\cite{ruan_platform_2014}  hashes a computer's firmware and stores its cryptographic hash in the TPM Platform Configuration Register (PCR) \cite{tcg_trusted_2014}. The final PCR value reflects the whole boot process. If the process is modified, the PCR value will be different.

In order to ease SMVisor attestation, we use the launch enclave provided by the Intel SGX Platform Software to attest SMVisor for one-time effort. Afterward, any application enclave running on the same machine can query the launch enclave to know if SMVisor attestation has succeeded. To attest  SMVisor, the launch enclave needs to verify the PCR value by requesting a TPM quote, which includes a cryptographic signature over the PCR value alongside with a fresh nonce. This ensures the integrity of the PCR value and prevents replay attacks. Besides, an application enclave attests itself to the launch enclave using Intel's local attestation.

\textbf{Key Agreement.}
After the mutual attestation, the SMVisor and an enclave can establish an authenticated secure channel via an ephemeral Diffie-Hellman key exchange.
At this point, a secure session is successfully established. We then use AES-GCM encryption scheme for further message exchange in order to prevent replay attacks. Furthermore, Intel processors with SGX feature support Advanced Encryption Standard New Instructions (AES-NI) to accelerate the AES-GSM encryption, which helps mitigate possible covert-channel attacks~\cite{xu_controlled-channel_2015, DBLP:conf/uss/BulckWKPS17, DBLP:conf/usenix/HahnelCP17}.

%\subsubsection{Communication}
%% 通信要依赖共享内存，在此基础上设计协议
%We design a protocol for message exchange between SMVisor and enclaves in a secure session.

%\textbf{Communication Protocol Interface.}
%%% 协议接口说明，关于EnclaveID看是用什么好，EPID拿不到的话
%Aurora proposes a uniform abstraction interface between Tlibaurora and SMVisor: \textit{IOCTL(DEVICE, ENCLAVEID, OPERATION, PAYLOAD)}. The first argument indicates the device that an enclave desires to communicate with. The second distinguishes the identity of requestor; an ENCLAVEID can be obtained using \textit{EREPORT} instruction. The third stands for the operation type to be performed, it can be either of the three: PROBE, READ and WRITE. The last argument carries the message data. All the arguments are marshaled and encrypted into the secure channel.

\textbf{Disconnection.}
%% 和进程退出释放资源一样，我们这个并不老是影响系统
When an enclave finishes its requests, its Tlibaurora logic will notify SMVisor to terminate the secure session and release resources. When there is no live session, SMVisor will disable its interrupt routing and thereafter make no impact on the system.

\subsubsection{Enhancement and Optimization}
To provide better security and performance, \textsc{Aurora} introduces \textit{data obliviousness}, \textit{hardware encryption} and \textit{batch mechanism for smcalls}.

\textbf{Data Obliviousness.}
%% 数据隐藏，保证每次内容的随机性
In an established session, if an enclave requests the same I/O path twice and the results happen to be the same, the encrypted messages will also be identical because the session key is not changed. An adversary can infer secrets by observing such covert channels. To prevent such secrecy leakage, \textsc{Aurora} pads all messages with random value to the same length (4KB, same size as one EPC page), which restricts possible information leakage at page-level. %The message buffers must start with page-aligned address.

%% 硬件加速效果如何
\textbf{Hardware Encryption.} The encryption process is a very attractive target for attackers~\cite{DBLP:conf/acns/BiryukovDC17}. Intel extends X86 ISA with AES-NI set and claims to prevent known side-channel attacks. We make use of it to address the same concern and use constant-time encryption algorithm to defeat cache timing attacks. The hardware-accelerated encryption also decreases the preemption time in SMM mode.

\textbf{Batched SMCALLs.}\label{batch}
To reduce the context switches between SMM mode and enclave mode, \textsc{Aurora} supports a batched \textit{smcalls} mechanism using two dedicated, lock-free ring buffers for input and output respectively. It is especially useful in the case of highly frequent requests. Enclaves can set a desired threshold, so Tlibaurora will coalesce these \textit{smcalls}. For asynchronous I/O requests, the mechanism can benefit the enclave with higher throughput. %We use this optimization in secure VPN services in our experiment~\autoref{openvpn}.% For instant requests like clock, the requestor can directly issue an \textit{smcall} which skips the batch.% when combined with asynchronous, batched mechanism~\cite{DBLP:conf/osdi/ArnautovTGKMPLM16}

\section{Trusted I/O Paths between Enclaves and Devices}\label{tpaths}
%\section{Trusted I/O Paths for Data-Provider/-Consumer Devices}\label{path1}

As described in section~\autoref{types},  trusted I/O paths  should assure that the users' data is transferred by a secure session. 
%The fundamental reason is that these devices can only understand data in plaintext form. To defeat eavesdropping attacks, the data is encrypted and sent through the secure session. Until it reaches the SMRAM will the encrypted data be decrypted into the clear text, so the untrusted system is unaware of the operations that SMVisor has performed to the target devices. 
In this section, we illustrate how to build trusted I/O paths for data-provider/consumer devices, e.g. human-interface-device (HID) keyboards, serial printers, and hardware clocks, and data-storage/transmitter devices, e.g. portable USB disk. (Reason why we choose USB, not others???)

\subsection{Trusted HID Keyboard Input}\label{input_service}
Trusted input ensures that third-party software on the same computer has no access to the user's input intended for an enclave application. In other words, trusted input paths exclude other untrusted software including the underlying OS from sharing the input device. We use \textsc{Aurora} to secure user's private textual inputs from the keyboard to the enclave.%, and SGX perfectly secures the input inside the enclave.

\textbf{Trusted Input Mode.}
When an enclave issues an input request, SMVisor routes the keyboard interrupt (IRQ 1 by default) to SMI. All of the subsequent keyboard scan codes are cached inside SMRAM. We call this case \emph{trusted input mode}. After an \emph{enter} key is hit and released, SMVisor recovers the I/O APIC redirection table and exits trusted input mode. Finally, SMVisor encrypts the inputs and sends it to the secure channel. The desired enclave can then take it from the channel and decrypt it. %the user hits the enter key and releases it

\textbf{User Verification.}
Phishing attacks, where an adversary exploits social engineering tricks to allure a user to leak her privacy data, are a threat to trusted input. For example, a malware might present a fake login interface that prompts a user to enter her password.
To mitigate this threat, we adopt an approach where PC speaker is used to indicate the trusted path has been established.
When the system first boots, the network is disabled by the SMVisor, and we assume that the loaded kernel is clean due to TPM's measure boot. \textsc{Aurora} asks the user to store a short, arbitrary MIDI-format melody (around 5 seconds) inside SMRAM via an temporary enclave, so that everytime when a trusted path is set up, the PC speaker will play the melody. Then the network is enabled by the SMVisor. Since the melody is a pre-shared secret only between the SMVisor and the user, it is impossible for the adversary to learn and mimic the process.
% Tlibaurora first generates a random integer $N$ in the interval of [1, 10], and displays the integer number in the screen as a captcha. Tlibaurora sends $N$ to SMVisor. SMVisor blinks the \textit{Caps Lock} LED light for exactly $N$ times. Since the captcha is generated with noises inside the enclave, it is hard for the adversary to mimic the process. %Before the enclave application displays the prompt that awaits the user to enter her password, a controlled computer might have displayed the same content and user directly inputs the secrecy without waiting for the computer to enter trusted input mode.

\subsection{Trusted Serial Printer Output}\label{output_service}
Today shared print services are very common, by which colleagues in a unit or students in a college print their documents. Users' private or sensitive data may also be printed using such infrastructures. Malware on these public machines/printers can easily steal these data for malicious purposes like industrial espionage or illegal data acquisition. To mitigate this threat, we build trusted serial-port path for shared print services.

When an enclave requests the trusted printer service, it encrypts the output packet and sends the encrypted packet to SMVisor.  SMVisor receives the packet and decrypts it to plaintext packet. As the packets are usually held with printer-specific format, SMVisor issues the corresponding serial port driver and adds this job into its task queue. Afterward, SMVisor returns the status code from the printer devices to the enclave end-point.

\subsection{Trusted Hardware Clock}\label{time service}
For the clock, its integrity and non-forgeability are much more vital than confidentiality. %Using a trusted clock source, one is able to create trusted timestamps. This is especially significant in a financial transaction (e.g. block chain) and secure network (e.g. TLS authentication).
In this section, we describe how to extend \textsc{Aurora} for trusted, high-resolution absolute clock. %by accessing multiple sources of hardware timers and detecting possible attacks. %The clock does not need to protect its confidentiality. Instead,

\textbf{Multiple Sources.}
%% 多源头获取时间，适应不同需求
\textsc{Aurora} uses multiple clock sources available on x86 platforms, such as programmable interval timer (PIT) and advanced configuration and power interface/power management (ACPI/PM) timer. To estimate the latency of obtaining time from hardware and adjust their values, SMVisor references invariant time stamp counter (TSC) via \textit{RDTSCP} instruction. The invariant TSC ensures that the duration of each clock tick is uniform (at the frequency relative to the crystal clock frequency of the processor core).

\textbf{Absolute Value.}
%% 绝对时间来自RTC驱动
We use Real-Time Clock (RTC) to provide the absolute wall-clock time (i.e. epoch) for enclaves. To avoid incorrect values due to hardware updating, SMVisor keeps obtaining the RTC values until the last two are consistent. After obtaining a valid wall-clock, SMVisor then obtains the rest timers. The order is critical because RTC time retrieval is the most expensive amongst others and will break the freshness of other timers' values.

\textbf{High Resolution.}
%% 根据时钟频率和差值计算时间精度
When a time value with high resolution (e.g. micro-second) is required, \textsc{Aurora} uses the invariant TSC and High Precision Event Timer (HPET) to satisfy the need. For instance, \textsc{Aurora} uses the following formulae to compute the \textit{tv\_usec} value in \textit{timeval} data structure: {$tv\_usec = (HPET\_value/ HPET\_Hz) / 1,000,000$;} where $(HPET\_value / HPET\_Hz)$ computes the absolute time in micro-seconds.

\textbf{Attack-Awareness.}
%% 如何避免时钟攻击
Though the hardware clocks can be controlled and modified by the malicious OS, diverse timers in Aurora offer enclaves the ability to validate the credibility of time values. Tlibaurora records last values read from all hardware clocks and obtains current values to calculate their differences respectively, and then uses clock frequencies to compute the actual elapsed time. When any of the measured time violates the monotonic rule, we assume a time attack.

For the case where the hardware clocks are modified in a consistent way, that is, all the timers are altered in the same offset, we propose a novel algorithm to detect such an attack. We use a dedicated counting thread \cite{DBLP:conf/dimva/SchwarzWGMM17} guarded inside an enclave occupying a logical thread on the same CPU core. Such a sibling thread will block the possibility of side-channel attacks when hyper-threading is active. The counting thread provides $dT$ and the difference of hardware timers provides $dt$, we use first-order derivative $dt/dT$ to detect the possible time attack. Currently, we set the confidence interval to 0.05, which denotes the possible altering in the timers' rising slope. If the slope changes much, we assume an attack.

%\section{Trusted I/O Paths for Data-Storage/-Transmitter Devices}\label{path2}
%As to trusted I/O paths for data-storage/-transmitter devices, \textsc{Aurora} reuses existing system services and verifies the correctness of the I/O services provided by the untrusted systems, as discussed in section~\autoref{types}. In this section, we present this kind of trusted paths by taking USB storage as an example.

\subsection{Trusted USB Storage}\label{storage_service}
Storage software contains block and file system. A compromised OS may silently discard data written by the application or return fabricated data during a read operation. It is a serious issue when secure data storage is  necessary for ensuring correct operation (e.g., secure logging, APT monitoring and compliance). In this section, we extend \textsc{Aurora} to support secure USB disk as a storage example.

% 对于不关注隐私的可信路径，我们主要是利用中断来判断读写的请求。因此每次都显式调用fsync；另外，最大的问题在于如何找到DMA高速缓存区域。
%\emph{Basic USB Workflow.}
%A USB host controller (UHC), consisting of several physical USB ports, is connected to one USB endpoints.  A UHC is controlled via a set of memory-mapped I/O (MMIO) registers and presented as a PCI device in an OS, which uses a USB Host Controller Driver (UHCD) to communicate with it. A USB driver talks to its device using one of three protocols (e.g., EHCI). %to issue request packets defined by the specific UHCD. % These contain a number of pointers to various linked lists that track attached devices and map requests to devices.  %A higher-level device driver communicates with the specific endpoint device via the HCD and hardware. 
%We take an EHCI device in Linux as an example, its device driver sends a USB request block (URB) to query information from the device. The UHCD creates a transfer descriptor (TD) for this request and links it to a list \textit{reqlist} for the device. Once this request is completed, the UHC will unlink the TD from \textit{reqlist} and link it to a \textit{donelist}. It also writes result data into memory via DMA and sends an interrupt indicating it has new data on \textit{donelist}. On receiving this interrupt, the UHCD walks \textit{donelist} and processes the TDs found. It then notifies the device driver (typically via an asynchronous callback) that its URB is serviced and the data is available.

\textbf{Secure Storage Protocol.}
%The IRQ number of the device is acquired by ashmd module and then notified from ashmd to the underlying SMVisor. 
When an enclave issues a request for a USB disk, SMVisor leverages I/O interrupt rerouting mechanism to monitor and deal with every operation of the USB device, including transferring data and control commands via a secure session in \textsc{Aurora}. In Linux, the data is by default transferred using bulk mode and is exchanged based on DMA mechanism, which stores the DMA address and buffers location in a {scatter-gather} list. The ashmd module can obtain these information from corresponding drivers.

% 描述了基本的协议，保证每次读写请求都能得到SSV的确认
%% 无法使用S2BR的设计，因为没有维护任何文件名和文件大小的基本信息，我们无法以文件作为MAC完整性检查的基本单位
After capturing the USB Request Blocks (URBs), SMVisor passes them to the USB device via a secure session.  Note that SMVisor leverages AES-GCM scheme to encrypt transferred blocks between enclaves and devices \ref{arch}. All data blocks from the enclave are encrypted by default, and a message authentication code (MAC) is generated for each block. SMVisor checks the MAC of each block to validate its authenticity and integrity. If it checks an inconsistent MAC, SMVisor will return an error to the enclave.

\section{Implementation}

\subsection{Components}

We modified the SMI handler of CoreBoot to implement \textsc{Aurora}'s SMVisor, and modified the drivers of CoreBoot project to export interfaces which can be invoked by SMVisor. We disable the caching mechanism in SMM and check the access permission using the memory type range registers (MTRR) to ensure SMVisor's protection. For the sake of compatibility, Tlibaurora supports standard
POSIX APIs, so enclave developers need not write OCALLs.

To avoid machine check exception within SMM, we enable the Streaming SIMD Extensions (SSE) bit in control register CR0. With SSE and AES-NI, we boost encryption performance. For example, with AES-NI support, AES-256-GCM encryption and decryption on 4KB data in SMM mode costs 9us on average, for comparison,  without AES-NI, AES-128-GCM implementation of Intel IPP Crypto library~\cite{Intel_IPP_2017_Update_2} costs 597us.

We implement a specific kernel model ashmd. Like Linux SGX driver, we use but do not trust them. the ashmd module is intended to relay the communications between hardware enclaves and SMVisor.
%We reused the implementations of i8042 driver from SeaBIOS. To issue a trusted input request, an enclave simply needs to link against libaurora. Tlibaurora automatically changes the semantics of read() API, i.e. reading  /dev/aurora instead of stdio (or /dev/tty). The raw inputs will be put in the buffer parameter of read() via the secure session. %eventually

%We reused the implementations of serial-port driver from SeaBIOS, SMVisor explicitly invokes the fflush operation to make sure that all writes to a serial port are completely sent. %After each write request from the enclave, SMVisor

%We reused the implementations of EHCI driver from SeaBIOS. To obtain the DMA address held in the \textit{scatter-gather} list structure, we use ashmd to inspect the address and hand it over to the SMVisor.

%We reused the implementations of timer/clock drivers from SeaBIOS, including RTC, HPET, PIT, TSC, and ACPI/PM timer. We minimize SMM preemption time by placing most of the clock processing logic in the Tlibaurora. For the sake of compatibility, Tlibaurora supports standard libc time APIs, therefore developers can benefit from trusted clock service without writing OCALLs. Tlibaurora performs the validation using attack-awareness algorithm and is responsible for detecting time attacks.

%% 强调TCB小
\subsection{Code Base and Binary Size}\label{codebase}
%% 说明移植的轻松程度，强调运行时占据物理内存的少
%We use SLOCCount\footnote{https://www.dwheeler.com/sloccount} to calculate the overall C Lines of Code (LoC) of current \textsc{Aurora} implementation. As shown in \autoref{code_base},  \textsc{Aurora}'s TCB (3393 LoC) is far less than other architectures (see \autoref{arch_compare}). 
\textsc{Aurora}'s trusted components (i.e., SMVisor, ashmd, Tlibaurora, Cryptography) have 3393 lines of C code, and untrusted component (i.e., Ulibaurora) has 273 lines of C code. Compared to Wimpy \cite{zhou_dancing_2014} which has 16K lines of code, it is smaller and simpler enough to facilitate formal verification.
Both SMRAM and EPC RAM are scarce memory resource. For instance, the system-wide EPC limit is approximately 93MB and the SMRAM is 4MB by default on our platform. We measure the final size of resulted stripped binary images. Our modification on CoreBoot only add 3.9\% on its total size (120.2KB V.S. 115.7KB). The enclave.so  linked against Tlibaurora is 696KB in size and 1MB including runtime stack and heap manager. Smaller codebase denotes smaller TCB introduced. %This implies that we could have roughly 56 enclaves with trusted I/O support in parallel without EPC paging.

\subsection{Code Quality}
To avoid exploitable vulnerabilities, we use well known static analysis tool Clang Static Analyzer\footnote{http://clang-analyzer.llvm.org/index.html} over \textsc{Aurora}'s code base and fix all bugs we found. Besides, as \textsc{Aurora} is quite small and its complexity is obviously lower than that of the formally verified seL4 microkernel [36],  we believe it is reasonable to put \textsc{Aurora} within the reach of formal verification.

%\begin{table}[t]
% \centering
%  \caption{The code base of \textsc{Aurora}}
% \label{code_base}
%\begin{tabular}{ llr }
% \toprule
%& Component & Lines of Code \\
% \midrule
% \multirow{4}{*}{Trusted} &  SMM Supervisor & 274 \\
%& ashmd module & 159 \\
%& Tlibaurora & 1841 \\
%& Cryptography & 1119 \\
%% \midrule  TCB & 3234 \\
% \midrule %\midrule
%Untrusted & Ulibaurora & 273 \\
% \midrule
%TCB/Total & & 3393/3666 \\
% \bottomrule
%\end{tabular}
%
%\end{table}

\subsection{Limitation}
Although  SMM-based mechanism can be used to route many peripheral I/O events, it itself cannot be used to protect the frame buffers and therefore fall short of providing a trusted display. This is because on X86 platform, SMRAM area by default starts at the same address as the VGA space, therefore SMVisor cannot obtain the frame buffer. It can be solved by redirecting  SMRAM to another higher memory area without overlaying the VGA space. However, as  SMM-based protection has performance implications~\cite{DBLP:conf/iiswc/DelgadoK13}, we recommend that users can use Intel PAVP (assisted by Intel ME) and SGX~\cite{DBLP:conf/isca/HoekstraLPPC13} for real-time scenarios such as an online-chatting conference.

%\begin{table*}[t]
%	\centering
%	\caption{Comparison of Different Trusted I/O Architecture. We do not know the exact lines of code of Intel Management Engine, however, since it consists of a MINIX system and JVM at least, we treat it 10KLoC or so.}
%	\label{arch_compare}
%		\small
%		%\footnotesize
%	\begin{tabular}{ lllll }
%		\toprule
%		& Driver Porting & Prog. Change & Main Components & TCB Size \\
%		\midrule
%		Wimpy kernel (HV-based)~\cite{zhou_dancing_2014} & In-app Driver & Intrusive & App drivers, wimpy kernel, hypervisor & 10KLoC \\
%		SGXIO~~~~~~~~ (HV-based)~\cite{weiser_sgxio:_2017} & In-enclave Driver & N/A & Enclave-driver, hypervisor & N/A\\
%		Intel PSW~~~~ (ME-based)~\cite{intel_psw} & None-effort & SGX SDK & Intel ME, Minix OS, JVM, firmware & $>$10KLoC \\
%		\textsc{Aurora}~~~ (SMM-based)~~~~~ & Minimal effort & SGX SDK & SMM Supervisor, libaurora & 3KLoC \\%LibC 
%		\bottomrule
%	\end{tabular}
%\end{table*}

%
%\textbf{SMM Transfer Monitor.}
%Intel has released a new technology called STM~\cite{intel_stm} on virtualized environments in its white paper about EDK II\footnote{https://github.com/tianocore/edk2}. EDK II is Intel's open source UEFI project. In their design, STM is responsible to regulate the UEFI drivers, based on restricted access control. This is very similar to SMVisor. We believe that the future version of \textsc{Aurora} can benefit from the various drivers in Intel EDK II and provide more trusted services for SGX enclaves.

%\textbf{Browser Password Manager.}
%We plan to strength the browser logins in the future. Most of the browser based password managers are implemented with JavaScript language. To use the SGX protection, we need to modify the browser itself. Both enhanced browser and its enhanced password managers can defeat many web-based attacks~\cite{DBLP:conf/uss/SilverJBCJ14}.
%
%%% 可以扩展至GPU通信，新的服务可能
%\textbf{Data Processing Services.} Machine learning infrastructures are now benefiting from the convenience of clouds. The computation heavily relies on the acceleration of GPUs. Malicious cloud administrators that control GPU configurations can make data breach on datasets as well as algorithms~\cite{DBLP:conf/ccs/SongRS17}. Building a trusted path between the GPU and in-enclave execution is vital to machine learning security. We plan to support secure GPU channel based on \textsc{Aurora} in the future.

\section{Case Studies}\label{casestudy}
Aurora provides uniform abstractions (standard POSIX APIs) for the SGX applications, which need not be modified, to maintain platform-independence and thus achieve nice usability. We implemented trusted I/O paths for three real-world applications to illustrate the usability of \textsc{Aurora}.

\subsection{Secure OpenSSH Login}\label{openssh}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.4\textwidth]{figures/ssh.pdf} %height=0.16\textheight,width=0.6\textwidth
	\caption{Aurora-OpenSSH with trusted input path.}
	\label{fig:openssh}
\end{figure}

Secure Shell (SSH) is widely used for shell access on UNIX-like systems. An SSH server uses a username and a password to authenticate an SSH client. If the client is infected with malware, the login credential can be stolen by key-loggers. To demonstrate the effectiveness of \textsc{Aurora}'s trusted input path, we modified OpenSSH 7.7 to protect its client login process. Specifically, we ported passphrase related logic into an enclave, and used \textsc{Aurora}'s \textit{trusted input path} to get passwords which users input. We call the enhanced client as Aurora-OpenSSH client, as depicted in \autoref{fig:openssh}.

Aurora-OpenSSH client first requests SMVisor to intercept the user's  keyboard events. This interception adds around 13\% overhead per keystroke. Only after SMVisor routes the keyboard interrupt into itself and acknowledges to the client, will the prompt "username@hostname password:"  be displayed on the screen. While the user is typing the passphrase, the client does not display any content on the screen, achieving the same effect as in the native OpenSSH client.

The user's input is buffered inside SMRAM. When the user releases "Enter" key, the password is then encrypted and sent to the secure channel, and SMVisor exits trust input mode.  Aurora-OpenSSH client reclaims the password message and sends it to the server. Note that the plaintext password is only available in SMRAM and enclave. The path between SMRAM and enclave is protected by \textsc{Aurora}'s secure channel and the path between Aurora-OpenSSH client and OpenSSH server is protected by TLS session.
%
%%Recall that SMVisor will manipulate the LED to blink random times to indicate that it has intervened the keyboard interrupts. Because we use virtualized environment to do the experiments, our current prototype uses serial output to indicate this.

\subsection{Secure OpenSSL Session}\label{openssl}

%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.35\textwidth]{figures/ssl.pdf} %height=0.2\textheight,
%	\caption{Aurora-OpenSSL with trusted clock.}
%	\label{figure:openssl}
%\end{figure}
%There are multiple in-enclave SSL/TLS project on going \cite{mbedtls, intel_sgx_ssl, wolfSSL}. These projects employ SGX to provide tamper-resistant cryptographic process.
SSL/TLS protocols are in widespread use in applications such as web browsing, email, instant messaging, and voice-over-IP. 
%To allow for a distributed communication, a secure session named TLS is established between two parties. 
An SSL/TLS session starts with SSL/TLS handshake protocol, including authentication, key exchange, etc. The procedures rely on system date and time. The SSL/TLS server needs to provide a certificate with a timestamp indicating the expiration time, and the SSL/TLS client needs to verify this certificate. Most of all, both parties require a reliable time source to detect possible timeout. For instance, both "ClientHello" and "ServerHello" messages use the system time to compose \textit{random} field, which is used to prevent replay attacks. If the time is emulated by an untrusted source, it may increase the collision probability of \emph{random} and compromise the security of SSL/TLS.

One of the in-enclave SSL/TLS projects is SGX-OpenSSL\footnote{https://github.com/sparkly9399/SGX-OpenSSL} from SGX-Tor project~\cite{DBLP:conf/nsdi/KimHHKH17}. It does not trust the system storage, therefore its server side creates the certificate inside the enclave each time it receives a new connection request from the client side. We enhanced the TLS handshake by using \textsc{Aurora}'s trusted clock. Specifically, we replaced time-related OCALLs in the original project with \textsc{Aurora}'s libaurora. %The new architecture of TLS handshake is demonstrated in \autoref{figure:openssl}.
We measured the time cost of certification generation at server side and TLS handshake at client side for 10,000 runs and take the average value. We also measured the native SGX-OpenSSL using original OCALLs. As shown in \autoref{table:openssl}, in our LAN setting, Aurora-OpenSSL introduced about 32\% latency in certificate generation and 21\% in the TLS handshaking because both of them use \textsc{Aurora}'s trusted clock. We anticipate the overhead ratio decreased in WAN environment.

\begin{table}[t]
	\centering
	\caption{Performance comparison between native SGX-OpenSSL and Aurora-OpenSSL.}
	\label{table:openssl}
	\small
	\begin{tabular}{lrr}
		\toprule
		& SGX-OpenSSL & Aurora-OpenSSL \\
		\midrule
		Certificate Generation & 77.4ms & 102.5ms \\
		TLS Handshaking & 2.8ms & 3.4ms \\
		\bottomrule
	\end{tabular}
\end{table}

%\subsection{Secure Online E-Banking}
%
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.45\textwidth]{usbkey.pdf} %height=0.1\textheight,
%	\caption{AuraKey with trusted USB path}
%	\label{fig:usb}
%\end{figure}
%
%State-of-the-art secure token mechanism employs a two-factor authentication, which combines a user password and a physical device (usually a USB key, e.g. Yubikey\footnote{https://www.yubico.com/products/yubikey-hardware/yubikey4/}). %that provides digital certificate to prove genuine user identity. One of the popular examples is Yubikey\footnote{https://www.yubico.com/products/yubikey-hardware/yubikey4/}. Because these USB key implementations are not open source, we built a secure E-Banking application according to their documentations. We name our USB key and secure E-Banking implementation as \textit{AuraKey} and \textit{AuraBank} respectively.
%Typically, a USB key identifies itself as a USB HID keyboard device so that any machine with a keyboard driver can easily read the textual outputs from it, therefore, we use an EHCI-based USB HID keyboard to emulate a USB key, named \textit{AuraKey}. We created an enclave program as a hardened E-Banking prototype, named \textit{AuraBank} and equipped \textit{AuraKey} with a PKCS format certificate from \textit{AuraBank}, as shown in \autoref{fig:usb}. We wrote a script to attach/detach the USB device during runtime, emulating the action of plugging/unplugging of \textit{AuraKey}. We deployed the server side of \textit{AuraBank} on a standalone machine in the local area network.
%
%We then illustrate how Aurora-assisted online E-Banking works. Firstly, a user launches the \textit{AuraBank} application and then performs some personal transactions. All of the confidential transaction logs are locally cached within the enclave of the \textit{AuraBank}. When the user commits her transactions to the bank server, she needs to hot-plugin the \textit{AuraKey} to confirm her operations. After being inserted into the USB slot, the \textit{AuraKey} triggers an SMI to notify SMVisor, which then intercepts all input interrupts of \textit{AuraKey} and obtains the security token. SMVisor hands the security token to \textit{AuraBank} via secure channel. Finally, \textit{AuraBank} sends transaction data and identity authentication information to the bank server via TLS protection, which then authenticates the user identity and validate her transaction. %with what the user knows (i.e. the personal identification number a.k.a PIN) and what the user has (i.e. physically secured private key).
%
%\begin{table}[t]
%	\centering
%	\caption{Aurora-secured Online E-Banking Benchmarks}
%	\label{table:usbkey}
%	\small
%	\begin{tabular}{lr}
%		\toprule
%		Procedure & Time Cost (ms) \\
%		\midrule
%		AuroKey -> AuroBank & 0.468  \\
%		AuroBank -> E-Banking server & 28.701 \\
%		\bottomrule
%	\end{tabular}
%\end{table}
%
%The experimental results are shown in \autoref{table:usbkey}. The first procedure contains the private data transferring from the physical device (AuroKey) to the userspace software (AuroBank); the token is transferred via the secure session with AES-NI based cryptographical protection. The second procedure contains the encrypted two-factor information with TLS protection between two machines. Since the TLS session usually takes 10~ microseconds or more, Aurora's two-factor adds negligible overhead to the authentication process. With the help of trusted path, it is impossible for any untrusted software on the user computer to access either USB token or user password. % or other local credentials. %An alternative would be the OTP (one-time password) device that allows the user to login without remembering any password. The OTP device can also be secure using Aurora's framework.

\subsection{Secure SQLite Database}
Databases are widely used to store financial transaction records and other sensitive information. Some databases are built upon block devices, while maintaining its own caching mechanisms and storage policies without support of OS's file system, e.g. SQLite database.

We integrated \textsc{Aurora}'s Tlibaurora into existing SGX-SQLite projects\footnote{https://github.com/yerzhan7/SGX\_SQLite} and added code to support standard file system calls such as \textit{open}, \textit{read}, \textit{write}, \textit{fsync}, \textit{fcntl} and \textit{ftruncate}. We then eliminated the file-related OCALLs for the untrusted system. 
%To protect the data, Tlibaurora's shim layer uses the symmetric key derived from user password and in-enclave nonce values to encrypt the file payloads, and uses the cryptographic primitives from Intel SGX SDK to compute MAC values for blocks. 
To avoid password leak, we use \textsc{Aurora}'s trusted input path to obtain users' password from keyboard devices. Moreover, \textsc{Aurora}'s secure session protects the confidentiality and integrity of data between SQLite enclaves and SMVisor.   %Last but not least, Tlibaurora library uses the cryptographic primitives from Intel SGX SDK to compute MAC values for block request and response messages.

We evaluated the enhanced SQLite performance by inserting a randomly generated record to a big table for 1000 times. To make a fair comparison, we set the synchronize flag to "FULL" to avoid the uncertainty of I/O caching. When SGX-SQLite invokes Tlibaurora file APIs, it opens the USB storage device as a raw block file in direct I/O mode and reads/writes data using 4KB block size. In our experiment, the native insertion transactions for 1000 times cost 17.3 seconds while the ones with \textsc{Aurora}'s trusted path cost 20.5 seconds. About 18\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}. %Since the USB DMA transfer is designed as an asynchronous mechanism, the delay is not that explicit. 
%We plan to combine with existing in-enclave filesystem support~\cite{OBLIVIATE2018} for \textsc{Aurora}'s trusted storage path.

%\subsection{Secure Password Manager}
%To ease the cumbersome memoir on multiple passwords, password manager is a convenient tool that allows the end-user to store and manage her passwords. It uses a master key to encrypt the rest of password in a local database. %Though convenient, it may still be vulnerable and render user critical information at risk. An advanced malware can hook the activity of the password manager application and log the corresponding the key events when a "new entry" GUI window is popped up, compromising the security of user password.
%Intel's SGX tutorial \cite{HoekstraUsingInnovativeInstructions2013} uses a password manager to demonstrate the usage of SGX. %Indeed, Intel SGX is a perfect technology for protecting the password manager software itself at runtime as well as the password processing process. 
%However, a user still needs to type in his username and password to initialize a password entry. Without a trusted input path, the SGX-assisted password manager cannot assure to protect the user's confidentiality.
%
%We retrofitted KeePassX, an open source GUI password manager, to demonstrate Aurora's trusted input path. We ported the crypto process, kdbx password database and entry editing functions into an enclave program, so that the user's passwords are clear text only in the enclave. When the user adds a new entry, a GUI message box is popped up, and SMVisor is activated to intercept all keyboard inputs. %Since the GUI logic is untrusted, we do not allow the GUI to touch the real password character, rather, after the user releases a key, the enclave sends the \textit{signal} to GUI and the GUI displays an asteroid. 
%After the user clicks the "OK" button, her username, password and other private information are then encrypted inside the enclave, and later restored into the database in encrypted format.

\section{Evaluation}\label{performance}

In this section, we evaluate the performance of \textsc{Aurora} framework and the trusted I/O paths. Our experiments are carried out on  an Intel Core i7-7700HQ 2.8GHz CPU with 16GB of memory, running Ubuntu 16.04 LTS and SGX SDK 2.4 and SGX driver 1.9.

\subsection{Framework Overhead}
%% 我们使用pi计算做评估，不同触发周期和抢占时间
We select  pi\_css5\footnote{http://myownlittleworld.com/miscellaneous/computers/piprogram.html} program, which has no interaction with the external system, to measure the performance of \textsc{Aurora} with as little noise as possible. We ran the program till achieving 4,000,000 digits of precision, and used two durations (70us and 150us) to emulate different real-world environments.

%% 一个线程触发，一个线程计时
%% 太高的请求我们认为不合理；OS有权拒绝SMI请求，以此降低性能影响
Specifically, we ran two threads: one thread (T1) running Pi number calculation, the other thread (T2) requesting the ashmd module to trigger an SMI in a given interval. Firstly, we ran T1 without the interference of T2 and took the time cost as baseline. Then we started T2 to see the slowdown of T1. From \autoref{table:pi}, we observe that when the interval decreases, the overhead increases. The worst case of overhead is around 21\%, where \textit{smcalls} are requested too frequently. Such situation is rare in real world applications because an enclave has to execute its own logic. We observe that intensive requests may impact the time-sensitive tasks on the same system. Since \textit{smcalls} are forwarded by ashmd module, it can use a threshold to block a malicious enclave from abusing. In our current setting, we allow an enclave to request up 10,000 times per second, which introduces about 11\% overhead to the system.

\begin{table}[t]
	\centering
	\caption{Measuring \textsc{Aurora}'s overhead by calculating Pi.}
	\label{table:pi}
	\begin{tabular}{rrrrr}
		\toprule
		\multirow{2}{*}{Interval} & \multicolumn{2}{c}{Time cost (s)} & \multicolumn{2}{c}{Overhead ratio} \\\cmidrule{2-3}	 \cmidrule{4-5}
		& 70us & 150us & 70us & 150us \\
		\midrule
		Baseline & 8.545 & 8.635 & 0 & 0\\
		1000ms & 9.045 & 9.025 & 5.85\% & 4.52\%\\
		100ms & 9.605 & 9.590 & 12.40\% & 11.06\%\\
		10ms & 10.180 & 10.455 & 18.90\% & 21.08\%\\
		\bottomrule
	\end{tabular}
\end{table}

\subsection{Trusted Clock Benchmark}\label{time_bench}
%It is important to quantify how much time is required to attain a trusted clock service since the potential service latency impacts the freshness of message and indicates the response speed. 
For this experiment, we measured the complete trusted clock procedure for 10000 time and used the average value. Table \ref{table:breaktime} shows the time cost for each step in a trusted clock path, as explained in \autoref{workflow}. We can see that the clock service takes most of time. This is because 1) the RTC driver has to read clock value twice to check if the clock is updating its time data; 2) The RTC involves several \textsf{INS} instructions to read each field of a calendar time, and costs 14us to obtain a complete wall-clock time in one request; 3) The other 4 timers cost roughly 10us in sum. The total  time cost (84us) satisfies the requirement of real-world trusted timestamps.
\begin{table}[t]
	\centering
	\caption{ Breakdown of the trusted clock service}
	\small
	\label{table:breaktime}
	\begin{tabular}{lr}
		\toprule
		Action step & Time Cost(us) \\
		\midrule
		EPC encryption & 2\\
		Copy to shared RAM & 2\\
		Switch to SMM & 13\\
		Copy to SMRAM & 0\\
		SMRAM decryption & 3\\
		Clock Service & 44\\
		SMRAM encryption & 3\\
		Copy to shared RAM & 0\\
		Return and enter SGX & 12\\
		Copy to EPC & 3\\
		EPC decryption & 2\\
		\bottomrule
	\end{tabular}
\end{table}
\begin{table*}[t]
	\centering
	\caption{Comparison of existing clock services that can be used for SGX enclaves. Clock services include network time protocol (NTP), precision time protocol (PTP), and the platform software (PSW) supported by Intel management engine (ME)}
	\label{table:timeservice}
	\small
	\begin{tabular}{llllrccr}%{ |c|c|c|c|c|c|c|c| }
		\toprule
		Clock Provider & Approach & Type & Resolution & Request Cost & Latency & Security & Use Cases \\
		\midrule
		Remote Clock & NTP/PTP & absolute & 1s & $>$100ms & high & trusted & Town Crier~\cite{DBLP:conf/ccs/ZhangCCJS16} \\
		Intel ME & PSW & relative & 1s & 10.3ms & medium & trusted & SGX-Tor~\cite{DBLP:conf/nsdi/KimHHKH17} \\
		OS & ocall & absolute & 1ns & 6us & low & untrusted & Panoply~\cite{shinde_panoply:_2017} \\
		Hardware Clock & \textit{smcall} & absolute & 1ns & 69us & low & trusted & Aurora-OpenSSL~\ref{openssl} \\
		\bottomrule
	\end{tabular}
\end{table*}

For comparison, we measured the performance of other clock providers. The results are shown in \autoref{table:timeservice}. Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks like timing attacks. 
Among existing approaches, \textsc{Aurora} outperforms remote clock (the 2nd row) and Intel's reference clock (the 3rd row) by introducing very low latency, while achieving the same resolution (nanosecond-level) as OS services (the 4th row). 
%Note that any approach can be arbitrarily delayed in that the untrusted OS is in charge of the enclave thread scheduling. We treat intentionally time delay as a form of Denial-of-Service attack.

% 测试结果说明Aurora方法下的串口响应速度更快，和Linux原生方法频繁的上下文代价有关
\subsection{Serial Port Output Benchmark}

\begin{table}[h]
	\centering
	\caption{Serial-port benchmark comparison between Linux and \textsc{Aurora}.}
	\label{table:serial}
	\small
	\begin{tabular}{lrrr}
		\toprule
		Payload Size(KB) & Linux(s) & Aurora(s) & Speedup(\%) \\
		\midrule
		4 & 0.03 & 0.03 & 0.0 \\
		64 & 0.32 & 0.24 & 25.0 \\
		256 & 1.08 & 0.87 & 19.4 \\
		1024 & 3.95 & 3.43 & 13.2 \\
		\bottomrule
	\end{tabular}
\end{table}

It is rather difficult to measure the overall time during which a printer accepts and finishes a print job, because we have to re-flash the printer firmware to hook its time function. Therefore, we redirected the serial port to a local file. 
To compare the serial output performance between native Linux and \textsc{Aurora}, we measured the time cost of writing the test data of different sizes to the serial-port address in Linux and in \textsc{Aurora}, respectively. \autoref{table:serial} shows the experimental results. \textsc{Aurora} performs better than native Linux because \textsc{Aurora} uses batch mechanism (\autoref{batch}) to reduce the frequent mode transitions while Linux has more user/kernel mode transitions when writing large data to serial port. Note that, for the larger outputted data, the speedup decreases due to cryptographic computations in \textsc{Aurora}.

\subsection{Trusted USB Storage Benchmark}

\begin{table}[h]	
	\centering
	\caption{Storage throughput comparison between Linux and \textsc{Aurora}.}
	\label{table:dd}
	\small
	\begin{tabular}{lllr}
		\toprule
		\multirow{2}{*}{Payload Size(MB)} &  Linux & Aurora & Slowdown \\ 
		& (MB/s) & (MB/s) & (\%) \\
		\midrule
		4 & 32.9 & 31.8 & 3.3 \\
		64 & 40.9 & 39.2 & 4.2 \\
		256 & 42.7 & 40.4 & 5.3 \\
		1024 & 53.2 & 47.5 & 10.7 \\
		\bottomrule
	\end{tabular}
\end{table}

To compare the overhead introduced when applying \textsc{Aurora}'s trusted I/O path on USB storage devices, we used \emph{dd} program with options "fsync" and "direct" to write variable sizes of contents to a USB mass storage device on native Linux system as the baseline. To avoid the side-effect of any buffer mechanism, we use Linux raw device to mount and initialize the USB device. % to bypass any file system interference. We then measure the overheads of using Aurora's SMVisor for MAC verification added to each block request in the request and response path. We did not use any encryption in this experiment. 
The throughput results are shown in \autoref{table:dd} where the size of each block is set to 4KB. \textsc{Aurora} achieves approximately 90\% of the baseline throughput when writing 1GB to device. The major overheads are contributed by SMM/Protected mode transitions and cryptographic computations on each block.

\subsection{Security Effectiveness}\label{security}
In this section, we evaluate \textsc{Aurora}'s reliability with several security tests.

\textbf{Keylogging Attack.}
To evaluate the effectiveness of \textsc{Aurora}'s trusted input path, we deployed multiple spyware to get a user's inputs under trusted input mode, including a stealthy root keylogger\footnote{https://github.com/vim2meta/keylogger}, a rootless X11-based keylogger ixkeylog\footnote{https://github.com/dorneanu/ixkeylog}, 
%and xkbcat\footnote{https://github.com/anko/xkbcat}, 
a kernel-level rootkit  keylogger\footnote{https://github.com/arunpn123/keylogger}, 
%and Linux-Keylogger\footnote{https://github.com/nijindal/Linux-Keylogger} 
and a remote keylogger\footnote{https://github.com/EinBaum/Totally-Not-A-Virus}. None of them can obtain the user's inputs.

\textbf{Output Corruption Attack.}
We leveraged a DMA-based NIC device to launch output corruption attack when using Aurora's trusted serial printer service. Since  SMRAM and EPC RAM are strongly isolated by architectural protections, only meaningless content (0xFF) is obtained. Therefore no secrets are leaked. We then conducted another DMA attack to corrupt SMM drivers outside of SMRAM. SMVisor detected its integrity tampered  and rejected subsequent requests, then notified the enclave application. Moreover, we conducted another DMA attack to corrupt the content of shared memory of the secure session. Both SMVisor and Tlibaurora can verify the broken MAC and restart a new session.

\textbf{Time Deception Attack.}
To evaluate \textsc{Aurora}’s trusted clock, we intentionally modified the RTC when an enclave issued a request for trusted clock. Tlibaurora detected the attacks successfully and indicated a failure. For instance, gettimeofday() returns -1 and sets the global variable \textit{errno} appropriately. Existing C library specification does not have a flag indicating time attacks, the enclave logic may keep requesting until obtaining a valid time value. We support failure handling in Tlibaurora to help enclaves deal with such situations.

\textbf{Storage Deception Attack.}
We modified the kernel driver of SCSI device and randomly dropped several disk I/O requests intentionally.  SMVisor detected such accidental conditions and notified the Tlibaurora of corresponding enclave. In our current setting, the Tlibaurora will automatically try issuing the lost I/O requests three times so as to avoid storage failure. In our experiments, the enclave finally received the attack warning from the Tlibaurora and logged these events for further forensic analysis.

\section{Related Work}
Our technique was inspired by Scotch~\cite{DBLP:conf/raid/LeachZW17} which is the first work that combines SGX and SMM to audit VM resource usage. Its motivation differs from ours.
Similar to \textsc{Aurora}'s SMVisor, previous research such as HyperCheck~\cite{DBLP:conf/raid/WangSG10}, HyperSentry~\cite{DBLP:conf/ccs/AzabNWJZS10} and IOCheck~\cite{DBLP:conf/esorics/ZhangWLS14}, also employ a dedicated SMI handler to protect the integrity of the OS kernel, hypervisor or firmware, respectively.
We next discuss related work of other trusted I/O architectures and trusted paths.

\subsection{Trusted I/O Architectures}
%\autoref{arch_compare} demonstrates the comparison between \textsc{Aurora} and other architectures. 
SGXIO~\cite{weiser_sgxio:_2017} is a conceptual framework that discusses how to provide trusted generic I/O paths for SGX enclaves. It introduces a trusted hypervisor to assist the establishment of the trusted path and requires users to port drivers into enclaves. However, SGXIO is a conceptual design without any implementation and evaluation. Moreover, it is hard for users to port commodity drivers into an enclave because 1) enclave mode does not support privileged instructions like IN/OUT or RDMSR/WRMSR with which drivers read/write I/O ports; 2) it is unclear in the paper \cite{weiser_sgxio:_2017} how to correctly partition drivers. In comparison, \textsc{Aurora}'s drivers are invoked in SMM mode without any instruction restricted. They are monitored and regulated by SMVisor protected inside SMRAM. This reusing technique allows \textsc{Aurora} easily deployed.

Zhou et al.~\cite{zhou_dancing_2014} introduce a micro-hypervisor (named Wimpy) under OS to build trusted paths (TP) between program end-points (PE) and device end-points (DE). They require the PE of a TP includes the device drivers for DEs associated with the TP, and admit that \textit{"running the PE in Ring 3 makes DE driver porting more difficult"}.  Although \textsc{Aurora} and Wimpy share many common security goals, e.g. interrupt isolation and MMIO protection, \textsc{Aurora} exploits CPU features to protect the PEs and reuse DEs securely. As a result, \textsc{Aurora} has smaller TCB than Wimpy.

Intel SGX platform services (PSW)~\cite{intel_psw} uses management engines (ME) to provide trusted time and monotonic counters services by running a co-processor with integrated NIC, RTC and SPI flash, etc. It brings separated hardware that cannot be controlled by untrusted system. However, since Intel ME runs simultaneously with the main CPUs, we believe that it is difficult and insecure for Intel ME to implement secure human-interface input for enclaves as \textsc{Aurora} does. Because the CPU controlled by untrusted OS and the ME co-processor controlled by trusted software may race a DMA access  to the keyboard buffer, which cannot guarantee protection on user's confidential input. In comparison, \textsc{Aurora}'s SMVisor in nature preempts the untrusted OS.

\subsection{Specific Trusted Paths}

\textbf{Trusted Input Paths.}
On the desktop side, TrustLogin~\cite{zhang_trustlogin:_2015} uses SMM to protect a user's password. In secure mode, it caches the keyboard input inside the SMRAM; when the user releases an “Enter” key, TrustLogin places the password inside corresponding packets in the NIC buffer. By contrast, \textsc{Aurora} does not need to intercept OS networking services at all, therefore decreasing its overall impact surface.
Fidelius \cite{DBLP:journals/corr/abs-1809-04774} leverages a Raspberry Pi to implement a secure channel between the keyboard and the hardware enclave. The specific LED is turned on when a secure channel is established.  \textsc{Aurora} does not need any specialized I/O devices and reuse existing hardware devices.
On the server side, SafeKeeper~\cite{DBLP:conf/www/KrawieckaKPMA18} leverages SGX to protect the password databases on untrusted clouds. It uses several strategies to mitigate attacks such as phishing. As Intel SGX is also available on personal laptops and mini PCs (i.e., NUCs), we take advantage of SGX to protect personal password when the user logs in on the client side, which differs from their scenarios.
On the mobile side, TrustUI~\cite{DBLP:conf/apsys/LiMHXZCL14} exploits ARM TrustZone to build a trusted path between a user and a service provider, since ARM TrustZone can isolate physical memory and peripheral interrupts. In design, SMVisor is similar to the trusted OS inside TrustZone's secure world.

\textbf{Trusted Clock Paths.} Intel PSW~\cite{intel_psw} supports coarse-grained trusted time but does not provide a wall-clock time. \textsc{Aurora} provides high resolution and absolute clock. ShieldBox~\cite{DBLP:conf/sosr/TrachKGABF18} achieves high-precision yet low-latency clock service by on-NIC PTP clock, however, the time source is not secure because enclaves cannot detect if  NIC-Timer is tampered. By contrast, \textsc{Aurora} can detect time attack via a validation algorithm. Déjà Vu~\cite{DBLP:conf/ccs/ChenZRZ17} implements a reference clock thread using transactional synchronization extensions (TSX) to protect a trustworthy source of time measurement. Déjà Vu's goal is to detect interrupt-based attacks, while \textsc{Aurora} can provide a general time service for enclaves. Compared to our previous work \cite{DBLP:conf/eurosys/LiangL18}, which provides a trusted clock to enclaves, this paper proposes a unified framework for different I/O devices, provides more trusted I/O paths, and presents more evaluation on real-world applications. ROTE~\cite{DBLP:conf/uss/MateticAKDSGJC17} proposes a protocol for distributed enclaves to provide a monotonic counter, which has high latency than \textsc{Aurora}'s trusted clock service.

\textbf{Trusted Storage Paths.}
AuditedIO~\cite{DBLP:conf/apsys/BalakrishnanCBS17} leverages SGX and a kernel module to implement verifiable data storage for disk I/O operations. However, it requires programmable SSD devices and modifies their firmware. % moreover, its kernel module is not isolated nor verified. 
By contrast, \textsc{Aurora} is a generic framework which can be used to support any storage devices. % and it protects SMM supervisor inside SMRAM and use mutual authentication to ensure its authenticity.
Jiang~\cite{Jang2017Building} builds a trusted path between a USB proxy device and an enclave. The proxy device uses LED display for user verification. It plays the role of  \textsc{Aurora}'s SMVisor while \textsc{Aurora} needn't introduce any dedicated hardware. % while meeting the same or better protection requirements.
BASTION-SGX~\cite{DBLP:conf/isca/PetersLVPK18} modifies the Bluetooth firmware to establish trusted  paths between Bluetooth  devices and enclave programs on SGX-enabled platforms. It has similar threat model with \textsc{Aurora} and rules the privileged software (OS, drivers, etc.) out of the TCB. %However, it requires enclave programs to take charge of handling the HID input, which is a burden for developers. 
By contrast, \textsc{Aurora} is a generic trusted I/O architecture and extensible to support new peripheral devices. % and outstands BASTION-SGX by its high extensibility.   It is a client/server architecture whereas Aurora reuses existing hardware features on one machine.% light-weight terminal on the end-host to,  Bumpy~\cite{DBLP:conf/ndss/McCunePR09} utilizes dedicated hardware to establish trusted user input path and hence cannot generalize to other devices. Cloud Terminal~\cite{DBLP:conf/usenix/MartignoniPZHMSPPSS12} is a micro-hypervisor-based method that provides terminals secure access to sensitive applications from an untrusted OS. 
SGX-FS \cite{DBLP:conf/cloudcom/BurihabwaFMS18} hardened a user-level filesystem in an enclave, which is more generic than \textsc{Aurora}. Similarly, Pesos~\cite{DBLP:conf/eurosys/KrahnTVKBF18} build a trusted path between enclaves and a storage device. However, Pesos requires a special storage device named Kinetic Open Storage as the device end, while \textsc{Aurora} does not.

\section{Conclusion}

We present \textsc{Aurora}, a novel architecture which provides trusted I/O paths on untrusted X86 platforms. Based on \textsc{Aurora}, we design and implement several trusted I/O paths for SGX enclaves, including HID keyboard, serial-port printer, USB mass storage and the hardware clock. To the best of our knowledge, we are the first to provide these \emph{realistic} trusted I/O paths for enclaves. Our implementation demonstrates that \textsc{Aurora} is extensible and transparent with underlying commodity systems. Security and performance evaluations with real-world applications show that \textsc{Aurora} can mitigate several I/O related attacks and provide trusted I/O paths with low overhead.

\section*{Acknowledgement}
The authors would like to thank Kai Huang from Intel and Shweta Shinde from NUS for their generous help and constructive comments. The authors also thank the anonymous reviewers for their valuable feedback that help improve the article.

### 2019-06-29 article.tex
minor fixes

% ------------------------------------------
%  IEEE ARTICLE TEMPLATE
% ------------------------------------------
% Author(s):
% Institution(s):
% ------------------------------------------
\documentclass[journal,twocolumn,letterpaper,10pt]{ieee-sty/IEEEtran}
\usepackage[acronym]{glossaries}

\usepackage{epsfig}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{blindtext}
\usepackage{xcolor}
\usepackage[ampersand]{easylist}
\usepackage[]{algorithm2e,algorithmicx}
\usepackage[bottom]{footmisc}
\usepackage{graphicx}

\usepackage{hyperref}

\renewcommand{\sectionautorefname}{\S}
\renewcommand{\subsectionautorefname}{\S}
\renewcommand{\subsubsectionautorefname}{\S}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{enumitem}
\usepackage{flushend}

% Generates the acronyms list
\makeglossaries

% Acronyms list
\input{acronyms/acronyms.tex}

% ------------------------------------------
%  MAIN DOCUMENT
% ------------------------------------------
\begin{document}

% Variables file
\input{variables.tex}

% Article title
\title{Aurora: Establishing Trusted I/O Paths\\ on SGX-Based Client Systems}

% Author(s) Name
\author{Hongliang~Liang,~\IEEEmembership{Member,~IEEE,}
	Mingyu Li,%~\IEEEmembership{Fellow,~OSA,}
	~Lin Jiang,~Zhuosi Xie,~Tianqi Yang,~Yixiu Chen\\
	TSIS Lab, BUPT
  %, Tianqi Yang, Mingyue Li, Yudong Wang % <-this % stops a space
	\thanks{H. Liang, M. Li, L. Jiang, Z. Xie, T. Yang, Y. Chen 
  %, T. Yang, M. Li, and Y. Wang 
  are with Beijing University of Posts and Telecommunications, Beijing 100876, China. e-mail: (\{hliang,maxul,jianglin,xiezhuosi,yangtianqi,chenyixiu\}@bupt.edu.cn)
  %; yangtianqi@bupt.edu.cn; li\_mingyue@bupt.edu.cn; wyd2013@bupt.edu.cn
  }% <-this % stops a space
	\thanks{This work was supported by the National Natural Science Foundation of China (NSFC) under Grant No. U1713212 and 91418206.}
}

\maketitle

% Abstract
\input{abstract/abstract.tex}

% Keywords
\input{keywords/keywords.tex}

% Sections
\input{sections/main.tex}

% Bibliography
\bibliographystyle{IEEEtran}
% Bibliography file
\bibliography{bibliography/article}

\end{document}

### 2019-06-29 sections/main.tex
minor fixes

@@
 Intel SGX enforces strong isolation in memory for security-sensitive compartments in a user-level application, called \textit{enclaves}, from untrusted privileged systems.
-Many SGX-based protection architectures~\cite{DBLP:journals/tocs/BaumannPH15,DBLP:conf/osdi/HuntZXPW16,DBLP:conf/osdi/ArnautovTGKMPLM16,DBLP:conf/icdcs/NguyenG17,7545819,DBLP:conf/sp/SchusterCFGPMR15,WangSET18} have already been proposed to secure data and code on untrusted servers.
+Many SGX-based protection architectures~\cite{DBLP:journals/tocs/BaumannPH15,DBLP:conf/osdi/HuntZXPW16,DBLP:conf/osdi/ArnautovTGKMPLM16,DBLP:conf/icdcs/NguyenG17,7545819,DBLP:conf/sp/SchusterCFGPMR15} have already been proposed to secure data and code on untrusted servers.
 
@@
 \subsection{Workflow}\label{workflow}
-To help understand the workflow of a trusted path in \textsc{Aurora}, we break down the process of output path and input path respectively into sequential-logic phases, as illustrated in left and right part respectively of \autoref{fig:workflow}.
+To help understand the workflow of a trusted path in \textsc{Aurora}, we break down the process of output path and input path respectively into sequential phases, as illustrated in left and right part respectively of \autoref{fig:workflow}.
 
@@
 portable USB disk.
-(Reason why we choose USB, not others???)
 
@@
 It is a serious issue when secure data storage is  necessary for ensuring correct operation (e.g., secure logging, APT monitoring and compliance).
-In this section, we extend \textsc{Aurora} to support secure USB disk as a storage example.
+In this section, we extend \textsc{Aurora} to support secure USB disk.
+Note that \textsc{Aurora}'s approach is also suitable and easy to support for other storage systems.
 
@@
 
-We integrated \textsc{Aurora}'s Tlibaurora into existing SGX-SQLite projects\footnote{https://github.com/yerzhan7/SGX\_SQLite} and added code to support standard file system calls such as \textit{open}, \textit{read}, \textit{write}, \textit{fsync}, \textit{fcntl} and \textit{ftruncate}.
+We integrated \textsc{Aurora}'s Tlibaurora into existing SGX-SQLite projects\footnote{https://github.com/yerzhan7/SGX\_SQLite} and added code to support standard file system calls such as \textit{open}, \textit{read}, \textit{write}, \textit{stat}, \textit{lstat}, \textit{fstat}, \textit{fsync}, \textit{fcntl}, \textit{ftruncate} and \textit{unlink}.
 We then eliminated the file-related OCALLs for the untrusted system.
@@
 \subsection{Trusted I/O Architectures}
-%\autoref{arch_compare} demonstrates the comparison between \textsc{Aurora} and other architectures. 
+
 SGXIO~\cite{weiser_sgxio:_2017} is a conceptual framework that discusses how to provide trusted generic I/O paths for SGX enclaves.
@@
 However, SGXIO is a conceptual design without any implementation and evaluation.
-Moreover, it is hard for users to port commodity drivers into an enclave because 1) enclave mode does not support privileged instructions like IN/OUT or RDMSR/WRMSR with which drivers read/write I/O ports; 2) it is unclear in the paper \cite{weiser_sgxio:_2017} how to correctly partition drivers.
+Moreover, it is hard for users to port commodity drivers into an enclave because 1) enclave mode does not support privileged instructions like \textsf{IN/OUT} or \textsf{RDMSR/WRMSR} with which drivers read/write I/O ports; 2) it is unclear in the paper \cite{weiser_sgxio:_2017} how to correctly partition drivers.
 In comparison, \textsc{Aurora}'s drivers are invoked in SMM mode without any instruction restricted.
@@
 On the desktop side, TrustLogin~\cite{zhang_trustlogin:_2015} uses SMM to protect a user's password.
-In secure mode, it caches the keyboard input inside the SMRAM; when the user releases an “Enter” key, TrustLogin places the password inside corresponding packets in the NIC buffer.
+In secure mode, it caches the keyboard input inside the SMRAM; when the user releases an \textsf{Enter} key, TrustLogin places the password inside corresponding packets in the NIC buffer.
 By contrast, \textsc{Aurora} does not need to intercept OS networking services at all, therefore decreasing its overall impact surface.
@@
 \textbf{Trusted Storage Paths.}
-AuditedIO~\cite{DBLP:conf/apsys/BalakrishnanCBS17} leverages SGX and a kernel module to implement verifiable data storage for disk I/O operations.
+AuditedIO \cite{DBLP:conf/apsys/BalakrishnanCBS17} leverages SGX and a kernel module to implement verifiable data storage for disk I/O operations.
 However, it requires programmable SSD devices and modifies their firmware.
-% moreover, its kernel module is not isolated nor verified.
 By contrast, \textsc{Aurora} is a generic framework which can be used to support any storage devices.
@@
 SGX-FS \cite{DBLP:conf/cloudcom/BurihabwaFMS18} hardened a user-level filesystem in an enclave, which is more generic than \textsc{Aurora}.
-Similarly, Pesos~\cite{DBLP:conf/eurosys/KrahnTVKBF18} build a trusted path between enclaves and a storage device.
-However, Pesos requires a special storage device named Kinetic Open Storage as the device end, while \textsc{Aurora} does not.
+Similarly, Pesos~\cite{DBLP:conf/eurosys/KrahnTVKBF18} builds a trusted path between enclaves and a storage device and supports policy-based object protection.
+However, Pesos requires a programmable storage device named Kinetic Open Storage as the device end, while \textsc{Aurora} aims for general storage devices.
 

### 2019-07-02 sections/main.tex
reclaim over related work ; rename SMM Supervisor to SMVisor

@@
 SGX-FS \cite{DBLP:conf/cloudcom/BurihabwaFMS18} hardened a user-level filesystem in an enclave, which is more generic than \textsc{Aurora}.
-Similarly, Pesos~\cite{DBLP:conf/eurosys/KrahnTVKBF18} builds a trusted path between enclaves and a storage device and supports policy-based object protection.
-However, Pesos requires a programmable storage device named Kinetic Open Storage as the device end, while \textsc{Aurora} aims for general storage devices.
+Similarly, Pesos~\cite{DBLP:conf/eurosys/KrahnTVKBF18} builds a trusted path between enclaves and a storage device and supports fine-grained policy-based object protection for cloud storage users.
+However, Pesos requires a programmable storage device named Kinetic Open Storage as the device end, while \textsc{Aurora} does not.
 

### 2019-07-03 sections/main.tex
new title; body polish; new figures in pptx

--- 2019-06-29 sections/main.tex
@@
 \section{Introduction}
-%% 从定义出发 “可信计算” 的定义出发，可信计算包含五个组件。%% 云环境下安全问题众多（引用云攻击综述）；用户安全与隐私问题受人关注，IntelSGX应运而生，已有不少工作，例如针对原装二进制、数据分析、网络中间件等一系列工作横空出世，都很好地利用SGX自身的特点，那就是内存对外不可见。但是缺乏对安全IO的保证。
+
+%% 从定义出发 “可信计算” 的定义出发，可信计算包含五个组件
+%% 云环境下安全问题众多（引用云攻击综述）；用户安全与隐私问题受人关注，IntelSGX应运而生，已有不少工作，例如针对原装二进制、数据分析、网络中间件等一系列工作横空出世，都很好地利用SGX自身的特点，那就是内存对外不可见。但是缺乏对安全IO的保证。
 Trusted computing~\cite{DBLP:journals/ieeesp/Felten03} encompasses six key technologies including: 1) endorsement key, 2) protected execution, 3) sealed storage, 4) secure input and output, 5) remote attestation, and 6) trusted third party.
 To this end, Intel provisions Software Guard eXtensions (SGX) \cite{DBLP:conf/isca/McKeenABRSSS13} to establish trusted execution environment that protects the integrity and confidentiality of desired computation.
-%This technology can be treated as "protected execution" in these six requirements.
-%% 比较可惜的是，这项技术本身并没有为数据的通道做任何加固。一个只计算不交互的应用几乎是不存在的，比如上面提到的工作，都对IO的吞吐做了评测。也就是说，SGX 不保护数据的安全进出，只保护计算过程本身。对于不可靠的数据，我们认为计算是没有价值的，例如时间。此外，我们认为，已有的SGX 网络工作更多保护了应用层数据，对底层的包数据没有很好的加固。这些都和SGX技术自身设计的出发点有关，那就是归根结底要依赖不可信的OS。
 Intel SGX enforces strong isolation in memory for security-sensitive compartments in a user-level application, called \textit{enclaves}, from untrusted privileged systems.
@@
 
+%% 比较可惜的是，这项技术本身并没有为数据的通道做任何加固。一个只计算不交互的应用几乎是不存在的，比如上面提到的工作，都对IO的吞吐做了评测。也就是说，SGX 不保护数据的安全进出，只保护计算过程本身。对于不可靠的数据，我们认为计算是没有价值的，例如时间。这些都和SGX技术自身设计的出发点有关，那就是归根结底要依赖不可信的OS。
 Unfortunately, Intel SGX enclaves have no direct access to any hardware resources because Intel SGX by design does not support any secure input/output mechanisms according to its Software Developer's Manual~\cite{Corporation2016Intel}.
@@
 %As for some enclave programs that require human interactions like keyboard/mice input and display on the screen,
-Today's SGX ecosystem has not yet come up with an off-the-shelf solution to trusted I/O paths. Enclaves themselves cannot authenticate whether they are communicating with trusted devices or not. 
-%Therefore, we make a bold judgment that: without trusted I/O paths, SGX enclaves themselves cannot fully accomplish their security purposes. 
+Today's SGX ecosystem has not yet come up with an off-the-shelf solution to trusted I/O paths.
+Enclaves themselves cannot authenticate whether they are communicating with trusted devices or not.
 It is significantly important to solve the problem on \textbf{\emph{how to establish trusted I/O paths for enclaves on untrusted systems}}, as almost all SGX-based projects exclude the underlying OS from the trusted computing base (TCB) while awkwardly depending on it for I/O requests.
-%In this paper, we concentrate on providing TIOS for enclaves, e.g.
-\textbf{device-to-enclave secure network, high-resolution absolute clock, and isolated keyboard input}, which are essentially significant yet rarely discussed in current SGX ecosystems.
 
@@
 Therefore, Intel SGX enclaves can safely use I/O devices while remaining  \textit{transparent} to the underlying OS.
-%of small code size and
-
-%% 我们的贡献点有：Aurora是个全新的系统服务框架；三款全新的服务；实际的应用评估证明其可用性。
+
+%% 我们的贡献点有：Aurora是个全新的系统服务框架；四款全新的服务；实际的应用评估证明其可用性。
 To summarize, this paper makes these contributions:
@@
 \subsection{Software Guard eXtension}
-%% SGX基本概念。不可见性
 Intel SGX \cite{DBLP:conf/isca/McKeenABRSSS13} provides trusted execution environments called enclaves in user level.
@@
 Local attestation allows an enclave to prove to one another that it is running on the same processor.
-%An enclave proves its identity to another target enclave via the EREPORT instruction.
-This instruction produces an attestation report that cryptographically binds a message supplied by the enclave with the enclave's measurement-based and certificate-based identities.
-Moreover, a particular enclave, called Quoting Enclave, is used for remote attestation.
-With the help of Quoting Enclave, an enclave can produce a secure assertion that identifies the hardware environment and itself.
-The enclave owner can use Intel Attestation Service to assess the trustworthiness of the assertion.
-Thereafter, the owner can establish a secure channel and provide sensitive data to the enclave.
 
 \subsection{System Management Mode}
-%% SMM模式的基本工作原理；对OS不可见；
 System Management Mode (SMM) is the most privileged mode for handling system-wide functions like power management, hardware control, etc.
@@
 We deem SMRAM as a special \textit{enclave} in SMM.
-%The CPU can enter SMM from any privilege mode upon a system management interrupt (SMI).
-
-%% SMI中断不可屏蔽。
+
 The SMI handler is initialized by UEFI, and  SMRAM can be locked by configuring D\_OPEN and D\_LCK bits in SMRAM control register.
@@
 \subsection{Trusted I/O Paths}\label{types}
+
 %% 传统的UNIX系统将设备分为字符设备、块设备和网络设备。每种设备都有自己的I/O端口号、IRQ中断号以及对应的物理内存。字符设备是最为原生的设备，这些设备包括鼠标、键盘、实时时钟、串口等。这些设备要么产生电平数据作为CPU的输入，要么得到CPU的输出作为指示。我们将此类设备归类为“生产/消费设备”。块设备和网络设备负责数据的持久化保存和在计算节点间传输，他们自身不产生也不消耗带有信息的数据，我们根据其功能将其命名为“存储/传输设备”。我们观察并认为所有的设备都可以归结为这两类，并为这两类设备与程序间构建可信路径。由于分类的不同，可信路径的工作原理也不同。参考Zhou，我们依旧将可信路径的组成分成三个组件：设备端、程序端和通信路径。“生产/消费设备”模型下可信路径要求设备的数据/指令必须通过通信路径传输。这是因为，这些设备参与了数据的产生或使用，而硬件自身并不支持加密协议来保证数据的隐私，这种情况下，我们需要在设备端引入新的TCB对数据做密码学处理。相比之下，“存储/传输设备”只是被动地接收或发送已有的数据，保护隐私的加密运算可以单独放在程序端完成。类型的不同导致了设计的不同，甚至实现代价也不同。我们会在后文中说明。
@@
 an SGX enclave) and a trusted peripheral device, a trusted I/O path is a secure channel of data transfers between them, even in the face of software adversaries such as host kernel, hypervisor, guest VM and kernel drivers.
-We classify trusted I/O paths into two categories based on their characteristics: %1) \textit{trusted I/O paths for data-provider/-consumer devices}, e.g., keyboard, mouse, printer, and clock; and 2)  \textit{trusted I/O paths for data-storage/-transmitter devices}, e.g.
-disk, network adapter.
-Both of them co-exist with the commodity OS and can isolate critical components from the untrusted OS and other manipulated devices.
+We classify trusted I/O paths into two categories based on their characteristics:
 
@@
 We consider an adversary that is able to compromise the target system.
-He can directly attack enclave interfaces visible to the OS, and actively reconfigure any devices (e.g., modify a device’s MMIO region, or change the operating mode of a device)
-and perform arbitrary operations (e.g., trigger interrupts, issue DMA write requests) using any I/O commands.
-%Logical attacks, e.g., unauthorized memory access by privileged software, are \textsc{Aurora}'s major concern.
+He can directly attack enclave interfaces visible to the OS, and actively reconfigure any devices (e.g., modify a device’s MMIO region, or change the operating mode of a device) and perform arbitrary operations (e.g., trigger interrupts, issue DMA write requests) using any I/O commands.
 
@@
 Our assumptions significantly reduce the TCB on the target host as modern commodity system contains a large system software (UEFI, possibly hypervisor, kernel and other applications) when dealing with I/O devices.
-%As SGX's threat model, we don't consider denial-of-service (e.g.
-disabled SMI) and side channel attacks.
-Even though we do not consider physical attacks on devices, side-channel attacks, or denial-of-service attacks, we adopt side-channel free cryptographic algorithms and apply an oblivious packet transferring method.
+Even though we do not consider physical attacks on devices, side-channel attacks~\cite{chen2019sgxpectre, ridl}, or denial-of-service attacks, we adopt side-channel free cryptographic algorithms and apply an oblivious packet transferring technique.
 
@@
 \section{Design}
-%% 再说一次，我们用的是SMM和SGX两种CPU特性组成的“可靠、可信”系统服务。Aurora命名缘由。
+%% 我们用的是SMM和SGX两种CPU特性组成的“可靠、可信”系统服务。Aurora命名缘由。
 To provide trusted I/O paths, we employ the combination of SGX and SMM, both of which are processor enforced protection features.
@@
 	\includegraphics[width=0.5\textwidth]{figures/workflow.pdf} %height=0.25\textheight,
-	\caption{The work-flow of a trusted I/O path. }%The white areas denote the TCB.
+	\caption{The workflow of a trusted I/O path in \textsc{Aurora}. }%The white areas denote the TCB.
 	\label{fig:workflow}
@@
 
-SMVisor is the core component in \textsc{Aurora}.  It may take charge of multiple devices simultaneously, so it needs to determine which device is requested and then invokes the matching driver.
+SMVisor is the core component in \textsc{Aurora}.
+It may take charge of multiple devices simultaneously, therefore it needs to determine which device is being requested and then invokes the corresponding driver.
 
@@
 Specifically, SMVisor intercepts device events by configuring the \textit{Redirection Table} defined in I/O APIC and modifying the destination of the device event to SMI.
-SMVisor distinguishes the interrupt source and thus notifies the untrusted system or a certain enclave.
-In order to forward the interrupt to upper software layer (i.e.
-ashmd), it launches an inter-processor interrupt (IPI) by writing the interrupt command request (ICR) register in the local APIC.
+SMVisor distinguishes the interrupt source and thus notifies a certain enclave or the untrusted kernel.
+In order to forward the interrupt to upper software layer, it issues an inter-processor interrupt (IPI) by writing the interrupt command request (ICR) register in the local APIC.
 
@@
 %\emph{Device Manipulation.} 
-To correctly perform I/O operations, a driver needs to know the exact I/O ports of the target device.
-At the time of system boot, SMVisor collects devices information and configures them.
-It also records their memory mapped I/O (MMIO) base addresses into a \textsf{PCI BAR table}, thereafter the corresponding drivers are able to manipulate the mapped PCI configuration space according to the \textsf{PCI BAR table}.
+To perform I/O operations correctly, a driver should know the exact I/O ports of the target device.
+At the time of system boot, SMVisor collects all device information and records their memory mapped I/O (MMIO) base addresses into a \textsf{PCI BAR Table}, thereafter the matching drivers can manipulate the mapped PCI configuration space according to the table.
 
@@
 SMVisor verifies the validity of parameters passed to the drivers (e.g.
-a PCI structure pointer should point to one of the entries in the \textsf{PCI BAR table} within SMRAM) and checks the return values according to the device specifications (e.g.
-each driver function has a specific range of error codes) as well as its correctness.
+a PCI structure pointer should point to one of the entries in the \textsf{PCI BAR Table} within SMRAM) and checks the return values according to the device specifications (e.g.
+each driver function has a specific range of error codes) as well as its functional correctness.
 When the parameters or return values are invalid, SMVisor notifies the enclave that a potential attack from OS may occur, and rejects the subsequent requests.
@@
 starting address and region range) that the driver tries to access to ensure that it can not write data outside of SMRAM.
-%leak information
-
-%% 没有说是dlmalloc还是tcmalloc，这些分配器代码量大，我们是简单的，但做访问检查
-%\textbf{Runtime Manager.}\label{secure_heap} 
-Furthermore, a driver may require more memory space during run-time (e.g.
+
+Furthermore, a driver may require more memory space during runtime (e.g.
 for DMA with devices), therefore SMVisor maintains a dynamic heap with a sanity-checking feature \cite{DBLP:conf/ccs/SilvestroLCLL17}.
@@
 \subsection{SMM Drivers}\label{driver}
-In this section, we describe how SMVisor can safely reuse existing drivers. %{\color{red}what kind of APIs the drivers are supposed to export for SMVisor} and explain
-%% 内核驱动不该用！移植量不大（见实现），述说移植的简单可行之处
-%\textbf{forward.}\label{forward}
-OS drivers are coupled with the kernel in modern monolithic systems.
-These drivers lack of effective isolation during runtime from the rest of the untrusted systems, therefore we do not use them.
-%There are two options that we can choose from.
-
-%The other is to exclude drivers from the TCB and leave them outside the SMRAM. We prefer this choice because of the following three advantages:
+In this section, we describe how SMVisor safely reuses existing drivers.
+In modern monolithic systems, OS drivers are coupled with the kernel.
+These drivers lack of effective isolation from the rest of the untrusted systems, therefore we do not use them.
+
 Instead, since existing open-source UEFI firmware, such as Coreboot\footnote{https://www.coreboot.org/} and Project Mu\footnote{https://microsoft.github.io/mu/}, contain various drivers in their Driver eXecution Environment (DXE), and the code of these drivers are significantly scrutinized compared to the proprietary code, we reuse these drivers and forward the device interrupt for them to handle.
@@
 
-%\textbf{Verification.}
-%Because the drivers are not protected inside SMRAM and may be tampered with by untrusted privileged software, we cannot simply forward without any verification. Instead, 
-Moreover, we reuse UEFI drivers in a secure manner.
+Furthermore, we reuse UEFI drivers in a secure manner.
 At the booting stage, SMVisor calculates the hash checksum of each driver and stores its integrity signature inside SMRAM.
 When receiving an I/O request, SMVisor verifies the integrity of the corresponding driver to ensure that it is not tampered with.
-%, then it invokes the drivers to response the requests.
 When executing a driver, SMVisor puts its data, heap, stack segments inside SMRAM, and thus ensures them inaccessible to OS/HV.
-Furthermore, SMVisor uses its sanitization module to validate the behavior of the driver, as described in \autoref{shield}.
-
-%% 驱动有个统一框架，方便未来扩展。probe判断设备可用性；读写操作，读写有个约束
-%\textbf{Uniform Interfaces.}
-%In order to accomplish TIOS in a safe manner, the drivers should provide three exported APIs for SMVisor: \textit{probe()} makes sure the device is available, \textit{write()} and \textit{read()} are used to process data flow from/to the devices.
-Using these APIs, we design and implement network, clock and keyboard input TIOSes.
-It illustrates that Aurora's uniform interfaces are sufficient.
-% We do not expose more interfaces to enclaves because these \textit{IOCTLs} may be abused by a malicious enclave to interfere the normal operations of the system.
+Moreover, SMVisor uses its sanitization module to validate the behavior of the driver, as described in \autoref{shield}.
 
@@
 We design a secure session that protects the message exchange between SMVisor and enclaves.
-We first describe \textsc{Aurora}'s kernel module that provides the shared memory for message exchange.
-Then we state the lifecycle of a secure session and optimization techniques upon it.
-
-\subsubsection{ashmd Kernel Module}
+We first describe \textsc{Aurora}'s kernel module that provides the shared memory for message exchange, then we state the lifecycle of a secure session and optimization techniques upon it.
+
+\subsubsection{Kernel Module (ashmd)}
 %% Enclave可以在内部操作不可信内存区数据，从而避免退出；Iago会导致DoS，不会泄漏数据
@@
 \textbf{Key Agreement.}
-After the mutual attestation, the SMVisor and an enclave can establish an authenticated secure channel via an ephemeral Diffie-Hellman key exchange.
-At this point, a secure session is successfully established.
+After the mutual attestation, the SMVisor and an enclave establish an authenticated secure channel via an ephemeral Diffie-Hellman key exchange.
 We then use AES-GCM encryption scheme for further message exchange in order to prevent replay attacks.
-Furthermore, Intel processors with SGX feature support Advanced Encryption Standard New Instructions (AES-NI) to accelerate the AES-GSM encryption, which helps mitigate possible covert-channel attacks~\cite{xu_controlled-channel_2015, DBLP:conf/uss/BulckWKPS17, DBLP:conf/usenix/HahnelCP17}.
+Intel processors with SGX feature support Advanced Encryption Standard New Instructions (AES-NI) to accelerate AES encryption and also can mitigate side-channel attacks~\cite{Corporation2016Intel}.
 
@@
 \subsubsection{Enhancement and Optimization}
-To provide better security and performance, \textsc{Aurora} introduces \textit{data obliviousness}, \textit{hardware encryption} and \textit{batch mechanism for smcalls}.
-
-\textbf{Data Obliviousness.}
-%% 数据隐藏，保证每次内容的随机性
-In an established session, if an enclave requests the same I/O path twice and the results happen to be the same, the encrypted messages will also be identical because the session key is not changed.
-An adversary can infer secrets by observing such covert channels.
-To prevent such secrecy leakage, \textsc{Aurora} pads all messages with random value to the same length (4KB, same size as one EPC page), which restricts possible information leakage at page-level.
-%The message buffers must start with page-aligned address.
+To provide better security and performance, \textsc{Aurora} introduces \textit{hardware encryption}, \textit{data obliviousness} and \textit{batch mechanism for smcalls}.
 
 %% 硬件加速效果如何
-\textbf{Hardware Encryption.} The encryption process is a very attractive target for attackers~\cite{DBLP:conf/acns/BiryukovDC17}.
+\textbf{Hardware Encryption.}
 Intel extends X86 ISA with AES-NI set and claims to prevent known side-channel attacks.
@@
 The hardware-accelerated encryption also decreases the preemption time in SMM mode.
+
+%% 数据隐藏，保证每次内容的随机性
+\textbf{Data Obliviousness.}
+In an established session, if an enclave requests the same I/O path twice and the results happen to be the same, the encrypted messages will also be identical because the session key is not changed.
+An adversary can infer secrets by observing such side channels.
+To prevent such secrecy leakage, \textsc{Aurora} pads all messages with random value to the same length (4KB, same size as one EPC page), which restricts possible information leakage at page-level.
+%The message buffers must start with page-aligned address.
 
@@
 \section{Trusted I/O Paths between Enclaves and Devices}\label{tpaths}
-%\section{Trusted I/O Paths for Data-Provider/-Consumer Devices}\label{path1}
 
@@
 
-%\begin{table*}[t]
-%	\centering
-%	\caption{Comparison of Different Trusted I/O Architecture.
-We do not know the exact lines of code of Intel Management Engine, however, since it consists of a MINIX system and JVM at least, we treat it 10KLoC or so.}
-%	\label{arch_compare}
-%		\small
-%		%\footnotesize
-%	\begin{tabular}{ lllll }
-%		\toprule
-%		& Driver Porting & Prog. Change & Main Components & TCB Size \\
-%		\midrule
-%		Wimpy kernel (HV-based)~\cite{zhou_dancing_2014} & In-app Driver & Intrusive & App drivers, wimpy kernel, hypervisor & 10KLoC \\
-%		SGXIO~~~~~~~~ (HV-based)~\cite{weiser_sgxio:_2017} & In-enclave Driver & N/A & Enclave-driver, hypervisor & N/A\\
-%		Intel PSW~~~~ (ME-based)~\cite{intel_psw} & None-effort & SGX SDK & Intel ME, Minix OS, JVM, firmware & $>$10KLoC \\
-%		\textsc{Aurora}~~~ (SMM-based)~~~~~ & Minimal effort & SGX SDK & SMM Supervisor, libaurora & 3KLoC \\%LibC 
-%		\bottomrule
-%	\end{tabular}
-%\end{table*}
-
-%
-%\textbf{SMM Transfer Monitor.}
-%Intel has released a new technology called STM~\cite{intel_stm} on virtualized environments in its white paper about EDK II\footnote{https://github.com/tianocore/edk2}.
-EDK II is Intel's open source UEFI project.
-In their design, STM is responsible to regulate the UEFI drivers, based on restricted access control.
-This is very similar to SMVisor.
-We believe that the future version of \textsc{Aurora} can benefit from the various drivers in Intel EDK II and provide more trusted services for SGX enclaves.
-
-%\textbf{Browser Password Manager.}
-%We plan to strength the browser logins in the future.
-Most of the browser based password managers are implemented with JavaScript language.
-To use the SGX protection, we need to modify the browser itself.
-Both enhanced browser and its enhanced password managers can defeat many web-based attacks~\cite{DBLP:conf/uss/SilverJBCJ14}.
-%
-%%% 可以扩展至GPU通信，新的服务可能
-%\textbf{Data Processing Services.} Machine learning infrastructures are now benefiting from the convenience of clouds.
-The computation heavily relies on the acceleration of GPUs.
-Malicious cloud administrators that control GPU configurations can make data breach on datasets as well as algorithms~\cite{DBLP:conf/ccs/SongRS17}.
-Building a trusted path between the GPU and in-enclave execution is vital to machine learning security.
-We plan to support secure GPU channel based on \textsc{Aurora} in the future.
-
 \section{Case Studies}\label{casestudy}
@@
 		\toprule
-		& SGX-OpenSSL & Aurora-OpenSSL \\
+		& \textbf{SGX-OpenSSL} & \textbf{Aurora-OpenSSL} \\
 		\midrule
-		Certificate Generation & 77.4ms & 102.5ms \\
-		TLS Handshaking & 2.8ms & 3.4ms \\
+		\textbf{Certificate Generation} & 77.4ms & 102.5ms \\
+		\textbf{TLS Handshaking} & 2.8ms & 3.4ms \\
 		\bottomrule
@@
 		\toprule
-		\multirow{2}{*}{Interval} & \multicolumn{2}{c}{Time cost (s)} & \multicolumn{2}{c}{Overhead ratio} \\\cmidrule{2-3}	 \cmidrule{4-5}
+		\multirow{2}{*}{\textbf{Interval}} & \multicolumn{2}{c}{\textbf{Time cost (s)}} & \multicolumn{2}{c}{\textbf{Overhead ratio}} \\\cmidrule{2-3}	 \cmidrule{4-5}
 		& 70us & 150us & 70us & 150us \\
@@
 		\toprule
-		Action step & Time Cost(us) \\
+		\textbf{Action Step} & \textbf{Time Cost(us)} \\
 		\midrule
 		EPC encryption & 2\\
-		Copy to shared RAM & 2\\
+		Copy to DRAM & 2\\
 		Switch to SMM & 13\\
 		Copy to SMRAM & 0\\
-		SMRAM decryption & 3\\
+		SMM decryption & 3\\
 		Clock Service & 44\\
-		SMRAM encryption & 3\\
-		Copy to shared RAM & 0\\
+		SMM encryption & 3\\
+		Copy to DRAM & 0\\
 		Return and enter SGX & 12\\
@@
 		\toprule
-		Clock Provider & Approach & Type & Resolution & Request Cost & Latency & Security & Use Cases \\
+		\textbf{Clock Provider} & \textbf{Approach} & \textbf{Type} & \textbf{Resolution} & \textbf{Request Cost} & \textbf{Latency} & \textbf{Security} & \textbf{Use Cases} \\
 		\midrule
@@
 		Intel ME & PSW & relative & 1s & 10.3ms & medium & trusted & SGX-Tor~\cite{DBLP:conf/nsdi/KimHHKH17} \\
-		OS & ocall & absolute & 1ns & 6us & low & untrusted & Panoply~\cite{shinde_panoply:_2017} \\
+		OS Kernel & ocall & absolute & 1ns & 6us & low & untrusted & Panoply~\cite{shinde_panoply:_2017} \\
 		Hardware Clock & \textit{smcall} & absolute & 1ns & 69us & low & trusted & Aurora-OpenSSL~\ref{openssl} \\
@@
 		\toprule
-		Payload Size(KB) & Linux(s) & Aurora(s) & Speedup(\%) \\
+		\textbf{Payload Size(KB)} & \textbf{Linux(s)} & \textbf{Aurora(s)} & \textbf{Speedup(\%)} \\
 		\midrule
@@
 		\toprule
-		\multirow{2}{*}{Payload Size(MB)} &  Linux & Aurora & Slowdown \\ 
-		& (MB/s) & (MB/s) & (\%) \\
+		\multirow{2}{*}{\textbf{Payload Size(MB)}} & \textbf{Linux} & \textbf{Aurora} & \textbf{Slowdown} \\ 
+		& \textbf{(MB/s)} & \textbf{(MB/s)} & \textbf{(\%)} \\
 		\midrule
@@
 Tlibaurora detected the attacks successfully and indicated a failure.
-For instance, gettimeofday() returns -1 and sets the global variable \textit{errno} appropriately.
+For instance, \textsf{gettimeofday()} returns -1 and sets the global variable \textit{errno} appropriately.
 Existing C library specification does not have a flag indicating time attacks, the enclave logic may keep requesting until obtaining a valid time value.
@@
 \textbf{Trusted Input Paths.}
-On the desktop side, TrustLogin~\cite{zhang_trustlogin:_2015} uses SMM to protect a user's password.
-In secure mode, it caches the keyboard input inside the SMRAM; when the user releases an \textsf{Enter} key, TrustLogin places the password inside corresponding packets in the NIC buffer.
-By contrast, \textsc{Aurora} does not need to intercept OS networking services at all, therefore decreasing its overall impact surface.
+On the desktop side, TrustLogin~\cite{zhang_trustlogin:_2015} uses SMM to protect user passwords.
+It caches the password inside the SMRAM; when the user releases the \textsf{Enter} key, TrustLogin places the password inside the packets of the NIC buffer.
+In contrast, \textsc{Aurora} does not need to intercept OS networking services, thus decreasing overall impact surfaces.
 Fidelius \cite{DBLP:journals/corr/abs-1809-04774} leverages a Raspberry Pi to implement a secure channel between the keyboard and the hardware enclave.
@@
 As Intel SGX is also available on personal laptops and mini PCs (i.e., NUCs), we take advantage of SGX to protect personal password when the user logs in on the client side, which differs from their scenarios.
-On the mobile side, TrustUI~\cite{DBLP:conf/apsys/LiMHXZCL14} exploits ARM TrustZone to build a trusted path between a user and a service provider, since ARM TrustZone can isolate physical memory and peripheral interrupts.
+On the mobile side, TrustUI~\cite{DBLP:conf/apsys/LiMHXZCL14} exploits ARM TrustZone to build a trusted path between a user and a service provider, because ARM TrustZone can isolate physical memory and peripheral interrupts.
 In design, SMVisor is similar to the trusted OS inside TrustZone's secure world.
@@
 Déjà Vu's goal is to detect interrupt-based attacks, while \textsc{Aurora} can provide a general time service for enclaves.
-Compared to our previous work \cite{DBLP:conf/eurosys/LiangL18}, which provides a trusted clock to enclaves, this paper proposes a unified framework for different I/O devices, provides more trusted I/O paths, and presents more evaluation on real-world applications.
-ROTE~\cite{DBLP:conf/uss/MateticAKDSGJC17} proposes a protocol for distributed enclaves to provide a monotonic counter, which has high latency than \textsc{Aurora}'s trusted clock service.
+Compared to our prior work \cite{DBLP:conf/eurosys/LiangL18}, which provides a trusted clock to enclaves, \textsc{Aurora} proposes a unified framework for different I/O devices and presents more evaluation on real-world applications.
+For distributed enclaves, ROTE~\cite{DBLP:conf/uss/MateticAKDSGJC17} proposes a protocol to provide a monotonic counter, which has high latency than \textsc{Aurora}'s trusted clock service.
 
@@
 AuditedIO \cite{DBLP:conf/apsys/BalakrishnanCBS17} leverages SGX and a kernel module to implement verifiable data storage for disk I/O operations.
-However, it requires programmable SSD devices and modifies their firmware.
-By contrast, \textsc{Aurora} is a generic framework which can be used to support any storage devices.
+It requires a programmable SSD device and modifies the firmware.
+By contrast, \textsc{Aurora} aims for a trusted-path framework which can be used to support general storage devices.
 % and it protects SMM supervisor inside SMRAM and use mutual authentication to ensure its authenticity.
@@
 The proxy device uses LED display for user verification.
-It plays the role of  \textsc{Aurora}'s SMVisor while \textsc{Aurora} needn't introduce any dedicated hardware.
+It plays the role of  \textsc{Aurora}'s SMVisor while \textsc{Aurora} does not need to introduce dedicated hardware.
 % while meeting the same or better protection requirements.
-BASTION-SGX~\cite{DBLP:conf/isca/PetersLVPK18} modifies the Bluetooth firmware to establish trusted  paths between Bluetooth  devices and enclave programs on SGX-enabled platforms.
+BASTION-SGX~\cite{DBLP:conf/isca/PetersLVPK18} modifies the Bluetooth firmware and establishes trusted paths between Bluetooth  devices and enclave programs.
 It has similar threat model with \textsc{Aurora} and rules the privileged software (OS, drivers, etc.) out of the TCB.
 %However, it requires enclave programs to take charge of handling the HID input, which is a burden for developers.
-By contrast, \textsc{Aurora} is a generic trusted I/O architecture and extensible to support new peripheral devices.
 % and outstands BASTION-SGX by its high extensibility.
@@
 SGX-FS \cite{DBLP:conf/cloudcom/BurihabwaFMS18} hardened a user-level filesystem in an enclave, which is more generic than \textsc{Aurora}.
-Similarly, Pesos~\cite{DBLP:conf/eurosys/KrahnTVKBF18} builds a trusted path between enclaves and a storage device and supports policy-based object protection.
-However, Pesos requires a programmable storage device named Kinetic Open Storage as the device end, while \textsc{Aurora} aims for general storage devices.
+Similarly, Pesos~\cite{DBLP:conf/eurosys/KrahnTVKBF18} builds a trusted path between enclaves and cloud-based storage, and supports policy-based object protection.
+Still, Pesos requires a programmable storage HDD named Kinetic Open Storage, while \textsc{Aurora} does not.
 
@@
 \section*{Acknowledgement}
+
 The authors would like to thank Kai Huang from Intel and Shweta Shinde from NUS for their generous help and constructive comments.

### 2019-07-03 article.tex
new title; body polish; new figures in pptx
review related work

@@
 % Article title
-\title{Aurora: Establishing Trusted I/O Paths\\ on SGX-Based Client Systems}
+\title{ Establishing Trusted I/O Paths for Client \\ Shielded Execution Systems with Aurora }
 
@@
 	~Lin Jiang,~Zhuosi Xie,~Tianqi Yang,~Yixiu Chen\\
-	TSIS Lab, BUPT
+	Trusted Software and Intelligent System Lab\\
+	Beijing University of Posts and Telecommunications
   %, Tianqi Yang, Mingyue Li, Yudong Wang % <-this % stops a space

### 2019-07-03 sections/main.tex
review related work

@@
 \textsc{Aurora}'s trusted components (i.e., SMVisor, ashmd, Tlibaurora, Cryptography) have 3393 lines of C code, and untrusted component (i.e., Ulibaurora) has 273 lines of C code.
-Compared to Wimpy \cite{zhou_dancing_2014} which has 16K lines of code, it is smaller and simpler enough to facilitate formal verification.
+Compared to Wimpy kernel \cite{zhou_dancing_2014} which has 16K lines of code, it is smaller and simpler enough to facilitate formal verification.
 Both SMRAM and EPC RAM are scarce memory resource.
@@
 To avoid exploitable vulnerabilities, we use well known static analysis tool Clang Static Analyzer\footnote{http://clang-analyzer.llvm.org/index.html} over \textsc{Aurora}'s code base and fix all bugs we found.
-Besides, as \textsc{Aurora} is quite small and its complexity is obviously lower than that of the formally verified seL4 microkernel [36],  we believe it is reasonable to put \textsc{Aurora} within the reach of formal verification.
+Besides, as \textsc{Aurora} is quite small and its complexity is obviously lower than that of the formally verified microkernel~\cite{DBLP:conf/sosp/KleinEHACDEEKNSTW09}, we believe it is reasonable to put \textsc{Aurora} within the reach of formal verification.
 
@@
 Cloud Terminal~\cite{DBLP:conf/usenix/MartignoniPZHMSPPSS12} is a micro-hypervisor-based method that provides terminals secure access to sensitive applications from an untrusted OS.
-SGX-FS \cite{DBLP:conf/cloudcom/BurihabwaFMS18} hardened a user-level filesystem in an enclave, which is more generic than \textsc{Aurora}.
-Similarly, Pesos~\cite{DBLP:conf/eurosys/KrahnTVKBF18} builds a trusted path between enclaves and cloud-based storage, and supports policy-based object protection.
+Pesos~\cite{DBLP:conf/eurosys/KrahnTVKBF18} builds a trusted path between enclaves and cloud-based storage, and supports policy-based object protection.
 Still, Pesos requires a programmable storage HDD named Kinetic Open Storage, while \textsc{Aurora} does not.
+%SGX-FS \cite{DBLP:conf/cloudcom/BurihabwaFMS18} hardened a user-level filesystem in an enclave, which is more generic than \textsc{Aurora}.
 

### 2019-07-03 sections/main.tex
sqlite tpc-h benchmark ; grammar checks

@@
 However, as  SMM-based protection has performance implications~\cite{DBLP:conf/iiswc/DelgadoK13}, we recommend that users can use Intel PAVP (assisted by Intel ME) and SGX~\cite{DBLP:conf/isca/HoekstraLPPC13} for real-time scenarios such as an online-chatting conference.
+
+\section{Evaluation}\label{performance}
+
+In this section, we evaluate the performance of \textsc{Aurora} framework and the trusted I/O paths.
+Our experiments are carried out on  an Intel Core i7-7700HQ 2.8GHz CPU with 16GB of memory, running Ubuntu 16.04 LTS and SGX SDK 2.4 and SGX driver 1.9.
+
+\subsection{Framework Overhead}
+%% 我们使用pi计算做评估，不同触发周期和抢占时间
+We select  pi\_css5\footnote{http://myownlittleworld.com/miscellaneous/computers/piprogram.html} program, which has no interaction with the external system, to measure the performance of \textsc{Aurora} with as little noise as possible.
+We ran the program till achieving 4,000,000 digits of precision, and used two durations (70us and 150us) to emulate different real-world environments.
+
+%% 一个线程触发，一个线程计时
+%% 太高的请求我们认为不合理；OS有权拒绝SMI请求，以此降低性能影响
+Specifically, we ran two threads: one thread (T1) running Pi number calculation, the other thread (T2) requesting the ashmd module to trigger an SMI in a given interval.
+Firstly, we ran T1 without the interference of T2 and took the time cost as baseline.
+Then we started T2 to see the slowdown of T1.
+From \autoref{table:pi}, we observe that when the interval decreases, the overhead increases.
+The worst case of overhead is around 21\%, where \textit{smcalls} are requested too frequently.
+Such situation is rare in real world applications because an enclave has to execute its own logic.
+We observe that intensive requests may impact the time-sensitive tasks on the same system.
+Since \textit{smcalls} are forwarded by ashmd module, it can use a threshold to block a malicious enclave from abusing.
+In our current setting, we allow an enclave to request up 10,000 times per second, which introduces about 11\% overhead to the system.
+
+\begin{table}[t]
+	\centering
+	\caption{Measuring \textsc{Aurora}'s overhead by calculating Pi.}
+	\label{table:pi}
+	\begin{tabular}{rrrrr}
+		\toprule
+		\multirow{2}{*}{\textbf{Interval}} & \multicolumn{2}{c}{\textbf{Time cost (s)}} & \multicolumn{2}{c}{\textbf{Overhead ratio}} \\\cmidrule{2-3}	 \cmidrule{4-5}
+		& 70us & 150us & 70us & 150us \\
+		\midrule
+		Baseline & 8.545 & 8.635 & 0 & 0\\
+		1000ms & 9.045 & 9.025 & 5.85\% & 4.52\%\\
+		100ms & 9.605 & 9.590 & 12.40\% & 11.06\%\\
+		10ms & 10.180 & 10.455 & 18.90\% & 21.08\%\\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\subsection{Trusted Clock Benchmark}\label{time_bench}
+%It is important to quantify how much time is required to attain a trusted clock service since the potential service latency impacts the freshness of message and indicates the response speed. 
+For this experiment, we measured the complete trusted clock procedure for 10000 time and used the average value.
+Table \ref{table:breaktime} shows the time cost for each step in a trusted clock path, as explained in \autoref{workflow}.
+We can see that the clock service takes most of time.
+This is because 1) the RTC driver has to read clock value twice to check if the clock is updating its time data; 2) The RTC involves several \textsf{INS} instructions to read each field of a calendar time, and costs 14us to obtain a complete wall-clock time in one request; 3) The other 4 timers cost roughly 10us in sum.
+The total  time cost (84us) satisfies the requirement of real-world trusted timestamps.
+\begin{table}[t]
+	\centering
+	\caption{ Breakdown of the trusted clock service}
+	\small
+	\label{table:breaktime}
+	\begin{tabular}{lr}
+		\toprule
+		\textbf{Action Step} & \textbf{Time Cost(us)} \\
+		\midrule
+		EPC encryption & 2\\
+		Copy to DRAM & 2\\
+		Switch to SMM & 13\\
+		Copy to SMRAM & 0\\
+		SMM decryption & 3\\
+		Clock Service & 44\\
+		SMM encryption & 3\\
+		Copy to DRAM & 0\\
+		Return and enter SGX & 12\\
+		Copy to EPC & 3\\
+		EPC decryption & 2\\
+		\bottomrule
+	\end{tabular}
+\end{table}
+\begin{table*}[t]
+	\centering
+	\caption{Comparison of existing clock services that can be used for SGX enclaves.
+Clock services include network time protocol (NTP), precision time protocol (PTP), and the platform software (PSW) supported by Intel management engine (ME)}
+	\label{table:timeservice}
+	\small
+	\begin{tabular}{llllrccr}%{ |c|c|c|c|c|c|c|c| }
+		\toprule
+		\textbf{Clock Provider} & \textbf{Approach} & \textbf{Type} & \textbf{Resolution} & \textbf{Request Cost} & \textbf{Latency} & \textbf{Security} & \textbf{Use Cases} \\
+		\midrule
+		Remote Clock & NTP/PTP & absolute & 1s & $>$100ms & high & trusted & Town Crier~\cite{DBLP:conf/ccs/ZhangCCJS16} \\
+		Intel ME & PSW & relative & 1s & 10.3ms & medium & trusted & SGX-Tor~\cite{DBLP:conf/nsdi/KimHHKH17} \\
+		OS Kernel & ocall & absolute & 1ns & 6us & low & untrusted & Panoply~\cite{shinde_panoply:_2017} \\
+		Hardware Clock & \textit{smcall} & absolute & 1ns & 69us & low & trusted & Aurora-OpenSSL~\ref{openssl} \\
+		\bottomrule
+	\end{tabular}
+\end{table*}
+
+For comparison, we measured the performance of other clock providers.
+The results are shown in \autoref{table:timeservice}.
+Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks such as the timing attacks.
+Among existing approaches, \textsc{Aurora} outperforms remote clock (the 2nd row) and Intel's reference clock (the 3rd row) by introducing very low latency, while achieving the same resolution (nanosecond-level) as OS services (the 4th row).
+%Note that any approach can be arbitrarily delayed in that the untrusted OS is in charge of the enclave thread scheduling. We treat intentionally time delay as a form of Denial-of-Service attack.
+
+% 测试结果说明Aurora方法下的串口响应速度更快，和Linux原生方法频繁的上下文代价有关
+\subsection{Serial Port Output Benchmark}
+
+\begin{table}[h]
+	\centering
+	\caption{Serial-port benchmark comparison between Linux and \textsc{Aurora}.}
+	\label{table:serial}
+	\small
+	\begin{tabular}{lrrr}
+		\toprule
+		\textbf{Payload Size(KB)} & \textbf{Linux(s)} & \textbf{Aurora(s)} & \textbf{Speedup(\%)} \\
+		\midrule
+		4 & 0.03 & 0.03 & 0.0 \\
+		64 & 0.32 & 0.24 & 25.0 \\
+		256 & 1.08 & 0.87 & 19.4 \\
+		1024 & 3.95 & 3.43 & 13.2 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+It is rather difficult to measure the overall time during which a printer accepts and finishes a print job, because we have to re-flash the printer firmware to hook its time function.
+Therefore, we redirected the serial port to a local file.
+To compare the serial output performance between native Linux and \textsc{Aurora}, we measured the time cost of writing the test data of different sizes to the serial-port address in Linux and in \textsc{Aurora}, respectively.
+\autoref{table:serial} shows the experimental results.
+\textsc{Aurora} performs better than native Linux because \textsc{Aurora} uses batch mechanism (\autoref{batch}) to reduce the frequent mode transitions while Linux has more user/kernel mode transitions when writing large data to serial port.
+Note that, for the larger outputted data, the speedup decreases due to cryptographic computations in \textsc{Aurora}.
+
+\subsection{Trusted USB Storage Benchmark}
+
+\begin{table}[h]	
+	\centering
+	\caption{Storage throughput comparison between Linux and \textsc{Aurora}.}
+	\label{table:dd}
+	\small
+	\begin{tabular}{lllr}
+		\toprule
+		\multirow{2}{*}{\textbf{Payload Size(MB)}} & \textbf{Linux} & \textbf{Aurora} & \textbf{Slowdown} \\ 
+		& \textbf{(MB/s)} & \textbf{(MB/s)} & \textbf{(\%)} \\
+		\midrule
+		4 & 32.9 & 31.8 & 3.3 \\
+		64 & 40.9 & 39.2 & 4.2 \\
+		256 & 42.7 & 40.4 & 5.3 \\
+		1024 & 53.2 & 47.5 & 10.7 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+To compare the overhead introduced when applying \textsc{Aurora}'s trusted I/O path on USB storage devices, we used \emph{dd} program with options \textsf{fsync} and \textsf{direct} to write variable sizes of contents to a USB mass storage device on native Linux system as the baseline.
+To avoid the side-effect of any buffer mechanism, we use Linux raw device to mount and initialize the USB device.
+% to bypass any file system interference.
+We then measure the overheads of using Aurora's SMVisor for MAC verification added to each block request in the request and response path.
+We did not use any encryption in this experiment.
+The throughput results are shown in \autoref{table:dd} where the size of each block is set to 4KB.
+\textsc{Aurora} achieves approximately 90\% of the baseline throughput when writing 1GB to device.
+The major overheads are contributed by SMM/Protected mode transitions and cryptographic computations on each block.
+
+\subsection{Security Effectiveness}\label{security}
+In this section, we evaluate \textsc{Aurora}'s reliability with several security tests.
+
+\textbf{Keylogging Attack.}
+To evaluate the effectiveness of \textsc{Aurora}'s trusted input path, we deployed multiple spyware to get a user's inputs under trusted input mode, including a stealthy root keylogger\footnote{https://github.com/vim2meta/keylogger}, a rootless X11-based keylogger ixkeylog\footnote{https://github.com/dorneanu/ixkeylog},
+%and xkbcat\footnote{https://github.com/anko/xkbcat}, 
+a kernel-level rootkit  keylogger\footnote{https://github.com/arunpn123/keylogger}, 
+%and Linux-Keylogger\footnote{https://github.com/nijindal/Linux-Keylogger} 
+and a remote keylogger\footnote{https://github.com/EinBaum/Totally-Not-A-Virus}. None of them can obtain the user's inputs.
+
+\textbf{Output Corruption Attack.}
+We leveraged a DMA-based NIC device to launch output corruption attack when using Aurora's trusted serial printer service.
+Since  SMRAM and EPC RAM are strongly isolated by architectural protections, only meaningless content (0xFF) is obtained.
+Therefore no secrets are leaked.
+We then conducted another DMA attack to corrupt SMM drivers outside of SMRAM.
+SMVisor detected its integrity tampered  and rejected subsequent requests, then notified the enclave application.
+Moreover, we conducted another DMA attack to corrupt the content of shared memory of the secure session.
+Both SMVisor and Tlibaurora can verify the broken MAC and restart a new session.
+
+\textbf{Time Deception Attack.}
+To evaluate \textsc{Aurora}’s trusted clock, we intentionally modified the RTC when an enclave issued a request for trusted clock.
+Tlibaurora detected the attacks successfully and indicated a failure.
+For instance, \textsf{gettimeofday()} returns -1 and sets the global variable \textit{errno} appropriately.
+Existing C library specification does not have a flag indicating time attacks, the enclave logic may keep requesting until obtaining a valid time value.
+We support failure handling in Tlibaurora to help enclaves deal with such situations.
+
+\textbf{Storage Deception Attack.}
+We modified the kernel driver of SCSI device and randomly dropped several disk I/O requests intentionally.
+SMVisor detected such accidental conditions and notified the Tlibaurora of corresponding enclave.
+In our current setting, the Tlibaurora will automatically try issuing the lost I/O requests three times so as to avoid storage failure.
+In our experiments, the enclave finally received the attack warning from the Tlibaurora and logged these events for further forensic analysis.
 
@@
 
-We evaluated the enhanced SQLite performance by inserting a randomly generated record to a big table for 1000 times.
-To make a fair comparison, we set the synchronize flag to "FULL" to avoid the uncertainty of I/O caching.
-When SGX-SQLite invokes Tlibaurora file APIs, it opens the USB storage device as a raw block file in direct I/O mode and reads/writes data using 4KB block size.
-In our experiment, the native insertion transactions for 1000 times cost 17.3 seconds while the ones with \textsc{Aurora}'s trusted path cost 20.5 seconds.
+\begin{table}	
+	\centering
+	\caption{TPC-H benchmark comparison between native SGX-SQLite and \textsc{Aurora}-SQLite.}
+	\label{table:tpch}
+	\small
+	\begin{tabular}{lrrr}
+		\toprule
+		\textbf{Query} & \textbf{SGX-SQLite(s)} & \textbf{Aurora-SQLite(s)} & \textbf{Slowdown(\%)} \\
+		\midrule
+		02 & 4.68 & 5.10 & 8.97 \\
+		11 & 1.29 & 1.42 & 10.08 \\
+		16 & 1.08 & 1.10 & 5.30 \\
+		17 & 91.26 & 93.30 & 2.23 \\
+		18 & 24.98 & 25.91 & 3.72 \\
+		19 & 93.15 & 98.25 & 5.47 \\
+		21 & 39.68 & 43.16 & 9.04 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+We evaluated the enhanced SQLite performance by running standardized TPC-H benchmark\footnote{http://www.tpc.org/tpch/} over a large database. % (around 1.3GB).
+We modified the benchmark queries in order to make them possible to be executed in SQLite. Unfortunately, not all queries can be executed.
+To directly measure the overhead introduced by \textsc{Aurora}'s infrastructure, we set the synchronize flag to \textsf{FULL} to avoid the uncertainty of I/O caching.
+When SQLite invokes Tlibaurora file APIs, it opens the USB storage device in direct I/O mode and reads/writes data using 4KB block size.
+%In our experiment, the native insertion transactions for 1000 times cost 17.3 seconds while the ones with \textsc{Aurora}'s trusted path cost 20.5 seconds.
 About 18\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.
-%Since the USB DMA transfer is designed as an asynchronous mechanism, the delay is not that explicit.
-%We plan to combine with existing in-enclave filesystem support~\cite{OBLIVIATE2018} for \textsc{Aurora}'s trusted storage path.
+
+\autoref{table:tpch} shows the successfully executed queries and their results of native SGX-SQLite and \textsc{Aurora}-SGLite respectively.
+In our experiments, no more than 10.08\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.
+Note that these are the worst-case overheads (because we have set \textsf{PRAGMA synchronous} to \textsf{FULL}) as almost all databases have their own optimized caching mechanisms for better performance.
 
@@
 %After the user clicks the "OK" button, her username, password and other private information are then encrypted inside the enclave, and later restored into the database in encrypted format.
-
-\section{Evaluation}\label{performance}
-
-In this section, we evaluate the performance of \textsc{Aurora} framework and the trusted I/O paths.
-Our experiments are carried out on  an Intel Core i7-7700HQ 2.8GHz CPU with 16GB of memory, running Ubuntu 16.04 LTS and SGX SDK 2.4 and SGX driver 1.9.
-
-\subsection{Framework Overhead}
-%% 我们使用pi计算做评估，不同触发周期和抢占时间
-We select  pi\_css5\footnote{http://myownlittleworld.com/miscellaneous/computers/piprogram.html} program, which has no interaction with the external system, to measure the performance of \textsc{Aurora} with as little noise as possible.
-We ran the program till achieving 4,000,000 digits of precision, and used two durations (70us and 150us) to emulate different real-world environments.
-
-%% 一个线程触发，一个线程计时
-%% 太高的请求我们认为不合理；OS有权拒绝SMI请求，以此降低性能影响
-Specifically, we ran two threads: one thread (T1) running Pi number calculation, the other thread (T2) requesting the ashmd module to trigger an SMI in a given interval.
-Firstly, we ran T1 without the interference of T2 and took the time cost as baseline.
-Then we started T2 to see the slowdown of T1.
-From \autoref{table:pi}, we observe that when the interval decreases, the overhead increases.
-The worst case of overhead is around 21\%, where \textit{smcalls} are requested too frequently.
-Such situation is rare in real world applications because an enclave has to execute its own logic.
-We observe that intensive requests may impact the time-sensitive tasks on the same system.
-Since \textit{smcalls} are forwarded by ashmd module, it can use a threshold to block a malicious enclave from abusing.
-In our current setting, we allow an enclave to request up 10,000 times per second, which introduces about 11\% overhead to the system.
-
-\begin{table}[t]
-	\centering
-	\caption{Measuring \textsc{Aurora}'s overhead by calculating Pi.}
-	\label{table:pi}
-	\begin{tabular}{rrrrr}
-		\toprule
-		\multirow{2}{*}{\textbf{Interval}} & \multicolumn{2}{c}{\textbf{Time cost (s)}} & \multicolumn{2}{c}{\textbf{Overhead ratio}} \\\cmidrule{2-3}	 \cmidrule{4-5}
-		& 70us & 150us & 70us & 150us \\
-		\midrule
-		Baseline & 8.545 & 8.635 & 0 & 0\\
-		1000ms & 9.045 & 9.025 & 5.85\% & 4.52\%\\
-		100ms & 9.605 & 9.590 & 12.40\% & 11.06\%\\
-		10ms & 10.180 & 10.455 & 18.90\% & 21.08\%\\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\subsection{Trusted Clock Benchmark}\label{time_bench}
-%It is important to quantify how much time is required to attain a trusted clock service since the potential service latency impacts the freshness of message and indicates the response speed. 
-For this experiment, we measured the complete trusted clock procedure for 10000 time and used the average value.
-Table \ref{table:breaktime} shows the time cost for each step in a trusted clock path, as explained in \autoref{workflow}.
-We can see that the clock service takes most of time.
-This is because 1) the RTC driver has to read clock value twice to check if the clock is updating its time data; 2) The RTC involves several \textsf{INS} instructions to read each field of a calendar time, and costs 14us to obtain a complete wall-clock time in one request; 3) The other 4 timers cost roughly 10us in sum.
-The total  time cost (84us) satisfies the requirement of real-world trusted timestamps.
-\begin{table}[t]
-	\centering
-	\caption{ Breakdown of the trusted clock service}
-	\small
-	\label{table:breaktime}
-	\begin{tabular}{lr}
-		\toprule
-		\textbf{Action Step} & \textbf{Time Cost(us)} \\
-		\midrule
-		EPC encryption & 2\\
-		Copy to DRAM & 2\\
-		Switch to SMM & 13\\
-		Copy to SMRAM & 0\\
-		SMM decryption & 3\\
-		Clock Service & 44\\
-		SMM encryption & 3\\
-		Copy to DRAM & 0\\
-		Return and enter SGX & 12\\
-		Copy to EPC & 3\\
-		EPC decryption & 2\\
-		\bottomrule
-	\end{tabular}
-\end{table}
-\begin{table*}[t]
-	\centering
-	\caption{Comparison of existing clock services that can be used for SGX enclaves.
-Clock services include network time protocol (NTP), precision time protocol (PTP), and the platform software (PSW) supported by Intel management engine (ME)}
-	\label{table:timeservice}
-	\small
-	\begin{tabular}{llllrccr}%{ |c|c|c|c|c|c|c|c| }
-		\toprule
-		\textbf{Clock Provider} & \textbf{Approach} & \textbf{Type} & \textbf{Resolution} & \textbf{Request Cost} & \textbf{Latency} & \textbf{Security} & \textbf{Use Cases} \\
-		\midrule
-		Remote Clock & NTP/PTP & absolute & 1s & $>$100ms & high & trusted & Town Crier~\cite{DBLP:conf/ccs/ZhangCCJS16} \\
-		Intel ME & PSW & relative & 1s & 10.3ms & medium & trusted & SGX-Tor~\cite{DBLP:conf/nsdi/KimHHKH17} \\
-		OS Kernel & ocall & absolute & 1ns & 6us & low & untrusted & Panoply~\cite{shinde_panoply:_2017} \\
-		Hardware Clock & \textit{smcall} & absolute & 1ns & 69us & low & trusted & Aurora-OpenSSL~\ref{openssl} \\
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-For comparison, we measured the performance of other clock providers.
-The results are shown in \autoref{table:timeservice}.
-Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks like timing attacks.
-Among existing approaches, \textsc{Aurora} outperforms remote clock (the 2nd row) and Intel's reference clock (the 3rd row) by introducing very low latency, while achieving the same resolution (nanosecond-level) as OS services (the 4th row).
-%Note that any approach can be arbitrarily delayed in that the untrusted OS is in charge of the enclave thread scheduling. We treat intentionally time delay as a form of Denial-of-Service attack.
-
-% 测试结果说明Aurora方法下的串口响应速度更快，和Linux原生方法频繁的上下文代价有关
-\subsection{Serial Port Output Benchmark}
-
-\begin{table}[h]
-	\centering
-	\caption{Serial-port benchmark comparison between Linux and \textsc{Aurora}.}
-	\label{table:serial}
-	\small
-	\begin{tabular}{lrrr}
-		\toprule
-		\textbf{Payload Size(KB)} & \textbf{Linux(s)} & \textbf{Aurora(s)} & \textbf{Speedup(\%)} \\
-		\midrule
-		4 & 0.03 & 0.03 & 0.0 \\
-		64 & 0.32 & 0.24 & 25.0 \\
-		256 & 1.08 & 0.87 & 19.4 \\
-		1024 & 3.95 & 3.43 & 13.2 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-It is rather difficult to measure the overall time during which a printer accepts and finishes a print job, because we have to re-flash the printer firmware to hook its time function.
-Therefore, we redirected the serial port to a local file.
-To compare the serial output performance between native Linux and \textsc{Aurora}, we measured the time cost of writing the test data of different sizes to the serial-port address in Linux and in \textsc{Aurora}, respectively.
-\autoref{table:serial} shows the experimental results.
-\textsc{Aurora} performs better than native Linux because \textsc{Aurora} uses batch mechanism (\autoref{batch}) to reduce the frequent mode transitions while Linux has more user/kernel mode transitions when writing large data to serial port.
-Note that, for the larger outputted data, the speedup decreases due to cryptographic computations in \textsc{Aurora}.
-
-\subsection{Trusted USB Storage Benchmark}
-
-\begin{table}[h]	
-	\centering
-	\caption{Storage throughput comparison between Linux and \textsc{Aurora}.}
-	\label{table:dd}
-	\small
-	\begin{tabular}{lllr}
-		\toprule
-		\multirow{2}{*}{\textbf{Payload Size(MB)}} & \textbf{Linux} & \textbf{Aurora} & \textbf{Slowdown} \\ 
-		& \textbf{(MB/s)} & \textbf{(MB/s)} & \textbf{(\%)} \\
-		\midrule
-		4 & 32.9 & 31.8 & 3.3 \\
-		64 & 40.9 & 39.2 & 4.2 \\
-		256 & 42.7 & 40.4 & 5.3 \\
-		1024 & 53.2 & 47.5 & 10.7 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-To compare the overhead introduced when applying \textsc{Aurora}'s trusted I/O path on USB storage devices, we used \emph{dd} program with options "fsync" and "direct" to write variable sizes of contents to a USB mass storage device on native Linux system as the baseline.
-To avoid the side-effect of any buffer mechanism, we use Linux raw device to mount and initialize the USB device.
-% to bypass any file system interference.
-We then measure the overheads of using Aurora's SMVisor for MAC verification added to each block request in the request and response path.
-We did not use any encryption in this experiment.
-The throughput results are shown in \autoref{table:dd} where the size of each block is set to 4KB.
-\textsc{Aurora} achieves approximately 90\% of the baseline throughput when writing 1GB to device.
-The major overheads are contributed by SMM/Protected mode transitions and cryptographic computations on each block.
-
-\subsection{Security Effectiveness}\label{security}
-In this section, we evaluate \textsc{Aurora}'s reliability with several security tests.
-
-\textbf{Keylogging Attack.}
-To evaluate the effectiveness of \textsc{Aurora}'s trusted input path, we deployed multiple spyware to get a user's inputs under trusted input mode, including a stealthy root keylogger\footnote{https://github.com/vim2meta/keylogger}, a rootless X11-based keylogger ixkeylog\footnote{https://github.com/dorneanu/ixkeylog},
-%and xkbcat\footnote{https://github.com/anko/xkbcat}, 
-a kernel-level rootkit  keylogger\footnote{https://github.com/arunpn123/keylogger}, 
-%and Linux-Keylogger\footnote{https://github.com/nijindal/Linux-Keylogger} 
-and a remote keylogger\footnote{https://github.com/EinBaum/Totally-Not-A-Virus}. None of them can obtain the user's inputs.
-
-\textbf{Output Corruption Attack.}
-We leveraged a DMA-based NIC device to launch output corruption attack when using Aurora's trusted serial printer service.
-Since  SMRAM and EPC RAM are strongly isolated by architectural protections, only meaningless content (0xFF) is obtained.
-Therefore no secrets are leaked.
-We then conducted another DMA attack to corrupt SMM drivers outside of SMRAM.
-SMVisor detected its integrity tampered  and rejected subsequent requests, then notified the enclave application.
-Moreover, we conducted another DMA attack to corrupt the content of shared memory of the secure session.
-Both SMVisor and Tlibaurora can verify the broken MAC and restart a new session.
-
-\textbf{Time Deception Attack.}
-To evaluate \textsc{Aurora}’s trusted clock, we intentionally modified the RTC when an enclave issued a request for trusted clock.
-Tlibaurora detected the attacks successfully and indicated a failure.
-For instance, \textsf{gettimeofday()} returns -1 and sets the global variable \textit{errno} appropriately.
-Existing C library specification does not have a flag indicating time attacks, the enclave logic may keep requesting until obtaining a valid time value.
-We support failure handling in Tlibaurora to help enclaves deal with such situations.
-
-\textbf{Storage Deception Attack.}
-We modified the kernel driver of SCSI device and randomly dropped several disk I/O requests intentionally.
-SMVisor detected such accidental conditions and notified the Tlibaurora of corresponding enclave.
-In our current setting, the Tlibaurora will automatically try issuing the lost I/O requests three times so as to avoid storage failure.
-In our experiments, the enclave finally received the attack warning from the Tlibaurora and logged these events for further forensic analysis.
 

### 2019-07-03 sections/main.tex
typo fixes

@@
 Therefore, the SMI handler is safe from corruption after booting.
-Moreover, the SMI handler can access all CPU registers, I/O devices, and physical memory (except for SGX EPCs), and thus we expand the SMI Handler to design \textsc{Aurora}'s SMM Supervisor in \autoref{arch}.
+Moreover, the SMI handler can access all CPU registers, I/O devices, and physical memory (except for SGX EPCs), and thus we expand the SMI Handler to design \textsc{Aurora}'s SMVisor in \autoref{arch}.
 
@@
 Establishing a trusted path in \textsc{Aurora} consists of the following three steps.
-First, \textsc{Aurora} builds a secure session between SMM Supervisor (SMVisor) and an enclave that performs an I/O request.
+First, \textsc{Aurora} builds a secure session between SMVisor and an enclave that performs an I/O request.
 Second, SMVisor receives the request via the secure session without leaking knowledge to the untrusted system.
@@
 \includegraphics[width=0.3\textwidth]{figures/mutual.pdf}%height=0.2\textheight,
-\caption{Mutual attestation and key agreement between SMM Supervisor and an application enclave.
+\caption{Mutual attestation and key agreement between SMVisor and an application enclave.
 The single line arrows denote the attestation direction, the double line arrow denotes the following key agreement.}
@@
 
-For the case where the hardware clocks are modified in a consistent way, that is, all the timers are altered in the same offset, we propose a novel algorithm to detect such an attack.
+For the case where the hardware clocks are altered in a consistent way, that is, all the timers are altered in the same offset, we propose a novel algorithm to detect such an attack.
 We use a dedicated counting thread \cite{DBLP:conf/dimva/SchwarzWGMM17} guarded inside an enclave occupying a logical thread on the same CPU core.
@@
 This interception adds around 13\% overhead per keystroke.
-Only after SMVisor routes the keyboard interrupt into itself and acknowledges to the client, will the prompt "username@hostname password:"  be displayed on the screen.
+Only after SMVisor routes the keyboard interrupt into itself and acknowledges to the client, will the prompt \textsf{"username@hostname password:"}  be displayed on the screen.
 While the user is typing the passphrase, the client does not display any content on the screen, achieving the same effect as in the native OpenSSH client.
@@
 The user's input is buffered inside SMRAM.
-When the user releases "Enter" key, the password is then encrypted and sent to the secure channel, and SMVisor exits trust input mode.
+When the user releases \textsf{Enter} key, the password is then encrypted and sent to the secure channel, and SMVisor exits trust input mode.
 Aurora-OpenSSH client reclaims the password message and sends it to the server.
@@
 Most of all, both parties require a reliable time source to detect possible timeout.
-For instance, both "ClientHello" and "ServerHello" messages use the system time to compose \textit{random} field, which is used to prevent replay attacks.
+For instance, both \emph{ClientHello} and \emph{ServerHello} messages use the system time to compose \textit{random} field, which is used to prevent replay attacks.
 If the time is emulated by an untrusted source, it may increase the collision probability of \emph{random} and compromise the security of SSL/TLS.
@@
 We evaluated the enhanced SQLite performance by running standardized TPC-H benchmark\footnote{http://www.tpc.org/tpch/} over a large database. % (around 1.3GB).
-We modified the benchmark queries in order to make them possible to be executed in SQLite. Unfortunately, not all queries can be executed.
+We make minor changes to these benchmark queries in order to make them possible to be executed in SQLite. Unfortunately, not all queries can be executed.
 To directly measure the overhead introduced by \textsc{Aurora}'s infrastructure, we set the synchronize flag to \textsf{FULL} to avoid the uncertainty of I/O caching.

### 2019-07-04 article.tex
body review

@@
 \author{Hongliang~Liang,~\IEEEmembership{Member,~IEEE,}
-	Mingyu Li,%~\IEEEmembership{Fellow,~OSA,}
-	~Lin Jiang,~Zhuosi Xie,~Tianqi Yang,~Yixiu Chen\\
+	Mingyu Li,~Yixiu Chen,~Lin Jiang,~Zhuosi Xie,~Tianqi Yang\\
 	Trusted Software and Intelligent System Lab\\
 	Beijing University of Posts and Telecommunications
-  %, Tianqi Yang, Mingyue Li, Yudong Wang % <-this % stops a space
-	\thanks{H. Liang, M. Li, L. Jiang, Z. Xie, T. Yang, Y. Chen 
-  %, T. Yang, M. Li, and Y. Wang 
+	\thanks{H. Liang, M. Li, Y. Chen, L. Jiang, Z. Xie, T. Yang
   are with Beijing University of Posts and Telecommunications, Beijing 100876, China. e-mail: (\{hliang,maxul,jianglin,xiezhuosi,yangtianqi,chenyixiu\}@bupt.edu.cn)
-  %; yangtianqi@bupt.edu.cn; li\_mingyue@bupt.edu.cn; wyd2013@bupt.edu.cn
   }% <-this % stops a space
-	\thanks{This work was supported by the National Natural Science Foundation of China (NSFC) under Grant No. U1713212 and 91418206.}
 }

### 2019-07-04 sections/main.tex
body review

@@
 
-In this paper, we present \textsc{Aurora}, a novel architecture that safeguards I/O paths for SGX enclaves.
+In this paper, we present \textsc{Aurora}, a novel architecture that safeguards I/O paths of SGX enclaves.
 To directly communicate with hardware devices without depending on the untrusted software, \textsc{Aurora} introduces System Management RAM (SMRAM) as a special enclave.
@@
 We call this particular SMI handler \textit{SMVisor}.
-In hardware, SMVisor is safe from any corruptions by other privileged software (including OS, hypervisor/HV).
+In hardware, SMVisor is safe from any corruptions by other privileged software (including OS and hypervisor).
 Therefore, Intel SGX enclaves can safely use I/O devices while remaining \textit{transparent} to the underlying OS.
@@
 
+\begin{figure*}[t]
+	\centering
+	\includegraphics[height=0.18\textheight]{figures/arch.pdf}
+	\caption{\textsc{Aurora}'s architecture. The gray areas denote untrusted parts, and the white ones represent \textsc{Aurora}'s trusted computing base.}
+	\label{fig:architecture}
+\end{figure*}
+
 \section{Background and Problem Definition}
@@
 
-The SMI handler is initialized by UEFI, and  SMRAM can be locked by configuring D\_OPEN and D\_LCK bits in SMRAM control register.
+The SMI handler is initialized by UEFI, and  SMRAM can be locked by configuring \emph{D\_OPEN} and \emph{D\_LCK} bits in SMRAM control register.
 Therefore, the SMI handler is safe from corruption after booting.
@@
 One possible approach is to decompose existing software stack and port them into the trusted applications, which will greatly swell the TCB and attack vectors.
-As an alternative, \textsc{Aurora} leverages a forward-and-verify method and reuses existing software stacks in a \emph{secure} manner.
+As an alternative, \textsc{Aurora} leverages a \emph{distrust but verify} method and reuses existing software stacks in a secure manner.
 
@@
 Our assumptions significantly reduce the TCB on the target host as modern commodity system contains a large system software (UEFI, possibly hypervisor, kernel and other applications) when dealing with I/O devices.
-Even though we do not consider physical attacks on devices, side-channel attacks~\cite{chen2019sgxpectre, ridl}, or denial-of-service attacks, we adopt side-channel free cryptographic algorithms and apply an oblivious packet transferring technique.
-
-\begin{figure*}[t]
-	\centering
-	\includegraphics[height=0.2\textheight]{figures/arch.pdf}
-	\caption{\textsc{Aurora}'s architecture. The gray areas denote untrusted parts, and the white ones represent \textsc{Aurora}'s trusted computing base.}
-	\label{fig:architecture}
-\end{figure*}
+Even though we do not consider physical attacks on devices, side-channel attacks~\cite{chen2019sgxpectre, ridl}, or denial-of-service attacks, we adopt side-channel free cryptographic algorithms and apply an oblivious packet transferring technique (\autoref{enhancement}).
 
@@
 To provide trusted I/O paths, we employ the combination of SGX and SMM, both of which are processor enforced protection features.
-As they are offered at the opposite ends of Intel privilege-level model, we name our framework after \textsc{Aurora}\footnote{Aurora takes place in the polar regions, i.e.
-south and north of the earth.}.
+Because they are offered at the opposite ends of Intel privilege-level model, we name our framework after \textsc{Aurora}\footnote{Aurora takes place in the polar regions, \emph{i.e.,} south and north of the earth.}.
 
@@
 Second, SMVisor receives the request via the secure session without leaking knowledge to the untrusted system.
-Third, SMVisor interacts with the target device on behalf of the enclave, and performs the desired I/O operations to respond to the request.
+Third, SMVisor interacts with the target device on behalf of the enclave, and performs desired I/O operations for the request.
 The procedure is conceptually similar to a \textit{syscall} or \textit{vmcall}.
-We name it an \textit{smcall} for convenience.
+We name this an \textit{smcall} for brevity.
 
@@
 
-To take a bird's eye view, \textsc{Aurora} is composed of three components: SMVisor, libaurora and a secure session established between SMVisor and libaurora, as shown in Figure \ref{fig:architecture}.
+\textsc{Aurora} is composed of three components: SMVisor, libaurora and a secure session established between SMVisor and libaurora, as shown in Figure \ref{fig:architecture}.
 
@@
 It dispatches device interrupts to either kernel or enclaves.
-SMVisor uses an forward-and-verify mechanism to securely invoke SMM drivers outside SMRAM.
+SMVisor securely invokes UEFI drivers outside of SMRAM (\autoref{driver}).
 \item Libaurora consists of two parts.
@@
 %; an ENCLAVEID can be obtained using \textit{EREPORT} instruction
-\item The secure session exchanges encrypted messages between SMVisor and enclaves via a shared memory provided by a kernel module named ashmd.
-\textsc{Aurora} leverages a 5-tuple for each message: \textit{(ENCLID, DEVID, OPTYPE, PAYLOAD, MAC)}.
+\item The secure session exchanges encrypted messages between SMVisor and an enclave via a shared memory provided by a kernel module named ashmd.
+\textsc{Aurora} leverages a 5-tuple: \textit{(ENCLID, DEVID, OPTYPE, PAYLOAD, MAC)} for each message.
 The first two arguments indicate the program endpoint and device endpoint respectively.
-The third stands for the I/O operation type.
-The fourth carries the message data and the last one is the message authentication code used for integrity protection.
+The third stands for the type of I/O operation.
+The fourth carries the message data and the last is the message authentication code used for integrity protection.
 All the arguments are marshaled and encrypted.
@@
 %Only interrupts are forwarded by the OS to SMVisor.
-The data plane of an enclave is protected by advanced encryption schemes accelerated by the processor (e.g.
-AES-GCM with AES-NI support), and the data flows between the enclave and SMVisor are completely invisible to the OS.
+The data plane of an enclave is protected by advanced encryption schemes accelerated by the processor (\emph{i.e.,} AES-GCM with AES-NI support), and the data flows between the enclave and SMVisor are completely invisible to the OS.
 Unlike library OSes, which delegate I/O operations to the untrusted OS, \textsc{Aurora} ships security-sensitive parts of these operations into SMVisor, thus eliminating the reliance on untrusted OS.
@@
 \subsection{Workflow}\label{workflow}
-To help understand the workflow of a trusted path in \textsc{Aurora}, we break down the process of output path and input path respectively into sequential phases, as illustrated in left and right part respectively of \autoref{fig:workflow}.
-
-An output request is triggered by an enclave as a synchronous exception, as depicted as follows:\\
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.46\textwidth]{figures/workflow.pdf} %height=0.25\textheight,
+	\caption{The workflow of a trusted I/O path in \textsc{Aurora}. }%The white areas denote the TCB.
+	\label{fig:workflow}
+\end{figure}
+
+To help understand the workflow of a trusted path in \textsc{Aurora}, we break down the process of the output path and input path respectively into sequential phases, as illustrated in left and right part of \autoref{fig:workflow}.
+
+An output request is triggered by an enclave as an exception, as depicted as follows:\\
 %\par
-~~\textcircled{\footnotesize{1}} The user logic in the enclave issues an output request by invoking  Tlibaurora's APIs;\\
+~~\textcircled{\footnotesize{1}} The user logic in an enclave issues an output request by invoking  Tlibaurora's APIs;\\
 ~~\textcircled{\footnotesize{2}} Tlibaurora marshals and encrypts the request's arguments, and invokes Ulibaurora outside the enclave to relay the request;\\ %sends the request via the secure session, via an OCALL
-~~\textcircled{\footnotesize{3}} Ulibaurora ioctls the ashmd module to trigger an \textit{smcall};\\
+~~\textcircled{\footnotesize{3}} Ulibaurora \emph{ioctls} the ashmd module to trigger an \textit{smcall};\\
 ~~\textcircled{\footnotesize{4}} SMVisor is notified and obtains the encrypted requests from the secure session;\\
-~~\textcircled{\footnotesize{5}} SMVisor decrypts the request and invokes the corresponding  driver;\\
-~~\textcircled{\footnotesize{6}} The driver operates the raw output data in PCI space or MMIO buffer;\\
-~~\textcircled{\footnotesize{7}} The driver returns a result code to SMVisor. Finally, SMVisor  executes \textit{RSM} to return to protected mode. \\
+~~\textcircled{\footnotesize{5}} SMVisor decrypts the request and invokes the driver;\\
+~~\textcircled{\footnotesize{6}} The driver processes output data in PCI space or MMIO buffer;\\
+~~\textcircled{\footnotesize{7}} The driver returns a result code to SMVisor. In the end, SMVisor executes \textit{RSM} to return to protected mode. \\
 
 \par
-An input request from an enclave results in a device interrupt, as depicted as follows:\\
+An input request from an enclave causes a device interrupt, as depicted as follows:\\
 %\par
-~~\textcircled{\footnotesize{1}} The target device triggers an interrupt, and the control is routed to SMVisor which is the interrupt handler;\\
-~~\textcircled{\footnotesize{2}} SMVisor invokes the device driver to handle the input request;\\
+~~\textcircled{\footnotesize{1}} The target device triggers an interrupt, and the control flow is rerouted to SMVisor which has the interrupt handler;\\
+~~\textcircled{\footnotesize{2}} SMVisor invokes the driver to handle the input request;\\
 ~~\textcircled{\footnotesize{3}} The driver gets the raw input data and sends it to SMVisor;\\
@@
 ~~\textcircled{\footnotesize{5}} The system switches back to protected mode and the ashmd module uses a signal to notify Ulibaurora;\\
-~~\textcircled{\footnotesize{6}} Ulibaurora invokes Tlibaurora via an ECALL to receive encrypted data;\\
+~~\textcircled{\footnotesize{6}} Ulibaurora invokes Tlibaurora to receive the encrypted data;\\
 ~~\textcircled{\footnotesize{7}} The enclave decrypts the encrypted data and finally obtains the raw input data. % from the secure session.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{figures/workflow.pdf} %height=0.25\textheight,
-	\caption{The workflow of a trusted I/O path in \textsc{Aurora}. }%The white areas denote the TCB.
-	\label{fig:workflow}
-\end{figure}
 
@@
 To perform I/O operations correctly, a driver should know the exact I/O ports of the target device.
-At the time of system boot, SMVisor collects all device information and records their memory mapped I/O (MMIO) base addresses into a \textsf{PCI BAR Table}, thereafter the matching drivers can manipulate the mapped PCI configuration space according to the table.
+At the time of system boot, SMVisor collects all device information and records their memory mapped I/O (MMIO) base addresses into a \emph{PCI BAR Table}, thereafter the matching drivers can manipulate the mapped PCI configuration space according to the table.
 
@@
 SMVisor verifies the validity of parameters passed to the drivers (e.g.
-a PCI structure pointer should point to one of the entries in the \textsf{PCI BAR Table} within SMRAM) and checks the return values according to the device specifications (e.g.
+a PCI structure pointer should point to one of the entries in the \emph{PCI BAR Table} within SMRAM) and checks the return values according to the device specifications (e.g.
 each driver function has a specific range of error codes) as well as its functional correctness.
@@
 starting address and region range) that the driver tries to access to ensure that it can not write data outside of SMRAM.
-
 Furthermore, a driver may require more memory space during runtime (e.g.
@@
 These drivers lack of effective isolation from the rest of the untrusted systems, therefore we do not use them.
-
 Instead, since existing open-source UEFI firmware, such as Coreboot\footnote{https://www.coreboot.org/} and Project Mu\footnote{https://microsoft.github.io/mu/}, contain various drivers in their Driver eXecution Environment (DXE), and the code of these drivers are significantly scrutinized compared to the proprietary code, we reuse these drivers and forward the device interrupt for them to handle.
@@
 At the booting stage, SMVisor calculates the hash checksum of each driver and stores its integrity signature inside SMRAM.
-When receiving an I/O request, SMVisor verifies the integrity of the corresponding driver to ensure that it is not tampered with.
+When receiving an I/O request, SMVisor verifies the integrity of the corresponding driver to ensure it is not tampered with.
 When executing a driver, SMVisor puts its data, heap, stack segments inside SMRAM, and thus ensures them inaccessible to OS/HV.
@@
 
-\subsection{Secure Session}\label{secure_session}
-
-We design a secure session that protects the message exchange between SMVisor and enclaves.
-We first describe \textsc{Aurora}'s kernel module that provides the shared memory for message exchange, then we state the lifecycle of a secure session and optimization techniques upon it.
-
-\subsubsection{Kernel Module (ashmd)}
+\subsection{Kernel Module (ashmd)}
 %% Enclave可以在内部操作不可信内存区数据，从而避免退出；Iago会导致DoS，不会泄漏数据
@@
 
+\subsection{Secure Session}\label{secure_session}
+
 %% 初始必须双发交换密钥，只要Intel服务器在机器启动时验证SSV，enclave加载时验证enclave，然后利用各自得到信道交换密钥就可以。虽然代价大，但只是初始化慢而已。
-\subsubsection{Secure Session Life-cycle}
+%\subsubsection{Secure Session Life-cycle}
+We design a secure session that protects the message exchange between SMVisor and enclaves. 
 The initial stage of the secure session is to ensure whether both parties are trusted or not.
@@
 \textbf{Mutual Attestation.}
-During a measured boot, Intel boot guard~\cite{ruan_platform_2014}  hashes a computer's firmware and stores its cryptographic hash in the TPM Platform Configuration Register (PCR) \cite{tcg_trusted_2014}.
+During a measured boot, Intel Boot Guard~\cite{ruan_platform_2014} hashes the firmware and stores its cryptographic hash in the TPM Platform Configuration Register (PCR) \cite{tcg_trusted_2014}.
 The final PCR value reflects the whole boot process.
-If the process is modified, the PCR value will be different.
+If the process is tampered with, the PCR value will differ.
 
@@
 When an enclave finishes its requests, its Tlibaurora logic will notify SMVisor to terminate the secure session and release resources.
-When there is no live session, SMVisor will disable its interrupt routing and thereafter make no impact on the system.
-
-\subsubsection{Enhancement and Optimization}
+When there remains no live session, SMVisor will disable its interrupt routing and thereafter make no impact on the system.
+
+\subsection{Enhancement and Optimization}\label{enhancement}
 To provide better security and performance, \textsc{Aurora} introduces \textit{hardware encryption}, \textit{data obliviousness} and \textit{batch mechanism for smcalls}.
@@
 \textbf{Hardware Encryption.}
-Intel extends X86 ISA with AES-NI set and claims to prevent known side-channel attacks.
-We make use of it to address the same concern and use constant-time encryption algorithm to defeat cache timing attacks.
-The hardware-accelerated encryption also decreases the preemption time in SMM mode.
+Intel extends x86 ISA with AES-NI and claims to prevent known side-channel attacks.
+We make use of it to address the same concern and use constant-time algorithm to defeat cache timing attacks.
+This hardware acceleration also decreases the preemption time in SMM.
 
@@
 \textbf{Batched SMCALLs.}\label{batch}
-To reduce the context switches between SMM mode and enclave mode, \textsc{Aurora} supports a batched \textit{smcalls} mechanism using two dedicated, lock-free ring buffers for input and output respectively.
-It is especially useful in the case of highly frequent requests.
-Enclaves can set a desired threshold, so Tlibaurora will coalesce these \textit{smcalls}.
-For asynchronous I/O requests, the mechanism can benefit the enclave with higher throughput.
-%We use this optimization in secure VPN services in our experiment~\autoref{openvpn}.% For instant requests like clock, the requestor can directly issue an \textit{smcall} which skips the batch.% when combined with asynchronous, batched mechanism~\cite{DBLP:conf/osdi/ArnautovTGKMPLM16}
+To reduce the context switches between SMVisor and enclaves, \textsc{Aurora} supports a batched \textit{smcalls} mechanism using two dedicated, lock-free ring buffers for input and output respectively.
+%It is especially useful in the case of highly frequent requests.
+Enclaves can set a desired threshold, so Tlibaurora will coalesce these \textit{smcalls}. For asynchronous I/O requests, the mechanism can benefit the enclave with higher throughput.
 
@@
 \textbf{Trusted Input Mode.}
-When an enclave issues an input request, SMVisor routes the keyboard interrupt (IRQ 1 by default) to SMI.
-All of the subsequent keyboard scan codes are cached inside SMRAM.
+When an enclave issues a trusted input request, SMVisor routes the keyboard interrupt (IRQ 1 by default) to SMI.
+All of the subsequent keyboard scan codes are then cached inside SMRAM.
 We call this case \emph{trusted input mode}.
 After an \emph{enter} key is hit and released, SMVisor recovers the I/O APIC redirection table and exits trusted input mode.
-Finally, SMVisor encrypts the inputs and sends it to the secure channel.
-The desired enclave can then take it from the channel and decrypt it.
-%the user hits the enter key and releases it
+Finally, SMVisor encrypts the input and sends it to the secure channel.
+The desired enclave obtains it from the channel and decrypt it.
 
@@
 \subsection{Trusted Serial Printer Output}\label{output_service}
-Today shared print services are very common, by which colleagues in a unit or students in a college print their documents.
+Shared print services are very common today, by which colleagues in a unit or students in a college print their documents using the same physical machine.
 Users' private or sensitive data may also be printed using such infrastructures.
-Malware on these public machines/printers can easily steal these data for malicious purposes like industrial espionage or illegal data acquisition.
+Malware or compromised systems running on these shared machines can steal these data for malicious purposes like industrial espionage or illegal data acquisition.
 To mitigate this threat, we build trusted serial-port path for shared print services.
@@
 
-%\section{Trusted I/O Paths for Data-Storage/-Transmitter Devices}\label{path2}
-%As to trusted I/O paths for data-storage/-transmitter devices, \textsc{Aurora} reuses existing system services and verifies the correctness of the I/O services provided by the untrusted systems, as discussed in section~\autoref{types}.
-In this section, we present this kind of trusted paths by taking USB storage as an example.
-
 \subsection{Trusted USB Storage}\label{storage_service}
@@
 % 对于不关注隐私的可信路径，我们主要是利用中断来判断读写的请求。因此每次都显式调用fsync；另外，最大的问题在于如何找到DMA高速缓存区域。
-%\emph{Basic USB Workflow.}
+%\textbf{Basic USB Workflow.}
 %A USB host controller (UHC), consisting of several physical USB ports, is connected to one USB endpoints.
 A UHC is controlled via a set of memory-mapped I/O (MMIO) registers and presented as a PCI device in an OS, which uses a USB Host Controller Driver (UHCD) to communicate with it.
-A USB driver talks to its device using one of three protocols (e.g., EHCI).
 %to issue request packets defined by the specific UHCD.
@@
 In Linux, the data is by default transferred using bulk mode and is exchanged based on DMA mechanism, which stores the DMA address and buffers location in a {scatter-gather} list.
-The ashmd module can obtain these information from corresponding drivers.
+The ashmd module obtains the information from the USB driver.
 
@@
 With SSE and AES-NI, we boost encryption performance.
-For example, with AES-NI support, AES-256-GCM encryption and decryption on 4KB data in SMM mode costs 9us on average, for comparison,  without AES-NI, AES-128-GCM implementation of Intel IPP Crypto library~\cite{Intel_IPP_2017_Update_2} costs 597us.
+For example, with AES-NI support, AES-256-GCM encryption and decryption on 4KB data in SMM costs 9us on average, for comparison,  without AES-NI, AES-128-GCM implementation of Intel IPP Crypto library~\cite{Intel_IPP_2017_Update_2} costs 597us.
 
 We implement a specific kernel model ashmd. Like Linux SGX driver, we use but do not trust them. the ashmd module is intended to relay the communications between hardware enclaves and SMVisor.
-%We reused the implementations of i8042 driver from SeaBIOS.
-To issue a trusted input request, an enclave simply needs to link against libaurora.
-Tlibaurora automatically changes the semantics of read() API, i.e.
-reading  /dev/aurora instead of stdio (or /dev/tty).
-The raw inputs will be put in the buffer parameter of read() via the secure session.
-%eventually
-
-%We reused the implementations of serial-port driver from SeaBIOS, SMVisor explicitly invokes the fflush operation to make sure that all writes to a serial port are completely sent.
-%After each write request from the enclave, SMVisor
-
-%We reused the implementations of EHCI driver from SeaBIOS.
-To obtain the DMA address held in the \textit{scatter-gather} list structure, we use ashmd to inspect the address and hand it over to the SMVisor.
-
-%We reused the implementations of timer/clock drivers from SeaBIOS, including RTC, HPET, PIT, TSC, and ACPI/PM timer.
-We minimize SMM preemption time by placing most of the clock processing logic in the Tlibaurora.
-For the sake of compatibility, Tlibaurora supports standard libc time APIs, therefore developers can benefit from trusted clock service without writing OCALLs.
-Tlibaurora performs the validation using attack-awareness algorithm and is responsible for detecting time attacks.
 
@@
 Smaller codebase denotes smaller TCB introduced.
-%This implies that we could have roughly 56 enclaves with trusted I/O support in parallel without EPC paging.
 
@@
 \subsection{Framework Overhead}
-%% 我们使用pi计算做评估，不同触发周期和抢占时间
-We select  pi\_css5\footnote{http://myownlittleworld.com/miscellaneous/computers/piprogram.html} program, which has no interaction with the external system, to measure the performance of \textsc{Aurora} with as little noise as possible.
-We ran the program till achieving 4,000,000 digits of precision, and used two durations (70us and 150us) to emulate different real-world environments.
-
-%% 一个线程触发，一个线程计时
-%% 太高的请求我们认为不合理；OS有权拒绝SMI请求，以此降低性能影响
-Specifically, we ran two threads: one thread (T1) running Pi number calculation, the other thread (T2) requesting the ashmd module to trigger an SMI in a given interval.
-Firstly, we ran T1 without the interference of T2 and took the time cost as baseline.
-Then we started T2 to see the slowdown of T1.
-From \autoref{table:pi}, we observe that when the interval decreases, the overhead increases.
-The worst case of overhead is around 21\%, where \textit{smcalls} are requested too frequently.
-Such situation is rare in real world applications because an enclave has to execute its own logic.
-We observe that intensive requests may impact the time-sensitive tasks on the same system.
-Since \textit{smcalls} are forwarded by ashmd module, it can use a threshold to block a malicious enclave from abusing.
-In our current setting, we allow an enclave to request up 10,000 times per second, which introduces about 11\% overhead to the system.
-
-\begin{table}[t]
+
+\begin{table}
 	\centering
@@
 
+%% 我们使用pi计算做评估，不同触发周期和抢占时间
+We select  pi\_css5\footnote{http://myownlittleworld.com/miscellaneous/computers/piprogram.html} program, which has no interaction with the external system, to measure the performance of \textsc{Aurora} with as little noise as possible.
+We ran the program till achieving 4,000,000 digits of precision, and used two durations (70us and 150us) to emulate different real-world environments.
+
+%% 一个线程触发，一个线程计时
+%% 太高的请求我们认为不合理；OS有权拒绝SMI请求，以此降低性能影响
+Specifically, we ran two threads: one thread (T1) running Pi number calculation, the other thread (T2) requesting the ashmd module to trigger an SMI in a given interval.
+Firstly, we ran T1 without the interference of T2 and took the time cost as baseline.
+Then we started T2 to see the slowdown of T1.
+From \autoref{table:pi}, we observe that when the interval decreases, the overhead increases.
+The worst case of overhead is around 21\%, where \textit{smcalls} are requested too frequently.
+Such situation is rare in real world applications because an enclave has to execute its own logic.
+We observe that intensive requests may impact the time-sensitive tasks on the same system.
+Since \textit{smcalls} are forwarded by ashmd module, it can use a threshold to block a malicious enclave from abusing.
+In our current setting, we allow an enclave to request up 10,000 times per second, which introduces about 11\% overhead to the system.
+
 \subsection{Trusted Clock Benchmark}\label{time_bench}
-%It is important to quantify how much time is required to attain a trusted clock service since the potential service latency impacts the freshness of message and indicates the response speed. 
-For this experiment, we measured the complete trusted clock procedure for 10000 time and used the average value.
-Table \ref{table:breaktime} shows the time cost for each step in a trusted clock path, as explained in \autoref{workflow}.
-We can see that the clock service takes most of time.
-This is because 1) the RTC driver has to read clock value twice to check if the clock is updating its time data; 2) The RTC involves several \textsf{INS} instructions to read each field of a calendar time, and costs 14us to obtain a complete wall-clock time in one request; 3) The other 4 timers cost roughly 10us in sum.
-The total  time cost (84us) satisfies the requirement of real-world trusted timestamps.
-\begin{table}[t]
+
+\begin{table}
 	\centering
@@
 \end{table}
+
+%It is important to quantify how much time is required to attain a trusted clock service since the potential service latency impacts the freshness of message and indicates the response speed. 
+For this experiment, we measured the complete trusted clock procedure for 1,000 time and used the average value.
+Table \ref{table:breaktime} shows the time cost for each step in a trusted clock path, as explained in \autoref{workflow}.
+We can see that the clock service takes most of time.
+This is because 1) the RTC driver has to read clock value twice to check if the clock is updating its time data; 2) The RTC involves several \textsf{INS} instructions to read each field of a calendar time, and costs 14us to obtain a complete wall-clock time in one request; 3) The other 4 timers cost roughly 10us in sum.
+The total  time cost (84us) satisfies the requirement of real-world trusted timestamps.
+
+For comparison, we measured the performance of other clock providers.
+The results are shown in \autoref{table:timeservice}.
+Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks such as the timing attacks.
+Among existing approaches, \textsc{Aurora} outperforms remote clock (the 2nd row) and Intel's reference clock (the 3rd row) by introducing very low latency, while achieving the same resolution (nanosecond-level) as OS services (the 4th row).
+%Note that any approach can be arbitrarily delayed in that the untrusted OS is in charge of the enclave thread scheduling. We treat intentionally time delay as a form of Denial-of-Service attack.
+
 \begin{table*}[t]
@@
 	\small
-	\begin{tabular}{llllrccr}%{ |c|c|c|c|c|c|c|c| }
+	\begin{tabular}{lllcrccr}
 		\toprule
@@
 		Intel ME & PSW & relative & 1s & 10.3ms & medium & trusted & SGX-Tor~\cite{DBLP:conf/nsdi/KimHHKH17} \\
-		OS Kernel & ocall & absolute & 1ns & 6us & low & untrusted & Panoply~\cite{shinde_panoply:_2017} \\
+		OS Kernel & OCALL & absolute & 1ns & 6us & low & untrusted & Panoply~\cite{shinde_panoply:_2017} \\
 		Hardware Clock & \textit{smcall} & absolute & 1ns & 69us & low & trusted & Aurora-OpenSSL~\ref{openssl} \\
@@
 
-For comparison, we measured the performance of other clock providers.
-The results are shown in \autoref{table:timeservice}.
-Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks such as the timing attacks.
-Among existing approaches, \textsc{Aurora} outperforms remote clock (the 2nd row) and Intel's reference clock (the 3rd row) by introducing very low latency, while achieving the same resolution (nanosecond-level) as OS services (the 4th row).
-%Note that any approach can be arbitrarily delayed in that the untrusted OS is in charge of the enclave thread scheduling. We treat intentionally time delay as a form of Denial-of-Service attack.
-
 % 测试结果说明Aurora方法下的串口响应速度更快，和Linux原生方法频繁的上下文代价有关
@@
 
-\begin{table}[h]
+\begin{table}[t]
 	\centering
@@
 
-\begin{table}[h]	
+\begin{table}[t]	
 	\centering
@@
 \textbf{Keylogging Attack.}
-To evaluate the effectiveness of \textsc{Aurora}'s trusted input path, we deployed multiple spyware to get a user's inputs under trusted input mode, including a stealthy root keylogger\footnote{https://github.com/vim2meta/keylogger}, a rootless X11-based keylogger ixkeylog\footnote{https://github.com/dorneanu/ixkeylog},
-%and xkbcat\footnote{https://github.com/anko/xkbcat}, 
-a kernel-level rootkit  keylogger\footnote{https://github.com/arunpn123/keylogger}, 
-%and Linux-Keylogger\footnote{https://github.com/nijindal/Linux-Keylogger} 
-and a remote keylogger\footnote{https://github.com/EinBaum/Totally-Not-A-Virus}. None of them can obtain the user's inputs.
+To evaluate the effectiveness of \textsc{Aurora}'s trusted input path, we deployed multiple spyware to get a user's inputs under trusted input mode, including a stealthy root keylogger\footnote{https://github.com/vim2meta/keylogger}, a rootless X11-based keylogger ixkeylog\footnote{https://github.com/dorneanu/ixkeylog}, a kernel-level rootkit keylogger\footnote{https://github.com/arunpn123/keylogger}, and a remote keylogger\footnote{https://github.com/EinBaum/Totally-Not-A-Virus}.
+None of them can obtain the user's inputs.
 
@@
 \section{Case Studies}\label{casestudy}
+
 Aurora provides uniform abstractions (standard POSIX APIs) for the SGX applications, which need not be modified, to maintain platform-independence and thus achieve nice usability.
@@
 Moreover, it is hard for users to port commodity drivers into an enclave because 1) enclave mode does not support privileged instructions like \textsf{IN/OUT} or \textsf{RDMSR/WRMSR} with which drivers read/write I/O ports; 2) it is unclear in the paper \cite{weiser_sgxio:_2017} how to correctly partition drivers.
-In comparison, \textsc{Aurora}'s drivers are invoked in SMM mode without any instruction restricted.
+In comparison, \textsc{Aurora}'s drivers are invoked in SMM without any instruction restricted.
 They are monitored and regulated by SMVisor protected inside SMRAM.
@@
 
-The authors would like to thank Kai Huang from Intel and Shweta Shinde from NUS for their generous help and constructive comments.
+The authors would like to thank Kai Huang from Intel Corporation and Shweta Shinde from National University of Singapore for their generous help and constructive comments.
 The authors also thank the anonymous reviewers for their valuable feedback that help improve the article.
+This work was supported by the National Natural Science Foundation of China (NSFC) under Grant No.
+U1713212 and 91418206.

### 2019-07-04 abstract/abstract.tex
refresh reviewers' comments

@@
 To this end, we propose a novel architecture called \textsc{Aurora} to provide trusted I/O paths for enclave programs even in the presence of untrusted system software.
-Specifically, \textsc{Aurora} exploits two commercial-off-the-shelf x86 platform features (System Management Mode, SMM and SGX) and establishes a secure channel between an enclave program and target device.
+Specifically, \textsc{Aurora} exploits two commercial-off-the-shelf features (System Management Mode, SMM and SGX) and establishes a secure channel between an enclave program and target device.
 Furthermore, we design and implement trusted paths for HID keyboard, serial port printer, hardware clocks, and USB mass storage, respectively.

### 2019-07-04 article.tex
refresh reviewers' comments

@@
 	Mingyu Li,~Yixiu Chen,~Lin Jiang,~Zhuosi Xie,~Tianqi Yang\\
-	Trusted Software and Intelligent System Lab\\
-	Beijing University of Posts and Telecommunications
-	\thanks{H. Liang, M. Li, Y. Chen, L. Jiang, Z. Xie, T. Yang
-  are with Beijing University of Posts and Telecommunications, Beijing 100876, China. e-mail: (\{hliang,maxul,jianglin,xiezhuosi,yangtianqi,chenyixiu\}@bupt.edu.cn)
-  }% <-this % stops a space
+	%\{hliang, maxul, chenyixiu, jianglin, xiezhuosi, yangtianqi\}@bupt.edu.cn\\
+	%Trusted Software and Intelligent System Lab\\
+	%Beijing University of Posts and Telecommunications
+	\thanks{H.
+Liang, M.
+Li, Y.
+Chen, L.
+Jiang, Z.
+Xie, T.
+Yang are with Trusted Software and Intelligent System Lab, Beijing University of Posts and Telecommunications, Beijing 100876, China.
+e-mail: (\{hliang, maxul, chenyixiu, jianglin, xiezhuosi, yangtianqi\}@bupt.edu.cn) }% <-this % stops a space
+    \thanks{This work was supported by the National Natural Science Foundation of China (NSFC) under Grant No. U1713212 and 91418206.}
 }

### 2019-07-04 sections/main.tex
sentences reorder

@@
 A trusted path between an enclave program and a target I/O device is a protected channel that assures the secrecy and authenticity of transferred data.
-It is extremely critical to user's privacy such as health information, financial account, personal documents, etc on personal computers.
-The private data can be protected inside an enclave during runtime, but it is impossible to protecte it at the time of being printed since typically printer devices only understand plaintext data and the corresponding drivers are under the control of the untrusted kernel.
+It is extremely critical to user's privacy on personal computers, such as health information, financial account and personal documents, etc.
+The private data can be protected inside an enclave during runtime, but it is impossible to protect it at the time of being printed since typically printer devices only understand plaintext data and the corresponding drivers are under the control of the untrusted kernel.
 Similarly, the textual input from users such as keystrokes can be recorded on a compromised computer, which is a very serious problem when it comes to password security~\cite{DBLP:conf/uss/SilverJBCJ14}.
@@
 Intel SGX enclaves also suffer from the loss of a high-precision trusted clock.
-State-of-the-art library OSes such as Haven~\cite{DBLP:journals/tocs/BaumannPH15}, Graphene-SGX~\cite{DBLP:conf/usenix/TsaiPV17} and Panoply \cite{shinde_panoply:_2017} relay the clock value from  untrusted systems.
+State-of-the-art library OSes such as Haven~\cite{DBLP:journals/tocs/BaumannPH15}, Graphene-SGX~\cite{DBLP:conf/usenix/TsaiPV17} and Panoply \cite{shinde_panoply:_2017} rely the clock value from  untrusted systems.
 As a result, these systems are vulnerable to time deception attacks.
@@
 Cryptographic libraries such as TaLos~\cite{TaLoS}, mbedTLS-SGX~\cite{mbedtls}, WolfSSL-SGX~\cite{wolfSSL} encounter the same problem as well.
-Additionaly, another trusted service named Intel monotonic counters are slow and the used NVRAM will wear out after a limited times of writes.
+Additionally, another trusted service named Intel monotonic counters are slow and the NVRAM used by it only supports limited times of writes.
 
@@
 %% 所以，我们有了Aurora，专门提供可信IO服务的Aurora，它负责为enclave提供一条直达IO设备的可信路径。这个方法引入了一个可以执行特权指令、访问IO 设备的特殊“enclave”，即系统管理模式RAM。它是现有X86架构下的一块高特权飞地，同一模式下的飞地外代码、其他模式都无法访问和修改它。我们在SMRAM 和enclave间构建本地的可信路径，就能很好地给enclave提供绕过不可信区域的IO可信路径！
-On Intel x86 platforms, we observe that 1) all peripheral I/O devices are connected with south-bridge to I/O Advanced Programmable Interrupt Controller (I/O APIC), 2) I/O interrupts can be rerouted to System Management Interrupt (SMI) via configuring I/O APIC and 3) the SMI handler is initialized by Unified Extensible Firmware Interface (UEFI) which contains kinds of device drivers; thus, we hold the insight that \textit{the SMI handler} is a perfect candidate to provide trusted I/O paths for security-critical applications.
+On Intel platforms, we observe that 1) all peripheral I/O devices are connected with south-bridge to I/O Advanced Programmable Interrupt Controller (I/O APIC), 2) I/O interrupts can be rerouted to System Management Interrupt (SMI) via configuring I/O APIC and 3) the SMI handler is initialized by Unified Extensible Firmware Interface (UEFI) which contains kinds of device drivers; thus, we hold the insight that \textit{the SMI handler} is a perfect candidate to provide trusted I/O paths for security-critical applications.
 
@@
 \begin{enumerate}[]
-\item The notion of two types of trusted I/O paths (\autoref{types}) for security-sensitive applications (enclave programs) on untrusted commodity X86 systems.
+\item The notion of two types of trusted I/O paths (\autoref{types}) for security-sensitive applications (enclave programs).
 \item A novel architecture named \textsc{Aurora} (\autoref{arch}) leveraging two hardware features of Intel processors (SMM and SGX) to provide enclaves trusted paths transparent to untrusted OSes/HVs with a minimal trusted computing base (\autoref{codebase}).
@@
 	\centering
-	\includegraphics[height=0.18\textheight]{figures/arch.pdf}
+	\includegraphics[height=0.22\textheight]{figures/arch.pdf}
 	\caption{\textsc{Aurora}'s architecture. The gray areas denote untrusted parts, and the white ones represent \textsc{Aurora}'s trusted computing base.}
@@
 \item \textbf{Trusted I/O paths for data-storage/-transmitter devices.} Storage disks and network adapters are typical storage/transmitter devices, and they don't require the stored/transmitted data in plaintext.
-Instead, both kinds of devices can deal with encrypted data without learning the semantics of the data.
+Instead, both kinds of devices can deal with encrypted data without knowing the semantics of the data.
 However, both devices need a pile of software stacks (e.g., file system, network protocol) to work correctly and remain compatible.
@@
 \subsection{Threat Model}
-We consider an adversary that is able to compromise the target system.
+We consider an adversary who is able to compromise the target system.
 He can directly attack enclave interfaces visible to the OS, and actively reconfigure any devices (e.g., modify a device’s MMIO region, or change the operating mode of a device) and perform arbitrary operations (e.g., trigger interrupts, issue DMA write requests) using any I/O commands.
@@
 	\centering
-	\includegraphics[width=0.46\textwidth]{figures/workflow.pdf} %height=0.25\textheight,
+	\includegraphics[width=0.5\textwidth]{figures/workflow.pdf} %height=0.25\textheight,
 	\caption{The workflow of a trusted I/O path in \textsc{Aurora}. }%The white areas denote the TCB.
@@
 To perform I/O operations correctly, a driver should know the exact I/O ports of the target device.
-At the time of system boot, SMVisor collects all device information and records their memory mapped I/O (MMIO) base addresses into a \emph{PCI BAR Table}, thereafter the matching drivers can manipulate the mapped PCI configuration space according to the table.
+At the time of system boot, SMVisor collects all device information and records their memory-mapped I/O (MMIO) base addresses into a \emph{PCI BAR Table}, thereafter the matching drivers can manipulate the mapped PCI configuration space according to the table.
 
@@
 These drivers lack of effective isolation from the rest of the untrusted systems, therefore we do not use them.
-Instead, since existing open-source UEFI firmware, such as Coreboot\footnote{https://www.coreboot.org/} and Project Mu\footnote{https://microsoft.github.io/mu/}, contain various drivers in their Driver eXecution Environment (DXE), and the code of these drivers are significantly scrutinized compared to the proprietary code, we reuse these drivers and forward the device interrupt for them to handle.
-This OS-neutral design allows \textsc{Aurora} to support different kinds of OS, e.g., Linux, Windows, or MacOS.
+Instead, since existing open-source UEFI firmware, such as Coreboot\footnote{https://www.coreboot.org/} and Project Mu\footnote{https://microsoft.github.io/mu/}, contains various drivers in their Driver eXecution Environment (DXE), and the code of these drivers are significantly scrutinized compared to the proprietary code, we reuse these drivers and forward the device interrupt for them to handle.
+This OS-neutral design allows \textsc{Aurora} to support different kinds of OS, e.g., Linux, Windows, or macOS.
 
@@
 As a result, Tlibaurora can directly operate on this memory in enclave mode.
-If the kernel launches memory-based Iago attacks~\cite{DBLP:conf/asplos/CheckowayS13} such as mapping to an illegal location, Tlibaurora will verify whether the whole mmaped memory is outside of the enclave, otherwise the secure channel will not be established.
+If the kernel launches memory-based Iago attacks~\cite{DBLP:conf/asplos/CheckowayS13} such as mapping to an illegal location, Tlibaurora will verify whether the whole mapped memory is outside of the enclave, otherwise the secure channel will not be established.
 
@@
 Intel extends x86 ISA with AES-NI and claims to prevent known side-channel attacks.
-We make use of it to address the same concern and use constant-time algorithm to defeat cache timing attacks.
+We make use of it to address the same concern and use a constant-time algorithm to defeat cache timing attacks.
 This hardware acceleration also decreases the preemption time in SMM.
@@
 An adversary can infer secrets by observing such side channels.
-To prevent such secrecy leakage, \textsc{Aurora} pads all messages with random value to the same length (4KB, same size as one EPC page), which restricts possible information leakage at page-level.
+To prevent such secrecy leakage, \textsc{Aurora} pads all messages with random values to the same length (4KB, same size as one EPC page), which restricts possible information leakage at page-level.
 %The message buffers must start with page-aligned address.
@@
 For example, a malware might present a fake login interface that prompts a user to enter her password.
-To mitigate this threat, we adopt an approach where PC speaker is used to indicate the trusted path has been established.
+To mitigate this threat, we leverage PC speaker to indicate that the trusted path has been established.
 When the system first boots, the network is disabled by the SMVisor, and we assume that the loaded kernel is clean due to TPM's measure boot.
-\textsc{Aurora} asks the user to store a short, arbitrary MIDI-format melody (around 5 seconds) inside SMRAM via an temporary enclave, so that everytime when a trusted path is set up, the PC speaker will play the melody.
+\textsc{Aurora} asks the user to store a short, arbitrary MIDI-format melody (around 5 seconds) inside SMRAM via a config enclave, so that every time when a trusted path is set up, the PC speaker will play the melody.
 Then the network is enabled by the SMVisor.
@@
 This is especially significant in a financial transaction (e.g.
-block chain) and secure network (e.g.
+blockchain) and secure network (e.g.
 TLS authentication).
@@
 \subsection{Trusted USB Storage}\label{storage_service}
-Storage software contains block and file system.
+Storage software usually supports block devices and file system.
 A compromised OS may silently discard data written by the application or return fabricated data during a read operation.
@@
 
-We implement a specific kernel model ashmd. Like Linux SGX driver, we use but do not trust them. the ashmd module is intended to relay the communications between hardware enclaves and SMVisor.
+We implement a specific kernel model ashmd. Like Linux SGX driver, we use but do not trust them. The ashmd module is intended to relay the communications between enclaves and SMVisor.
 
@@
 For instance, the system-wide EPC limit is approximately 93MB and the SMRAM is 4MB by default on our platform.
-We measure the final size of resulted stripped binary images.
-Our modification on CoreBoot only add 3.9\% on its total size (120.2KB V.S.
+We measure the final size of the resulted stripped binary images.
+Our modification on CoreBoot only adds 3.9\% on its total size (120.2KB V.S.
 115.7KB).
@@
 \subsection{Code Quality}
-To avoid exploitable vulnerabilities, we use well known static analysis tool Clang Static Analyzer\footnote{http://clang-analyzer.llvm.org/index.html} over \textsc{Aurora}'s code base and fix all bugs we found.
-Besides, as \textsc{Aurora} is quite small and its complexity is obviously lower than that of the formally verified microkernel~\cite{DBLP:conf/sosp/KleinEHACDEEKNSTW09}, we believe it is reasonable to put \textsc{Aurora} within the reach of formal verification.
+To avoid exploitable vulnerabilities, we use several well known static analysis tools, e.g., Clang Static Analyzer\footnote{http://clang-analyzer.llvm.org/index.html}, over \textsc{Aurora}'s code base and fix all found bugs.
+Besides, as \textsc{Aurora} is quite small and its complexity is obviously lower than that of the formally verified microkernel~\cite{DBLP:conf/sosp/KleinEHACDEEKNSTW09}, we believe it is reasonable to put \textsc{Aurora} within reach of formal verification.
 
@@
 \subsection{Limitation}
-Although  SMM-based mechanism can be used to route many peripheral I/O events, it itself cannot be used to protect the frame buffers and therefore fall short of providing a trusted display.
-This is because on X86 platform, SMRAM area by default starts at the same address as the VGA space, therefore SMVisor cannot obtain the frame buffer.
+Although SMM-based mechanism can be used to route many peripheral I/O events, it itself cannot be used to protect the framebuffers and therefore fails to provide a trusted display.
+This is because SMRAM area by default starts at the same address as the VGA space, therefore SMVisor cannot obtain the framebuffer.
 It can be solved by redirecting  SMRAM to another higher memory area without overlaying the VGA space.
-However, as  SMM-based protection has performance implications~\cite{DBLP:conf/iiswc/DelgadoK13}, we recommend that users can use Intel PAVP (assisted by Intel ME) and SGX~\cite{DBLP:conf/isca/HoekstraLPPC13} for real-time scenarios such as an online-chatting conference.
+However, as SMM-based protection has performance implications~\cite{DBLP:conf/iiswc/DelgadoK13}, we recommend that users choose Intel PAVP (assisted by Intel ME) and SGX~\cite{DBLP:conf/isca/HoekstraLPPC13} for real-time scenarios such as video chattings or conferences.
 
@@
 Specifically, we ran two threads: one thread (T1) running Pi number calculation, the other thread (T2) requesting the ashmd module to trigger an SMI in a given interval.
-Firstly, we ran T1 without the interference of T2 and took the time cost as baseline.
+Firstly, we ran T1 without the interference of T2 and took the time cost as a baseline.
 Then we started T2 to see the slowdown of T1.
@@
 The worst case of overhead is around 21\%, where \textit{smcalls} are requested too frequently.
-Such situation is rare in real world applications because an enclave has to execute its own logic.
+Such a situation is rare in real world applications because an enclave has to execute its own logic.
 We observe that intensive requests may impact the time-sensitive tasks on the same system.
@@
 In our current setting, we allow an enclave to request up 10,000 times per second, which introduces about 11\% overhead to the system.
-
-\subsection{Trusted Clock Benchmark}\label{time_bench}
 
@@
 
-%It is important to quantify how much time is required to attain a trusted clock service since the potential service latency impacts the freshness of message and indicates the response speed. 
-For this experiment, we measured the complete trusted clock procedure for 1,000 time and used the average value.
-Table \ref{table:breaktime} shows the time cost for each step in a trusted clock path, as explained in \autoref{workflow}.
-We can see that the clock service takes most of time.
-This is because 1) the RTC driver has to read clock value twice to check if the clock is updating its time data; 2) The RTC involves several \textsf{INS} instructions to read each field of a calendar time, and costs 14us to obtain a complete wall-clock time in one request; 3) The other 4 timers cost roughly 10us in sum.
-The total  time cost (84us) satisfies the requirement of real-world trusted timestamps.
-
-For comparison, we measured the performance of other clock providers.
-The results are shown in \autoref{table:timeservice}.
-Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks such as the timing attacks.
-Among existing approaches, \textsc{Aurora} outperforms remote clock (the 2nd row) and Intel's reference clock (the 3rd row) by introducing very low latency, while achieving the same resolution (nanosecond-level) as OS services (the 4th row).
-%Note that any approach can be arbitrarily delayed in that the untrusted OS is in charge of the enclave thread scheduling. We treat intentionally time delay as a form of Denial-of-Service attack.
-
 \begin{table*}[t]
@@
 \end{table*}
+
+\subsection{Trusted Clock Benchmark}\label{time_bench}
+
+%It is important to quantify how much time is required to attain a trusted clock service since the potential service latency impacts the freshness of message and indicates the response speed. 
+For this experiment, we measured the complete trusted clock procedure for 1,000 times and used the average value.
+Table \ref{table:breaktime} shows the time cost for each step in a trusted clock path, as explained in \autoref{workflow}.
+We can see that the clock service takes most of the time.
+This is because 1) the RTC driver has to read clock value twice to check if the clock is updating its time data; 2) The RTC involves several \textsf{INS} instructions to read each field of a calendar time, and costs 14us to obtain a complete wall-clock time in one request; 3) The other 4 timers cost roughly 10us in sum.
+The total  time cost (84us) satisfies the requirement of real-world trusted timestamps.
+
+For comparison, we measured the performance of other clock providers.
+The results are shown in \autoref{table:timeservice}.
+Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks such as the timing attacks.
+Among existing approaches, \textsc{Aurora} outperforms remote clock (the 2nd row) and Intel's reference clock (the 3rd row) by introducing very low latency, while achieving the same resolution (nanosecond-level) as OS services (the 4th row).
+%Note that any approach can be arbitrarily delayed in that the untrusted OS is in charge of the enclave thread scheduling. We treat intentionally time delay as a form of Denial-of-Service attack.
 
@@
 \autoref{table:serial} shows the experimental results.
-\textsc{Aurora} performs better than native Linux because \textsc{Aurora} uses batch mechanism (\autoref{batch}) to reduce the frequent mode transitions while Linux has more user/kernel mode transitions when writing large data to serial port.
-Note that, for the larger outputted data, the speedup decreases due to cryptographic computations in \textsc{Aurora}.
+\textsc{Aurora} performs better than native Linux because \textsc{Aurora} uses batch mechanism (\autoref{batch}) to reduce the frequent mode transitions while Linux has more user/kernel mode transitions when writing large data to a serial port.
+Note that, for the larger output data, the speedup decreases due to cryptographic computations in \textsc{Aurora}.
 
@@
 
-To compare the overhead introduced when applying \textsc{Aurora}'s trusted I/O path on USB storage devices, we used \emph{dd} program with options \textsf{fsync} and \textsf{direct} to write variable sizes of contents to a USB mass storage device on native Linux system as the baseline.
+To compare the overhead introduced when applying \textsc{Aurora}'s trusted I/O path on USB storage devices, we wrote variable sizes of contents to a USB storage device on native Linux system as the baseline, by using \textsf{dd} program with options \textsf{fsync} and \textsf{direct}.
 To avoid the side-effect of any buffer mechanism, we use Linux raw device to mount and initialize the USB device.
@@
 We did not use any encryption in this experiment.
+
 The throughput results are shown in \autoref{table:dd} where the size of each block is set to 4KB.
-\textsc{Aurora} achieves approximately 90\% of the baseline throughput when writing 1GB to device.
+\textsc{Aurora} achieves approximately 90\% of the baseline throughput when writing 1GB to the device.
 The major overheads are contributed by SMM/Protected mode transitions and cryptographic computations on each block.
@@
 %There are multiple in-enclave SSL/TLS project on going \cite{mbedtls, intel_sgx_ssl, wolfSSL}. These projects employ SGX to provide tamper-resistant cryptographic process.
-SSL/TLS protocols are in widespread use in applications such as web browsing, email, instant messaging, and voice-over-IP. 
+SSL/TLS protocols are in widespread use in web browsing, email, instant messaging, and voice-over-IP, etc. 
 %To allow for a distributed communication, a secure session named TLS is established between two parties. 
@@
 Most of all, both parties require a reliable time source to detect possible timeout.
-For instance, both \emph{ClientHello} and \emph{ServerHello} messages use the system time to compose \textit{random} field, which is used to prevent replay attacks.
-If the time is emulated by an untrusted source, it may increase the collision probability of \emph{random} and compromise the security of SSL/TLS.
+For instance, both \emph{ClientHello} and \emph{ServerHello} messages use the system time to prevent replay attacks.
+If the time is emulated by an untrusted source, it may %increase the collision probability of \emph{random} and
+compromise the security of OpenSSL sessions.
 
@@
 		\midrule
-		\textbf{Certificate Generation} & 77.4ms & 102.5ms \\
-		\textbf{TLS Handshaking} & 2.8ms & 3.4ms \\
+		{Certificate Generation} & 77.4ms & 102.5ms \\
+		{TLS Handshaking} & 2.8ms & 3.4ms \\
 		\bottomrule
@@
 We integrated \textsc{Aurora}'s Tlibaurora into existing SGX-SQLite projects\footnote{https://github.com/yerzhan7/SGX\_SQLite} and added code to support standard file system calls such as \textit{open}, \textit{read}, \textit{write}, \textit{stat}, \textit{lstat}, \textit{fstat}, \textit{fsync}, \textit{fcntl}, \textit{ftruncate} and \textit{unlink}.
-We then eliminated the file-related OCALLs for the untrusted system.
-%To protect the data, Tlibaurora's shim layer uses the symmetric key derived from user password and in-enclave nonce values to encrypt the file payloads, and uses the cryptographic primitives from Intel SGX SDK to compute MAC values for blocks.
-To avoid password leak, we use \textsc{Aurora}'s trusted input path to obtain users' password from keyboard devices.
+We then eliminated the file-related OCALLs from the untrusted system.
+To protect the data, Tlibaurora's shim layer uses a symmetric key derived from user password and in-enclave nonces to encrypt the file payloads. %, and computes MAC values for blocks. 
+To avoid password leak, we use \textsc{Aurora}'s trusted input path to obtain users' passwords from keyboard devices.
 Moreover, \textsc{Aurora}'s secure session protects the confidentiality and integrity of data between SQLite enclaves and SMVisor.
-%Last but not least, Tlibaurora library uses the cryptographic primitives from Intel SGX SDK to compute MAC values for block request and response messages.
+When SQLite invokes Tlibaurora file APIs, it opens the USB storage device in direct I/O mode and reads/writes data using 4KB block size. 
+Finally, %to directly measure the overhead introduced by \textsc{Aurora}'s infrastructure, 
+we set the synchronize flag to \textsf{FULL} to avoid the uncertainty of I/O caching.
 
@@
 We evaluated the enhanced SQLite performance by running standardized TPC-H benchmark\footnote{http://www.tpc.org/tpch/} over a large database. % (around 1.3GB).
-We make minor changes to these benchmark queries in order to make them possible to be executed in SQLite. Unfortunately, not all queries can be executed.
-To directly measure the overhead introduced by \textsc{Aurora}'s infrastructure, we set the synchronize flag to \textsf{FULL} to avoid the uncertainty of I/O caching.
-When SQLite invokes Tlibaurora file APIs, it opens the USB storage device in direct I/O mode and reads/writes data using 4KB block size.
+We make minor changes to these benchmark queries in order to make them possible to be executed in SQLite.
+Unfortunately, not all queries can be executed due to the experiment environment and system configration.
 %In our experiment, the native insertion transactions for 1000 times cost 17.3 seconds while the ones with \textsc{Aurora}'s trusted path cost 20.5 seconds.
 About 18\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.
-
 \autoref{table:tpch} shows the successfully executed queries and their results of native SGX-SQLite and \textsc{Aurora}-SGLite respectively.
@@
 Our technique was inspired by Scotch~\cite{DBLP:conf/raid/LeachZW17} which is the first work that combines SGX and SMM to audit VM resource usage. Its motivation differs from ours.
-Similar to \textsc{Aurora}'s SMVisor, previous research such as HyperCheck~\cite{DBLP:conf/raid/WangSG10}, HyperSentry~\cite{DBLP:conf/ccs/AzabNWJZS10} and IOCheck~\cite{DBLP:conf/esorics/ZhangWLS14}, also employ a dedicated SMI handler to protect the integrity of the OS kernel, hypervisor or firmware, respectively.
+Similar to \textsc{Aurora}'s SMVisor, previous research efforts such as HyperCheck~\cite{DBLP:conf/raid/WangSG10}, HyperSentry~\cite{DBLP:conf/ccs/AzabNWJZS10} and IOCheck~\cite{DBLP:conf/esorics/ZhangWLS14}, also employ a dedicated SMI handler to protect the integrity of the OS kernel, hypervisor or firmware, respectively.
 We next discuss related work of other trusted I/O architectures and trusted paths.
@@
 In contrast, \textsc{Aurora} does not need to intercept OS networking services, thus decreasing overall impact surfaces.
-Fidelius \cite{DBLP:journals/corr/abs-1809-04774} leverages a Raspberry Pi to implement a secure channel between the keyboard and the hardware enclave.
-The specific LED is turned on when a secure channel is established.
+Fidelius \cite{DBLP:journals/corr/abs-1809-04774} leverages a Raspberry Pi to implement a secure channel between a keyboard and a hardware enclave.
+The specific LED is turned on when the secure channel is established.
 \textsc{Aurora} does not need any specialized I/O devices and reuse existing hardware devices.
@@
 It uses several strategies to mitigate attacks such as phishing.
-As Intel SGX is also available on personal laptops and mini PCs (i.e., NUCs), we take advantage of SGX to protect personal password when the user logs in on the client side, which differs from their scenarios.
+As Intel SGX is also available on personal laptops and mini PCs (i.e., NUCs), we take advantage of SGX to protect a use's password when he logs in his client computer, which differs from their scenarios.
 On the mobile side, TrustUI~\cite{DBLP:conf/apsys/LiMHXZCL14} exploits ARM TrustZone to build a trusted path between a user and a service provider, because ARM TrustZone can isolate physical memory and peripheral interrupts.
@@
 
-We present \textsc{Aurora}, a novel architecture which provides trusted I/O paths on untrusted X86 platforms.
+We present \textsc{Aurora}, a novel architecture which provides trusted I/O paths on client Intel SGX platforms.
 Based on \textsc{Aurora}, we design and implement several trusted I/O paths for SGX enclaves, including HID keyboard, serial-port printer, USB mass storage and the hardware clock.
@@
 
-The authors would like to thank Kai Huang from Intel Corporation and Shweta Shinde from National University of Singapore for their generous help and constructive comments.
-The authors also thank the anonymous reviewers for their valuable feedback that help improve the article.
-This work was supported by the National Natural Science Foundation of China (NSFC) under Grant No.
-U1713212 and 91418206.
+The authors would like to thank Kai Huang from Intel Corporation and Shweta Shinde from National University of Singapore for their generous help and constructive advices.
+The authors also thank the anonymous reviewers for their valuable comments that help improve the article.

### 2019-07-04 abstract/abstract.tex
final reviewed version for submission.

@@
 Leveraging these trusted paths, we protect real-world applications including OpenSSH client, OpenSSL server/client and SQLite database.
-Security evaluations show that \textsc{Aurora} mitigates several kinds of I/O related attacks. Performance evaluations demonstrate that \textsc{Aurora} introduces acceptable overheads.
+Security and performance evaluations show that \textsc{Aurora} mitigates several kinds of I/O related attacks %. Performance evaluations demonstrate that \textsc{Aurora} 
+and introduces acceptable overheads.
 

### 2019-07-04 article.tex
final reviewed version for submission.

@@
 % Article title
-\title{ Establishing Trusted I/O Paths for Client \\ Shielded Execution Systems with Aurora }
-
+\title{ Establishing Trusted I/O Paths for \\SGX Client Systems with Aurora }
+%Shielded Execution
 % Author(s) Name
@@
 	Mingyu Li,~Yixiu Chen,~Lin Jiang,~Zhuosi Xie,~Tianqi Yang\\
-	%\{hliang, maxul, chenyixiu, jianglin, xiezhuosi, yangtianqi\}@bupt.edu.cn\\
-	%Trusted Software and Intelligent System Lab\\
-	%Beijing University of Posts and Telecommunications
-	\thanks{H.
+	Trusted Software and Intelligent System Lab.,
+	Beijing University of Posts and Telecommunications\\
+	\{hliang, maxul, chenyixiu, jianglin, xiezhuosi, yangtianqi\}@bupt.edu.cn\\
+%	\thanks{H.
 Liang, M.

### 2019-07-04 sections/main.tex
final reviewed version for submission.

@@
 We do not trust the UEFI drivers but verify whether they operate following their specifications, or perform unintended operations: e.g., intercept bus traffic, or write to an address that is not specified in DMA commands.
-Our assumptions significantly reduce the TCB on the target host as modern commodity system contains a large system software (UEFI, possibly hypervisor, kernel and other applications) when dealing with I/O devices.
+Our assumptions  reduce the TCB on the target host as modern commodity system usually contains a large software stacks (e.g., UEFI, possibly hypervisor, kernel and other applications) when dealing with I/O devices.
 Even though we do not consider physical attacks on devices, side-channel attacks~\cite{chen2019sgxpectre, ridl}, or denial-of-service attacks, we adopt side-channel free cryptographic algorithms and apply an oblivious packet transferring technique (\autoref{enhancement}).
@@
 We can see that the clock service takes most of the time.
-This is because 1) the RTC driver has to read clock value twice to check if the clock is updating its time data; 2) The RTC involves several \textsf{INS} instructions to read each field of a calendar time, and costs 14us to obtain a complete wall-clock time in one request; 3) The other 4 timers cost roughly 10us in sum.
+This is because 1) the RTC driver has to read clock value twice to check if the clock is updating its time data; 2) The RTC involves several \texttt{INS} instructions to read each field of a calendar time, and costs 14us to obtain a complete wall-clock time in one request; 3) The other 4 timers cost roughly 10us in sum.
 The total  time cost (84us) satisfies the requirement of real-world trusted timestamps.
@@
 
-To compare the overhead introduced when applying \textsc{Aurora}'s trusted I/O path on USB storage devices, we wrote variable sizes of contents to a USB storage device on native Linux system as the baseline, by using \textsf{dd} program with options \textsf{fsync} and \textsf{direct}.
+To compare the overhead introduced when applying \textsc{Aurora}'s trusted I/O path on USB storage devices, we wrote variable sizes of contents to a USB storage device on native Linux system as the baseline, by using \texttt{dd} program with options \texttt{fsync} and \texttt{direct}.
 To avoid the side-effect of any buffer mechanism, we use Linux raw device to mount and initialize the USB device.
@@
 Tlibaurora detected the attacks successfully and indicated a failure.
-For instance, \textsf{gettimeofday()} returns -1 and sets the global variable \textit{errno} appropriately.
+For instance, \texttt{gettimeofday()} returns -1 and sets the global variable \textit{errno} appropriately.
 Existing C library specification does not have a flag indicating time attacks, the enclave logic may keep requesting until obtaining a valid time value.
@@
 This interception adds around 13\% overhead per keystroke.
-Only after SMVisor routes the keyboard interrupt into itself and acknowledges to the client, will the prompt \textsf{"username@hostname password:"}  be displayed on the screen.
+Only after SMVisor routes the keyboard interrupt into itself and acknowledges to the client, will the prompt \texttt{"username@hostname password:"}  be displayed on the screen.
 While the user is typing the passphrase, the client does not display any content on the screen, achieving the same effect as in the native OpenSSH client.
@@
 The user's input is buffered inside SMRAM.
-When the user releases \textsf{Enter} key, the password is then encrypted and sent to the secure channel, and SMVisor exits trust input mode.
+When the user releases \texttt{Enter} key, the password is then encrypted and sent to the secure channel, and SMVisor exits trust input mode.
 Aurora-OpenSSH client reclaims the password message and sends it to the server.
@@
 Finally, %to directly measure the overhead introduced by \textsc{Aurora}'s infrastructure, 
-we set the synchronize flag to \textsf{FULL} to avoid the uncertainty of I/O caching.
+we set the synchronize flag to \texttt{FULL} to avoid the uncertainty of I/O caching.
 
@@
 In our experiments, no more than 10.08\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.
-Note that these are the worst-case overheads (because we have set \textsf{PRAGMA synchronous} to \textsf{FULL}) as almost all databases have their own optimized caching mechanisms for better performance.
+Note that these are the worst-case overheads (because we have set \texttt{PRAGMA synchronous} to \texttt{FULL}) as almost all databases have their own optimized caching mechanisms for better performance.
 
@@
 However, SGXIO is a conceptual design without any implementation and evaluation.
-Moreover, it is hard for users to port commodity drivers into an enclave because 1) enclave mode does not support privileged instructions like \textsf{IN/OUT} or \textsf{RDMSR/WRMSR} with which drivers read/write I/O ports; 2) it is unclear in the paper \cite{weiser_sgxio:_2017} how to correctly partition drivers.
+Moreover, it is hard for users to port commodity drivers into an enclave because 1) enclave mode does not support privileged instructions like \texttt{IN/OUT} or \texttt{RDMSR/WRMSR} with which drivers read/write I/O ports; 2) it is unclear in the paper \cite{weiser_sgxio:_2017} how to correctly partition drivers.
 In comparison, \textsc{Aurora}'s drivers are invoked in SMM without any instruction restricted.
@@
 On the desktop side, TrustLogin~\cite{zhang_trustlogin:_2015} uses SMM to protect user passwords.
-It caches the password inside the SMRAM; when the user releases the \textsf{Enter} key, TrustLogin places the password inside the packets of the NIC buffer.
+It caches the password inside the SMRAM; when the user releases the \texttt{Enter} key, TrustLogin places the password inside the packets of the NIC buffer.
 In contrast, \textsc{Aurora} does not need to intercept OS networking services, thus decreasing overall impact surfaces.

### 2019-08-24 article.tex
new draft layout

@@
-% ------------------------------------------
-%  IEEE ARTICLE TEMPLATE
-% ------------------------------------------
-% Author(s):
-% Institution(s):
-% ------------------------------------------
-\documentclass[journal,twocolumn,letterpaper,10pt]{ieee-sty/IEEEtran}
+\documentclass[journal,twocolumn,letterpaper,10pt]{IEEEtran}
 \usepackage[acronym]{glossaries}
@@
 
-% Generates the acronyms list
 \makeglossaries
 
-% Acronyms list
-\input{acronyms/acronyms.tex}
+\newacronym{IEEE}{IEEE}{Transactions on Information Forensics and Security}
 
-% ------------------------------------------
-%  MAIN DOCUMENT
-% ------------------------------------------
-\begin{document}
-
-% Variables file
 \input{variables.tex}
 
-% Article title
-\title{ Establishing Trusted I/O Paths for \\SGX Client Systems with Aurora }
-%Shielded Execution
+\title{ Establishing Trusted I/O Paths for \\ Client Shielded Executions with Aurora }
+
 % Author(s) Name
@@
 
+\begin{document}
+
 \maketitle
 
-% Abstract
-\input{abstract/abstract.tex}
+\begin{abstract}
 
-% Keywords
-\input{keywords/keywords.tex}
+Nowadays, users' sensitive data in edge computing devices (desktops, laptops, and tablets, etc.) is at high risk because they run applications on potentially compromised or malicious systems.
+To address this problem, hardware manufacturers such as Intel released a new processor feature called Software Guard eXtension (SGX), and provisions shielded executions (i.e., enclaves) for security-sensitive computations.
+Regrettably, Intel SGX's design objectives omit trusted I/O paths.
+Without such guarantees, it is unlikely for an enclave to fulfill its security and privacy purposes because the source or sink of data may have been corrupted.
 
-% Sections
-\input{sections/main.tex}
+To this end, we propose a novel architecture called \textsc{Aurora} to provide trusted I/O paths for enclave programs even in the presence of untrusted system software.
+Specifically, \textsc{Aurora} exploits two commercial-off-the-shelf features (System Management Mode, SMM and SGX) and establishes a secure channel between an enclave program and target device.
+Furthermore, we design and implement trusted paths for HID keyboard, serial port printer, hardware clocks, and USB mass storage, respectively.
+Leveraging these trusted paths, we protect real-world applications including OpenSSH client, OpenSSL server/client and SQLite database.
+Security and performance evaluations show that \textsc{Aurora} mitigates several kinds of I/O related attacks %. Performance evaluations demonstrate that \textsc{Aurora} 
+and introduces acceptable overheads.
 
-% Bibliography
+\end{abstract}
+
+\begin{IEEEkeywords}
+
+Trusted Path, Hardware Trust, Intel SGX, System Security
+
+\end{IEEEkeywords}
+
+\section{Introduction}
+
+%% 从定义出发 “可信计算” 的定义出发，可信计算包含五个组件
+%% 云环境下安全问题众多（引用云攻击综述）；用户安全与隐私问题受人关注，IntelSGX应运而生，已有不少工作，例如针对原装二进制、数据分析、网络中间件等一系列工作横空出世，都很好地利用SGX自身的特点，那就是内存对外不可见。但是缺乏对安全IO的保证。
+Trusted computing~\cite{DBLP:journals/ieeesp/Felten03} encompasses six key technologies including: 1) endorsement key, 2) protected execution, 3) sealed storage, 4) secure input and output, 5) remote attestation, and 6) trusted third party.
+To this end, Intel provisions Software Guard eXtensions (SGX) \cite{DBLP:conf/isca/McKeenABRSSS13} to establish trusted execution environment that protects the integrity and confidentiality of desired computation.
+Intel SGX enforces strong isolation in memory for security-sensitive compartments in a user-level application, called \textit{enclaves}, from untrusted privileged systems.
+Many SGX-based protection architectures~\cite{DBLP:journals/tocs/BaumannPH15,DBLP:conf/osdi/HuntZXPW16,DBLP:conf/osdi/ArnautovTGKMPLM16,DBLP:conf/icdcs/NguyenG17,7545819,DBLP:conf/sp/SchusterCFGPMR15} have already been proposed to secure data and code on untrusted servers.
+
+%% 比较可惜的是，这项技术本身并没有为数据的通道做任何加固。一个只计算不交互的应用几乎是不存在的，比如上面提到的工作，都对IO的吞吐做了评测。也就是说，SGX 不保护数据的安全进出，只保护计算过程本身。对于不可靠的数据，我们认为计算是没有价值的，例如时间。这些都和SGX技术自身设计的出发点有关，那就是归根结底要依赖不可信的OS。
+Unfortunately, Intel SGX enclaves have no direct access to any hardware resources because Intel SGX by design does not support any secure input/output mechanisms according to its Software Developer's Manual~\cite{Corporation2016Intel}.
+Concerning I/O requests, an enclave has to rely upon the untrusted compartments through system call interfaces.
+This unreliable dependency is susceptible to attacks such as memory-based Iago attacks~\cite{DBLP:conf/asplos/CheckowayS13} and I/O-based traffic analysis~\cite{DBLP:conf/ccs/MittalKJCB11}.
+
+A trusted path between an enclave program and a target I/O device is a protected channel that assures the secrecy and authenticity of transferred data.
+It is extremely critical to user's privacy on personal computers, such as health information, financial account and personal documents, etc.
+The private data can be protected inside an enclave during runtime, but it is impossible to protect it at the time of being printed since typically printer devices only understand plaintext data and the corresponding drivers are under the control of the untrusted kernel.
+Similarly, the textual input from users such as keystrokes can be recorded on a compromised computer, which is a very serious problem when it comes to password security~\cite{DBLP:conf/uss/SilverJBCJ14}.
+Previous research like SafeKeeper \cite{DBLP:conf/www/KrawieckaKPMA18} only protects the password on the server side, but cannot protect the user's password from keylogging threats on the client side.
+
+%% 以时间为例，LibOS的shield模块对系统毫无检验的能力；一些必须依赖正确时间的区块链程序只好去远程取绝对时间；Intel虽然在17 年从AMT/ME给出了可信时间服务，但依旧没有妥善解决这个问题，那就是高频时间戳请求下的精度问题。结果就是，来Intel自家的OpenSSL库都要用系统ftime接口，得到毫秒精度时间戳。
+Intel SGX enclaves also suffer from the loss of a high-precision trusted clock.
+State-of-the-art library OSes such as Haven~\cite{DBLP:journals/tocs/BaumannPH15}, Graphene-SGX~\cite{DBLP:conf/usenix/TsaiPV17} and Panoply \cite{shinde_panoply:_2017} rely the clock value from  untrusted systems.
+As a result, these systems are vulnerable to time deception attacks.
+Blockchain systems like Town Crier~\cite{DBLP:conf/ccs/ZhangCCJS16} depend on a remote server for a trusted time; however, this clock latency is high (usually hundreds of milliseconds) and uncertain.
+Intel Management Engine (ME) offers a trusted clock service for SGX enclaves, but the time value is coarse-grained (second-resolution) and not absolute at all \cite{intel_psw}.
+It is not satisfactory for those enclaves that request the timestamp information at a high frequency, (e.g., tens or hundreds of times per second).
+Hence, to achieve millisecond-resolution time, Intel SGX SSL~\cite{intel_sgx_ssl} has to use \textit{ftime}, offered by the OS, which contradicts original SGX threat model.
+Cryptographic libraries such as TaLos~\cite{TaLoS}, mbedTLS-SGX~\cite{mbedtls}, WolfSSL-SGX~\cite{wolfSSL} encounter the same problem as well.
+Additionally, another trusted service named Intel monotonic counters are slow and the NVRAM used by it only supports limited times of writes.
+
+%% 我们不禁要反诘：如今的方案真的能保护好Enclave吗？尤其是那些会和不可信OS 交互的enclave？如果不行，我们继续问：那么到底怎样才能做好呢？所以，本文就是要探索一种方法，给SGX程序强有力的IO安全保护，本质还是为了保护enclave。当然，我们的场景设在云上，没有变。
+%As for some enclave programs that require human interactions like keyboard/mice input and display on the screen,
+Today's SGX ecosystem has not yet come up with an off-the-shelf solution to trusted I/O paths.
+Enclaves themselves cannot authenticate whether they are communicating with trusted devices or not.
+It is significantly important to solve the problem on \textbf{\emph{how to establish trusted I/O paths for enclaves on untrusted systems}}, as almost all SGX-based projects exclude the underlying OS from the trusted computing base (TCB) while awkwardly depending on it for I/O requests.
+
+%% 所以，我们有了Aurora，专门提供可信IO服务的Aurora，它负责为enclave提供一条直达IO设备的可信路径。这个方法引入了一个可以执行特权指令、访问IO 设备的特殊“enclave”，即系统管理模式RAM。它是现有X86架构下的一块高特权飞地，同一模式下的飞地外代码、其他模式都无法访问和修改它。我们在SMRAM 和enclave间构建本地的可信路径，就能很好地给enclave提供绕过不可信区域的IO可信路径！
+On Intel platforms, we observe that 1) all peripheral I/O devices are connected with south-bridge to I/O Advanced Programmable Interrupt Controller (I/O APIC), 2) I/O interrupts can be rerouted to System Management Interrupt (SMI) via configuring I/O APIC and 3) the SMI handler is initialized by Unified Extensible Firmware Interface (UEFI) which contains kinds of device drivers; thus, we hold the insight that \textit{the SMI handler} is a perfect candidate to provide trusted I/O paths for security-critical applications.
+
+In this paper, we present \textsc{Aurora}, a novel architecture that safeguards I/O paths of SGX enclaves.
+To directly communicate with hardware devices without depending on the untrusted software, \textsc{Aurora} introduces System Management RAM (SMRAM) as a special enclave.
+SMRAM is a tamper-proof memory region used only in System Management Mode (SMM), much like the enclave region with SGX protection in user mode.
+\textsc{Aurora} delegates I/O requests from enclaves to the SMI handler protected inside SMRAM.
+We call this particular SMI handler \textit{SMVisor}.
+In hardware, SMVisor is safe from any corruptions by other privileged software (including OS and hypervisor).
+Therefore, Intel SGX enclaves can safely use I/O devices while remaining \textit{transparent} to the underlying OS.
+
+%% 我们的贡献点有：Aurora是个全新的系统服务框架；四款全新的服务；实际的应用评估证明其可用性。
+To summarize, this paper makes these contributions:
+\begin{enumerate}[]
+\item The notion of two types of trusted I/O paths (\autoref{types}) for security-sensitive applications (enclave programs).
+\item A novel architecture named \textsc{Aurora} (\autoref{arch}) leveraging two hardware features of Intel processors (SMM and SGX) to provide enclaves trusted paths transparent to untrusted OSes/HVs with a minimal trusted computing base (\autoref{codebase}).
+\item Design and implementation of four types of trusted I/O paths (\autoref{tpaths}): keyboard, printer, clock, and storage, based on \textsc{Aurora}.
+To the best of our knowledge, we are the first to provide these \emph{realistic} trusted I/O paths for SGX enclaves on the client side.
+\item Three case studies: OpenSSH client, OpenSSL client, and SQLite database using trusted I/O paths provided by \textsc{Aurora} (\autoref{casestudy}).
+Experimental results show that \textsc{Aurora} can protect them from typical I/O related attacks (\autoref{security}) with acceptable performance overhead (\autoref{performance}).
+\end{enumerate}
+
+\begin{figure*}[t]
+	\centering
+	\includegraphics[height=0.22\textheight]{figures/arch.pdf}
+	\caption{\textsc{Aurora}'s architecture. The gray areas denote untrusted parts, and the white ones represent \textsc{Aurora}'s trusted computing base.}
+	\label{fig:architecture}
+\end{figure*}
+
+\section{Background and Problem Definition}
+In this section, we first describe two architecture features of Intel's CPU, and then propose two types of trusted I/O paths based on the characteristics of devices.
+Finally, we describe the threat model and assumptions.
+
+\subsection{Software Guard eXtension}
+Intel SGX \cite{DBLP:conf/isca/McKeenABRSSS13} provides trusted execution environments called enclaves in user level.
+Enclaves' code and data reside in a hardware-protected memory named enclave page cache (EPC), which is inaccessible to any software including OS/HV or SMI handler.
+Enclave code can access the memory outside the enclave.
+As enclave code is only allowed to be executed in user mode, any interaction with devices must execute outside of the enclave and through untrusted system calls.
+SGX enables a threat model where users only trust the Intel CPUs and the code running inside the enclaves.
+
+Intel SGX SDK provides a function call mechanism for enclaves via ECALL and OCALL.
+Thus, an application can invoke an enclave's code via an ECALL and get the return values.
+The enclave can invoke an OCALL to execute a function in the untrusted portion of the application and receive a return value.
+With SGX's remote attestation ability \cite{Anati2013InnovativeTF}, one can gain confidence that the target application is securely running within an enclave.
+Local attestation allows an enclave to prove to one another that it is running on the same processor.
+
+\subsection{System Management Mode}
+System Management Mode (SMM) is the most privileged mode for handling system-wide functions like power management, hardware control, etc.
+Upon a System Management Interrupt (SMI), the CPU saves the system states and switches to SMM, and then executes a predefined logic (SMI handler) inside system management memory (SMRAM).
+SMRAM is fully transparent to the OS/HV since they are essentially suspended.
+An \textit{RSM} (resume) instruction is executed at the end of the SMI handler to switch back to the protected mode.
+SMRAM is fully isolated by the hardware, any code outside SMRAM cannot access or modify it.
+We deem SMRAM as a special \textit{enclave} in SMM.
+
+The SMI handler is initialized by UEFI, and  SMRAM can be locked by configuring \emph{D\_OPEN} and \emph{D\_LCK} bits in SMRAM control register.
+Therefore, the SMI handler is safe from corruption after booting.
+Moreover, the SMI handler can access all CPU registers, I/O devices, and physical memory (except for SGX EPCs), and thus we expand the SMI Handler to design \textsc{Aurora}'s SMVisor in \autoref{arch}.
+
+\subsection{Trusted I/O Paths}\label{types}
+
+%% 传统的UNIX系统将设备分为字符设备、块设备和网络设备。每种设备都有自己的I/O端口号、IRQ中断号以及对应的物理内存。字符设备是最为原生的设备，这些设备包括鼠标、键盘、实时时钟、串口等。这些设备要么产生电平数据作为CPU的输入，要么得到CPU的输出作为指示。我们将此类设备归类为“生产/消费设备”。块设备和网络设备负责数据的持久化保存和在计算节点间传输，他们自身不产生也不消耗带有信息的数据，我们根据其功能将其命名为“存储/传输设备”。我们观察并认为所有的设备都可以归结为这两类，并为这两类设备与程序间构建可信路径。由于分类的不同，可信路径的工作原理也不同。参考Zhou，我们依旧将可信路径的组成分成三个组件：设备端、程序端和通信路径。“生产/消费设备”模型下可信路径要求设备的数据/指令必须通过通信路径传输。这是因为，这些设备参与了数据的产生或使用，而硬件自身并不支持加密协议来保证数据的隐私，这种情况下，我们需要在设备端引入新的TCB对数据做密码学处理。相比之下，“存储/传输设备”只是被动地接收或发送已有的数据，保护隐私的加密运算可以单独放在程序端完成。类型的不同导致了设计的不同，甚至实现代价也不同。我们会在后文中说明。
+%% 面向“生产/消费设备”考虑隐私数据的保护，而面向“存储/传输设备”的可信路径用于对攻击检测、预期行为验证等。
+We define the term \emph{trusted I/O paths} in trusted execution environments (TEEs, e.g.
+SGX) as follows.
+Given a trusted application (e.g.
+an SGX enclave) and a trusted peripheral device, a trusted I/O path is a secure channel of data transfers between them, even in the face of software adversaries such as host kernel, hypervisor, guest VM and kernel drivers.
+We classify trusted I/O paths into two categories based on their characteristics:
+
+\begin{enumerate}
+
+\item \textbf{Trusted I/O paths for data-provider/-consumer devices.}
+Although SGX provides user-space strong isolation for program end-points (i.e.
+enclaves), most of the devices provide and/or consume plaintext messages.
+Cases vary from human input data (e.g., keyboard scan code) to outputted data (e.g., a stream of bits to printer/display), which cannot guarantee the confidentiality and integrity in an untrusted or compromised system.
+Therefore, for trusted paths of this kind, \textsc{Aurora} encrypts/decrypts in SMRAM the data from/to devices for enclaves to protect the data from the untrusted system.
+
+\item \textbf{Trusted I/O paths for data-storage/-transmitter devices.} Storage disks and network adapters are typical storage/transmitter devices, and they don't require the stored/transmitted data in plaintext.
+Instead, both kinds of devices can deal with encrypted data without knowing the semantics of the data.
+However, both devices need a pile of software stacks (e.g., file system, network protocol) to work correctly and remain compatible.
+Building trusted paths for them is very challenging.
+One possible approach is to decompose existing software stack and port them into the trusted applications, which will greatly swell the TCB and attack vectors.
+As an alternative, \textsc{Aurora} leverages a \emph{distrust but verify} method and reuses existing software stacks in a secure manner.
+
+\end{enumerate}
+
+\subsection{Threat Model}
+We consider an adversary who is able to compromise the target system.
+He can directly attack enclave interfaces visible to the OS, and actively reconfigure any devices (e.g., modify a device’s MMIO region, or change the operating mode of a device) and perform arbitrary operations (e.g., trigger interrupts, issue DMA write requests) using any I/O commands.
+
+\textsc{Aurora} requires a modern Intel platform with SGX and TPM support.
+We assume the hardware and SMRAM firmware (the microkernel we implement) of the host machine is trusted.
+We do not trust the UEFI drivers but verify whether they operate following their specifications, or perform unintended operations: e.g., intercept bus traffic, or write to an address that is not specified in DMA commands.
+Our assumptions  reduce the TCB on the target host as modern commodity system usually contains a large software stacks (e.g., UEFI, possibly hypervisor, kernel and other applications) when dealing with I/O devices.
+Even though we do not consider physical attacks on devices, side-channel attacks~\cite{chen2019sgxpectre, ridl}, or denial-of-service attacks, we adopt side-channel free cryptographic algorithms and apply an oblivious packet transferring technique (\autoref{enhancement}).
+
+\section{Design}
+%% 我们用的是SMM和SGX两种CPU特性组成的“可靠、可信”系统服务。Aurora命名缘由。
+To provide trusted I/O paths, we employ the combination of SGX and SMM, both of which are processor enforced protection features.
+Because they are offered at the opposite ends of Intel privilege-level model, we name our framework after \textsc{Aurora}\footnote{Aurora takes place in the polar regions, \emph{i.e.,} south and north of the earth.}.
+
+%% SMM call，代理+模拟 模式。Enclave的请求最终在SSV处得到响应，和syscall、vmcall是一个道理。
+Establishing a trusted path in \textsc{Aurora} consists of the following three steps.
+First, \textsc{Aurora} builds a secure session between SMVisor and an enclave that performs an I/O request.
+Second, SMVisor receives the request via the secure session without leaking knowledge to the untrusted system.
+Third, SMVisor interacts with the target device on behalf of the enclave, and performs desired I/O operations for the request.
+The procedure is conceptually similar to a \textit{syscall} or \textit{vmcall}.
+We name this an \textit{smcall} for brevity.
+
+\subsection{Architecture}\label{arch}
+
+\textsc{Aurora} is composed of three components: SMVisor, libaurora and a secure session established between SMVisor and libaurora, as shown in Figure \ref{fig:architecture}.
+
+%% SMVisor 负责判断中断源/设备，调用驱动，以此提供服务。SSV对驱动模型有限制。
+%% libaurora 把SGX缺少的IO相关接口补上，方便移植
+%% SSV和libaurora之间有信道连接
+\begin{enumerate}%[(1)]
+\item SMVisor takes charge of the target devices from the untrusted kernel.
+It dispatches device interrupts to either kernel or enclaves.
+SMVisor securely invokes UEFI drivers outside of SMRAM (\autoref{driver}).
+\item Libaurora consists of two parts.
+The trusted part (Tlibaurora) complements unsupported I/O APIs in Intel SGX SDK library, helping developers secure enclave's I/O paths.
+The untrusted part (Ulibaurora) is responsible for forwarding \textit{smcalls} to SMVisor.
+%; an ENCLAVEID can be obtained using \textit{EREPORT} instruction
+\item The secure session exchanges encrypted messages between SMVisor and an enclave via a shared memory provided by a kernel module named ashmd.
+\textsc{Aurora} leverages a 5-tuple: \textit{(ENCLID, DEVID, OPTYPE, PAYLOAD, MAC)} for each message.
+The first two arguments indicate the program endpoint and device endpoint respectively.
+The third stands for the type of I/O operation.
+The fourth carries the message data and the last is the message authentication code used for integrity protection.
+All the arguments are marshaled and encrypted.
+
+\end{enumerate}
+
+%% 和LibOS一样，我们也是要减小对不可信OS的依赖，我们甚至没有和OS交互的数据流接口，只有中断对其是不透明的。
+%% 但又和LibOS不一样，我们连驱动都不用不可信OS的，以此保证数据来源的可靠性和流出的不受干扰。
+Like library OSes~\cite{DBLP:journals/tocs/BaumannPH15, DBLP:conf/usenix/TsaiPV17, shinde_panoply:_2017}, \textsc{Aurora} has few interfaces with the untrusted OS.
+%Only interrupts are forwarded by the OS to SMVisor.
+The data plane of an enclave is protected by advanced encryption schemes accelerated by the processor (\emph{i.e.,} AES-GCM with AES-NI support), and the data flows between the enclave and SMVisor are completely invisible to the OS.
+Unlike library OSes, which delegate I/O operations to the untrusted OS, \textsc{Aurora} ships security-sensitive parts of these operations into SMVisor, thus eliminating the reliance on untrusted OS.
+
+\subsection{Workflow}\label{workflow}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{figures/workflow.pdf} %height=0.25\textheight,
+	\caption{The workflow of a trusted I/O path in \textsc{Aurora}. }%The white areas denote the TCB.
+	\label{fig:workflow}
+\end{figure}
+
+To help understand the workflow of a trusted path in \textsc{Aurora}, we break down the process of the output path and input path respectively into sequential phases, as illustrated in left and right part of \autoref{fig:workflow}.
+
+An output request is triggered by an enclave as an exception, as depicted as follows:\\
+%\par
+~~\textcircled{\footnotesize{1}} The user logic in an enclave issues an output request by invoking  Tlibaurora's APIs;\\
+~~\textcircled{\footnotesize{2}} Tlibaurora marshals and encrypts the request's arguments, and invokes Ulibaurora outside the enclave to relay the request;\\ %sends the request via the secure session, via an OCALL
+~~\textcircled{\footnotesize{3}} Ulibaurora \emph{ioctls} the ashmd module to trigger an \textit{smcall};\\
+~~\textcircled{\footnotesize{4}} SMVisor is notified and obtains the encrypted requests from the secure session;\\
+~~\textcircled{\footnotesize{5}} SMVisor decrypts the request and invokes the driver;\\
+~~\textcircled{\footnotesize{6}} The driver processes output data in PCI space or MMIO buffer;\\
+~~\textcircled{\footnotesize{7}} The driver returns a result code to SMVisor. In the end, SMVisor executes \textit{RSM} to return to protected mode. \\
+
+\par
+An input request from an enclave causes a device interrupt, as depicted as follows:\\
+%\par
+~~\textcircled{\footnotesize{1}} The target device triggers an interrupt, and the control flow is rerouted to SMVisor which has the interrupt handler;\\
+~~\textcircled{\footnotesize{2}} SMVisor invokes the driver to handle the input request;\\
+~~\textcircled{\footnotesize{3}} The driver gets the raw input data and sends it to SMVisor;\\
+~~\textcircled{\footnotesize{4}} SMVisor encrypts the data inside SMRAM, and sends it to the target enclave via the secure session;\\
+~~\textcircled{\footnotesize{5}} The system switches back to protected mode and the ashmd module uses a signal to notify Ulibaurora;\\
+~~\textcircled{\footnotesize{6}} Ulibaurora invokes Tlibaurora to receive the encrypted data;\\
+~~\textcircled{\footnotesize{7}} The enclave decrypts the encrypted data and finally obtains the raw input data. % from the secure session.
+
+\subsection{SMVisor}\label{ssv}
+
+SMVisor is the core component in \textsc{Aurora}.
+It may take charge of multiple devices simultaneously, therefore it needs to determine which device is being requested and then invokes the corresponding driver.
+
+%% 数据来的时候首先被SSV拦下，判断好了再转发，避免OS污染隐私数据
+%It protects the device ends from any other logical attacks.
+When SMVisor receives a request, it takes control of the target device interrupts to prevent the untrusted system from interrupt spoofing attacks.
+\textbf{Interrupt Handler.} To deal with a device interrupt, SMVisor reroutes the interrupt to SMI.
+Specifically, SMVisor intercepts device events by configuring the \textit{Redirection Table} defined in I/O APIC and modifying the destination of the device event to SMI.
+SMVisor distinguishes the interrupt source and thus notifies a certain enclave or the untrusted kernel.
+In order to forward the interrupt to upper software layer, it issues an inter-processor interrupt (IPI) by writing the interrupt command request (ICR) register in the local APIC.
+
+%% SSV不用管OS要地址，自己能找到设备对应PCI内存区；当然，要是OS重新初始化了这个设备，把PCI空间移到被的地方，我是没有办法的|##|
+%\emph{Device Manipulation.} 
+To perform I/O operations correctly, a driver should know the exact I/O ports of the target device.
+At the time of system boot, SMVisor collects all device information and records their memory-mapped I/O (MMIO) base addresses into a \emph{PCI BAR Table}, thereafter the matching drivers can manipulate the mapped PCI configuration space according to the table.
+
+%% 为了防止传给driver的数据有问题，每次请求的参数都会被SSV检查；同时也限制driver的内存访问，防止隐私泄漏
+%To avoid possible data leakage, SMVisor checks the memory access of the driver and clears the allocated RAM for the driver.
+\textbf{Sanitization Module.}\label{shield}
+SMVisor verifies the validity of parameters passed to the drivers (e.g.
+a PCI structure pointer should point to one of the entries in the \emph{PCI BAR Table} within SMRAM) and checks the return values according to the device specifications (e.g.
+each driver function has a specific range of error codes) as well as its functional correctness.
+When the parameters or return values are invalid, SMVisor notifies the enclave that a potential attack from OS may occur, and rejects the subsequent requests.
+Moreover, SMVisor checks the memory boundary (i.e.
+starting address and region range) that the driver tries to access to ensure that it can not write data outside of SMRAM.
+Furthermore, a driver may require more memory space during runtime (e.g.
+for DMA with devices), therefore SMVisor maintains a dynamic heap with a sanity-checking feature \cite{DBLP:conf/ccs/SilvestroLCLL17}.
+To avoid possible memory leaks, the manager frees all allocated memory for the driver before returning to the protected mode.
+
+\subsection{SMM Drivers}\label{driver}
+In this section, we describe how SMVisor safely reuses existing drivers.
+In modern monolithic systems, OS drivers are coupled with the kernel.
+These drivers lack of effective isolation from the rest of the untrusted systems, therefore we do not use them.
+Instead, since existing open-source UEFI firmware, such as Coreboot\footnote{https://www.coreboot.org/} and Project Mu\footnote{https://microsoft.github.io/mu/}, contains various drivers in their Driver eXecution Environment (DXE), and the code of these drivers are significantly scrutinized compared to the proprietary code, we reuse these drivers and forward the device interrupt for them to handle.
+This OS-neutral design allows \textsc{Aurora} to support different kinds of OS, e.g., Linux, Windows, or macOS.
+
+Furthermore, we reuse UEFI drivers in a secure manner.
+At the booting stage, SMVisor calculates the hash checksum of each driver and stores its integrity signature inside SMRAM.
+When receiving an I/O request, SMVisor verifies the integrity of the corresponding driver to ensure it is not tampered with.
+When executing a driver, SMVisor puts its data, heap, stack segments inside SMRAM, and thus ensures them inaccessible to OS/HV.
+Moreover, SMVisor uses its sanitization module to validate the behavior of the driver, as described in \autoref{shield}.
+
+\subsection{Kernel Module (ashmd)}
+%% Enclave可以在内部操作不可信内存区数据，从而避免退出；Iago会导致DoS，不会泄漏数据
+SGX memory model is asymmetric: the processor prohibits code outside of enclave to access the enclave, whereas the enclave code can access addresses outside the enclave.
+\textsc{Aurora} leverages shared memory to bridge SMVisor and enclaves.
+For instance, we use a kernel module \emph{ashmd} to allocate contiguous physical memory as shared memory.
+For an enclave program, Ulibaurora opens and mmaps this device into its  address space.
+As a result, Tlibaurora can directly operate on this memory in enclave mode.
+If the kernel launches memory-based Iago attacks~\cite{DBLP:conf/asplos/CheckowayS13} such as mapping to an illegal location, Tlibaurora will verify whether the whole mapped memory is outside of the enclave, otherwise the secure channel will not be established.
+
+In order to distinguish interrupts to enclaves from others, ashmd module allocates an IRQ from the system. When ashmd receives an IPI from  SMVisor, it knows this is a response to an enclave.
+Moreover, to prevent OS from modifying I/O redirection table, ashmd module spawns a kernel thread which holds a copy of  I/O APIC table and continually check the status of I/O APIC  table.
+Once it detects a modification by OS, it tries to restore it with the reserved one.
+If the attempt fails, ashmd  immediately notifies the target enclave with an error code.
+We treat the denial of ashmd thread scheduling as a kind of DoS attack, which is beyond the scope of the paper.
+
+\subsection{Secure Session}\label{secure_session}
+
+%% 初始必须双发交换密钥，只要Intel服务器在机器启动时验证SSV，enclave加载时验证enclave，然后利用各自得到信道交换密钥就可以。虽然代价大，但只是初始化慢而已。
+%\subsubsection{Secure Session Life-cycle}
+We design a secure session that protects the message exchange between SMVisor and enclaves. 
+The initial stage of the secure session is to ensure whether both parties are trusted or not.
+On one hand, the untrusted privileged system may launch SMI-specific fuzzing attacks on  SMVisor.
+On the other hand, the privileged system may fake the identity as  SMVisor since it can emulate an SMI and try to \textit{handshake} with an enclave.
+To mitigate such a man-in-the-middle attack, we introduce \textit{mutual attestation}.
+When each of both parties trusts the other, they can exchange a symmetric secret key using \textit{key agreement}, as depicted in \autoref{fig:mutual}.
+%both parties are acknowledged
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.3\textwidth]{figures/mutual.pdf}%height=0.2\textheight,
+\caption{Mutual attestation and key agreement between SMVisor and an application enclave.
+The single line arrows denote the attestation direction, the double line arrow denotes the following key agreement.}
+\label{fig:mutual}
+\end{figure}
+
+\textbf{Mutual Attestation.}
+During a measured boot, Intel Boot Guard~\cite{ruan_platform_2014} hashes the firmware and stores its cryptographic hash in the TPM Platform Configuration Register (PCR) \cite{tcg_trusted_2014}.
+The final PCR value reflects the whole boot process.
+If the process is tampered with, the PCR value will differ.
+
+In order to ease SMVisor attestation, we use the launch enclave provided by the Intel SGX Platform Software to attest SMVisor for one-time effort.
+Afterward, any application enclave running on the same machine can query the launch enclave to know if SMVisor attestation has succeeded.
+To attest  SMVisor, the launch enclave needs to verify the PCR value by requesting a TPM quote, which includes a cryptographic signature over the PCR value alongside with a fresh nonce.
+This ensures the integrity of the PCR value and prevents replay attacks.
+Besides, an application enclave attests itself to the launch enclave using Intel's local attestation.
+
+\textbf{Key Agreement.}
+After the mutual attestation, the SMVisor and an enclave establish an authenticated secure channel via an ephemeral Diffie-Hellman key exchange.
+We then use AES-GCM encryption scheme for further message exchange in order to prevent replay attacks.
+Intel processors with SGX feature support Advanced Encryption Standard New Instructions (AES-NI) to accelerate AES encryption and also can mitigate side-channel attacks~\cite{Corporation2016Intel}.
+
+%\subsubsection{Communication}
+%% 通信要依赖共享内存，在此基础上设计协议
+%We design a protocol for message exchange between SMVisor and enclaves in a secure session.
+
+%\textbf{Communication Protocol Interface.}
+%%% 协议接口说明，关于EnclaveID看是用什么好，EPID拿不到的话
+%Aurora proposes a uniform abstraction interface between Tlibaurora and SMVisor: \textit{IOCTL(DEVICE, ENCLAVEID, OPERATION, PAYLOAD)}.
+The first argument indicates the device that an enclave desires to communicate with.
+The second distinguishes the identity of requestor; an ENCLAVEID can be obtained using \textit{EREPORT} instruction.
+The third stands for the operation type to be performed, it can be either of the three: PROBE, READ and WRITE.
+The last argument carries the message data.
+All the arguments are marshaled and encrypted into the secure channel.
+
+\textbf{Disconnection.}
+%% 和进程退出释放资源一样，我们这个并不老是影响系统
+When an enclave finishes its requests, its Tlibaurora logic will notify SMVisor to terminate the secure session and release resources.
+When there remains no live session, SMVisor will disable its interrupt routing and thereafter make no impact on the system.
+
+\subsection{Enhancement and Optimization}\label{enhancement}
+To provide better security and performance, \textsc{Aurora} introduces \textit{hardware encryption}, \textit{data obliviousness} and \textit{batch mechanism for smcalls}.
+
+%% 硬件加速效果如何
+\textbf{Hardware Encryption.}
+Intel extends x86 ISA with AES-NI and claims to prevent known side-channel attacks.
+We make use of it to address the same concern and use a constant-time algorithm to defeat cache timing attacks.
+This hardware acceleration also decreases the preemption time in SMM.
+
+%% 数据隐藏，保证每次内容的随机性
+\textbf{Data Obliviousness.}
+In an established session, if an enclave requests the same I/O path twice and the results happen to be the same, the encrypted messages will also be identical because the session key is not changed.
+An adversary can infer secrets by observing such side channels.
+To prevent such secrecy leakage, \textsc{Aurora} pads all messages with random values to the same length (4KB, same size as one EPC page), which restricts possible information leakage at page-level.
+%The message buffers must start with page-aligned address.
+
+\textbf{Batched SMCALLs.}\label{batch}
+To reduce the context switches between SMVisor and enclaves, \textsc{Aurora} supports a batched \textit{smcalls} mechanism using two dedicated, lock-free ring buffers for input and output respectively.
+%It is especially useful in the case of highly frequent requests.
+Enclaves can set a desired threshold, so Tlibaurora will coalesce these \textit{smcalls}. For asynchronous I/O requests, the mechanism can benefit the enclave with higher throughput.
+
+\section{Trusted I/O Paths between Enclaves and Devices}\label{tpaths}
+
+As described in section~\autoref{types},  trusted I/O paths  should assure that the users' data is transferred by a secure session. 
+%The fundamental reason is that these devices can only understand data in plaintext form.
+To defeat eavesdropping attacks, the data is encrypted and sent through the secure session.
+Until it reaches the SMRAM will the encrypted data be decrypted into the clear text, so the untrusted system is unaware of the operations that SMVisor has performed to the target devices.
+In this section, we illustrate how to build trusted I/O paths for data-provider/consumer devices, e.g.
+human-interface-device (HID) keyboards, serial printers, and hardware clocks, and data-storage/transmitter devices, e.g.
+portable USB disk.
+
+\subsection{Trusted HID Keyboard Input}\label{input_service}
+Trusted input ensures that third-party software on the same computer has no access to the user's input intended for an enclave application.
+In other words, trusted input paths exclude other untrusted software including the underlying OS from sharing the input device.
+We use \textsc{Aurora} to secure user's private textual inputs from the keyboard to the enclave.%, and SGX perfectly secures the input inside the enclave.
+
+\textbf{Trusted Input Mode.}
+When an enclave issues a trusted input request, SMVisor routes the keyboard interrupt (IRQ 1 by default) to SMI.
+All of the subsequent keyboard scan codes are then cached inside SMRAM.
+We call this case \emph{trusted input mode}.
+After an \emph{enter} key is hit and released, SMVisor recovers the I/O APIC redirection table and exits trusted input mode.
+Finally, SMVisor encrypts the input and sends it to the secure channel.
+The desired enclave obtains it from the channel and decrypt it.
+
+\textbf{User Verification.}
+Phishing attacks, where an adversary exploits social engineering tricks to allure a user to leak her privacy data, are a threat to trusted input.
+For example, a malware might present a fake login interface that prompts a user to enter her password.
+To mitigate this threat, we leverage PC speaker to indicate that the trusted path has been established.
+When the system first boots, the network is disabled by the SMVisor, and we assume that the loaded kernel is clean due to TPM's measure boot.
+\textsc{Aurora} asks the user to store a short, arbitrary MIDI-format melody (around 5 seconds) inside SMRAM via a config enclave, so that every time when a trusted path is set up, the PC speaker will play the melody.
+Then the network is enabled by the SMVisor.
+Since the melody is a pre-shared secret only between the SMVisor and the user, it is impossible for the adversary to learn and mimic the process.
+% Tlibaurora first generates a random integer $N$ in the interval of [1, 10], and displays the integer number in the screen as a captcha.
+Tlibaurora sends $N$ to SMVisor.
+SMVisor blinks the \textit{Caps Lock} LED light for exactly $N$ times.
+Since the captcha is generated with noises inside the enclave, it is hard for the adversary to mimic the process.
+%Before the enclave application displays the prompt that awaits the user to enter her password, a controlled computer might have displayed the same content and user directly inputs the secrecy without waiting for the computer to enter trusted input mode.
+
+\subsection{Trusted Serial Printer Output}\label{output_service}
+Shared print services are very common today, by which colleagues in a unit or students in a college print their documents using the same physical machine.
+Users' private or sensitive data may also be printed using such infrastructures.
+Malware or compromised systems running on these shared machines can steal these data for malicious purposes like industrial espionage or illegal data acquisition.
+To mitigate this threat, we build trusted serial-port path for shared print services.
+
+When an enclave requests the trusted printer service, it encrypts the output packet and sends the encrypted packet to SMVisor.
+SMVisor receives the packet and decrypts it to plaintext packet.
+As the packets are usually held with printer-specific format, SMVisor issues the corresponding serial port driver and adds this job into its task queue.
+Afterward, SMVisor returns the status code from the printer devices to the enclave end-point.
+
+\subsection{Trusted Hardware Clock}\label{time service}
+For the clock, its integrity and non-forgeability are much more vital than confidentiality.
+%Using a trusted clock source, one is able to create trusted timestamps.
+This is especially significant in a financial transaction (e.g.
+blockchain) and secure network (e.g.
+TLS authentication).
+In this section, we describe how to extend \textsc{Aurora} for trusted, high-resolution absolute clock.
+%by accessing multiple sources of hardware timers and detecting possible attacks.
+%The clock does not need to protect its confidentiality.
+Instead,
+
+\textbf{Multiple Sources.}
+%% 多源头获取时间，适应不同需求
+\textsc{Aurora} uses multiple clock sources available on x86 platforms, such as programmable interval timer (PIT) and advanced configuration and power interface/power management (ACPI/PM) timer.
+To estimate the latency of obtaining time from hardware and adjust their values, SMVisor references invariant time stamp counter (TSC) via \textit{RDTSCP} instruction.
+The invariant TSC ensures that the duration of each clock tick is uniform (at the frequency relative to the crystal clock frequency of the processor core).
+
+\textbf{Absolute Value.}
+%% 绝对时间来自RTC驱动
+We use Real-Time Clock (RTC) to provide the absolute wall-clock time (i.e.
+epoch) for enclaves.
+To avoid incorrect values due to hardware updating, SMVisor keeps obtaining the RTC values until the last two are consistent.
+After obtaining a valid wall-clock, SMVisor then obtains the rest timers.
+The order is critical because RTC time retrieval is the most expensive amongst others and will break the freshness of other timers' values.
+
+\textbf{High Resolution.}
+%% 根据时钟频率和差值计算时间精度
+When a time value with high resolution (e.g.
+micro-second) is required, \textsc{Aurora} uses the invariant TSC and High Precision Event Timer (HPET) to satisfy the need.
+For instance, \textsc{Aurora} uses the following formulae to compute the \textit{tv\_usec} value in \textit{timeval} data structure: {$tv\_usec = (HPET\_value/ HPET\_Hz) / 1,000,000$;} where $(HPET\_value / HPET\_Hz)$ computes the absolute time in micro-seconds.
+
+\textbf{Attack-Awareness.}
+%% 如何避免时钟攻击
+Though the hardware clocks can be controlled and modified by the malicious OS, diverse timers in Aurora offer enclaves the ability to validate the credibility of time values.
+Tlibaurora records last values read from all hardware clocks and obtains current values to calculate their differences respectively, and then uses clock frequencies to compute the actual elapsed time.
+When any of the measured time violates the monotonic rule, we assume a time attack.
+
+For the case where the hardware clocks are altered in a consistent way, that is, all the timers are altered in the same offset, we propose a novel algorithm to detect such an attack.
+We use a dedicated counting thread \cite{DBLP:conf/dimva/SchwarzWGMM17} guarded inside an enclave occupying a logical thread on the same CPU core.
+Such a sibling thread will block the possibility of side-channel attacks when hyper-threading is active.
+The counting thread provides $dT$ and the difference of hardware timers provides $dt$, we use first-order derivative $dt/dT$ to detect the possible time attack.
+Currently, we set the confidence interval to 0.05, which denotes the possible altering in the timers' rising slope.
+If the slope changes much, we assume an attack.
+
+\subsection{Trusted USB Storage}\label{storage_service}
+Storage software usually supports block devices and file system.
+A compromised OS may silently discard data written by the application or return fabricated data during a read operation.
+It is a serious issue when secure data storage is  necessary for ensuring correct operation (e.g., secure logging, APT monitoring and compliance).
+In this section, we extend \textsc{Aurora} to support secure USB disk.
+Note that \textsc{Aurora}'s approach is also suitable and easy to support for other storage systems.
+
+% 对于不关注隐私的可信路径，我们主要是利用中断来判断读写的请求。因此每次都显式调用fsync；另外，最大的问题在于如何找到DMA高速缓存区域。
+%\textbf{Basic USB Workflow.}
+%A USB host controller (UHC), consisting of several physical USB ports, is connected to one USB endpoints.
+A UHC is controlled via a set of memory-mapped I/O (MMIO) registers and presented as a PCI device in an OS, which uses a USB Host Controller Driver (UHCD) to communicate with it.
+%to issue request packets defined by the specific UHCD.
+% These contain a number of pointers to various linked lists that track attached devices and map requests to devices.
+%A higher-level device driver communicates with the specific endpoint device via the HCD and hardware.
+%We take an EHCI device in Linux as an example, its device driver sends a USB request block (URB) to query information from the device.
+The UHCD creates a transfer descriptor (TD) for this request and links it to a list \textit{reqlist} for the device.
+Once this request is completed, the UHC will unlink the TD from \textit{reqlist} and link it to a \textit{donelist}.
+It also writes result data into memory via DMA and sends an interrupt indicating it has new data on \textit{donelist}.
+On receiving this interrupt, the UHCD walks \textit{donelist} and processes the TDs found.
+It then notifies the device driver (typically via an asynchronous callback) that its URB is serviced and the data is available.
+
+\textbf{Secure Storage Protocol.}
+%The IRQ number of the device is acquired by ashmd module and then notified from ashmd to the underlying SMVisor. 
+When an enclave issues a request for a USB disk, SMVisor leverages I/O interrupt rerouting mechanism to monitor and deal with every operation of the USB device, including transferring data and control commands via a secure session in \textsc{Aurora}.
+In Linux, the data is by default transferred using bulk mode and is exchanged based on DMA mechanism, which stores the DMA address and buffers location in a {scatter-gather} list.
+The ashmd module obtains the information from the USB driver.
+
+% 描述了基本的协议，保证每次读写请求都能得到SSV的确认
+%% 无法使用S2BR的设计，因为没有维护任何文件名和文件大小的基本信息，我们无法以文件作为MAC完整性检查的基本单位
+After capturing the USB Request Blocks (URBs), SMVisor passes them to the USB device via a secure session.
+Note that SMVisor leverages AES-GCM scheme to encrypt transferred blocks between enclaves and devices \ref{arch}.
+All data blocks from the enclave are encrypted by default, and a message authentication code (MAC) is generated for each block.
+SMVisor checks the MAC of each block to validate its authenticity and integrity.
+If it checks an inconsistent MAC, SMVisor will return an error to the enclave.
+
+\section{Implementation}
+
+\subsection{Components}
+
+We modified the SMI handler of CoreBoot to implement \textsc{Aurora}'s SMVisor, and modified the drivers of CoreBoot project to export interfaces which can be invoked by SMVisor.
+We disable the caching mechanism in SMM and check the access permission using the memory type range registers (MTRR) to ensure SMVisor's protection.
+For the sake of compatibility, Tlibaurora supports standard
+POSIX APIs, so enclave developers need not write OCALLs.
+
+To avoid machine check exception within SMM, we enable the Streaming SIMD Extensions (SSE) bit in control register CR0.
+With SSE and AES-NI, we boost encryption performance.
+For example, with AES-NI support, AES-256-GCM encryption and decryption on 4KB data in SMM costs 9us on average, for comparison,  without AES-NI, AES-128-GCM implementation of Intel IPP Crypto library~\cite{Intel_IPP_2017_Update_2} costs 597us.
+
+We implement a specific kernel model ashmd. Like Linux SGX driver, we use but do not trust them. The ashmd module is intended to relay the communications between enclaves and SMVisor.
+
+%% 强调TCB小
+\subsection{Code Base and Binary Size}\label{codebase}
+%% 说明移植的轻松程度，强调运行时占据物理内存的少
+%We use SLOCCount\footnote{https://www.dwheeler.com/sloccount} to calculate the overall C Lines of Code (LoC) of current \textsc{Aurora} implementation.
+As shown in \autoref{code_base},  \textsc{Aurora}'s TCB (3393 LoC) is far less than other architectures (see \autoref{arch_compare}).
+\textsc{Aurora}'s trusted components (i.e., SMVisor, ashmd, Tlibaurora, Cryptography) have 3393 lines of C code, and untrusted component (i.e., Ulibaurora) has 273 lines of C code.
+Compared to Wimpy kernel \cite{zhou_dancing_2014} which has 16K lines of code, it is smaller and simpler enough to facilitate formal verification.
+Both SMRAM and EPC RAM are scarce memory resource.
+For instance, the system-wide EPC limit is approximately 93MB and the SMRAM is 4MB by default on our platform.
+We measure the final size of the resulted stripped binary images.
+Our modification on CoreBoot only adds 3.9\% on its total size (120.2KB V.S.
+115.7KB).
+The enclave.so  linked against Tlibaurora is 696KB in size and 1MB including runtime stack and heap manager.
+Smaller codebase denotes smaller TCB introduced.
+
+\subsection{Code Quality}
+To avoid exploitable vulnerabilities, we use several well known static analysis tools, e.g., Clang Static Analyzer\footnote{http://clang-analyzer.llvm.org/index.html}, over \textsc{Aurora}'s code base and fix all found bugs.
+Besides, as \textsc{Aurora} is quite small and its complexity is obviously lower than that of the formally verified microkernel~\cite{DBLP:conf/sosp/KleinEHACDEEKNSTW09}, we believe it is reasonable to put \textsc{Aurora} within reach of formal verification.
+
+%\begin{table}[t]
+% \centering
+%  \caption{The code base of \textsc{Aurora}}
+% \label{code_base}
+%\begin{tabular}{ llr }
+% \toprule
+%& Component & Lines of Code \\
+% \midrule
+% \multirow{4}{*}{Trusted} &  SMM Supervisor & 274 \\
+%& ashmd module & 159 \\
+%& Tlibaurora & 1841 \\
+%& Cryptography & 1119 \\
+%% \midrule  TCB & 3234 \\
+% \midrule %\midrule
+%Untrusted & Ulibaurora & 273 \\
+% \midrule
+%TCB/Total & & 3393/3666 \\
+% \bottomrule
+%\end{tabular}
+%
+%\end{table}
+
+\subsection{Limitation}
+Although SMM-based mechanism can be used to route many peripheral I/O events, it itself cannot be used to protect the framebuffers and therefore fails to provide a trusted display.
+This is because SMRAM area by default starts at the same address as the VGA space, therefore SMVisor cannot obtain the framebuffer.
+It can be solved by redirecting  SMRAM to another higher memory area without overlaying the VGA space.
+However, as SMM-based protection has performance implications~\cite{DBLP:conf/iiswc/DelgadoK13}, we recommend that users choose Intel PAVP (assisted by Intel ME) and SGX~\cite{DBLP:conf/isca/HoekstraLPPC13} for real-time scenarios such as video chattings or conferences.
+
+\section{Evaluation}\label{performance}
+
+In this section, we evaluate the performance of \textsc{Aurora} framework and the trusted I/O paths.
+Our experiments are carried out on  an Intel Core i7-7700HQ 2.8GHz CPU with 16GB of memory, running Ubuntu 16.04 LTS and SGX SDK 2.4 and SGX driver 1.9.
+
+\subsection{Framework Overhead}
+
+\begin{table}
+	\centering
+	\caption{Measuring \textsc{Aurora}'s overhead by calculating Pi.}
+	\label{table:pi}
+	\begin{tabular}{rrrrr}
+		\toprule
+		\multirow{2}{*}{\textbf{Interval}} & \multicolumn{2}{c}{\textbf{Time cost (s)}} & \multicolumn{2}{c}{\textbf{Overhead ratio}} \\\cmidrule{2-3}	 \cmidrule{4-5}
+		& 70us & 150us & 70us & 150us \\
+		\midrule
+		Baseline & 8.545 & 8.635 & 0 & 0\\
+		1000ms & 9.045 & 9.025 & 5.85\% & 4.52\%\\
+		100ms & 9.605 & 9.590 & 12.40\% & 11.06\%\\
+		10ms & 10.180 & 10.455 & 18.90\% & 21.08\%\\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+%% 我们使用pi计算做评估，不同触发周期和抢占时间
+We select  pi\_css5\footnote{http://myownlittleworld.com/miscellaneous/computers/piprogram.html} program, which has no interaction with the external system, to measure the performance of \textsc{Aurora} with as little noise as possible.
+We ran the program till achieving 4,000,000 digits of precision, and used two durations (70us and 150us) to emulate different real-world environments.
+
+%% 一个线程触发，一个线程计时
+%% 太高的请求我们认为不合理；OS有权拒绝SMI请求，以此降低性能影响
+Specifically, we ran two threads: one thread (T1) running Pi number calculation, the other thread (T2) requesting the ashmd module to trigger an SMI in a given interval.
+Firstly, we ran T1 without the interference of T2 and took the time cost as a baseline.
+Then we started T2 to see the slowdown of T1.
+From \autoref{table:pi}, we observe that when the interval decreases, the overhead increases.
+The worst case of overhead is around 21\%, where \textit{smcalls} are requested too frequently.
+Such a situation is rare in real world applications because an enclave has to execute its own logic.
+We observe that intensive requests may impact the time-sensitive tasks on the same system.
+Since \textit{smcalls} are forwarded by ashmd module, it can use a threshold to block a malicious enclave from abusing.
+In our current setting, we allow an enclave to request up 10,000 times per second, which introduces about 11\% overhead to the system.
+
+\begin{table}
+	\centering
+	\caption{ Breakdown of the trusted clock service}
+	\small
+	\label{table:breaktime}
+	\begin{tabular}{lr}
+		\toprule
+		\textbf{Action Step} & \textbf{Time Cost(us)} \\
+		\midrule
+		EPC encryption & 2\\
+		Copy to DRAM & 2\\
+		Switch to SMM & 13\\
+		Copy to SMRAM & 0\\
+		SMM decryption & 3\\
+		Clock Service & 44\\
+		SMM encryption & 3\\
+		Copy to DRAM & 0\\
+		Return and enter SGX & 12\\
+		Copy to EPC & 3\\
+		EPC decryption & 2\\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\begin{table*}[t]
+	\centering
+	\caption{Comparison of existing clock services that can be used for SGX enclaves.
+Clock services include network time protocol (NTP), precision time protocol (PTP), and the platform software (PSW) supported by Intel management engine (ME)}
+	\label{table:timeservice}
+	\small
+	\begin{tabular}{lllcrccr}
+		\toprule
+		\textbf{Clock Provider} & \textbf{Approach} & \textbf{Type} & \textbf{Resolution} & \textbf{Request Cost} & \textbf{Latency} & \textbf{Security} & \textbf{Use Cases} \\
+		\midrule
+		Remote Clock & NTP/PTP & absolute & 1s & $>$100ms & high & trusted & Town Crier~\cite{DBLP:conf/ccs/ZhangCCJS16} \\
+		Intel ME & PSW & relative & 1s & 10.3ms & medium & trusted & SGX-Tor~\cite{DBLP:conf/nsdi/KimHHKH17} \\
+		OS Kernel & OCALL & absolute & 1ns & 6us & low & untrusted & Panoply~\cite{shinde_panoply:_2017} \\
+		Hardware Clock & \textit{smcall} & absolute & 1ns & 69us & low & trusted & Aurora-OpenSSL~\ref{openssl} \\
+		\bottomrule
+	\end{tabular}
+\end{table*}
+
+\subsection{Trusted Clock Benchmark}\label{time_bench}
+
+%It is important to quantify how much time is required to attain a trusted clock service since the potential service latency impacts the freshness of message and indicates the response speed. 
+For this experiment, we measured the complete trusted clock procedure for 1,000 times and used the average value.
+Table \ref{table:breaktime} shows the time cost for each step in a trusted clock path, as explained in \autoref{workflow}.
+We can see that the clock service takes most of the time.
+This is because 1) the RTC driver has to read clock value twice to check if the clock is updating its time data; 2) The RTC involves several \texttt{INS} instructions to read each field of a calendar time, and costs 14us to obtain a complete wall-clock time in one request; 3) The other 4 timers cost roughly 10us in sum.
+The total  time cost (84us) satisfies the requirement of real-world trusted timestamps.
+
+For comparison, we measured the performance of other clock providers.
+The results are shown in \autoref{table:timeservice}.
+Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks such as the timing attacks.
+Among existing approaches, \textsc{Aurora} outperforms remote clock (the 2nd row) and Intel's reference clock (the 3rd row) by introducing very low latency, while achieving the same resolution (nanosecond-level) as OS services (the 4th row).
+%Note that any approach can be arbitrarily delayed in that the untrusted OS is in charge of the enclave thread scheduling. We treat intentionally time delay as a form of Denial-of-Service attack.
+
+% 测试结果说明Aurora方法下的串口响应速度更快，和Linux原生方法频繁的上下文代价有关
+\subsection{Serial Port Output Benchmark}
+
+\begin{table}[t]
+	\centering
+	\caption{Serial-port benchmark comparison between Linux and \textsc{Aurora}.}
+	\label{table:serial}
+	\small
+	\begin{tabular}{lrrr}
+		\toprule
+		\textbf{Payload Size(KB)} & \textbf{Linux(s)} & \textbf{Aurora(s)} & \textbf{Speedup(\%)} \\
+		\midrule
+		4 & 0.03 & 0.03 & 0.0 \\
+		64 & 0.32 & 0.24 & 25.0 \\
+		256 & 1.08 & 0.87 & 19.4 \\
+		1024 & 3.95 & 3.43 & 13.2 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+It is rather difficult to measure the overall time during which a printer accepts and finishes a print job, because we have to re-flash the printer firmware to hook its time function.
+Therefore, we redirected the serial port to a local file.
+To compare the serial output performance between native Linux and \textsc{Aurora}, we measured the time cost of writing the test data of different sizes to the serial-port address in Linux and in \textsc{Aurora}, respectively.
+\autoref{table:serial} shows the experimental results.
+\textsc{Aurora} performs better than native Linux because \textsc{Aurora} uses batch mechanism (\autoref{batch}) to reduce the frequent mode transitions while Linux has more user/kernel mode transitions when writing large data to a serial port.
+Note that, for the larger output data, the speedup decreases due to cryptographic computations in \textsc{Aurora}.
+
+\subsection{Trusted USB Storage Benchmark}
+
+\begin{table}[t]	
+	\centering
+	\caption{Storage throughput comparison between Linux and \textsc{Aurora}.}
+	\label{table:dd}
+	\small
+	\begin{tabular}{lllr}
+		\toprule
+		\multirow{2}{*}{\textbf{Payload Size(MB)}} & \textbf{Linux} & \textbf{Aurora} & \textbf{Slowdown} \\ 
+		& \textbf{(MB/s)} & \textbf{(MB/s)} & \textbf{(\%)} \\
+		\midrule
+		4 & 32.9 & 31.8 & 3.3 \\
+		64 & 40.9 & 39.2 & 4.2 \\
+		256 & 42.7 & 40.4 & 5.3 \\
+		1024 & 53.2 & 47.5 & 10.7 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+To compare the overhead introduced when applying \textsc{Aurora}'s trusted I/O path on USB storage devices, we wrote variable sizes of contents to a USB storage device on native Linux system as the baseline, by using \texttt{dd} program with options \texttt{fsync} and \texttt{direct}.
+To avoid the side-effect of any buffer mechanism, we use Linux raw device to mount and initialize the USB device.
+% to bypass any file system interference.
+We then measure the overheads of using Aurora's SMVisor for MAC verification added to each block request in the request and response path.
+We did not use any encryption in this experiment.
+
+The throughput results are shown in \autoref{table:dd} where the size of each block is set to 4KB.
+\textsc{Aurora} achieves approximately 90\% of the baseline throughput when writing 1GB to the device.
+The major overheads are contributed by SMM/Protected mode transitions and cryptographic computations on each block.
+
+\subsection{Security Effectiveness}\label{security}
+In this section, we evaluate \textsc{Aurora}'s reliability with several security tests.
+
+\textbf{Keylogging Attack.}
+To evaluate the effectiveness of \textsc{Aurora}'s trusted input path, we deployed multiple spyware to get a user's inputs under trusted input mode, including a stealthy root keylogger\footnote{https://github.com/vim2meta/keylogger}, a rootless X11-based keylogger ixkeylog\footnote{https://github.com/dorneanu/ixkeylog}, a kernel-level rootkit keylogger\footnote{https://github.com/arunpn123/keylogger}, and a remote keylogger\footnote{https://github.com/EinBaum/Totally-Not-A-Virus}.
+None of them can obtain the user's inputs.
+
+\textbf{Output Corruption Attack.}
+We leveraged a DMA-based NIC device to launch output corruption attack when using Aurora's trusted serial printer service.
+Since  SMRAM and EPC RAM are strongly isolated by architectural protections, only meaningless content (0xFF) is obtained.
+Therefore no secrets are leaked.
+We then conducted another DMA attack to corrupt SMM drivers outside of SMRAM.
+SMVisor detected its integrity tampered  and rejected subsequent requests, then notified the enclave application.
+Moreover, we conducted another DMA attack to corrupt the content of shared memory of the secure session.
+Both SMVisor and Tlibaurora can verify the broken MAC and restart a new session.
+
+\textbf{Time Deception Attack.}
+To evaluate \textsc{Aurora}’s trusted clock, we intentionally modified the RTC when an enclave issued a request for trusted clock.
+Tlibaurora detected the attacks successfully and indicated a failure.
+For instance, \texttt{gettimeofday()} returns -1 and sets the global variable \textit{errno} appropriately.
+Existing C library specification does not have a flag indicating time attacks, the enclave logic may keep requesting until obtaining a valid time value.
+We support failure handling in Tlibaurora to help enclaves deal with such situations.
+
+\textbf{Storage Deception Attack.}
+We modified the kernel driver of SCSI device and randomly dropped several disk I/O requests intentionally.
+SMVisor detected such accidental conditions and notified the Tlibaurora of corresponding enclave.
+In our current setting, the Tlibaurora will automatically try issuing the lost I/O requests three times so as to avoid storage failure.
+In our experiments, the enclave finally received the attack warning from the Tlibaurora and logged these events for further forensic analysis.
+
+\section{Case Studies}\label{casestudy}
+
+Aurora provides uniform abstractions (standard POSIX APIs) for the SGX applications, which need not be modified, to maintain platform-independence and thus achieve nice usability.
+We implemented trusted I/O paths for three real-world applications to illustrate the usability of \textsc{Aurora}.
+
+\subsection{Secure OpenSSH Login}\label{openssh}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.4\textwidth]{figures/ssh.pdf} %height=0.16\textheight,width=0.6\textwidth
+	\caption{Aurora-OpenSSH with trusted input path.}
+	\label{fig:openssh}
+\end{figure}
+
+Secure Shell (SSH) is widely used for shell access on UNIX-like systems.
+An SSH server uses a username and a password to authenticate an SSH client.
+If the client is infected with malware, the login credential can be stolen by key-loggers.
+To demonstrate the effectiveness of \textsc{Aurora}'s trusted input path, we modified OpenSSH 7.7 to protect its client login process.
+Specifically, we ported passphrase related logic into an enclave, and used \textsc{Aurora}'s \textit{trusted input path} to get passwords which users input.
+We call the enhanced client as Aurora-OpenSSH client, as depicted in \autoref{fig:openssh}.
+
+Aurora-OpenSSH client first requests SMVisor to intercept the user's  keyboard events.
+This interception adds around 13\% overhead per keystroke.
+Only after SMVisor routes the keyboard interrupt into itself and acknowledges to the client, will the prompt \texttt{"username@hostname password:"}  be displayed on the screen.
+While the user is typing the passphrase, the client does not display any content on the screen, achieving the same effect as in the native OpenSSH client.
+
+The user's input is buffered inside SMRAM.
+When the user releases \texttt{Enter} key, the password is then encrypted and sent to the secure channel, and SMVisor exits trust input mode.
+Aurora-OpenSSH client reclaims the password message and sends it to the server.
+Note that the plaintext password is only available in SMRAM and enclave.
+The path between SMRAM and enclave is protected by \textsc{Aurora}'s secure channel and the path between Aurora-OpenSSH client and OpenSSH server is protected by TLS session.
+%
+%%Recall that SMVisor will manipulate the LED to blink random times to indicate that it has intervened the keyboard interrupts.
+Because we use virtualized environment to do the experiments, our current prototype uses serial output to indicate this.
+
+\subsection{Secure OpenSSL Session}\label{openssl}
+
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=0.35\textwidth]{figures/ssl.pdf} %height=0.2\textheight,
+%	\caption{Aurora-OpenSSL with trusted clock.}
+%	\label{figure:openssl}
+%\end{figure}
+%There are multiple in-enclave SSL/TLS project on going \cite{mbedtls, intel_sgx_ssl, wolfSSL}. These projects employ SGX to provide tamper-resistant cryptographic process.
+SSL/TLS protocols are in widespread use in web browsing, email, instant messaging, and voice-over-IP, etc. 
+%To allow for a distributed communication, a secure session named TLS is established between two parties. 
+An SSL/TLS session starts with SSL/TLS handshake protocol, including authentication, key exchange, etc.
+The procedures rely on system date and time.
+The SSL/TLS server needs to provide a certificate with a timestamp indicating the expiration time, and the SSL/TLS client needs to verify this certificate.
+Most of all, both parties require a reliable time source to detect possible timeout.
+For instance, both \emph{ClientHello} and \emph{ServerHello} messages use the system time to prevent replay attacks.
+If the time is emulated by an untrusted source, it may %increase the collision probability of \emph{random} and
+compromise the security of OpenSSL sessions.
+
+One of the in-enclave SSL/TLS projects is SGX-OpenSSL\footnote{https://github.com/sparkly9399/SGX-OpenSSL} from SGX-Tor project~\cite{DBLP:conf/nsdi/KimHHKH17}.
+It does not trust the system storage, therefore its server side creates the certificate inside the enclave each time it receives a new connection request from the client side.
+We enhanced the TLS handshake by using \textsc{Aurora}'s trusted clock.
+Specifically, we replaced time-related OCALLs in the original project with \textsc{Aurora}'s libaurora.
+%The new architecture of TLS handshake is demonstrated in \autoref{figure:openssl}.
+We measured the time cost of certification generation at server side and TLS handshake at client side for 10,000 runs and take the average value.
+We also measured the native SGX-OpenSSL using original OCALLs.
+As shown in \autoref{table:openssl}, in our LAN setting, Aurora-OpenSSL introduced about 32\% latency in certificate generation and 21\% in the TLS handshaking because both of them use \textsc{Aurora}'s trusted clock.
+We anticipate the overhead ratio decreased in WAN environment.
+
+\begin{table}[t]
+	\centering
+	\caption{Performance comparison between native SGX-OpenSSL and Aurora-OpenSSL.}
+	\label{table:openssl}
+	\small
+	\begin{tabular}{lrr}
+		\toprule
+		& \textbf{SGX-OpenSSL} & \textbf{Aurora-OpenSSL} \\
+		\midrule
+		{Certificate Generation} & 77.4ms & 102.5ms \\
+		{TLS Handshaking} & 2.8ms & 3.4ms \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+%\subsection{Secure Online E-Banking}
+%
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=0.45\textwidth]{usbkey.pdf} %height=0.1\textheight,
+%	\caption{AuraKey with trusted USB path}
+%	\label{fig:usb}
+%\end{figure}
+%
+%State-of-the-art secure token mechanism employs a two-factor authentication, which combines a user password and a physical device (usually a USB key, e.g.
+Yubikey\footnote{https://www.yubico.com/products/yubikey-hardware/yubikey4/}).
+%that provides digital certificate to prove genuine user identity.
+One of the popular examples is Yubikey\footnote{https://www.yubico.com/products/yubikey-hardware/yubikey4/}.
+Because these USB key implementations are not open source, we built a secure E-Banking application according to their documentations.
+We name our USB key and secure E-Banking implementation as \textit{AuraKey} and \textit{AuraBank} respectively.
+%Typically, a USB key identifies itself as a USB HID keyboard device so that any machine with a keyboard driver can easily read the textual outputs from it, therefore, we use an EHCI-based USB HID keyboard to emulate a USB key, named \textit{AuraKey}.
+We created an enclave program as a hardened E-Banking prototype, named \textit{AuraBank} and equipped \textit{AuraKey} with a PKCS format certificate from \textit{AuraBank}, as shown in \autoref{fig:usb}.
+We wrote a script to attach/detach the USB device during runtime, emulating the action of plugging/unplugging of \textit{AuraKey}.
+We deployed the server side of \textit{AuraBank} on a standalone machine in the local area network.
+%
+%We then illustrate how Aurora-assisted online E-Banking works.
+Firstly, a user launches the \textit{AuraBank} application and then performs some personal transactions.
+All of the confidential transaction logs are locally cached within the enclave of the \textit{AuraBank}.
+When the user commits her transactions to the bank server, she needs to hot-plugin the \textit{AuraKey} to confirm her operations.
+After being inserted into the USB slot, the \textit{AuraKey} triggers an SMI to notify SMVisor, which then intercepts all input interrupts of \textit{AuraKey} and obtains the security token.
+SMVisor hands the security token to \textit{AuraBank} via secure channel.
+Finally, \textit{AuraBank} sends transaction data and identity authentication information to the bank server via TLS protection, which then authenticates the user identity and validate her transaction.
+%with what the user knows (i.e.
+the personal identification number a.k.a PIN) and what the user has (i.e.
+physically secured private key).
+%
+%\begin{table}[t]
+%	\centering
+%	\caption{Aurora-secured Online E-Banking Benchmarks}
+%	\label{table:usbkey}
+%	\small
+%	\begin{tabular}{lr}
+%		\toprule
+%		Procedure & Time Cost (ms) \\
+%		\midrule
+%		AuroKey -> AuroBank & 0.468  \\
+%		AuroBank -> E-Banking server & 28.701 \\
+%		\bottomrule
+%	\end{tabular}
+%\end{table}
+%
+%The experimental results are shown in \autoref{table:usbkey}.
+The first procedure contains the private data transferring from the physical device (AuroKey) to the userspace software (AuroBank); the token is transferred via the secure session with AES-NI based cryptographical protection.
+The second procedure contains the encrypted two-factor information with TLS protection between two machines.
+Since the TLS session usually takes 10~ microseconds or more, Aurora's two-factor adds negligible overhead to the authentication process.
+With the help of trusted path, it is impossible for any untrusted software on the user computer to access either USB token or user password.
+% or other local credentials.
+%An alternative would be the OTP (one-time password) device that allows the user to login without remembering any password.
+The OTP device can also be secure using Aurora's framework.
+
+\subsection{Secure SQLite Database}
+Databases are widely used to store financial transaction records and other sensitive information.
+Some databases are built upon block devices, while maintaining its own caching mechanisms and storage policies without support of OS's file system, e.g.
+SQLite database.
+
+We integrated \textsc{Aurora}'s Tlibaurora into existing SGX-SQLite projects\footnote{https://github.com/yerzhan7/SGX\_SQLite} and added code to support standard file system calls such as \textit{open}, \textit{read}, \textit{write}, \textit{stat}, \textit{lstat}, \textit{fstat}, \textit{fsync}, \textit{fcntl}, \textit{ftruncate} and \textit{unlink}.
+We then eliminated the file-related OCALLs from the untrusted system.
+To protect the data, Tlibaurora's shim layer uses a symmetric key derived from user password and in-enclave nonces to encrypt the file payloads. %, and computes MAC values for blocks. 
+To avoid password leak, we use \textsc{Aurora}'s trusted input path to obtain users' passwords from keyboard devices.
+Moreover, \textsc{Aurora}'s secure session protects the confidentiality and integrity of data between SQLite enclaves and SMVisor.
+When SQLite invokes Tlibaurora file APIs, it opens the USB storage device in direct I/O mode and reads/writes data using 4KB block size. 
+Finally, %to directly measure the overhead introduced by \textsc{Aurora}'s infrastructure, 
+we set the synchronize flag to \texttt{FULL} to avoid the uncertainty of I/O caching.
+
+\begin{table}	
+	\centering
+	\caption{TPC-H benchmark comparison between native SGX-SQLite and \textsc{Aurora}-SQLite.}
+	\label{table:tpch}
+	\small
+	\begin{tabular}{lrrr}
+		\toprule
+		\textbf{Query} & \textbf{SGX-SQLite(s)} & \textbf{Aurora-SQLite(s)} & \textbf{Slowdown(\%)} \\
+		\midrule
+		02 & 4.68 & 5.10 & 8.97 \\
+		11 & 1.29 & 1.42 & 10.08 \\
+		16 & 1.08 & 1.10 & 5.30 \\
+		17 & 91.26 & 93.30 & 2.23 \\
+		18 & 24.98 & 25.91 & 3.72 \\
+		19 & 93.15 & 98.25 & 5.47 \\
+		21 & 39.68 & 43.16 & 9.04 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+We evaluated the enhanced SQLite performance by running standardized TPC-H benchmark\footnote{http://www.tpc.org/tpch/} over a large database. % (around 1.3GB).
+We make minor changes to these benchmark queries in order to make them possible to be executed in SQLite.
+Unfortunately, not all queries can be executed due to the experiment environment and system configration.
+%In our experiment, the native insertion transactions for 1000 times cost 17.3 seconds while the ones with \textsc{Aurora}'s trusted path cost 20.5 seconds.
+About 18\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.
+\autoref{table:tpch} shows the successfully executed queries and their results of native SGX-SQLite and \textsc{Aurora}-SGLite respectively.
+In our experiments, no more than 10.08\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.
+Note that these are the worst-case overheads (because we have set \texttt{PRAGMA synchronous} to \texttt{FULL}) as almost all databases have their own optimized caching mechanisms for better performance.
+
+%\subsection{Secure Password Manager}
+%To ease the cumbersome memoir on multiple passwords, password manager is a convenient tool that allows the end-user to store and manage her passwords.
+It uses a master key to encrypt the rest of password in a local database.
+%Though convenient, it may still be vulnerable and render user critical information at risk.
+An advanced malware can hook the activity of the password manager application and log the corresponding the key events when a "new entry" GUI window is popped up, compromising the security of user password.
+%Intel's SGX tutorial \cite{HoekstraUsingInnovativeInstructions2013} uses a password manager to demonstrate the usage of SGX.
+%Indeed, Intel SGX is a perfect technology for protecting the password manager software itself at runtime as well as the password processing process.
+%However, a user still needs to type in his username and password to initialize a password entry.
+Without a trusted input path, the SGX-assisted password manager cannot assure to protect the user's confidentiality.
+%
+%We retrofitted KeePassX, an open source GUI password manager, to demonstrate Aurora's trusted input path.
+We ported the crypto process, kdbx password database and entry editing functions into an enclave program, so that the user's passwords are clear text only in the enclave.
+When the user adds a new entry, a GUI message box is popped up, and SMVisor is activated to intercept all keyboard inputs.
+%Since the GUI logic is untrusted, we do not allow the GUI to touch the real password character, rather, after the user releases a key, the enclave sends the \textit{signal} to GUI and the GUI displays an asteroid.
+%After the user clicks the "OK" button, her username, password and other private information are then encrypted inside the enclave, and later restored into the database in encrypted format.
+
+\section{Related Work}
+Our technique was inspired by Scotch~\cite{DBLP:conf/raid/LeachZW17} which is the first work that combines SGX and SMM to audit VM resource usage. Its motivation differs from ours.
+Similar to \textsc{Aurora}'s SMVisor, previous research efforts such as HyperCheck~\cite{DBLP:conf/raid/WangSG10}, HyperSentry~\cite{DBLP:conf/ccs/AzabNWJZS10} and IOCheck~\cite{DBLP:conf/esorics/ZhangWLS14}, also employ a dedicated SMI handler to protect the integrity of the OS kernel, hypervisor or firmware, respectively.
+We next discuss related work of other trusted I/O architectures and trusted paths.
+
+\subsection{Trusted I/O Architectures}
+
+SGXIO~\cite{weiser_sgxio:_2017} is a conceptual framework that discusses how to provide trusted generic I/O paths for SGX enclaves.
+It introduces a trusted hypervisor to assist the establishment of the trusted path and requires users to port drivers into enclaves.
+However, SGXIO is a conceptual design without any implementation and evaluation.
+Moreover, it is hard for users to port commodity drivers into an enclave because 1) enclave mode does not support privileged instructions like \texttt{IN/OUT} or \texttt{RDMSR/WRMSR} with which drivers read/write I/O ports; 2) it is unclear in the paper \cite{weiser_sgxio:_2017} how to correctly partition drivers.
+In comparison, \textsc{Aurora}'s drivers are invoked in SMM without any instruction restricted.
+They are monitored and regulated by SMVisor protected inside SMRAM.
+This reusing technique allows \textsc{Aurora} easily deployed.
+
+Zhou et al.~\cite{zhou_dancing_2014} introduce a micro-hypervisor (named Wimpy) under OS to build trusted paths (TP) between program end-points (PE) and device end-points (DE).
+They require the PE of a TP includes the device drivers for DEs associated with the TP, and admit that \textit{"running the PE in Ring 3 makes DE driver porting more difficult"}.
+Although \textsc{Aurora} and Wimpy share many common security goals, e.g.
+interrupt isolation and MMIO protection, \textsc{Aurora} exploits CPU features to protect the PEs and reuse DEs securely.
+As a result, \textsc{Aurora} has smaller TCB than Wimpy.
+
+Intel SGX platform services (PSW)~\cite{intel_psw} uses management engines (ME) to provide trusted time and monotonic counters services by running a co-processor with integrated NIC, RTC and SPI flash, etc.
+It brings separated hardware that cannot be controlled by untrusted system.
+However, since Intel ME runs simultaneously with the main CPUs, we believe that it is difficult and insecure for Intel ME to implement secure human-interface input for enclaves as \textsc{Aurora} does.
+Because the CPU controlled by untrusted OS and the ME co-processor controlled by trusted software may race a DMA access  to the keyboard buffer, which cannot guarantee protection on user's confidential input.
+In comparison, \textsc{Aurora}'s SMVisor in nature preempts the untrusted OS.
+
+\subsection{Specific Trusted Paths}
+
+\textbf{Trusted Input Paths.}
+On the desktop side, TrustLogin~\cite{zhang_trustlogin:_2015} uses SMM to protect user passwords.
+It caches the password inside the SMRAM; when the user releases the \texttt{Enter} key, TrustLogin places the password inside the packets of the NIC buffer.
+In contrast, \textsc{Aurora} does not need to intercept OS networking services, thus decreasing overall impact surfaces.
+Fidelius \cite{DBLP:journals/corr/abs-1809-04774} leverages a Raspberry Pi to implement a secure channel between a keyboard and a hardware enclave.
+The specific LED is turned on when the secure channel is established.
+\textsc{Aurora} does not need any specialized I/O devices and reuse existing hardware devices.
+On the server side, SafeKeeper~\cite{DBLP:conf/www/KrawieckaKPMA18} leverages SGX to protect the password databases on untrusted clouds.
+It uses several strategies to mitigate attacks such as phishing.
+As Intel SGX is also available on personal laptops and mini PCs (i.e., NUCs), we take advantage of SGX to protect a use's password when he logs in his client computer, which differs from their scenarios.
+On the mobile side, TrustUI~\cite{DBLP:conf/apsys/LiMHXZCL14} exploits ARM TrustZone to build a trusted path between a user and a service provider, because ARM TrustZone can isolate physical memory and peripheral interrupts.
+In design, SMVisor is similar to the trusted OS inside TrustZone's secure world.
+
+\textbf{Trusted Clock Paths.} Intel PSW~\cite{intel_psw} supports coarse-grained trusted time but does not provide a wall-clock time.
+\textsc{Aurora} provides high resolution and absolute clock.
+ShieldBox~\cite{DBLP:conf/sosr/TrachKGABF18} achieves high-precision yet low-latency clock service by on-NIC PTP clock, however, the time source is not secure because enclaves cannot detect if NIC-Timer is tampered.
+By contrast, \textsc{Aurora} can detect time attack via a validation algorithm.
+Déjà Vu~\cite{DBLP:conf/ccs/ChenZRZ17} implements a reference clock thread using transactional synchronization extensions (TSX) to protect a trustworthy source of time measurement.
+Déjà Vu's goal is to detect interrupt-based attacks, while \textsc{Aurora} can provide a general time service for enclaves.
+Compared to our prior work \cite{DBLP:conf/eurosys/LiangL18}, which provides a trusted clock to enclaves, \textsc{Aurora} proposes a unified framework for different I/O devices and presents more evaluation on real-world applications.
+For distributed enclaves, ROTE~\cite{DBLP:conf/uss/MateticAKDSGJC17} proposes a protocol to provide a monotonic counter, which has high latency than \textsc{Aurora}'s trusted clock service.
+
+\textbf{Trusted Storage Paths.}
+AuditedIO \cite{DBLP:conf/apsys/BalakrishnanCBS17} leverages SGX and a kernel module to implement verifiable data storage for disk I/O operations.
+It requires a programmable SSD device and modifies the firmware.
+By contrast, \textsc{Aurora} aims for a trusted-path framework which can be used to support general storage devices.
+% and it protects SMM supervisor inside SMRAM and use mutual authentication to ensure its authenticity.
+Jiang~\cite{Jang2017Building} builds a trusted path between a USB proxy device and an enclave.
+The proxy device uses LED display for user verification.
+It plays the role of  \textsc{Aurora}'s SMVisor while \textsc{Aurora} does not need to introduce dedicated hardware.
+% while meeting the same or better protection requirements.
+BASTION-SGX~\cite{DBLP:conf/isca/PetersLVPK18} modifies the Bluetooth firmware and establishes trusted paths between Bluetooth  devices and enclave programs.
+It has similar threat model with \textsc{Aurora} and rules the privileged software (OS, drivers, etc.) out of the TCB.
+%However, it requires enclave programs to take charge of handling the HID input, which is a burden for developers.
+% and outstands BASTION-SGX by its high extensibility.
+It is a client/server architecture whereas Aurora reuses existing hardware features on one machine.% light-weight terminal on the end-host to,  Bumpy~\cite{DBLP:conf/ndss/McCunePR09} utilizes dedicated hardware to establish trusted user input path and hence cannot generalize to other devices.
+Cloud Terminal~\cite{DBLP:conf/usenix/MartignoniPZHMSPPSS12} is a micro-hypervisor-based method that provides terminals secure access to sensitive applications from an untrusted OS.
+Pesos~\cite{DBLP:conf/eurosys/KrahnTVKBF18} builds a trusted path between enclaves and cloud-based storage, and supports policy-based object protection.
+Still, Pesos requires a programmable storage HDD named Kinetic Open Storage, while \textsc{Aurora} does not.
+%SGX-FS \cite{DBLP:conf/cloudcom/BurihabwaFMS18} hardened a user-level filesystem in an enclave, which is more generic than \textsc{Aurora}.
+
+\section{Conclusion}
+
+We present \textsc{Aurora}, a novel architecture which provides trusted I/O paths on client Intel SGX platforms.
+Based on \textsc{Aurora}, we design and implement several trusted I/O paths for SGX enclaves, including HID keyboard, serial-port printer, USB mass storage and the hardware clock.
+To the best of our knowledge, we are the first to provide these \emph{realistic} trusted I/O paths for enclaves.
+Our implementation demonstrates that \textsc{Aurora} is extensible and transparent with underlying commodity systems.
+Security and performance evaluations with real-world applications show that \textsc{Aurora} can mitigate several I/O related attacks and provide trusted I/O paths with low overhead.
+
+\section*{Acknowledgement}
+
+The authors would like to thank Kai Huang from Intel Corporation and Shweta Shinde from National University of Singapore for their generous help and constructive advices.
+The authors also thank the anonymous reviewers for their valuable comments that help improve the article.
+
 \bibliographystyle{IEEEtran}
-% Bibliography file
-\bibliography{bibliography/article}
+\bibliography{article}
 

### 2019-08-24 clean.sh

@@ -1,17 +1,0 @@
-FILES="*.aux .bb *.bl *.lo *.lo *.nl *.ou *.to *.bc *.run.xml *.bbl *.blg *.fdb_latexmk *.fls *.log *.toc *.synctex.gz *.acn *.glo *.ist *.lof *.lot *.out *.acr *.alg *.glg *.gls *.glsdefs"
-rm -f $FILES
-cd abstract
-rm -f $FILES
-cd ..
-cd acronyms
-rm -rf $FILES
-cd ..
-cd keywords
-rm -f $FILES
-cd ..
-cd bibliography
-rm -f $FILES
-cd ..
-cd sections
-rm -f $FILES
-cd ..

### 2019-08-24 toPDF.sh

@@ -1,7 +1,0 @@
-BASENAME=article
-NAME=article.tex
-pdflatex $NAME
-bibtex $BASENAME
-makeglossaries $BASENAME
-pdflatex $NAME
-pdflatex $NAME

### 2019-08-24 article.tex
clean old trace ; new display style

@@
 \documentclass[journal,twocolumn,letterpaper,10pt]{IEEEtran}
+\pagestyle{plain}
+
 \usepackage[acronym]{glossaries}
+\newacronym{IEEE}{IEEE}{Transactions on Information Forensics and Security}
 
@@
 \usepackage{graphicx}
-
-\usepackage{hyperref}
+\usepackage[tight,footnotesize]{subfigure}
+\usepackage{booktabs} % For formal tables
+\usepackage[colorlinks, linkcolor=blue,anchorcolor=black,citecolor=blue]{hyperref}
 
@@
 
+\usepackage{textcomp}
 \usepackage[T1]{fontenc}
@@
 
-\usepackage{enumitem}
-\usepackage{flushend}
-
 \makeglossaries
-
-\newacronym{IEEE}{IEEE}{Transactions on Information Forensics and Security}
-
-\input{variables.tex}
 
@@
 Leveraging these trusted paths, we protect real-world applications including OpenSSH client, OpenSSL server/client and SQLite database.
-Security and performance evaluations show that \textsc{Aurora} mitigates several kinds of I/O related attacks %. Performance evaluations demonstrate that \textsc{Aurora} 
-and introduces acceptable overheads.
+Security and performance evaluations show that \textsc{Aurora} mitigates several kinds of I/O related attacks and introduces acceptable overheads.
 

### 2019-08-24 Gruntfile.js

@@ -1,40 +1,0 @@
-/*global module:false*/
-module.exports = function(grunt) {
-
-  // Project configuration.
-  grunt.initConfig({
-   shell: {
-        build: {
-          command: 'make'
-        },
-        clean: {
-          command: 'make clean'
-        },
-        bibliography: {
-          command: 'make bibliography_pdf'
-        },
-        pdf: {
-          command: 'make pdf'
-        }
-    },
-    watch: {
-      latex: {
-        files: ['./**/*.tex'],
-        tasks: ['shell:pdf']
-      },
-      bibliography: {
-        files: ['./**/*.bib'],
-        tasks: ['shell:bibliography']
-      }
-    }
-  });
-
-  require('load-grunt-tasks')(grunt);
-
-  // Default task.
-  grunt.registerTask('build', ['shell:build']);
-  grunt.registerTask('work', ['build', 'watch']);
-  grunt.registerTask('clean', ['shell:clean']);
-  grunt.registerTask('default', ['work']);
-
-};

### 2019-08-24 article.tex
major revisions according to reviewer's comments

@@
 
-\title{ Establishing Trusted I/O Paths for \\ Client Shielded Executions with Aurora }
+\title{Establishing Trusted I/O Paths for \\ Client Shielded Executions with Aurora}
 
@@
 Nowadays, users' sensitive data in edge computing devices (desktops, laptops, and tablets, etc.) is at high risk because they run applications on potentially compromised or malicious systems.
-To address this problem, hardware manufacturers such as Intel released a new processor feature called Software Guard eXtension (SGX), and provisions shielded executions (i.e., enclaves) for security-sensitive computations.
+To address this problem, hardware vendors propose Trusted Execution Environment (TEE).
+Particularly, Intel has released a new processor feature called Software Guard eXtension (SGX), and provisions shielded executions (i.e., enclaves) for security-sensitive computations.
 Regrettably, Intel SGX's design objectives omit trusted I/O paths.
@@
 Intel SGX enclaves also suffer from the loss of a high-precision trusted clock.
-State-of-the-art library OSes such as Haven~\cite{DBLP:journals/tocs/BaumannPH15}, Graphene-SGX~\cite{DBLP:conf/usenix/TsaiPV17} and Panoply \cite{shinde_panoply:_2017} rely the clock value from  untrusted systems.
-As a result, these systems are vulnerable to time deception attacks.
-Blockchain systems like Town Crier~\cite{DBLP:conf/ccs/ZhangCCJS16} depend on a remote server for a trusted time; however, this clock latency is high (usually hundreds of milliseconds) and uncertain.
+State-of-the-art library OSes such as Haven~\cite{DBLP:journals/tocs/BaumannPH15}, Graphene-SGX~\cite{DBLP:conf/usenix/TsaiPV17} and Panoply \cite{shinde_panoply:_2017} rely on the clock value from  untrusted systems.
+As a result, these systems are vulnerable to time deception attacks~\cite{DBLP:conf/ccs/ChenZRZ17}.
+Blockchain-oriented systems like Town Crier~\cite{DBLP:conf/ccs/ZhangCCJS16} depend on a remote server for a trusted time; however, this clock latency is high (usually hundreds of milliseconds) and uncertain.
 Intel Management Engine (ME) offers a trusted clock service for SGX enclaves, but the time value is coarse-grained (second-resolution) and not absolute at all \cite{intel_psw}.
@@
 Cryptographic libraries such as TaLos~\cite{TaLoS}, mbedTLS-SGX~\cite{mbedtls}, WolfSSL-SGX~\cite{wolfSSL} encounter the same problem as well.
-Additionally, another trusted service named Intel monotonic counters are slow and the NVRAM used by it only supports limited times of writes.
+Additionally, another trusted service named Intel monotonic counters are slow and the NVRAM used by it only supports limited times of writes \cite{DBLP:conf/uss/MateticAKDSGJC17}.
 
@@
 \begin{enumerate}[]
-\item The notion of two types of trusted I/O paths (\autoref{types}) for security-sensitive applications (enclave programs).
+\item The notion of two types of trusted I/O paths: data-provider/-consumer and data-storage/-transmitter (\autoref{types}), for security-sensitive applications (enclave programs).
 \item A novel architecture named \textsc{Aurora} (\autoref{arch}) leveraging two hardware features of Intel processors (SMM and SGX) to provide enclaves trusted paths transparent to untrusted OSes/HVs with a minimal trusted computing base (\autoref{codebase}).
@@
 The enclave can invoke an OCALL to execute a function in the untrusted portion of the application and receive a return value.
-With SGX's remote attestation ability \cite{Anati2013InnovativeTF}, one can gain confidence that the target application is securely running within an enclave.
+SGX provisions remote attestation and local attestation \cite{Anati2013InnovativeTF}.
+With SGX's remote attestation ability, one can gain confidence that the target application is securely running within an enclave.
 Local attestation allows an enclave to prove to one another that it is running on the same processor.
@@
 \subsection{System Management Mode}
-System Management Mode (SMM) is the most privileged mode for handling system-wide functions like power management, hardware control, etc.
-Upon a System Management Interrupt (SMI), the CPU saves the system states and switches to SMM, and then executes a predefined logic (SMI handler) inside system management memory (SMRAM).
-SMRAM is fully transparent to the OS/HV since they are essentially suspended.
-An \textit{RSM} (resume) instruction is executed at the end of the SMI handler to switch back to the protected mode.
-SMRAM is fully isolated by the hardware, any code outside SMRAM cannot access or modify it.
-We deem SMRAM as a special \textit{enclave} in SMM.
+System Management Mode (SMM) \cite{Corporation2016Intel} is the most privileged mode for handling system-wide functions like power management, etc.
+Upon a system management interrupt (SMI), the CPU saves the system context and switches to SMM, and executes a predefined logic (SMI handler) in system management memory (SMRAM).
+We deem SMRAM as a special \textit{enclave}, because SMRAM cannot be accessed by OS/HV after initialization, and therefore protects the confidentiality and integrity of SMI handler.
+An \textit{RSM} (resume) instruction is executed to switch back to the protected mode.
 
 The SMI handler is initialized by UEFI, and  SMRAM can be locked by configuring \emph{D\_OPEN} and \emph{D\_LCK} bits in SMRAM control register.
-Therefore, the SMI handler is safe from corruption after booting.
+Therefore, the SMI handler is safe from tampering after boot.
 Moreover, the SMI handler can access all CPU registers, I/O devices, and physical memory (except for SGX EPCs), and thus we expand the SMI Handler to design \textsc{Aurora}'s SMVisor in \autoref{arch}.
@@
 %% 面向“生产/消费设备”考虑隐私数据的保护，而面向“存储/传输设备”的可信路径用于对攻击检测、预期行为验证等。
-We define the term \emph{trusted I/O paths} in trusted execution environments (TEEs, e.g.
+We define \emph{trusted I/O paths} in trusted execution environments (TEEs, e.g.
 SGX) as follows.
@@
 
-\item \textbf{Trusted I/O paths for data-provider/-consumer devices.}
+\item \textbf{Data-provider/-consumer type.}
 Although SGX provides user-space strong isolation for program end-points (i.e.
@@
 
-\item \textbf{Trusted I/O paths for data-storage/-transmitter devices.} Storage disks and network adapters are typical storage/transmitter devices, and they don't require the stored/transmitted data in plaintext.
-Instead, both kinds of devices can deal with encrypted data without knowing the semantics of the data.
+\item \textbf{Data-storage/-transmitter type.} Storage disks and network adapters are typical storage/transmitter devices.
+Both kinds of devices can deal with encrypted data without knowing the semantics of the data.
 However, both devices need a pile of software stacks (e.g., file system, network protocol) to work correctly and remain compatible.
 Building trusted paths for them is very challenging.
-One possible approach is to decompose existing software stack and port them into the trusted applications, which will greatly swell the TCB and attack vectors.
-As an alternative, \textsc{Aurora} leverages a \emph{distrust but verify} method and reuses existing software stacks in a secure manner.
+One possible approach is to decompose existing software stack and port them into the trusted applications, which will greatly swell the TCB and attack vectors \cite{weiser_sgxio:_2017}.
+As an alternative, \textsc{Aurora} leverages a \emph{verify-then-use} method that reuses existing software stacks in a secure manner (\autoref{driver}).
 
@@
 
+The main difference between these two types is that \textit{data-provider/-consumer} is either the sink or the source of data.
+This type of trusted path must handle data in plaintext, which requires careful isolation or confidential protection.
+The \textit{data-storage/-transmitter} type acts as a medium for data at rest or in transition.
+It focuses on the freshness and integrity of data.
+
 \subsection{Threat Model}
-We consider an adversary who is able to compromise the target system.
-He can directly attack enclave interfaces visible to the OS, and actively reconfigure any devices (e.g., modify a device’s MMIO region, or change the operating mode of a device) and perform arbitrary operations (e.g., trigger interrupts, issue DMA write requests) using any I/O commands.
+We consider an adversary who can compromise the system via software attacks.
+He can directly attack enclave interfaces visible to the OS, and actively reconfigure any devices (e.g., modify MMIO region, or change the operating mode of a device) and perform arbitrary operations (e.g., trigger interrupts, issue DMA write requests) using any I/O commands.
 
@@
 Our assumptions  reduce the TCB on the target host as modern commodity system usually contains a large software stacks (e.g., UEFI, possibly hypervisor, kernel and other applications) when dealing with I/O devices.
-Even though we do not consider physical attacks on devices, side-channel attacks~\cite{chen2019sgxpectre, ridl}, or denial-of-service attacks, we adopt side-channel free cryptographic algorithms and apply an oblivious packet transferring technique (\autoref{enhancement}).
+Physical attacks on devices, side-channel attacks~\cite{chen2019sgxpectre, ridl}, information leakage (I/O size and request/response frequency) and denial-of-service attacks are not considered.
+The adversary cannot access the physical machine and modify its hardware setup.
+%we adopt side-channel free cryptographic algorithms and apply an oblivious packet transferring technique (\autoref{enhancement}).
 
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=0.5\textwidth]{figures/workflow.pdf} %height=0.25\textheight,
+	\caption{The workflow of a trusted I/O path in \textsc{Aurora}. %The white areas denote the TCB.
+	1) An output request is triggered by an enclave as an exception:
+\textcircled{\scriptsize{1}} The user logic in an enclave issues an output request by invoking  Tlibaurora's APIs;
+\textcircled{\scriptsize{2}} Tlibaurora marshals and encrypts the request's arguments, and invokes Ulibaurora outside the enclave to relay the request;
+\textcircled{\scriptsize{3}} Ulibaurora \emph{ioctls} the ashmd module to trigger an \textit{smcall};
+\textcircled{\scriptsize{4}} SMVisor is notified and obtains the encrypted requests from the secure session;
+\textcircled{\scriptsize{5}} SMVisor decrypts the request and invokes the driver;
+\textcircled{\scriptsize{6}} The driver processes output data in PCI space or MMIO buffer;
+\textcircled{\scriptsize{7}} The driver returns a result code to SMVisor. In the end, SMVisor executes \textit{RSM} to return to protected mode. 
+	2) An input request from an enclave causes a device interrupt:
+\textcircled{\scriptsize{1}} The target device triggers an interrupt, and the control flow is rerouted to SMVisor which has the interrupt handler;
+\textcircled{\scriptsize{2}} SMVisor invokes the driver to handle the input request;
+\textcircled{\scriptsize{3}} The driver gets the raw input data and sends it to SMVisor;
+\textcircled{\scriptsize{4}} SMVisor encrypts the data inside SMRAM, and sends it to the target enclave via the secure session;
+\textcircled{\scriptsize{5}} The system switches back to protected mode and the ashmd module uses a signal to notify Ulibaurora;
+\textcircled{\scriptsize{6}} Ulibaurora invokes Tlibaurora to receive the encrypted data;
+\textcircled{\scriptsize{7}} The enclave decrypts the encrypted data and finally obtains the raw input data.
+	}
+	\label{fig:workflow}
+\end{figure}
+
+To help understand the workflow of a trusted path in \textsc{Aurora}, we break down the process of the output path and input path respectively into sequential phases, as illustrated in left and right part of \autoref{fig:workflow}.
+
 %% 和LibOS一样，我们也是要减小对不可信OS的依赖，我们甚至没有和OS交互的数据流接口，只有中断对其是不透明的。
@@
 
+\iffalse
+
 \subsection{Workflow}\label{workflow}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\textwidth]{figures/workflow.pdf} %height=0.25\textheight,
-	\caption{The workflow of a trusted I/O path in \textsc{Aurora}. }%The white areas denote the TCB.
-	\label{fig:workflow}
-\end{figure}
-
-To help understand the workflow of a trusted path in \textsc{Aurora}, we break down the process of the output path and input path respectively into sequential phases, as illustrated in left and right part of \autoref{fig:workflow}.
 
@@
 ~~\textcircled{\footnotesize{7}} The enclave decrypts the encrypted data and finally obtains the raw input data. % from the secure session.
+\fi
 
@@
 If the process is tampered with, the PCR value will differ.
-
 In order to ease SMVisor attestation, we use the launch enclave provided by the Intel SGX Platform Software to attest SMVisor for one-time effort.
-Afterward, any application enclave running on the same machine can query the launch enclave to know if SMVisor attestation has succeeded.
+Afterwards, any application enclave running on the same machine can query the launch enclave to know if SMVisor attestation has succeeded.
 To attest  SMVisor, the launch enclave needs to verify the PCR value by requesting a TPM quote, which includes a cryptographic signature over the PCR value alongside with a fresh nonce.
@@
 
-\textbf{Disconnection.}
+\textbf{Termination.}
 %% 和进程退出释放资源一样，我们这个并不老是影响系统
@@
 
-\subsection{Enhancement and Optimization}\label{enhancement}
+\subsection{Security Enhancement and Performance Optimization}\label{enhancement}
 To provide better security and performance, \textsc{Aurora} introduces \textit{hardware encryption}, \textit{data obliviousness} and \textit{batch mechanism for smcalls}.
@@
 Intel extends x86 ISA with AES-NI and claims to prevent known side-channel attacks.
-We make use of it to address the same concern and use a constant-time algorithm to defeat cache timing attacks.
-This hardware acceleration also decreases the preemption time in SMM.
+We make use of it to address the same concern and use a constant-time AES-128-GCM algorithm to defeat cache timing attacks.
+Nonces are used for replay proof.
+This hardware accelerated encryption also decreases the preemption time in SMM.
 
@@
 To prevent such secrecy leakage, \textsc{Aurora} pads all messages with random values to the same length (4KB, same size as one EPC page), which restricts possible information leakage at page-level.
-%The message buffers must start with page-aligned address.
+The maximum length of a message is 4080 Bytes, leaving at least 16 bytes for random padding.%The message buffers must start with page-aligned address.
 
@@
 For example, a malware might present a fake login interface that prompts a user to enter her password.
-To mitigate this threat, we leverage PC speaker to indicate that the trusted path has been established.
+To mitigate this threat, we leverage the PC speaker to indicate that the trusted path has been established.
 When the system first boots, the network is disabled by the SMVisor, and we assume that the loaded kernel is clean due to TPM's measure boot.
-\textsc{Aurora} asks the user to store a short, arbitrary MIDI-format melody (around 5 seconds) inside SMRAM via a config enclave, so that every time when a trusted path is set up, the PC speaker will play the melody.
-Then the network is enabled by the SMVisor.
-Since the melody is a pre-shared secret only between the SMVisor and the user, it is impossible for the adversary to learn and mimic the process.
+\textsc{Aurora} asks the user to store a short, arbitrary MIDI-format melody (around 5 seconds) inside SMRAM via a config enclave, so that every time when a trusted path is set up, the PC speaker will play the melody, and then the network is enabled by the SMVisor.
+Since the melody is a pre-shared secret only known by SMVisor and the user, it is impossible for the adversary to learn and mimic this process.
 % Tlibaurora first generates a random integer $N$ in the interval of [1, 10], and displays the integer number in the screen as a captcha.
@@
 As the packets are usually held with printer-specific format, SMVisor issues the corresponding serial port driver and adds this job into its task queue.
-Afterward, SMVisor returns the status code from the printer devices to the enclave end-point.
+Afterwards, SMVisor returns the status code from the printer devices to the enclave end-point.
 
 \subsection{Trusted Hardware Clock}\label{time service}
-For the clock, its integrity and non-forgeability are much more vital than confidentiality.
-%Using a trusted clock source, one is able to create trusted timestamps.
-This is especially significant in a financial transaction (e.g.
-blockchain) and secure network (e.g.
-TLS authentication).
-In this section, we describe how to extend \textsc{Aurora} for trusted, high-resolution absolute clock.
-%by accessing multiple sources of hardware timers and detecting possible attacks.
-%The clock does not need to protect its confidentiality.
-Instead,
+The integrity and non-forgeability of the clock value is much more vital. In this section, we describe how to extend \textsc{Aurora} for trusted, high-resolution, absolute and attack-aware clock.
 
@@
 We use a dedicated counting thread \cite{DBLP:conf/dimva/SchwarzWGMM17} guarded inside an enclave occupying a logical thread on the same CPU core.
-Such a sibling thread will block the possibility of side-channel attacks when hyper-threading is active.
+Such a sibling thread will block the possibility of side-channel attacks when hyper-threading is active \cite{DBLP:conf/sp/ChenWCCZWLL18}.
 The counting thread provides $dT$ and the difference of hardware timers provides $dt$, we use first-order derivative $dt/dT$ to detect the possible time attack.
@@
 If the slope changes much, we assume an attack.
+
+Aurora's trusted hardware clock is immune to the TOCTOU attack because it leverages SMM which guarantees that the operation of check and use are atomically performed.
 
@@
 It is a serious issue when secure data storage is  necessary for ensuring correct operation (e.g., secure logging, APT monitoring and compliance).
-In this section, we extend \textsc{Aurora} to support secure USB disk.
-Note that \textsc{Aurora}'s approach is also suitable and easy to support for other storage systems.
+We extend \textsc{Aurora} to support secure USB massive storage devices.
+Note that \textsc{Aurora}'s approach is also suitable and easy to support for other storage systems such as SATA HDD, NVMe SSD, etc.
 
@@
 %The IRQ number of the device is acquired by ashmd module and then notified from ashmd to the underlying SMVisor. 
-When an enclave issues a request for a USB disk, SMVisor leverages I/O interrupt rerouting mechanism to monitor and deal with every operation of the USB device, including transferring data and control commands via a secure session in \textsc{Aurora}.
+When an enclave issues a request for a USB storage device, SMVisor leverages I/O interrupt rerouting mechanism to monitor and deal with every operation of the USB device, including transferring data and control commands via a secure session in \textsc{Aurora}.
 In Linux, the data is by default transferred using bulk mode and is exchanged based on DMA mechanism, which stores the DMA address and buffers location in a {scatter-gather} list.
@@
 %% 强调TCB小
-\subsection{Code Base and Binary Size}\label{codebase}
+\subsection{Trusted Computing Base}\label{codebase}
 %% 说明移植的轻松程度，强调运行时占据物理内存的少
@@
 \textsc{Aurora}'s trusted components (i.e., SMVisor, ashmd, Tlibaurora, Cryptography) have 3393 lines of C code, and untrusted component (i.e., Ulibaurora) has 273 lines of C code.
-Compared to Wimpy kernel \cite{zhou_dancing_2014} which has 16K lines of code, it is smaller and simpler enough to facilitate formal verification.
-Both SMRAM and EPC RAM are scarce memory resource.
-For instance, the system-wide EPC limit is approximately 93MB and the SMRAM is 4MB by default on our platform.
-We measure the final size of the resulted stripped binary images.
+%Compared to Wimpy kernel \cite{zhou_dancing_2014} which has 16K lines of code, it is smaller and simpler enough to facilitate formal verification.
+To avoid exploitable vulnerabilities, we use static analysis tools, e.g., Clang Static Analyzer\footnote{http://clang-analyzer.llvm.org/index.html}, over \textsc{Aurora}'s code base and fix all found bugs.
+Besides, as \textsc{Aurora} is quite small and its complexity is obviously lower than that of the formally verified microkernel~\cite{DBLP:conf/sosp/KleinEHACDEEKNSTW09}, we believe it is reasonable to put \textsc{Aurora} within reach of formal verification.
+
+On our platform, the system-wide EPC limit is approximately 93MB and the SMRAM is 4MB by default.
+Both are scarce memory resource.
+We therefore measure the final size of the resulted stripped binary images.
 Our modification on CoreBoot only adds 3.9\% on its total size (120.2KB V.S.
@@
 Smaller codebase denotes smaller TCB introduced.
-
-\subsection{Code Quality}
-To avoid exploitable vulnerabilities, we use several well known static analysis tools, e.g., Clang Static Analyzer\footnote{http://clang-analyzer.llvm.org/index.html}, over \textsc{Aurora}'s code base and fix all found bugs.
-Besides, as \textsc{Aurora} is quite small and its complexity is obviously lower than that of the formally verified microkernel~\cite{DBLP:conf/sosp/KleinEHACDEEKNSTW09}, we believe it is reasonable to put \textsc{Aurora} within reach of formal verification.
 
@@
 
-\begin{table}
+\begin{table}[t]
 	\centering
@@
 In our current setting, we allow an enclave to request up 10,000 times per second, which introduces about 11\% overhead to the system.
+
+\begin{table}[t]
+	\centering
+	\caption{Serial-port benchmark comparison between Linux and \textsc{Aurora}.}
+	\label{table:serial}
+	\small
+	\begin{tabular}{lrrr}
+		\toprule
+		\textbf{Payload Size(KB)} & \textbf{Linux(s)} & \textbf{Aurora(s)} & \textbf{Speedup(\%)} \\
+		\midrule
+		4 & 0.03 & 0.03 & 0.0 \\
+		64 & 0.32 & 0.24 & 25.0 \\
+		256 & 1.08 & 0.87 & 19.4 \\
+		1024 & 3.95 & 3.43 & 13.2 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\begin{table}[t]	
+	\centering
+	\caption{Storage throughput comparison between Linux and \textsc{Aurora}.}
+	\label{table:dd}
+	\small
+	\begin{tabular}{lllr}
+		\toprule
+		\multirow{2}{*}{\textbf{Payload Size(MB)}} & \textbf{Linux} & \textbf{Aurora} & \textbf{Slowdown} \\ 
+		& \textbf{(MB/s)} & \textbf{(MB/s)} & \textbf{(\%)} \\
+		\midrule
+		4 & 32.9 & 31.8 & 3.3 \\
+		64 & 40.9 & 39.2 & 4.2 \\
+		256 & 42.7 & 40.4 & 5.3 \\
+		1024 & 53.2 & 47.5 & 10.7 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\subsection{Security Effectiveness}\label{security}
+We evaluate \textsc{Aurora}'s reliability with several security tests.
+\\
+\textbf{Keylogging Attack.}
+To evaluate the effectiveness of \textsc{Aurora}'s trusted input path, we deployed multiple spyware to get a user's inputs under trusted input mode, including a stealthy root keylogger\footnote{https://github.com/vim2meta/keylogger}, a rootless X11-based keylogger ixkeylog\footnote{https://github.com/dorneanu/ixkeylog}, a kernel-level rootkit keylogger\footnote{https://github.com/arunpn123/keylogger}, and a remote keylogger\footnote{https://github.com/EinBaum/Totally-Not-A-Virus}.
+None of them can obtain the user's inputs.
+\\
+\textbf{Output Corruption Attack.}
+We leveraged a DMA-based NIC device to launch output corruption attack when using Aurora's trusted serial printer service.
+Since  SMRAM and EPC RAM are strongly isolated by architectural protections, only meaningless content (0xFF) is obtained.
+No secrets are leaked.
+We then conducted another DMA attack to corrupt SMM drivers outside of SMRAM.
+SMVisor detected its integrity tampered  and rejected subsequent requests, then notified the enclave application.
+Moreover, we conducted another DMA attack to corrupt the content of shared memory of the secure session.
+Both SMVisor and Tlibaurora can verify the broken MAC and restart a new session.
+\\
+\textbf{Time Deception Attack.}
+To evaluate the trusted clock, we intentionally modified the RTC when an enclave issued a request for trusted clock.
+Tlibaurora detected the attacks successfully and indicated a failure.
+For instance, \texttt{gettimeofday()} returns -1 and sets the global variable \textit{errno} appropriately.
+Existing C library specification does not have a flag indicating time attacks, the enclave logic may keep requesting until obtaining a valid time value.
+We support failure handling in Tlibaurora to help enclaves deal with such situations.
+\\
+\textbf{Storage Deception Attack.}
+We modified the kernel driver of SCSI device and randomly dropped several disk I/O requests intentionally.
+SMVisor detected such accidental conditions and notified the Tlibaurora of corresponding enclave.
+In our current setting, the Tlibaurora will automatically try issuing the lost I/O requests three times so as to avoid storage failure.
+In our experiments, the enclave finally received the attack warning from the Tlibaurora and logged these events for further forensic analysis.
+
+\iftrue
+
+\begin{table*}[t]
+	\centering
+	\caption{Comparison of existing clock services that can be used for SGX enclaves.
+Clock services include network time protocol (NTP), precision time protocol (PTP), and the platform software (PSW) supported by Intel management engine (ME), monotonic counter supported by Byzantine Fault Tolerance (BFT) protocol.}
+	\label{table:timeservice}
+	\small
+	\begin{tabular}{lllcrccr}
+		\toprule
+		\textbf{Clock Provider} & \textbf{Approach} & \textbf{Type} & \textbf{Resolution} & \textbf{Request Cost} & \textbf{Latency} & \textbf{Security} & \textbf{Use Cases} \\
+		\midrule
+		Remote Clock & NTP/PTP & absolute & 1s & $>$100ms & high & trusted & Town Crier~\cite{DBLP:conf/ccs/ZhangCCJS16} \\
+		Intel ME & PSW & relative & 1s & 10.3ms & medium & trusted & SGX-Tor~\cite{DBLP:conf/nsdi/KimHHKH17} \\
+		OS Kernel & OCALL & absolute & 1ns & 6us & low & untrusted & Panoply~\cite{shinde_panoply:_2017} \\
+		Distributed Network & BFT & N/A & N/A & 1--2ms & medium & trusted & ROTE~\cite{DBLP:conf/uss/MateticAKDSGJC17} \\
+		Hardware Clock & \textit{smcall} & absolute & 1ns & 69us & low & trusted & Aurora-OpenSSL~\ref{openssl} \\
+		\bottomrule
+	\end{tabular}
+\end{table*}
 
@@
 
-\begin{table*}[t]
-	\centering
-	\caption{Comparison of existing clock services that can be used for SGX enclaves.
-Clock services include network time protocol (NTP), precision time protocol (PTP), and the platform software (PSW) supported by Intel management engine (ME)}
-	\label{table:timeservice}
-	\small
-	\begin{tabular}{lllcrccr}
-		\toprule
-		\textbf{Clock Provider} & \textbf{Approach} & \textbf{Type} & \textbf{Resolution} & \textbf{Request Cost} & \textbf{Latency} & \textbf{Security} & \textbf{Use Cases} \\
-		\midrule
-		Remote Clock & NTP/PTP & absolute & 1s & $>$100ms & high & trusted & Town Crier~\cite{DBLP:conf/ccs/ZhangCCJS16} \\
-		Intel ME & PSW & relative & 1s & 10.3ms & medium & trusted & SGX-Tor~\cite{DBLP:conf/nsdi/KimHHKH17} \\
-		OS Kernel & OCALL & absolute & 1ns & 6us & low & untrusted & Panoply~\cite{shinde_panoply:_2017} \\
-		Hardware Clock & \textit{smcall} & absolute & 1ns & 69us & low & trusted & Aurora-OpenSSL~\ref{openssl} \\
-		\bottomrule
-	\end{tabular}
-\end{table*}
-
-\subsection{Trusted Clock Benchmark}\label{time_bench}
-
-%It is important to quantify how much time is required to attain a trusted clock service since the potential service latency impacts the freshness of message and indicates the response speed. 
-For this experiment, we measured the complete trusted clock procedure for 1,000 times and used the average value.
-Table \ref{table:breaktime} shows the time cost for each step in a trusted clock path, as explained in \autoref{workflow}.
-We can see that the clock service takes most of the time.
-This is because 1) the RTC driver has to read clock value twice to check if the clock is updating its time data; 2) The RTC involves several \texttt{INS} instructions to read each field of a calendar time, and costs 14us to obtain a complete wall-clock time in one request; 3) The other 4 timers cost roughly 10us in sum.
-The total  time cost (84us) satisfies the requirement of real-world trusted timestamps.
-
-For comparison, we measured the performance of other clock providers.
-The results are shown in \autoref{table:timeservice}.
-Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks such as the timing attacks.
-Among existing approaches, \textsc{Aurora} outperforms remote clock (the 2nd row) and Intel's reference clock (the 3rd row) by introducing very low latency, while achieving the same resolution (nanosecond-level) as OS services (the 4th row).
-%Note that any approach can be arbitrarily delayed in that the untrusted OS is in charge of the enclave thread scheduling. We treat intentionally time delay as a form of Denial-of-Service attack.
+\fi
 
@@
 \subsection{Serial Port Output Benchmark}
-
-\begin{table}[t]
-	\centering
-	\caption{Serial-port benchmark comparison between Linux and \textsc{Aurora}.}
-	\label{table:serial}
-	\small
-	\begin{tabular}{lrrr}
-		\toprule
-		\textbf{Payload Size(KB)} & \textbf{Linux(s)} & \textbf{Aurora(s)} & \textbf{Speedup(\%)} \\
-		\midrule
-		4 & 0.03 & 0.03 & 0.0 \\
-		64 & 0.32 & 0.24 & 25.0 \\
-		256 & 1.08 & 0.87 & 19.4 \\
-		1024 & 3.95 & 3.43 & 13.2 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
 
@@
 
-\begin{table}[t]	
-	\centering
-	\caption{Storage throughput comparison between Linux and \textsc{Aurora}.}
-	\label{table:dd}
-	\small
-	\begin{tabular}{lllr}
-		\toprule
-		\multirow{2}{*}{\textbf{Payload Size(MB)}} & \textbf{Linux} & \textbf{Aurora} & \textbf{Slowdown} \\ 
-		& \textbf{(MB/s)} & \textbf{(MB/s)} & \textbf{(\%)} \\
-		\midrule
-		4 & 32.9 & 31.8 & 3.3 \\
-		64 & 40.9 & 39.2 & 4.2 \\
-		256 & 42.7 & 40.4 & 5.3 \\
-		1024 & 53.2 & 47.5 & 10.7 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
 To compare the overhead introduced when applying \textsc{Aurora}'s trusted I/O path on USB storage devices, we wrote variable sizes of contents to a USB storage device on native Linux system as the baseline, by using \texttt{dd} program with options \texttt{fsync} and \texttt{direct}.
@@
 
-\subsection{Security Effectiveness}\label{security}
-In this section, we evaluate \textsc{Aurora}'s reliability with several security tests.
-
-\textbf{Keylogging Attack.}
-To evaluate the effectiveness of \textsc{Aurora}'s trusted input path, we deployed multiple spyware to get a user's inputs under trusted input mode, including a stealthy root keylogger\footnote{https://github.com/vim2meta/keylogger}, a rootless X11-based keylogger ixkeylog\footnote{https://github.com/dorneanu/ixkeylog}, a kernel-level rootkit keylogger\footnote{https://github.com/arunpn123/keylogger}, and a remote keylogger\footnote{https://github.com/EinBaum/Totally-Not-A-Virus}.
-None of them can obtain the user's inputs.
-
-\textbf{Output Corruption Attack.}
-We leveraged a DMA-based NIC device to launch output corruption attack when using Aurora's trusted serial printer service.
-Since  SMRAM and EPC RAM are strongly isolated by architectural protections, only meaningless content (0xFF) is obtained.
-Therefore no secrets are leaked.
-We then conducted another DMA attack to corrupt SMM drivers outside of SMRAM.
-SMVisor detected its integrity tampered  and rejected subsequent requests, then notified the enclave application.
-Moreover, we conducted another DMA attack to corrupt the content of shared memory of the secure session.
-Both SMVisor and Tlibaurora can verify the broken MAC and restart a new session.
-
-\textbf{Time Deception Attack.}
-To evaluate \textsc{Aurora}’s trusted clock, we intentionally modified the RTC when an enclave issued a request for trusted clock.
-Tlibaurora detected the attacks successfully and indicated a failure.
-For instance, \texttt{gettimeofday()} returns -1 and sets the global variable \textit{errno} appropriately.
-Existing C library specification does not have a flag indicating time attacks, the enclave logic may keep requesting until obtaining a valid time value.
-We support failure handling in Tlibaurora to help enclaves deal with such situations.
-
-\textbf{Storage Deception Attack.}
-We modified the kernel driver of SCSI device and randomly dropped several disk I/O requests intentionally.
-SMVisor detected such accidental conditions and notified the Tlibaurora of corresponding enclave.
-In our current setting, the Tlibaurora will automatically try issuing the lost I/O requests three times so as to avoid storage failure.
-In our experiments, the enclave finally received the attack warning from the Tlibaurora and logged these events for further forensic analysis.
+\subsection{Trusted Clock Benchmark}\label{time_bench}
+
+%It is important to quantify how much time is required to attain a trusted clock service since the potential service latency impacts the freshness of message and indicates the response speed. 
+For this experiment, we measured the complete trusted clock procedure for 1,000 times and used the average value.
+Table \ref{table:breaktime} shows the time cost for each step in a trusted clock path.
+We can see that the clock service takes most of the time.
+This is because 1) the RTC driver has to read clock value twice to check if the clock is updating its time data; 2) The RTC involves several \texttt{INS} instructions to read each field of a calendar time, and costs 14us to obtain a complete wall-clock time in one request; 3) The other 4 timers cost roughly 10us in sum.
+The total  time cost (84us) satisfies the requirement of real-world trusted timestamps.
+
+For comparison, we measured the performance of other clock providers.
+The results are shown in \autoref{table:timeservice}.
+Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks such as the timing attacks.
+Among existing approaches, \textsc{Aurora} outperforms remote clock (the 2nd row) and Intel's reference clock (the 3rd row) by introducing very low latency, while achieving the same resolution (nanosecond-level) as OS services (the 4th row).
+%Note that any approach can be arbitrarily delayed in that the untrusted OS is in charge of the enclave thread scheduling. We treat intentionally time delay as a form of Denial-of-Service attack.
 
@@
 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=0.4\textwidth]{figures/ssh.pdf} %height=0.16\textheight,width=0.6\textwidth
-	\caption{Aurora-OpenSSH with trusted input path.}
-	\label{fig:openssh}
-\end{figure}
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=0.4\textwidth]{figures/ssh.pdf} %height=0.16\textheight,width=0.6\textwidth
+%	\caption{Aurora-OpenSSH with trusted input path.}
+%	\label{fig:openssh}
+%\end{figure}
 
@@
 Specifically, we ported passphrase related logic into an enclave, and used \textsc{Aurora}'s \textit{trusted input path} to get passwords which users input.
-We call the enhanced client as Aurora-OpenSSH client, as depicted in \autoref{fig:openssh}.
+We call the enhanced client as Aurora-OpenSSH client.
+%, as depicted in \autoref{fig:openssh}.
 
@@
 For instance, both \emph{ClientHello} and \emph{ServerHello} messages use the system time to prevent replay attacks.
-If the time is emulated by an untrusted source, it may %increase the collision probability of \emph{random} and
-compromise the security of OpenSSL sessions.
+If the time is emulated by an untrusted source, it may compromise the security of OpenSSL sessions.
 
@@
 As shown in \autoref{table:openssl}, in our LAN setting, Aurora-OpenSSL introduced about 32\% latency in certificate generation and 21\% in the TLS handshaking because both of them use \textsc{Aurora}'s trusted clock.
-We anticipate the overhead ratio decreased in WAN environment.
-
-\begin{table}[t]
-	\centering
-	\caption{Performance comparison between native SGX-OpenSSL and Aurora-OpenSSL.}
-	\label{table:openssl}
-	\small
-	\begin{tabular}{lrr}
-		\toprule
-		& \textbf{SGX-OpenSSL} & \textbf{Aurora-OpenSSL} \\
-		\midrule
-		{Certificate Generation} & 77.4ms & 102.5ms \\
-		{TLS Handshaking} & 2.8ms & 3.4ms \\
-		\bottomrule
-	\end{tabular}
-\end{table}
+We anticipate the overhead ratio to decrease in a WAN environment because of the larger delays of a geographically distributed public network.
 
@@
 
-\subsection{Secure SQLite Database}
-Databases are widely used to store financial transaction records and other sensitive information.
-Some databases are built upon block devices, while maintaining its own caching mechanisms and storage policies without support of OS's file system, e.g.
-SQLite database.
-
-We integrated \textsc{Aurora}'s Tlibaurora into existing SGX-SQLite projects\footnote{https://github.com/yerzhan7/SGX\_SQLite} and added code to support standard file system calls such as \textit{open}, \textit{read}, \textit{write}, \textit{stat}, \textit{lstat}, \textit{fstat}, \textit{fsync}, \textit{fcntl}, \textit{ftruncate} and \textit{unlink}.
-We then eliminated the file-related OCALLs from the untrusted system.
-To protect the data, Tlibaurora's shim layer uses a symmetric key derived from user password and in-enclave nonces to encrypt the file payloads. %, and computes MAC values for blocks. 
-To avoid password leak, we use \textsc{Aurora}'s trusted input path to obtain users' passwords from keyboard devices.
-Moreover, \textsc{Aurora}'s secure session protects the confidentiality and integrity of data between SQLite enclaves and SMVisor.
-When SQLite invokes Tlibaurora file APIs, it opens the USB storage device in direct I/O mode and reads/writes data using 4KB block size. 
-Finally, %to directly measure the overhead introduced by \textsc{Aurora}'s infrastructure, 
-we set the synchronize flag to \texttt{FULL} to avoid the uncertainty of I/O caching.
-
-\begin{table}	
+\begin{table}[t]
+	\centering
+	\caption{Performance comparison between native SGX-OpenSSL and Aurora-OpenSSL.}
+	\label{table:openssl}
+	\small
+	\scalebox{0.8}{
+	\begin{tabular}{lrrr}
+		\toprule
+		& \textbf{SGX-OpenSSL} & \textbf{Aurora-OpenSSL} & \textbf{Slowdown(\%)}\\
+		\midrule
+		{Certificate Generation} & 77.4ms & 102.5ms & 32.4\\
+		{TLS Handshaking} & 2.8ms & 3.4ms & 21.4 \\
+		\bottomrule
+	\end{tabular}}
+\end{table}
+
+\begin{table}[t]
 	\centering
@@
 
+\subsection{Secure SQLite Database}
+Databases are widely used to store financial transaction records and other sensitive information.
+Some databases are built upon block devices, while maintaining its own caching mechanisms and storage policies without support of OS's file system, e.g.
+SQLite database.
+
+We integrated \textsc{Aurora}'s Tlibaurora into existing SGX-SQLite projects\footnote{https://github.com/yerzhan7/SGX\_SQLite} and added code to support standard file system calls such as \textit{open}, \textit{read}, \textit{write}, \textit{stat}, \textit{lstat}, \textit{fstat}, \textit{fsync}, \textit{fcntl}, \textit{ftruncate} and \textit{unlink}.
+We then eliminated the file-related OCALLs from the untrusted system.
+To protect the data, Tlibaurora's shim layer uses a symmetric key derived from user password and in-enclave nonces to encrypt the file payloads. %, and computes MAC values for blocks. 
+To avoid password leak, we use \textsc{Aurora}'s trusted input path to obtain users' passwords from keyboard devices.
+Moreover, \textsc{Aurora}'s secure session protects the confidentiality and integrity of data between SQLite enclaves and SMVisor.
+When SQLite invokes Tlibaurora file APIs, it opens the USB storage device in direct I/O mode and reads/writes data using 4KB block size. 
+Finally, %to directly measure the overhead introduced by \textsc{Aurora}'s infrastructure, 
+we set the synchronize flag to \texttt{FULL} to avoid the uncertainty of I/O caching.
+
 We evaluated the enhanced SQLite performance by running standardized TPC-H benchmark\footnote{http://www.tpc.org/tpch/} over a large database. % (around 1.3GB).
 We make minor changes to these benchmark queries in order to make them possible to be executed in SQLite.
-Unfortunately, not all queries can be executed due to the experiment environment and system configration.
+Unfortunately, not all queries can be executed due to the partial porting of the original project.
+These queries include \textit{select from, order by, group by}.
 %In our experiment, the native insertion transactions for 1000 times cost 17.3 seconds while the ones with \textsc{Aurora}'s trusted path cost 20.5 seconds.
 About 18\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.
-\autoref{table:tpch} shows the successfully executed queries and their results of native SGX-SQLite and \textsc{Aurora}-SGLite respectively.
+\autoref{table:tpch} shows the completed queries and their results of native SGX-SQLite and \textsc{Aurora}-SGLite respectively.
 In our experiments, no more than 10.08\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.
@@
 
-SGXIO~\cite{weiser_sgxio:_2017} is a conceptual framework that discusses how to provide trusted generic I/O paths for SGX enclaves.
-It introduces a trusted hypervisor to assist the establishment of the trusted path and requires users to port drivers into enclaves.
+SGXIO~\cite{weiser_sgxio:_2017} discusses how to provide trusted generic I/O paths for SGX enclaves.
+It introduces a trusted hypervisor to assist the establishment of the trusted path, and requires users to port drivers into enclaves.
 However, SGXIO is a conceptual design without any implementation and evaluation.
-Moreover, it is hard for users to port commodity drivers into an enclave because 1) enclave mode does not support privileged instructions like \texttt{IN/OUT} or \texttt{RDMSR/WRMSR} with which drivers read/write I/O ports; 2) it is unclear in the paper \cite{weiser_sgxio:_2017} how to correctly partition drivers.
-In comparison, \textsc{Aurora}'s drivers are invoked in SMM without any instruction restricted.
-They are monitored and regulated by SMVisor protected inside SMRAM.
-This reusing technique allows \textsc{Aurora} easily deployed.
-
-Zhou et al.~\cite{zhou_dancing_2014} introduce a micro-hypervisor (named Wimpy) under OS to build trusted paths (TP) between program end-points (PE) and device end-points (DE).
-They require the PE of a TP includes the device drivers for DEs associated with the TP, and admit that \textit{"running the PE in Ring 3 makes DE driver porting more difficult"}.
-Although \textsc{Aurora} and Wimpy share many common security goals, e.g.
-interrupt isolation and MMIO protection, \textsc{Aurora} exploits CPU features to protect the PEs and reuse DEs securely.
-As a result, \textsc{Aurora} has smaller TCB than Wimpy.
-
-Intel SGX platform services (PSW)~\cite{intel_psw} uses management engines (ME) to provide trusted time and monotonic counters services by running a co-processor with integrated NIC, RTC and SPI flash, etc.
-It brings separated hardware that cannot be controlled by untrusted system.
-However, since Intel ME runs simultaneously with the main CPUs, we believe that it is difficult and insecure for Intel ME to implement secure human-interface input for enclaves as \textsc{Aurora} does.
-Because the CPU controlled by untrusted OS and the ME co-processor controlled by trusted software may race a DMA access  to the keyboard buffer, which cannot guarantee protection on user's confidential input.
-In comparison, \textsc{Aurora}'s SMVisor in nature preempts the untrusted OS.
+It is hard for users to port commodity drivers into an enclave because 1) enclave mode does not support privileged instructions; 2) it is unclear how to partition drivers.
+In contrast, \textsc{Aurora}'s drivers are invoked in SMM with no instruction restricted.
+Drivers are regulated by SMVisor protected inside SMRAM.
+This reusing technique allows \textsc{Aurora} to be deployed easily.
+
+Zhou et al.~\cite{zhou_dancing_2014} introduce a microhypervisor named Wimpy to build trusted paths between a program  and a device.
+This work requires the program to contain the driver associated with the device.
+It admittedly claimed that running drivers in user model (Ring 3) is difficult.
+\textsc{Aurora} and Wimpy share many common security goals, e.g.
+interrupt isolation and MMIO protection.
+\textsc{Aurora} has smaller TCB than Wimpy.
+
+Intel platform services (PSW)~\cite{intel_psw} provisions trusted time and monotonic counters by running a coprocessor (Intel Management Engines).
+It brings separated hardware (e.g., NIC, RTC and SPI flash) that cannot be controlled by untrusted host system.
+However, since Intel ME runs concurrently with host CPUs, it is difficult and insecure to implement secure human-interface inputs as \textsc{Aurora} does; the host CPUs controlled by untrusted OS and the ME coprocessor controlled by trusted firmware will race a DMA access to the keyboard buffer, which may corrupt or leak user's confidential input.
+By contrast, \textsc{Aurora}'s SMVisor in nature preempts the untrusted OS.
 
@@
 % and it protects SMM supervisor inside SMRAM and use mutual authentication to ensure its authenticity.
-Jiang~\cite{Jang2017Building} builds a trusted path between a USB proxy device and an enclave.
+Jang~\cite{Jang2017Building} builds a trusted path between a USB proxy device and an enclave.
 The proxy device uses LED display for user verification.

### 2019-08-24 article.tex
full paper review

@@
 
-\title{Establishing Trusted I/O Paths for \\ Client Shielded Executions with Aurora}
+\title{Establishing Trusted I/O Paths for Client \\ Shielded Executions with Aurora}
 
@@
 
-Nowadays, users' sensitive data in edge computing devices (desktops, laptops, and tablets, etc.) is at high risk because they run applications on potentially compromised or malicious systems.
+Today users' private data in edge computing devices (desktops, laptops, and tablets, etc.) is at high risk because they run applications on potentially compromised or malicious systems.
 To address this problem, hardware vendors propose Trusted Execution Environment (TEE).
@@
 We call this particular SMI handler \textit{SMVisor}.
-In hardware, SMVisor is safe from any corruptions by other privileged software (including OS and hypervisor).
-Therefore, Intel SGX enclaves can safely use I/O devices while remaining \textit{transparent} to the underlying OS.
+In hardware, SMVisor is safe from any corruptions by other privileged software.
+Therefore, Intel SGX enclaves can safely use I/O devices while remaining \textit{transparent} to the underlying OS and hypervisor.
 
@@
 
-\subsection{Threat Model}
+\subsection{Threat Model and Assumptions}
 We consider an adversary who can compromise the system via software attacks.
@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{figures/workflow.pdf} %height=0.25\textheight,
+	\includegraphics[width=0.49\textwidth]{figures/workflow.pdf} %height=0.25\textheight,
 	\caption{The workflow of a trusted I/O path in \textsc{Aurora}. %The white areas denote the TCB.
@@
 
+To help understand the workflow of a trusted path in \textsc{Aurora}, we break down the process of the output path and input path respectively into sequential phases, as illustrated in left and right part of \autoref{fig:workflow}.
+
 An output request is triggered by an enclave as an exception, as depicted as follows:\\
@@
 \subsection{Trusted Hardware Clock}\label{time service}
-The integrity and non-forgeability of the clock value is much more vital. In this section, we describe how to extend \textsc{Aurora} for trusted, high-resolution, absolute and attack-aware clock.
-
-\textbf{Multiple Sources.}
-%% 多源头获取时间，适应不同需求
-\textsc{Aurora} uses multiple clock sources available on x86 platforms, such as programmable interval timer (PIT) and advanced configuration and power interface/power management (ACPI/PM) timer.
-To estimate the latency of obtaining time from hardware and adjust their values, SMVisor references invariant time stamp counter (TSC) via \textit{RDTSCP} instruction.
-The invariant TSC ensures that the duration of each clock tick is uniform (at the frequency relative to the crystal clock frequency of the processor core).
+The integrity and non-forgeability of the clock value is much more vital. In this section, we describe how to extend \textsc{Aurora} for trusted, absolute, high-resolution and attack-aware clock.
+
+%\textbf{Diverse Sources.}
+%%% 多源头获取时间，适应不同需求
+%\textsc{Aurora} uses multiple clock sources available on x86 platforms, such as programmable interval timer (PIT) and advanced configuration and power interface/power management (ACPI/PM) timer.
 
@@
 When a time value with high resolution (e.g.
-micro-second) is required, \textsc{Aurora} uses the invariant TSC and High Precision Event Timer (HPET) to satisfy the need.
+micro-second) is required, \textsc{Aurora} uses invariant time stamp counter (TSC) and High Precision Event Timer (HPET).
 For instance, \textsc{Aurora} uses the following formulae to compute the \textit{tv\_usec} value in \textit{timeval} data structure: {$tv\_usec = (HPET\_value/ HPET\_Hz) / 1,000,000$;} where $(HPET\_value / HPET\_Hz)$ computes the absolute time in micro-seconds.
+SMVisor references invariant TSC to estimate the latency of hardware response and adjust the value.
+Invariant TSC ensures that the duration of each clock tick is uniform.
 
@@
 %% 如何避免时钟攻击
-Though the hardware clocks can be controlled and modified by the malicious OS, diverse timers in Aurora offer enclaves the ability to validate the credibility of time values.
+Though hardware clocks can be controlled and modified by the malicious OS, diverse timers in Aurora offer enclaves the ability to validate the credibility of time values.
 Tlibaurora records last values read from all hardware clocks and obtains current values to calculate their differences respectively, and then uses clock frequencies to compute the actual elapsed time.
@@
 In our current setting, we allow an enclave to request up 10,000 times per second, which introduces about 11\% overhead to the system.
-
-\begin{table}[t]
-	\centering
-	\caption{Serial-port benchmark comparison between Linux and \textsc{Aurora}.}
-	\label{table:serial}
-	\small
-	\begin{tabular}{lrrr}
-		\toprule
-		\textbf{Payload Size(KB)} & \textbf{Linux(s)} & \textbf{Aurora(s)} & \textbf{Speedup(\%)} \\
-		\midrule
-		4 & 0.03 & 0.03 & 0.0 \\
-		64 & 0.32 & 0.24 & 25.0 \\
-		256 & 1.08 & 0.87 & 19.4 \\
-		1024 & 3.95 & 3.43 & 13.2 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}[t]	
-	\centering
-	\caption{Storage throughput comparison between Linux and \textsc{Aurora}.}
-	\label{table:dd}
-	\small
-	\begin{tabular}{lllr}
-		\toprule
-		\multirow{2}{*}{\textbf{Payload Size(MB)}} & \textbf{Linux} & \textbf{Aurora} & \textbf{Slowdown} \\ 
-		& \textbf{(MB/s)} & \textbf{(MB/s)} & \textbf{(\%)} \\
-		\midrule
-		4 & 32.9 & 31.8 & 3.3 \\
-		64 & 40.9 & 39.2 & 4.2 \\
-		256 & 42.7 & 40.4 & 5.3 \\
-		1024 & 53.2 & 47.5 & 10.7 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
 
@@
 
-\iftrue
-
-\begin{table*}[t]
+\begin{table}[t]
 	\centering
-	\caption{Comparison of existing clock services that can be used for SGX enclaves.
-Clock services include network time protocol (NTP), precision time protocol (PTP), and the platform software (PSW) supported by Intel management engine (ME), monotonic counter supported by Byzantine Fault Tolerance (BFT) protocol.}
-	\label{table:timeservice}
+	\caption{Serial-port benchmark comparison between Linux and \textsc{Aurora}.}
+	\label{table:serial}
 	\small
-	\begin{tabular}{lllcrccr}
+	\begin{tabular}{lrrr}
 		\toprule
-		\textbf{Clock Provider} & \textbf{Approach} & \textbf{Type} & \textbf{Resolution} & \textbf{Request Cost} & \textbf{Latency} & \textbf{Security} & \textbf{Use Cases} \\
+		\textbf{Payload Size(KB)} & \textbf{Linux(s)} & \textbf{Aurora(s)} & \textbf{Speedup(\%)} \\
 		\midrule
-		Remote Clock & NTP/PTP & absolute & 1s & $>$100ms & high & trusted & Town Crier~\cite{DBLP:conf/ccs/ZhangCCJS16} \\
-		Intel ME & PSW & relative & 1s & 10.3ms & medium & trusted & SGX-Tor~\cite{DBLP:conf/nsdi/KimHHKH17} \\
-		OS Kernel & OCALL & absolute & 1ns & 6us & low & untrusted & Panoply~\cite{shinde_panoply:_2017} \\
-		Distributed Network & BFT & N/A & N/A & 1--2ms & medium & trusted & ROTE~\cite{DBLP:conf/uss/MateticAKDSGJC17} \\
-		Hardware Clock & \textit{smcall} & absolute & 1ns & 69us & low & trusted & Aurora-OpenSSL~\ref{openssl} \\
+		4 & 0.03 & 0.03 & 0.0 \\
+		64 & 0.32 & 0.24 & 25.0 \\
+		256 & 1.08 & 0.87 & 19.4 \\
+		1024 & 3.95 & 3.43 & 13.2 \\
 		\bottomrule
 	\end{tabular}
-\end{table*}
+\end{table}
+
+\begin{table}[t]	
+	\centering
+	\caption{Storage throughput comparison between Linux and \textsc{Aurora}.}
+	\label{table:dd}
+	\small
+	\begin{tabular}{lllr}
+		\toprule
+		\multirow{2}{*}{\textbf{Payload Size(MB)}} & \textbf{Linux} & \textbf{Aurora} & \textbf{Slowdown} \\ 
+		& \textbf{(MB/s)} & \textbf{(MB/s)} & \textbf{(\%)} \\
+		\midrule
+		4 & 32.9 & 31.8 & 3.3 \\
+		64 & 40.9 & 39.2 & 4.2 \\
+		256 & 42.7 & 40.4 & 5.3 \\
+		1024 & 53.2 & 47.5 & 10.7 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\iftrue
 
@@
 
+\begin{table*}[t]
+	\centering
+	\caption{Comparison of existing clock services that can be used for SGX enclaves.
+Clock services include network time protocol (NTP), precision time protocol (PTP), and the platform software (PSW) supported by Intel management engine (ME), monotonic counter supported by Byzantine Fault Tolerance (BFT) protocol.}
+	\label{table:timeservice}
+	\small
+	\begin{tabular}{lllcrccr}
+		\toprule
+		\textbf{Clock Provider} & \textbf{Approach} & \textbf{Type} & \textbf{Resolution} & \textbf{Request Cost} & \textbf{Latency} & \textbf{Security} & \textbf{Use Cases} \\
+		\midrule
+		Remote Clock & NTP/PTP & absolute & 1s & $>$100ms & high & trusted & Town Crier~\cite{DBLP:conf/ccs/ZhangCCJS16} \\
+		Intel ME & PSW & relative & 1s & 10.3ms & medium & trusted & SGX-Tor~\cite{DBLP:conf/nsdi/KimHHKH17} \\
+		OS Kernel & OCALL & absolute & 1ns & 6us & low & untrusted & Panoply~\cite{shinde_panoply:_2017} \\
+		Distributed Network & BFT & N/A & N/A & 1--2ms & medium & trusted & ROTE~\cite{DBLP:conf/uss/MateticAKDSGJC17} \\
+		Hardware Clock & \textit{smcall} & absolute & 1ns & 69us & low & trusted & Aurora-OpenSSL~\ref{openssl} \\
+		\bottomrule
+	\end{tabular}
+\end{table*}
+
 \fi
@@
 We did not use any encryption in this experiment.
-
 The throughput results are shown in \autoref{table:dd} where the size of each block is set to 4KB.

### 2019-08-25 article.tex
modify the response and article

@@
 \begin{enumerate}[]
-\item The notion of two types of trusted I/O paths: data-provider/-consumer and data-storage/-transmitter (\autoref{types}), for security-sensitive applications (enclave programs).
+\item The notion of two types of trusted I/O paths: data-provider/-consumer path and data-storage/-transmitter (\autoref{types}) path, for security-sensitive applications (enclave programs).
 \item A novel architecture named \textsc{Aurora} (\autoref{arch}) leveraging two hardware features of Intel processors (SMM and SGX) to provide enclaves trusted paths transparent to untrusted OSes/HVs with a minimal trusted computing base (\autoref{codebase}).
@@
 
-The main difference between these two types is that \textit{data-provider/-consumer} is either the sink or the source of data.
-This type of trusted path must handle data in plaintext, which requires careful isolation or confidential protection.
-The \textit{data-storage/-transmitter} type acts as a medium for data at rest or in transition.
+The main difference between these two types is that \textit{data-provider/-consumer} is either the sink or the source of data and must handle data in plain-text, which requires careful isolation or confidential protection; Whereas the \textit{data-storage/-transmitter} type acts as a medium for data at rest or in transition.
 It focuses on the freshness and integrity of data.
@@
 	\caption{The workflow of a trusted I/O path in \textsc{Aurora}. %The white areas denote the TCB.
-	1) An output request is triggered by an enclave as an exception:
+	1) An \textbf{output} request is triggered by an enclave as an exception:
 \textcircled{\scriptsize{1}} The user logic in an enclave issues an output request by invoking  Tlibaurora's APIs;
@@
 \textcircled{\scriptsize{7}} The driver returns a result code to SMVisor. In the end, SMVisor executes \textit{RSM} to return to protected mode. 
-	2) An input request from an enclave causes a device interrupt:
+	2) An \textbf{input} request from an enclave causes a device interrupt:
 \textcircled{\scriptsize{1}} The target device triggers an interrupt, and the control flow is rerouted to SMVisor which has the interrupt handler;
@@
 \textbf{User Verification.}
-Phishing attacks, where an adversary exploits social engineering tricks to allure a user to leak her privacy data, are a threat to trusted input.
+%Phishing attacks, where an adversary exploits social engineering tricks to allure a user to leak her privacy data, are a threat to trusted input.
 For example, a malware might present a fake login interface that prompts a user to enter her password.
+Attackers can use keyloggers to steal passwords or credit card information.
+Most keyloggers are not stopped by HTTPS encryption which only protects data in transit between computers.
+For example, they are frequently implemented as rootkits that subvert the operating system kernel to gain unauthorized access to the hardware.
 To mitigate this threat, we leverage the PC speaker to indicate that the trusted path has been established.
 When the system first boots, the network is disabled by the SMVisor, and we assume that the loaded kernel is clean due to TPM's measure boot.
-\textsc{Aurora} asks the user to store a short, arbitrary MIDI-format melody (around 5 seconds) inside SMRAM via a config enclave, so that every time when a trusted path is set up, the PC speaker will play the melody, and then the network is enabled by the SMVisor.
-Since the melody is a pre-shared secret only known by SMVisor and the user, it is impossible for the adversary to learn and mimic this process.
+\textsc{Aurora} asks a user to store a short, arbitrary MIDI-format melody (around 5 seconds) inside SMRAM via a configure enclave, so that every time when a trusted path is set up, the PC speaker will play the melody, and then the network is enabled by the SMVisor.
+Since the melody is a pre-shared secret only known by SMVisor and the user, it is impossible for the attackers to learn and mimic this process.
 % Tlibaurora first generates a random integer $N$ in the interval of [1, 10], and displays the integer number in the screen as a captcha.
@@
 
-Aurora's trusted hardware clock is immune to the TOCTOU attack because it leverages SMM which guarantees that the operation of check and use are atomically performed.
+Aurora's trusted hardware clock is immune to the TOCTOU attack because it leverages SMM which guarantees that the operations of check and use are atomically performed.
 
@@
 It is a serious issue when secure data storage is  necessary for ensuring correct operation (e.g., secure logging, APT monitoring and compliance).
-We extend \textsc{Aurora} to support secure USB massive storage devices.
-Note that \textsc{Aurora}'s approach is also suitable and easy to support for other storage systems such as SATA HDD, NVMe SSD, etc.
+We extend \textsc{Aurora} to support secure USB massive storage devices as an example.
+Note that we believe that \textsc{Aurora}'s approach is also suitable to support for other storage systems such as SATA HDD, NVMe SSD, etc.
 
@@
 The results are shown in \autoref{table:timeservice}.
-Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks such as the timing attacks.
+%Due to the fact that there are no input dependent branches in the secure channel (the channel simply transfers the I/O packets), we argue that our secure session is safe from side-channel attacks such as the timing attacks.
 Among existing approaches, \textsc{Aurora} outperforms remote clock (the 2nd row) and Intel's reference clock (the 3rd row) by introducing very low latency, while achieving the same resolution (nanosecond-level) as OS services (the 4th row).
@@
 As shown in \autoref{table:openssl}, in our LAN setting, Aurora-OpenSSL introduced about 32\% latency in certificate generation and 21\% in the TLS handshaking because both of them use \textsc{Aurora}'s trusted clock.
-We anticipate the overhead ratio to decrease in a WAN environment because of the larger delays of a geographically distributed public network.
+We anticipate the overhead ratio to decrease in a WAN environment because the delays of a geographically distributed public network is larger than our LAN setting.
 
@@
 We make minor changes to these benchmark queries in order to make them possible to be executed in SQLite. 
-Unfortunately, not all queries can be executed due to the partial porting of the original project.
-These queries include \textit{select from, order by, group by}.
 %In our experiment, the native insertion transactions for 1000 times cost 17.3 seconds while the ones with \textsc{Aurora}'s trusted path cost 20.5 seconds.
 About 18\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.
-\autoref{table:tpch} shows the completed queries and their results of native SGX-SQLite and \textsc{Aurora}-SGLite respectively.
+\autoref{table:tpch} shows the completed queries\footnote{Note that several queries, i.e., \textit{select from, order by, group by}, cannot be executed due to our partial porting of the original project.} and their results of native SGX-SQLite and \textsc{Aurora}-SGLite respectively.
 In our experiments, no more than 10.08\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.

### 2020-04-30 IEEE-TIFS-2020-tex/article.tex
Add TIFS 2020 citation

--- 2019-08-25 article.tex
@@
-\documentclass[journal,twocolumn,letterpaper,10pt]{IEEEtran}
+\documentclass[journal,twocolumn,10pt]{IEEEtran}
 \pagestyle{plain}
@@
 \usepackage[tight,footnotesize]{subfigure}
-\usepackage{booktabs} % For formal tables
+\usepackage{booktabs}
 \usepackage[colorlinks, linkcolor=blue,anchorcolor=black,citecolor=blue]{hyperref}
@@
 
-\title{Establishing Trusted I/O Paths for Client \\ Shielded Executions with Aurora}
+\title{Establishing Trusted I/O Paths for \\ SGX Client Systems with Aurora}
 
@@
 Our assumptions  reduce the TCB on the target host as modern commodity system usually contains a large software stacks (e.g., UEFI, possibly hypervisor, kernel and other applications) when dealing with I/O devices.
-Physical attacks on devices, side-channel attacks~\cite{chen2019sgxpectre, ridl}, information leakage (I/O size and request/response frequency) and denial-of-service attacks are not considered.
+Physical attacks on devices, side-channel attacks~\cite{chen2019sgxpectre, ridl}, information leakage (I/O size and request/response frequency) and denial-of-service attacks to Aurora's framework are not considered.
 The adversary cannot access the physical machine and modify its hardware setup.
@@
 We extend \textsc{Aurora} to support secure USB massive storage devices as an example.
-Note that we believe that \textsc{Aurora}'s approach is also suitable to support for other storage systems such as SATA HDD, NVMe SSD, etc.
+We believe that \textsc{Aurora}'s approach is suitable to support other storage systems such as SATA HDD, NVMe SSD, etc.
 
@@
 
-\subsection{Security Effectiveness}\label{security}
+\subsection{Security Evaluation}\label{security}
 We evaluate \textsc{Aurora}'s reliability with several security tests.
@@
 In our experiments, the enclave finally received the attack warning from the Tlibaurora and logged these events for further forensic analysis.
+Note that denial-of-service to Aurora's kernel module is not considered in this work.
 
@@
 As shown in \autoref{table:openssl}, in our LAN setting, Aurora-OpenSSL introduced about 32\% latency in certificate generation and 21\% in the TLS handshaking because both of them use \textsc{Aurora}'s trusted clock.
-We anticipate the overhead ratio to decrease in a WAN environment because the delays of a geographically distributed public network is larger than our LAN setting.
+We anticipate the overhead ratio to decrease in a WAN environment, because the delay of a geographically distributed public network should be larger than our LAN setting.
 
@@
 One of the popular examples is Yubikey\footnote{https://www.yubico.com/products/yubikey-hardware/yubikey4/}.
-Because these USB key implementations are not open source, we built a secure E-Banking application according to their documentations.
+Because these USB key implementations are not open source, we built a secure E-Banking application according to their documentation.
 We name our USB key and secure E-Banking implementation as \textit{AuraKey} and \textit{AuraBank} respectively.
@@
 When SQLite invokes Tlibaurora file APIs, it opens the USB storage device in direct I/O mode and reads/writes data using 4KB block size. 
-Finally, %to directly measure the overhead introduced by \textsc{Aurora}'s infrastructure, 
-we set the synchronize flag to \texttt{FULL} to avoid the uncertainty of I/O caching.
-
-We evaluated the enhanced SQLite performance by running standardized TPC-H benchmark\footnote{http://www.tpc.org/tpch/} over a large database. % (around 1.3GB).
-We make minor changes to these benchmark queries in order to make them possible to be executed in SQLite. 
+Finally, we set the synchronize flag to \texttt{FULL} to avoid the uncertainty of I/O caching.
+
+We evaluated the enhanced SQLite performance by running standardized TPC-H benchmark\footnote{http://www.tpc.org/tpch/} over a large database.
+These queries include \textit{select from, order by, group by} benchmarks.
+% (around 1.3GB).
+We make minor changes to these query scripts to make them possible to be executed in SQLite. 
 %In our experiment, the native insertion transactions for 1000 times cost 17.3 seconds while the ones with \textsc{Aurora}'s trusted path cost 20.5 seconds.
 About 18\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.
-\autoref{table:tpch} shows the completed queries\footnote{Note that several queries, i.e., \textit{select from, order by, group by}, cannot be executed due to our partial porting of the original project.} and their results of native SGX-SQLite and \textsc{Aurora}-SGLite respectively.
+\autoref{table:tpch} shows the completed queries\footnote{Note that not all queries can be executed due to the partial porting of the original project.} and their results of native SGX-SQLite and \textsc{Aurora}-SGLite respectively.
 In our experiments, no more than 10.08\% overhead is introduced because of the extra encrypt/decrypt computation and mode transitions in \textsc{Aurora}.
@@
 %Since the GUI logic is untrusted, we do not allow the GUI to touch the real password character, rather, after the user releases a key, the enclave sends the \textit{signal} to GUI and the GUI displays an asteroid.
-%After the user clicks the "OK" button, her username, password and other private information are then encrypted inside the enclave, and later restored into the database in encrypted format.
+%After the user clicks the "OK" button, her username, password and other private information are then encrypted inside the enclave, and later restored into the database in an encrypted format.
 
@@
 BASTION-SGX~\cite{DBLP:conf/isca/PetersLVPK18} modifies the Bluetooth firmware and establishes trusted paths between Bluetooth devices and enclave programs.
-It has similar threat model with \textsc{Aurora} and rules the privileged software (OS, drivers, etc.) out of the TCB.
+It has a similar threat model with \textsc{Aurora} and rules the privileged software (OS, drivers, etc.) out of the TCB.
 %However, it requires enclave programs to take charge of handling the HID input, which is a burden for developers.
@@
 
-The authors would like to thank Kai Huang from Intel Corporation and Shweta Shinde from National University of Singapore for their generous help and constructive advices.
+The authors would like to thank Kai Huang from Intel Corporation and Shweta Shinde from National University of Singapore for their generous help and constructive advice.
 The authors also thank the anonymous reviewers for their valuable comments that help improve the article.

### 2020-04-30 Aurora-lwip-sgx/App/App.cpp

@@ -1,0 +1,525 @@
+/*
+ * Copyright (C) 2011-2017 Intel Corporation. All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ *
+ *   * Redistributions of source code must retain the above copyright
+ *     notice, this list of conditions and the following disclaimer.
+ *   * Redistributions in binary form must reproduce the above copyright
+ *     notice, this list of conditions and the following disclaimer in
+ *     the documentation and/or other materials provided with the
+ *     distribution.
+ *   * Neither the name of Intel Corporation nor the names of its
+ *     contributors may be used to endorse or promote products derived
+ *     from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+ * "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+ * LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
+ * A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+ * OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+ * SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
+ * LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
+ * DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
+ * THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+ * (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
+ * OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+ *
+ */
+
+
+#include <stdio.h>
+#include <string.h>
+#include <assert.h>
+#include <thread>
+
+# include <unistd.h>
[…]

### 2020-04-30 Aurora-lwip-sgx/App/lwip/core/ipv4/etharp.cpp

@@ -1,0 +1,1208 @@
+/**
+ * @file
+ * Address Resolution Protocol module for IP over Ethernet
+ *
+ * Functionally, ARP is divided into two parts. The first maps an IP address
+ * to a physical address when sending a packet, and the second part answers
+ * requests from other machines for our physical address.
+ *
+ * This implementation complies with RFC 826 (Ethernet ARP). It supports
+ * Gratuitious ARP from RFC3220 (IP Mobility Support for IPv4) section 4.6
+ * if an interface calls etharp_gratuitous(our_netif) upon address change.
+ */
+
+/*
+ * Copyright (c) 2001-2003 Swedish Institute of Computer Science.
+ * Copyright (c) 2003-2004 Leon Woestenberg <leon.woestenberg@axon.tv>
+ * Copyright (c) 2003-2004 Axon Digital Design B.V., The Netherlands.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without modification,
+ * are permitted provided that the following conditions are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ *    this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright notice,
+ *    this list of conditions and the following disclaimer in the documentation
+ *    and/or other materials provided with the distribution.
+ * 3. The name of the author may not be used to endorse or promote products
+ *    derived from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR IMPLIED
+ * WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF
+ * MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT
+ * SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
+ * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT
[…]

### 2020-04-30 Aurora-lwip-sgx/App/lwip/core/netif.cpp

@@ -1,0 +1,1577 @@
+/**
+ * @file
+ * lwIP network interface abstraction
+ *
+ * @defgroup netif Network interface (NETIF)
+ * @ingroup callbackstyle_api
+ *
+ * @defgroup netif_ip4 IPv4 address handling
+ * @ingroup netif
+ *
+ * @defgroup netif_ip6 IPv6 address handling
+ * @ingroup netif
+ *
+ * @defgroup netif_cd Client data handling
+ * Store data (void*) on a netif for application usage.
+ * @see @ref LWIP_NUM_NETIF_CLIENT_DATA
+ * @ingroup netif
+ */
+
+/*
+ * Copyright (c) 2001-2004 Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without modification,
+ * are permitted provided that the following conditions are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ *    this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright notice,
+ *    this list of conditions and the following disclaimer in the documentation
+ *    and/or other materials provided with the distribution.
+ * 3. The name of the author may not be used to endorse or promote products
+ *    derived from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR IMPLIED
+ * WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF
+ * MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT
+ * SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
+ * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT
+ * OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
[…]

### 2020-04-30 Aurora-lwip-sgx/App/lwip/core/pbuf.cpp

@@ -1,0 +1,1508 @@
+/**
+ * @file
+ * Packet buffer management
+ */
+
+/**
+ * @defgroup pbuf Packet buffers (PBUF)
+ * @ingroup infrastructure
+ *
+ * Packets are built from the pbuf data structure. It supports dynamic
+ * memory allocation for packet contents or can reference externally
+ * managed packet contents both in RAM and ROM. Quick allocation for
+ * incoming packets is provided through pools with fixed sized pbufs.
+ *
+ * A packet may span over multiple pbufs, chained as a singly linked
+ * list. This is called a "pbuf chain".
+ *
+ * Multiple packets may be queued, also using this singly linked list.
+ * This is called a "packet queue".
+ *
+ * So, a packet queue consists of one or more pbuf chains, each of
+ * which consist of one or more pbufs. CURRENTLY, PACKET QUEUES ARE
+ * NOT SUPPORTED!!! Use helper structs to queue multiple packets.
+ *
+ * The differences between a pbuf chain and a packet queue are very
+ * precise but subtle.
+ *
+ * The last pbuf of a packet has a ->tot_len field that equals the
+ * ->len field. It can be found by traversing the list. If the last
+ * pbuf of a packet has a ->next field other than NULL, more packets
+ * are on the queue.
+ *
+ * Therefore, looping through a pbuf of a single packet, has an
+ * loop end condition (tot_len == p->len), NOT (next == NULL).
+ *
+ * Example of custom pbuf usage: @ref zerocopyrx
+ */
+
+/*
+ * Copyright (c) 2001-2004 Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without modification,
+ * are permitted provided that the following conditions are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ *    this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright notice,
[…]

### 2020-04-30 Aurora-lwip-sgx/App/lwip/core/raw.cpp

@@ -1,0 +1,658 @@
+/**
+ * @file
+ * Implementation of raw protocol PCBs for low-level handling of
+ * different types of protocols besides (or overriding) those
+ * already available in lwIP.\n
+ * See also @ref raw_raw
+ *
+ * @defgroup raw_raw RAW
+ * @ingroup callbackstyle_api
+ * Implementation of raw protocol PCBs for low-level handling of
+ * different types of protocols besides (or overriding) those
+ * already available in lwIP.\n
+ * @see @ref api
+ */
+
+/*
+ * Copyright (c) 2001-2004 Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without modification,
+ * are permitted provided that the following conditions are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ *    this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright notice,
+ *    this list of conditions and the following disclaimer in the documentation
+ *    and/or other materials provided with the distribution.
+ * 3. The name of the author may not be used to endorse or promote products
+ *    derived from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR IMPLIED
+ * WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF
+ * MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT
+ * SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
+ * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT
+ * OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
[…]

### 2020-04-30 Aurora-lwip-sgx/App/lwip/core/tcp_out.cpp

@@ -1,0 +1,2048 @@
+/**
+ * @file
+ * Transmission Control Protocol, outgoing traffic
+ *
+ * The output functions of TCP.
+ *
+ */
+
+/*
+ * Copyright (c) 2001-2004 Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without modification,
+ * are permitted provided that the following conditions are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ *    this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright notice,
+ *    this list of conditions and the following disclaimer in the documentation
+ *    and/or other materials provided with the distribution.
+ * 3. The name of the author may not be used to endorse or promote products
+ *    derived from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR IMPLIED
+ * WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF
+ * MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT
+ * SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
+ * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT
+ * OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
+ * CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING
+ * IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY
+ * OF SUCH DAMAGE.
+ *
+ * This file is part of the lwIP TCP/IP stack.
+ *
+ * Author: Adam Dunkels <adam@sics.se>
+ *
+ */
+
+#include "lwip/opt.h"
+
[…]

### 2020-04-30 Aurora-lwip-sgx/App/lwip/include/lwip/opt.h

@@ -1,0 +1,3191 @@
+/**
+ * @file
+ *
+ * lwIP Options Configuration
+ */
+
+/*
+ * Copyright (c) 2001-2004 Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without modification,
+ * are permitted provided that the following conditions are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ *    this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright notice,
+ *    this list of conditions and the following disclaimer in the documentation
+ *    and/or other materials provided with the distribution.
+ * 3. The name of the author may not be used to endorse or promote products
+ *    derived from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR IMPLIED
+ * WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF
+ * MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT
+ * SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
+ * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT
+ * OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
+ * CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING
+ * IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY
+ * OF SUCH DAMAGE.
+ *
+ * This file is part of the lwIP TCP/IP stack.
+ *
+ * Author: Adam Dunkels <adam@sics.se>
+ *
+ */
+
+/*
+ * NOTE: || defined __DOXYGEN__ is a workaround for doxygen bug -
[…]

### 2020-04-30 Aurora-lwip-sgx/App/lwip/netif/ethernetif.cpp

@@ -1,0 +1,369 @@
+/**
+ * @file
+ * Ethernet Interface Skeleton
+ *
+ */
+
+/*
+ * Copyright (c) 2001-2004 Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without modification,
+ * are permitted provided that the following conditions are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ *    this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright notice,
+ *    this list of conditions and the following disclaimer in the documentation
+ *    and/or other materials provided with the distribution.
+ * 3. The name of the author may not be used to endorse or promote products
+ *    derived from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR IMPLIED
+ * WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF
+ * MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT
+ * SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
+ * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT
+ * OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
+ * CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING
+ * IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY
+ * OF SUCH DAMAGE.
+ *
+ * This file is part of the lwIP TCP/IP stack.
+ *
+ * Author: Adam Dunkels <adam@sics.se>
+ *
+ */
+
+/*
+ * This file is a skeleton for developing Ethernet network interface
+ * drivers for lwIP. Add code to the low_level functions and do a
[…]

### 2020-04-30 Aurora-lwip-sgx/App/lwip/unit/arch/sys_arch.cpp

@@ -1,0 +1,385 @@
+/*
+ * Copyright (c) 2017 Simon Goldschmidt
+ * All rights reserved. 
+ * 
+ * Redistribution and use in source and binary forms, with or without modification, 
+ * are permitted provided that the following conditions are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ *    this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright notice,
+ *    this list of conditions and the following disclaimer in the documentation
+ *    and/or other materials provided with the distribution.
+ * 3. The name of the author may not be used to endorse or promote products
+ *    derived from this software without specific prior written permission. 
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR IMPLIED 
+ * WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF 
+ * MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT 
+ * SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, 
+ * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT 
+ * OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS 
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN 
+ * CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING 
+ * IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY 
+ * OF SUCH DAMAGE.
+ *
+ * This file is part of the lwIP TCP/IP stack.
+ * 
+ * Author: Simon Goldschmidt
+ *
+ */
+
+
+#include <lwip/opt.h>
+#include <lwip/arch.h>
[…]

### 2020-04-30 Aurora-lwip-sgx/App/lwip/unit/tcp/test_tcp.cpp

@@ -1,0 +1,1361 @@
+#include "test_tcp.h"
+
+#include "lwip/priv/tcp_priv.h"
+#include "lwip/stats.h"
+#include "tcp_helper.h"
+#include "lwip/inet_chksum.h"
+
+#ifdef _MSC_VER
+#pragma warning(disable: 4307) /* we explicitly wrap around TCP seqnos */
+#endif
+
+#if !LWIP_STATS || !TCP_STATS || !MEMP_STATS
+#error "This tests needs TCP- and MEMP-statistics enabled"
+#endif
+#if TCP_SND_BUF <= TCP_WND
+#error "This tests needs TCP_SND_BUF to be > TCP_WND"
+#endif
+
+/* used with check_seqnos() */
+#define SEQNO1 (0xFFFFFF00 - TCP_MSS)
+#define ISS    6510
+static u32_t seqnos[] = {
+    SEQNO1,
+    SEQNO1 + (1 * TCP_MSS),
+    SEQNO1 + (2 * TCP_MSS),
+    SEQNO1 + (3 * TCP_MSS),
+    SEQNO1 + (4 * TCP_MSS),
+    SEQNO1 + (5 * TCP_MSS) };
+
+static u8_t test_tcp_timer;
+
+/* our own version of tcp_tmr so we can reset fast/slow timer state */
+static void
+test_tcp_tmr(void)
+{
+  tcp_fasttmr();
+  if (++test_tcp_timer & 1) {
+    tcp_slowtmr();
+  }
+}
+
+/* Setups/teardown functions */
+static struct netif *old_netif_list;
+static struct netif *old_netif_default;
+
+static void
+tcp_setup(void)
+{
+  old_netif_list = netif_list;
+  old_netif_default = netif_default;
+  netif_list = NULL;
+  netif_default = NULL;
+  /* reset iss to default (6510) */
+  tcp_ticks = 0;
+  tcp_ticks = 0 - (tcp_next_iss(NULL) - 6510);
+  tcp_next_iss(NULL);
+  tcp_ticks = 0;
+
+  test_tcp_timer = 0;
+  tcp_remove_all();
+  lwip_check_ensure_no_alloc(SKIP_POOL(MEMP_SYS_TIMEOUT));
+}
+
+static void
+tcp_teardown(void)
+{
+  netif_list = NULL;
+  netif_default = NULL;
+  tcp_remove_all();
+  /* restore netif_list for next tests (e.g. loopif) */
+  netif_list = old_netif_list;
+  netif_default = old_netif_default;
[…]

### 2020-04-30 Aurora-lwip-sgx/App/smx/rdrand.cpp

@@ -1,0 +1,557 @@
+/* Copyright © 2012, Intel Corporation.  All rights reserved. 
+ 
+Redistribution and use in source and binary forms, with or without
+modification, are permitted provided that the following conditions are met:
+ 
+-       Redistributions of source code must retain the above copyright notice,
+		this list of conditions and the following disclaimer.
+-       Redistributions in binary form must reproduce the above copyright 
+		notice, this list of conditions and the following disclaimer in the
+		documentation and/or other materials provided with the distribution.
+-       Neither the name of Intel Corporation nor the names of its contributors
+		may be used to endorse or promote products derived from this software
+		without specific prior written permission.
+ 
+THIS SOFTWARE IS PROVIDED BY INTEL CORPORATION "AS IS" AND ANY EXPRESS OR
+IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF
+MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO
+EVENT SHALL INTEL CORPORATION BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO,
+PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR
+BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER
+IN CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) 
+ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE
+POSSIBILITY OF SUCH DAMAGE. */
+
+/* Copyright © 2012, Intel Corporation.  All rights reserved. 
+ 
+Redistribution and use in source and binary forms, with or without
+modification, are permitted provided that the following conditions are met:
+ 
+-       Redistributions of source code must retain the above copyright notice,
+		this list of conditions and the following disclaimer.
+-       Redistributions in binary form must reproduce the above copyright 
[…]

### 2020-04-30 Aurora-lwip-sgx/App/smx/utils.cpp

@@ -1,0 +1,755 @@
+#ifndef __STDC_WANT_LIB_EXT1__
+# define __STDC_WANT_LIB_EXT1__ 1
+#endif
+#include <assert.h>
+#include <errno.h>
+#include <limits.h>
+//#include <signal.h>
+#include <stddef.h>
+#include <stdint.h>
+#include <stdlib.h>
+#include <string.h>
+
+#ifdef HAVE_SYS_MMAN_H
+# include <sys/mman.h>
+#endif
+
+#ifdef _WIN32
+# include <windows.h>
+# include <wincrypt.h>
+#else
+# include <unistd.h>
+#endif
+
+#if HAVE_ALLOCA_H
+# include <alloca.h>
+#elif defined __GNUC__
+# define alloca __builtin_alloca
+#elif defined _AIX
+# define alloca __alloca
+#elif defined _MSC_VER
+# include <malloc.h>
+# define alloca _alloca
+#else
+# include <stddef.h>
+# ifdef  __cplusplus
+extern "C"
+# endif
+void *alloca (size_t);
+#endif
+
+#include "core.h"
+#include "randombytes.h"
+#include "utils.h"
+
+///
+
+void
+sodium_misuse(void)
+{
+#if 0
+    void (*handler)(void);
+
+    (void) sodium_crit_leave();
+    if (sodium_crit_enter() == 0) {
+        handler = _misuse_handler;
+        if (handler != NULL) {
+            handler();
+        }
+    }
+/* LCOV_EXCL_START */
+#endif
+    abort();
+}
+
+///
+
+#ifndef ENOSYS
+# define ENOSYS ENXIO
+#endif
+
+#if defined(_WIN32) && \
+    (!defined(WINAPI_FAMILY) || WINAPI_FAMILY == WINAPI_FAMILY_DESKTOP_APP)
+# define WINAPI_DESKTOP
+#endif
+
+#define CANARY_SIZE 16U
+#define GARBAGE_VALUE 0xdb
+
+#ifndef MAP_NOCORE
+# define MAP_NOCORE 0
+#endif
+#if !defined(MAP_ANON) && defined(MAP_ANONYMOUS)
+# define MAP_ANON MAP_ANONYMOUS
+#endif
+#if defined(WINAPI_DESKTOP) || (defined(MAP_ANON) && defined(HAVE_MMAP)) || \
+    defined(HAVE_POSIX_MEMALIGN)
[…]

### 2020-04-30 Aurora-lwip-sgx/App/test.cpp

@@ -1,0 +1,711 @@
+#if 0
+#include "lwip/mem.h"
+#include "lwip/opt.h"
+#include "lwip/sockets.h"
+#include "lwip/priv/sockets_priv.h"
+#include "lwip/stats.h"
+
+#include "lwip/tcpip.h"
+#include "lwip/priv/tcp_priv.h"
+#include "lwip/api.h"
+
+#include "lwip/udp.h"
+#include "lwip/etharp.h"
+#include "netif/ethernet.h"
+#include "lwip/stats.h"
+#include "lwip/prot/iana.h"
+#include "lwip/sockets.h"
+#include "lwip/netif.h"
+#include "lwip/etharp.h"
+#include "netif/ethernet.h"
+
+struct eth_addr test_ethaddr =  {{6,2,9,3,8,1}};
+struct eth_addr test_ethaddr2 = {{6,2,9,3,8,2}};
+struct eth_addr test_ethaddr3 = {{6,2,9,3,8,3}};
+struct eth_addr test_ethaddr4 = {{6,2,9,3,8,4}};
+
+int linkoutput_ctr;
+
+#define fail_unless(x) { if (0 != (x)) {;} \
+    else {printf("FILE: %s LINE: %d\n", __FILE__, __LINE__); abort();} }
+#define fail abort
+
+#define NUM_SOCKETS MEMP_NUM_NETCONN
+
+static int
+test_sockets_alloc_socket_nonblocking(int domain, int type)
+{
+  int s = lwip_socket(domain, type, 0);
+  if (s >= 0) {
+    int ret = lwip_fcntl(s, F_SETFL, O_NONBLOCK);
+    fail_unless(ret == 0);
+  }
+  return s;
+}
+
+static void test_sockets_msgapi_update_iovs(struct msghdr *msg, size_t bytes)
+{
+  int i;
+
+  /* note: this modifies the underyling iov_base and iov_len for a partial
+     read for an individual vector. This updates the msg->msg_iov pointer
+     to skip fully consumed vecotrs */
+
+  /* process fully consumed vectors */
+  for (i = 0; i < msg->msg_iovlen; i++) {
+    if (msg->msg_iov[i].iov_len <= bytes) {
+      /* reduce bytes by amount of this vector */
+      bytes -= msg->msg_iov[i].iov_len;
+    } else {
+      break; /* iov not fully consumed */
+    }
+  }
+
[…]

### 2020-04-30 Aurora-lwip-sgx/App/utils.cpp

@@ -1,0 +1,132 @@
+#include <errno.h>
+#include <fcntl.h>
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+#include <sys/mman.h>
+#include <sys/select.h>
+#include <unistd.h>
+
+#include <ctype.h>
+void _print_hex(const char* what, const void* v, const unsigned long l)
+{
+  const unsigned char* p = (unsigned char*)v;
+  unsigned long x, y = 0, z;
+  printf("%s contents: \n", what);
+  for (x = 0; x < l; ) {
+      printf("%02X ", p[x]);
+      if (!(++x % 16) || x == l) {
+         if((x % 16) != 0) {
+            z = 16 - (x % 16);
+            if(z >= 8)
+               printf(" ");
+            for (; z != 0; --z) {
+               printf("   ");
+            }
+         }
+         printf(" | ");
+         for(; y < x; y++) {
+            if((y % 8) == 0)
+               printf(" ");
+            if(isgraph(p[y]))
+               printf("%c", p[y]);
+            else
+               printf(".");
+         }
+         printf("\n");
+      }
+      else if((x % 8) == 0) {
+         printf(" ");
+      }
+  }
+}
+
+#define N	10000
+
+static inline void synch_tsc(void)
+{
+	asm volatile("cpuid" : : : "%rax", "%rbx", "%rcx", "%rdx");
+}
+
+static inline unsigned long rdtscll(void)
+{
+	unsigned int a, d;
+	asm volatile("rdtsc" : "=a" (a), "=d" (d) : : "%rbx", "%rcx");
+	return ((unsigned long) a) | (((unsigned long) d) << 32);
+}
+
+static inline unsigned long rdtscllp(void)
+{
+	unsigned int a, d;
+	asm volatile("rdtscp" : "=a" (a), "=d" (d) : : "%rbx", "%rcx");
+	return ((unsigned long) a) | (((unsigned long) d) << 32);
+}
+
+static unsigned long measure_tsc_overhead(void)
+{
+	unsigned long t0, t1, overhead = ~0UL;
+	int i;
+
+	for (i = 0; i < N; i++) {
+		t0 = rdtscll();
+		asm volatile("");
+		t1 = rdtscllp();
+		if (t1 - t0 < overhead)
+			overhead = t1 - t0;
+	}
+
+	return overhead;
+}
+
+unsigned long trap_tsc, overhead;
+
+#define SVM_SIZE ((1<<20))
+
[…]

### 2020-04-30 Aurora-lwip-sgx/Enclave/Enclave.cpp

@@ -1,0 +1,551 @@
+/*
+ * Copyright (C) 2011-2017 Intel Corporation. All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ *
+ *   * Redistributions of source code must retain the above copyright
+ *     notice, this list of conditions and the following disclaimer.
+ *   * Redistributions in binary form must reproduce the above copyright
+ *     notice, this list of conditions and the following disclaimer in
+ *     the documentation and/or other materials provided with the
+ *     distribution.
+ *   * Neither the name of Intel Corporation nor the names of its
+ *     contributors may be used to endorse or promote products derived
+ *     from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+ * "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+ * LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
+ * A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+ * OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+ * SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
+ * LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
+ * DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
+ * THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+ * (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
+ * OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+ *
+ */
+
+#include <stdlib.h>
+#include <stdarg.h>
+#include <stdio.h>      /* vsnprintf */
+#include <string.h>
+#include <errno.h>
+#include <assert.h>
+
+#include "sgx_tcrypto.h"
[…]

### 2020-04-30 Aurora-lwip-sgx/Enclave/Enclave.h

@@ -1,0 +1,50 @@
+/*
+ * Copyright (C) 2011-2017 Intel Corporation. All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ *
+ *   * Redistributions of source code must retain the above copyright
+ *     notice, this list of conditions and the following disclaimer.
+ *   * Redistributions in binary form must reproduce the above copyright
+ *     notice, this list of conditions and the following disclaimer in
+ *     the documentation and/or other materials provided with the
+ *     distribution.
+ *   * Neither the name of Intel Corporation nor the names of its
+ *     contributors may be used to endorse or promote products derived
+ *     from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+ * "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+ * LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
+ * A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+ * OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+ * SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
+ * LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
+ * DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
+ * THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+ * (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
+ * OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+ *
+ */
+
+
+#ifndef _ENCLAVE_H_
+#define _ENCLAVE_H_
+
+#include <stdlib.h>
+#include <assert.h>
+
+#if defined(__cplusplus)
+extern "C" {
+#endif
+
[…]

### 2020-04-30 Aurora-lwip-sgx/Enclave/lwip/apps/httpd/httpd.cpp

@@ -1,0 +1,2670 @@
+/**
+ * @file
+ * LWIP HTTP server implementation
+ */
+
+/*
+ * Copyright (c) 2001-2003 Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without modification,
+ * are permitted provided that the following conditions are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ *    this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright notice,
+ *    this list of conditions and the following disclaimer in the documentation
+ *    and/or other materials provided with the distribution.
+ * 3. The name of the author may not be used to endorse or promote products
+ *    derived from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR IMPLIED
+ * WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF
+ * MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT
+ * SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
+ * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT
+ * OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
+ * CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING
+ * IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY
+ * OF SUCH DAMAGE.
+ *
+ * This file is part of the lwIP TCP/IP stack.
+ *
+ * Author: Adam Dunkels <adam@sics.se>
+ *         Simon Goldschmidt
+ *
+ */
+
+/**
[…]

### 2020-04-30 Aurora-lwip-sgx/Enclave/lwip/include/arch/cc.h

@@ -1,0 +1,113 @@
+/*
+ * Copyright (c) 2001-2003 Swedish Institute of Computer Science.
+ * All rights reserved. 
+ * 
+ * Redistribution and use in source and binary forms, with or without modification, 
+ * are permitted provided that the following conditions are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ *    this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright notice,
+ *    this list of conditions and the following disclaimer in the documentation
+ *    and/or other materials provided with the distribution.
+ * 3. The name of the author may not be used to endorse or promote products
+ *    derived from this software without specific prior written permission. 
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR IMPLIED 
+ * WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF 
+ * MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT 
+ * SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, 
+ * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT 
+ * OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS 
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN 
+ * CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING 
+ * IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY 
+ * OF SUCH DAMAGE.
+ *
+ * This file is part of the lwIP TCP/IP stack.
+ * 
+ * Author: Adam Dunkels <adam@sics.se>
+ *
+ */
+#ifndef LWIP_ARCH_CC_H
+#define LWIP_ARCH_CC_H
+
[…]

### 2020-04-30 Aurora-lwip-sgx/Enclave/lwip/include/lwip/lwipopts.h

@@ -1,0 +1,110 @@
+/*
+ * Copyright (c) 2001-2003 Swedish Institute of Computer Science.
+ * All rights reserved. 
+ * 
+ * Redistribution and use in source and binary forms, with or without modification, 
+ * are permitted provided that the following conditions are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ *    this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright notice,
+ *    this list of conditions and the following disclaimer in the documentation
+ *    and/or other materials provided with the distribution.
+ * 3. The name of the author may not be used to endorse or promote products
+ *    derived from this software without specific prior written permission. 
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR IMPLIED 
+ * WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF 
+ * MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT 
+ * SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, 
+ * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT 
+ * OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS 
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN 
+ * CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING 
+ * IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY 
+ * OF SUCH DAMAGE.
+ *
+ * This file is part of the lwIP TCP/IP stack.
+ * 
+ * Author: Simon Goldschmidt
+ *
+ */
+#ifndef LWIP_HDR_LWIPOPTS_H
+#define LWIP_HDR_LWIPOPTS_H
+
+#define CHECKSUM_CHECK_IP               0
+#define CHECKSUM_CHECK_UDP              0
[…]

### 2020-04-30 Aurora-lwip-sgx/Enclave/lwip/netif/ethernet.cpp

@@ -1,0 +1,341 @@
+/**
+ * @file
+ * Ethernet common functions
+ *
+ * @defgroup ethernet Ethernet
+ * @ingroup callbackstyle_api
+ */
+
+/*
+ * Copyright (c) 2001-2003 Swedish Institute of Computer Science.
+ * Copyright (c) 2003-2004 Leon Woestenberg <leon.woestenberg@axon.tv>
+ * Copyright (c) 2003-2004 Axon Digital Design B.V., The Netherlands.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without modification,
+ * are permitted provided that the following conditions are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ *    this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright notice,
+ *    this list of conditions and the following disclaimer in the documentation
+ *    and/or other materials provided with the distribution.
+ * 3. The name of the author may not be used to endorse or promote products
+ *    derived from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR IMPLIED
+ * WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF
+ * MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT
+ * SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
+ * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT
+ * OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
+ * CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING
[…]

### 2020-04-30 Aurora-lwip-sgx/Enclave/lwip/netif/ethernetif.cpp

@@ -1,0 +1,370 @@
+/**
+ * @file
+ * Ethernet Interface Skeleton
+ *
+ */
+
+/*
+ * Copyright (c) 2001-2004 Swedish Institute of Computer Science.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without modification,
+ * are permitted provided that the following conditions are met:
+ *
+ * 1. Redistributions of source code must retain the above copyright notice,
+ *    this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright notice,
+ *    this list of conditions and the following disclaimer in the documentation
+ *    and/or other materials provided with the distribution.
+ * 3. The name of the author may not be used to endorse or promote products
+ *    derived from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR IMPLIED
+ * WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF
+ * MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT
+ * SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL,
+ * EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT
+ * OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS
+ * INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN
+ * CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING
+ * IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY
+ * OF SUCH DAMAGE.
+ *
+ * This file is part of the lwIP TCP/IP stack.
+ *
+ * Author: Adam Dunkels <adam@sics.se>
+ *
+ */
+
+/*
+ * This file is a skeleton for developing Ethernet network interface
+ * drivers for lwIP. Add code to the low_level functions and do a
[…]

### 2020-04-30 Aurora-lwip-sgx/Enclave/smx/aead_aes256gcm_aesni.cpp

@@ -1,0 +1,1079 @@
+
+/*
+ * AES256-GCM, based on the "Intel Carry-Less Multiplication Instruction and its Usage for Computing
+ * the GCM Mode" paper and reference code, using the aggregated reduction method.
+ * Originally adapted by Romain Dolbeau.
+ */
+
+#include <errno.h>
+#include <stdint.h>
+#include <stdlib.h>
+#include <string.h>
+
+#include "core.h"
+#include "crypto_aead_aes256gcm.h"
+#include "export.h"
+#include "private/common.h"
+#include "private/sse2_64_32.h"
+#include "randombytes.h"
+#include "runtime.h"
+#include "utils.h"
+
+#if 1//defined(HAVE_TMMINTRIN_H) && defined(HAVE_WMMINTRIN_H)
+
+# ifdef __GNUC__
+#  pragma GCC target("ssse3")
+#  pragma GCC target("aes")
+#  pragma GCC target("pclmul")
+# endif
+
+#include <tmmintrin.h>
+#include <wmmintrin.h>
+
+#ifndef ENOSYS
+# define ENOSYS ENXIO
+#endif
+
+#if defined(__INTEL_COMPILER) || defined(_bswap64)
+#elif defined(_MSC_VER)
+# define _bswap64(a) _byteswap_uint64(a)
+#elif defined(__GNUC__) && (__GNUC__ > 4 || (__GNUC__ == 4 && __GNUC_MINOR__ >= 2))
+# define _bswap64(a) __builtin_bswap64(a)
+#else
+static inline uint64_t
+_bswap64(const uint64_t x)
+{
+    return
+        ((x << 56) & 0xFF00000000000000UL) | ((x << 40) & 0x00FF000000000000UL) |
+        ((x << 24) & 0x0000FF0000000000UL) | ((x <<  8) & 0x000000FF00000000UL) |
+        ((x >>  8) & 0x00000000FF000000UL) | ((x >> 24) & 0x0000000000FF0000UL) |
+        ((x >> 40) & 0x000000000000FF00UL) | ((x >> 56) & 0x00000000000000FFUL);
+}
+#endif
+
+typedef struct context {
+    CRYPTO_ALIGN(16) unsigned char H[16];
+    __m128i          rkeys[16];
+} context;
+
+static inline void
+aesni_key256_expand(const unsigned char *key, __m128i * const rkeys)
+{
+    __m128i  X0, X1, X2, X3;
[…]

### 2020-04-30 Aurora-lwip-sgx/Enclave/smx/ring_buffer.cpp

@@ -1,0 +1,196 @@
+#include <stdarg.h>
+#include <string.h>
+#include <stdio.h>      /* vsnprintf */
+
+#include "Enclave.h"
+#include "Enclave_t.h"  /* print_string */
+#include "user_types.h"
+
+#include "sodium.h"
+
+void _print_hex(const char* what, const void* v, const unsigned long l);
+void checkpoint(const char *what);
+
+#define printf
+#define checkpoint
+
+/**
+    In/Out Ring Buffer ownership
+*/
+
+#define IN_SMM  0x00
+#define IN_SGX  0x01
+#define OUT_SMM 0x02
+#define OUT_SGX 0x03
+
+// Currently we only set 64 entries for one buffer
+#define MAX_ENTRY (64)
+
+struct metadata {
+    char in_bitmap[MAX_ENTRY];
+    char out_bitmap[MAX_ENTRY];
+    char reserved[PKT_SIZE - 2*MAX_ENTRY];
+};
+
+extern unsigned char *uio_ram;
+
+void init_metadata()
+{
+    int i;
+    struct metadata *p_meta = (struct metadata *)uio_ram;
+
+    // initially, all OUT belong to SGX
+    for (i = 0; i < MAX_ENTRY; ++i) {
+        printf("0x%0x\n", p_meta->out_bitmap[i]);
+    }
+
+    // initially, all IN belong to SMM
+    for (i = 0; i < MAX_ENTRY; ++i) {
+        printf("0x%0x\n", p_meta->in_bitmap[i]);
+    }
+}
+
+/**
+    This method will encrypt the raw message inside SGX EPC,
+    then search for available OUT buffer and put it there.
+    The out_bit will be marked at the end.
+*/
+int put_out_buffer(unsigned char *raw_msg, const int msg_len)
+{
+checkpoint("EPC encrypt begin");
+    unsigned char      message[MSG_SIZE];
+    unsigned char      ciphertext[PKT_SIZE];
+    unsigned char      *ad = (unsigned char *)"";
+    unsigned char      nonce[crypto_aead_aes256gcm_NPUBBYTES];
+    unsigned char      key[crypto_aead_aes256gcm_KEYBYTES];
+    size_t             ad_len = 0;
+    unsigned long long found_ciphertext_len;
+
+    int i;
+    unsigned char *pos;
+    struct metadata *p_meta = (struct metadata *)uio_ram;
+
+    // too large. TODO: fragment
+    if (MSG_SIZE < msg_len)
+        return -1;
+
[…]

### 2020-04-30 Aurora-lwip-sgx/Enclave/test.cpp

@@ -1,0 +1,711 @@
+
+#include "lwip/mem.h"
+#include "lwip/opt.h"
+#include "lwip/sockets.h"
+#include "lwip/priv/sockets_priv.h"
+#include "lwip/stats.h"
+
+#include "lwip/tcpip.h"
+#include "lwip/priv/tcp_priv.h"
+#include "lwip/api.h"
+
+#include "lwip/udp.h"
+#include "lwip/etharp.h"
+#include "netif/ethernet.h"
+#include "lwip/stats.h"
+#include "lwip/prot/iana.h"
+#include "lwip/sockets.h"
+#include "lwip/netif.h"
+#include "lwip/etharp.h"
+#include "netif/ethernet.h"
+
+struct eth_addr test_ethaddr =  {{6,2,9,3,8,1}};
+struct eth_addr test_ethaddr2 = {{6,2,9,3,8,2}};
+struct eth_addr test_ethaddr3 = {{6,2,9,3,8,3}};
+struct eth_addr test_ethaddr4 = {{6,2,9,3,8,4}};
+
+int linkoutput_ctr;
+
+#define fail_unless(x) { if (0 != (x)) {;} \
+    else {printf("FILE: %s LINE: %d\n", __FILE__, __LINE__); abort();} }
+#define fail abort
+
+#define NUM_SOCKETS MEMP_NUM_NETCONN
+
+static int
+test_sockets_alloc_socket_nonblocking(int domain, int type)
+{
+  int s = lwip_socket(domain, type, 0);
+  if (s >= 0) {
+    int ret = lwip_fcntl(s, F_SETFL, O_NONBLOCK);
+    fail_unless(ret == 0);
+  }
+  return s;
+}
+
+static void test_sockets_msgapi_update_iovs(struct msghdr *msg, size_t bytes)
+{
+  int i;
+
+  /* note: this modifies the underyling iov_base and iov_len for a partial
+     read for an individual vector. This updates the msg->msg_iov pointer
+     to skip fully consumed vecotrs */
+
+  /* process fully consumed vectors */
+  for (i = 0; i < msg->msg_iovlen; i++) {
+    if (msg->msg_iov[i].iov_len <= bytes) {
+      /* reduce bytes by amount of this vector */
+      bytes -= msg->msg_iov[i].iov_len;
+    } else {
+      break; /* iov not fully consumed */
+    }
+  }
+
[…]

### 2020-04-30 Aurora-lwip-sgx/Include/libsodium/sodium/crypto_onetimeauth_poly1305.h

@@ -1,0 +1,67 @@
+#ifndef crypto_onetimeauth_poly1305_H
+#define crypto_onetimeauth_poly1305_H
+
+#ifdef __cplusplus
+# ifdef __GNUC__
+#  pragma GCC diagnostic ignored "-Wlong-long"
+# endif
+extern "C" {
+#endif
+
+#include <stdint.h>
+#include <stdio.h>
+#include <stdlib.h>
+
+//#include <sys/types.h>
+
+#include "export.h"
+
+typedef struct CRYPTO_ALIGN(16) crypto_onetimeauth_poly1305_state {
+    unsigned char opaque[256];
+} crypto_onetimeauth_poly1305_state;
+
+SODIUM_EXPORT
+size_t crypto_onetimeauth_poly1305_statebytes(void);
+
+#define crypto_onetimeauth_poly1305_BYTES 16U
+SODIUM_EXPORT
+size_t crypto_onetimeauth_poly1305_bytes(void);
+
+#define crypto_onetimeauth_poly1305_KEYBYTES 32U
+SODIUM_EXPORT
+size_t crypto_onetimeauth_poly1305_keybytes(void);
+
+SODIUM_EXPORT
+int crypto_onetimeauth_poly1305(unsigned char *out,
+                                const unsigned char *in,
+                                unsigned long long inlen,
+                                const unsigned char *k);
+
+SODIUM_EXPORT
+int crypto_onetimeauth_poly1305_verify(const unsigned char *h,
+                                       const unsigned char *in,
+                                       unsigned long long inlen,
+                                       const unsigned char *k)
+            __attribute__ ((warn_unused_result));
+
+SODIUM_EXPORT
+int crypto_onetimeauth_poly1305_init(crypto_onetimeauth_poly1305_state *state,
+                                     const unsigned char *key);
+
+SODIUM_EXPORT
+int crypto_onetimeauth_poly1305_update(crypto_onetimeauth_poly1305_state *state,
+                                       const unsigned char *in,
+                                       unsigned long long inlen);
+
+SODIUM_EXPORT
+int crypto_onetimeauth_poly1305_final(crypto_onetimeauth_poly1305_state *state,
+                                      unsigned char *out);
+
+SODIUM_EXPORT
+void crypto_onetimeauth_poly1305_keygen(unsigned char k[crypto_onetimeauth_poly1305_KEYBYTES]);
+
+#ifdef __cplusplus
+}
+#endif
+
+#endif

### 2020-04-30 Aurora-lwip-sgx/Include/libsodium/sodium/randombytes.h

@@ -1,0 +1,68 @@
+
+#ifndef randombytes_H
+#define randombytes_H
+
+#include <stddef.h>
+#include <stdint.h>
+
+//#include <sys/types.h>
+
+#include "export.h"
+
+#ifdef __cplusplus
+# ifdef __GNUC__
+#  pragma GCC diagnostic ignored "-Wlong-long"
+# endif
+extern "C" {
+#endif
+
+typedef struct randombytes_implementation {
+    const char *(*implementation_name)(void); /* required */
+    uint32_t    (*random)(void);              /* required */
+    void        (*stir)(void);                /* optional */
+    uint32_t    (*uniform)(const uint32_t upper_bound); /* optional, a default implementation will be used if NULL */
+    void        (*buf)(void * const buf, const size_t size); /* required */
+    int         (*close)(void);               /* optional */
+} randombytes_implementation;
+
+#define randombytes_BYTES_MAX SODIUM_MIN(SODIUM_SIZE_MAX, 0xffffffffUL)
+
+#define randombytes_SEEDBYTES 32U
+SODIUM_EXPORT
+size_t randombytes_seedbytes(void);
+
+SODIUM_EXPORT
+void randombytes_buf(void * const buf, const size_t size);
+
+SODIUM_EXPORT
+void randombytes_buf_deterministic(void * const buf, const size_t size,
+                                   const unsigned char seed[randombytes_SEEDBYTES]);
+
+SODIUM_EXPORT
+uint32_t randombytes_random(void);
+
+SODIUM_EXPORT
+uint32_t randombytes_uniform(const uint32_t upper_bound);
+
+SODIUM_EXPORT
+void randombytes_stir(void);
+
+SODIUM_EXPORT
+int randombytes_close(void);
+
+SODIUM_EXPORT
+int randombytes_set_implementation(randombytes_implementation *impl);
+
+SODIUM_EXPORT
+const char *randombytes_implementation_name(void);
+
+/* -- NaCl compatibility interface -- */
+
+SODIUM_EXPORT
+void randombytes(unsigned char * const buf, const unsigned long long buf_len);
+
+#ifdef __cplusplus
+}
+#endif
+
+#endif

### 2020-04-30 Aurora-lwip-sgx/Include/sys/socket.h

@@ -1,0 +1,507 @@
+/*
+ * Copyright (C) 2013-15 Freie Universität Berlin
+ *
+ * This file is subject to the terms and conditions of the GNU Lesser
+ * General Public License v2.1. See the file LICENSE in the top level
+ * directory for more details.
+ */
+
+/**
+ * @addtogroup  posix_sockets
+ * @{
+ */
+
+/**
+ * @file
+ * @brief   Main socket header
+ * @see     <a href="http://pubs.opengroup.org/onlinepubs/9699919799/basedefs/sys_socket.h.html">
+ *              The Open Group Base Specifications Issue 7, <sys/socket.h>
+ *          </a>
+ *
+ * @todo Omitted from original specification for now:
+ * * struct msghdr, struct cmesghdr, and struct linger and all related defines
+ * * getsockopt()/setsockopt() and all related defines.
+ * * shutdown() and all related defines.
+ * * sockatmark()
+ *
+ * @author  Martine Lenders <mlenders@inf.fu-berlin.de>
+ */
+#ifndef SYS_SOCKET_H
+#define SYS_SOCKET_H
+
+#ifdef CPU_NATIVE
+/* Ignore Linux definitions in native */
+#define _BITS_SOCKADDR_H    1
+#define __SOCKADDR_COMMON(sa_prefix) \
+  sa_family_t sa_prefix##family
+
+#define __SOCKADDR_COMMON_SIZE  (sizeof (unsigned short int))
+#endif
+
+#include <stdlib.h>
+#include <sys/types.h>
+/*
+#include <sys/uio.h>
+
+#include "kernel_types.h"
+#include "net/af.h"
+#include "sys/bytes.h"
+*/
+#ifdef __cplusplus
+extern "C" {
+#endif
+
+/**
+ * @brief Maximum number of sockets available on for creation with @ref socket()
+ */
+#ifndef SOCKET_POOL_SIZE
+#ifdef MODULE_SOCK_TCP
+#define SOCKET_POOL_SIZE        (6)    /* define enough for accepted sockets */
+#else
+#define SOCKET_POOL_SIZE        (4)
+#endif
+#endif
+
+/**
+ * @brief Maximum number of incoming TCP connections a listening socket can
+ *        handle
+ */
+#ifndef SOCKET_TCP_QUEUE_SIZE
+#ifdef MODULE_SOCK_TCP
+#define SOCKET_TCP_QUEUE_SIZE   (2)
+#else
[…]

### 2020-04-30 Aurora-openssh-sgx/App/App.cpp

@@ -1,0 +1,382 @@
+/*
+ * Copyright (C) 2011-2017 Intel Corporation. All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ *
+ *   * Redistributions of source code must retain the above copyright
+ *     notice, this list of conditions and the following disclaimer.
+ *   * Redistributions in binary form must reproduce the above copyright
+ *     notice, this list of conditions and the following disclaimer in
+ *     the documentation and/or other materials provided with the
+ *     distribution.
+ *   * Neither the name of Intel Corporation nor the names of its
+ *     contributors may be used to endorse or promote products derived
+ *     from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+ * "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+ * LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
+ * A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+ * OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+ * SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
+ * LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
+ * DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
+ * THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+ * (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
+ * OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+ *
+ */
+
+#include <stdio.h>
+#include <string.h>
+#include <assert.h>
+
+# include <unistd.h>
+# include <pwd.h>
+# define MAX_PATH FILENAME_MAX
+
+#include "sgx_urts.h"
[…]

### 2020-04-30 Aurora-openssh-sgx/App/ssh/mux.cpp

@@ -1,0 +1,2306 @@
+/* $OpenBSD: mux.c,v 1.69 2017/09/20 05:19:00 dtucker Exp $ */
+/*
+ * Copyright (c) 2002-2008 Damien Miller <djm@openbsd.org>
+ *
+ * Permission to use, copy, modify, and distribute this software for any
+ * purpose with or without fee is hereby granted, provided that the above
+ * copyright notice and this permission notice appear in all copies.
+ *
+ * THE SOFTWARE IS PROVIDED "AS IS" AND THE AUTHOR DISCLAIMS ALL WARRANTIES
+ * WITH REGARD TO THIS SOFTWARE INCLUDING ALL IMPLIED WARRANTIES OF
+ * MERCHANTABILITY AND FITNESS. IN NO EVENT SHALL THE AUTHOR BE LIABLE FOR
+ * ANY SPECIAL, DIRECT, INDIRECT, OR CONSEQUENTIAL DAMAGES OR ANY DAMAGES
+ * WHATSOEVER RESULTING FROM LOSS OF USE, DATA OR PROFITS, WHETHER IN AN
+ * ACTION OF CONTRACT, NEGLIGENCE OR OTHER TORTIOUS ACTION, ARISING OUT OF
+ * OR IN CONNECTION WITH THE USE OR PERFORMANCE OF THIS SOFTWARE.
+ */
+
+/* ssh session multiplexing support */
+
+/*
+ * TODO:
+ *   - Better signalling from master to slave, especially passing of
+ *      error messages
+ *   - Better fall-back from mux slave error to new connection.
+ *   - ExitOnForwardingFailure
+ *   - Maybe extension mechanisms for multi-X11/multi-agent forwarding
+ *   - Support ~^Z in mux slaves.
+ *   - Inspect or control sessions in master.
+ *   - If we ever support the "signal" channel request, send signals on
+ *     sessions in master.
+ */
+extern "C" {
+#include "includes.h"
+
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <sys/socket.h>
+#include <sys/un.h>
+
+#include <errno.h>
+#include <fcntl.h>
+#include <signal.h>
+#include <stdarg.h>
+#include <stddef.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <string.h>
+#include <unistd.h>
+#ifdef HAVE_PATHS_H
+#include <paths.h>
+#endif
+
[…]

### 2020-04-30 Aurora-openssh-sgx/App/ssh/readconf.cpp

@@ -1,0 +1,2633 @@
+/* $OpenBSD: readconf.c,v 1.283 2018/02/23 15:58:37 markus Exp $ */
+/*
+ * Author: Tatu Ylonen <ylo@cs.hut.fi>
+ * Copyright (c) 1995 Tatu Ylonen <ylo@cs.hut.fi>, Espoo, Finland
+ *                    All rights reserved
+ * Functions for reading the configuration files.
+ *
+ * As far as I am concerned, the code I have written for this software
+ * can be used freely for any purpose.  Any derived versions of this
+ * software must be clearly marked as such, and if the derived work is
+ * incompatible with the protocol description in the RFC file, it must be
+ * called by a name other than "ssh" or "Secure Shell".
+ */
+extern "C" {
+#include "includes.h"
+
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <sys/socket.h>
+#include <sys/wait.h>
+#include <sys/un.h>
+
+#include <netinet/in.h>
+#include <netinet/in_systm.h>
+#include <netinet/ip.h>
+#include <arpa/inet.h>
+
+#include <ctype.h>
+#include <errno.h>
+#include <fcntl.h>
+#include <limits.h>
+#include <netdb.h>
+#ifdef HAVE_PATHS_H
+# include <paths.h>
+#endif
+#include <pwd.h>
+#include <signal.h>
+#include <stdarg.h>
+#include <stdio.h>
+#include <string.h>
+#include <unistd.h>
+#ifdef USE_SYSTEM_GLOB
+# include <glob.h>
+#else
+# include "openbsd-compat/glob.h"
+#endif
+#ifdef HAVE_UTIL_H
+#include <util.h>
+#endif
+#if defined(HAVE_STRNVIS) && defined(HAVE_VIS_H) && !defined(BROKEN_STRNVIS)
+# include <vis.h>
+#endif
+
+#include "xmalloc.h"
+#include "ssh.h"
+#include "compat.h"
+#include "cipher.h"
+#include "pathnames.h"
+#include "log.h"
+#include "sshkey.h"
+#include "misc.h"
+#include "readconf.h"
+#include "match.h"
+#include "kex.h"
+#include "mac.h"
+#include "uidswap.h"
+#include "myproposal.h"
+#include "digest.h"
+}
+/* Format of the configuration file:
+
+   # Configuration data is parsed as follows:
[…]

### 2020-04-30 Aurora-openssh-sgx/App/ssh/sshconnect.cpp

@@ -1,0 +1,1601 @@
+/* $OpenBSD: sshconnect.c,v 1.297 2018/02/23 15:58:38 markus Exp $ */
+/*
+ * Author: Tatu Ylonen <ylo@cs.hut.fi>
+ * Copyright (c) 1995 Tatu Ylonen <ylo@cs.hut.fi>, Espoo, Finland
+ *                    All rights reserved
+ * Code to connect to a remote host, and to perform the client side of the
+ * login (authentication) dialog.
+ *
+ * As far as I am concerned, the code I have written for this software
+ * can be used freely for any purpose.  Any derived versions of this
+ * software must be clearly marked as such, and if the derived work is
+ * incompatible with the protocol description in the RFC file, it must be
+ * called by a name other than "ssh" or "Secure Shell".
+ */
+extern "C" {
+#include "includes.h"
+
+#include <sys/types.h>
+#include <sys/wait.h>
+#include <sys/stat.h>
+#include <sys/socket.h>
+#ifdef HAVE_SYS_TIME_H
+# include <sys/time.h>
+#endif
+
+#include <net/if.h>
+#include <netinet/in.h>
+#include <arpa/inet.h>
+
+#include <ctype.h>
+#include <errno.h>
+#include <fcntl.h>
+#include <netdb.h>
+#ifdef HAVE_PATHS_H
+#include <paths.h>
+#endif
+#include <pwd.h>
+#ifdef HAVE_POLL_H
+#include <poll.h>
+#endif
+#include <signal.h>
+#include <stdarg.h>
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+#include <unistd.h>
+#ifdef HAVE_IFADDRS_H
+# include <ifaddrs.h>
+#endif
+
+#include "xmalloc.h"
+#include "key.h"
+#include "hostfile.h"
+#include "ssh.h"
+#include "buffer.h"
+#include "packet.h"
+#include "uidswap.h"
+#include "compat.h"
+#include "key.h"
+#include "sshconnect.h"
+#include "hostfile.h"
+#include "log.h"
+#include "misc.h"
+#include "readconf.h"
+#include "atomicio.h"
+#include "dns.h"
+#include "monitor_fdpass.h"
+#include "ssh2.h"
+#include "version.h"
+#include "authfile.h"
+#include "ssherr.h"
+#include "authfd.h"
+}
+char *client_version_string = NULL;
[…]

### 2020-04-30 Aurora-openssh-sgx/App/ssh/sshconnect2.cpp

@@ -1,0 +1,2043 @@
+/* $OpenBSD: sshconnect2.c,v 1.270 2018/03/24 19:28:43 markus Exp $ */
+/*
+ * Copyright (c) 2000 Markus Friedl.  All rights reserved.
+ * Copyright (c) 2008 Damien Miller.  All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR
+ * IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES
+ * OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED.
+ * IN NO EVENT SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT,
+ * INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT
+ * NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
+ * DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
+ * THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+ * (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF
+ * THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+ */
+extern "C" {
+#include "includes.h"
+
+#include <sys/types.h>
+#include <sys/socket.h>
+#include <sys/wait.h>
+#include <sys/stat.h>
+
+#include <errno.h>
+#include <fcntl.h>
+#include <netdb.h>
+#include <pwd.h>
+#include <signal.h>
+#include <stdarg.h>
+#include <stdio.h>
+#include <string.h>
[…]

### 2020-04-30 Aurora-openssh-sgx/App/ssh/sshtty.cpp

@@ -1,0 +1,96 @@
+/* $OpenBSD: sshtty.c,v 1.14 2010/01/09 05:04:24 djm Exp $ */
+/*
+ * Author: Tatu Ylonen <ylo@cs.hut.fi>
+ * Copyright (c) 1995 Tatu Ylonen <ylo@cs.hut.fi>, Espoo, Finland
+ *                    All rights reserved
+ *
+ * As far as I am concerned, the code I have written for this software
+ * can be used freely for any purpose.  Any derived versions of this
+ * software must be clearly marked as such, and if the derived work is
+ * incompatible with the protocol description in the RFC file, it must be
+ * called by a name other than "ssh" or "Secure Shell".
+ */
+/*
+ * Copyright (c) 2001 Markus Friedl.  All rights reserved.
+ * Copyright (c) 2001 Kevin Steves.  All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 1. Redistributions of source code must retain the above copyright
+ *    notice, this list of conditions and the following disclaimer.
+ * 2. Redistributions in binary form must reproduce the above copyright
+ *    notice, this list of conditions and the following disclaimer in the
+ *    documentation and/or other materials provided with the distribution.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE AUTHOR ``AS IS'' AND ANY EXPRESS OR
+ * IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES
+ * OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED.
+ * IN NO EVENT SHALL THE AUTHOR BE LIABLE FOR ANY DIRECT, INDIRECT,
+ * INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT
+ * NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
[…]

### 2020-04-30 Aurora-openssh-sgx/Enclave/debug.cpp

@@ -1,0 +1,79 @@
+#include "Enclave.h"
+#include "Enclave_t.h"  /* print_string */
+
+#include <stddef.h>
+#include <ctype.h>
+
+//#define TIMESTAMP_DEBUG
+
+typedef struct __check_point {
+    unsigned char *event;
+    unsigned long timestamp;
+} check_point;
+
+check_point checkpoints[64];
+
+static size_t occurence = 0;
+
+void checkpoint(const char *what)
+{
+#ifdef TIMESTAMP_DEBUG
+    long unsigned tsc = 0;
+    ocall_tsc(&tsc);
+
+    checkpoints[occurence].event = (unsigned char *)what;
+    checkpoints[occurence].timestamp = tsc;
+    occurence++;
+#endif
+}
+
+void _print_info()
+{
+#ifdef TIMESTAMP_DEBUG
+    static int n = 1;
+    printf("Microbenchmark inside SGX : %d\n", n++);
+    for (int i = 1; i < occurence; ++i) {
+        printf("%s - %s: TSC delta = %lu == %lu us\n", checkpoints[i].event, checkpoints[i-1].event,
+            checkpoints[i].timestamp - checkpoints[i-1].timestamp,
+            (checkpoints[i].timestamp - checkpoints[i-1].timestamp) / 2808);
+    }
+
+    long unsigned diff = checkpoints[occurence-1].timestamp - checkpoints[0].timestamp;
+    printf("Summary: loopback used %lu ticks == %lu us.\n\n", diff, diff / 2808);
+
+    occurence = 0;
+#endif
+}
+
+void _print_hex(const char* what, const void* v, const unsigned long l)
+{
+  const unsigned char* p = (unsigned char*)v;
+  unsigned long x, y = 0, z;
+  printf("%s contents: \n", what);
+  for (x = 0; x < l; ) {
+      printf("%02X ", p[x]);
+      if (!(++x % 16) || x == l) {
+         if((x % 16) != 0) {
+            z = 16 - (x % 16);
+            if(z >= 8)
+               printf(" ");
+            for (; z != 0; --z) {
+               printf("   ");
+            }
+         }
+         printf(" | ");
+         for(; y < x; y++) {
+            if((y % 8) == 0)
+               printf(" ");
+            if(isgraph(p[y]))
+               printf("%c", p[y]);
+            else
+               printf(".");
+         }
+         printf("\n");
+      }
+      else if((x % 8) == 0) {
+         printf(" ");
+      }
+  }
+}

### 2020-04-30 Aurora-openssh-sgx/Enclave/ring_buffer.cpp

@@ -1,0 +1,204 @@
+#include <stdarg.h>
+#include <string.h>
+#include <stdio.h>      /* vsnprintf */
+
+#include "Enclave.h"
+#include "Enclave_t.h"  /* print_string */
+#include "sgx_trts.h"
+
+#include "sodium.h"
+
+void _print_info();
+void checkpoint(const char *what);
+void _print_hex(const char* what, const void* v, const unsigned long l);
+
+/**
+    In/Out Ring Buffer ownership
+*/
+
+#define PKT_SIZE  (1 << 12)
+#define MSG_SIZE  (PKT_SIZE - 16)
+
+#define IN_SMM  0x00
+#define IN_SGX  0x01
+#define OUT_SMM 0x02
+#define OUT_SGX 0x03
+
+// Currently we only set 64 entries for one buffer
+#define MAX_ENTRY (64)
+
+struct metadata {
+    char in_bitmap[MAX_ENTRY];
+    char out_bitmap[MAX_ENTRY];
+    char reserved[PKT_SIZE - 2*MAX_ENTRY];
+};
+
+extern unsigned char *uio_ram;
+
+/**
+    This method will encrypt the raw message inside SGX EPC,
+    then search for available OUT buffer and put it there.
+    The out_bit will be marked at the end.
+*/
+int put_out_buffer(unsigned char *raw_msg, const int msg_len)
+{
+    unsigned char      message[MSG_SIZE];
+    unsigned char      ciphertext[PKT_SIZE];
+    unsigned char      *ad = (unsigned char *)"";
+    unsigned char      nonce[crypto_aead_aes256gcm_NPUBBYTES];
+    unsigned char      key[crypto_aead_aes256gcm_KEYBYTES];
+    size_t             ad_len = 0;
+    unsigned long long found_ciphertext_len;
+
+    int i;
+    unsigned char *pos;
+    struct metadata *p_meta = (struct metadata *)uio_ram;
+    
+    // the message must come from enclave
+    if (0 == sgx_is_within_enclave(raw_msg, msg_len)) {
+        return -1;
+    }
+    
+    if (msg_len < 0)
+        return -1;
+
+    // too large. TODO: fragment
+    if (MSG_SIZE < msg_len)
+        return -1;
+
+    memcpy(message, raw_msg, msg_len);
+    // pad if short
+    if (MSG_SIZE > msg_len) {
+        randombytes_buf(message + msg_len, MSG_SIZE - msg_len);
+    }
+#if 1
[…]

### 2020-04-30 Aurora-qemu-sgx/block/gluster.c

@@ -1,0 +1,1531 @@
+/*
+ * GlusterFS backend for QEMU
+ *
+ * Copyright (C) 2012 Bharata B Rao <bharata@linux.vnet.ibm.com>
+ *
+ * This work is licensed under the terms of the GNU GPL, version 2 or later.
+ * See the COPYING file in the top-level directory.
+ *
+ */
+#include "qemu/osdep.h"
+#include <glusterfs/api/glfs.h>
+#include "block/block_int.h"
+#include "qapi/error.h"
+#include "qapi/qmp/qerror.h"
+#include "qemu/uri.h"
+#include "qemu/error-report.h"
+#include "qemu/cutils.h"
+
+#define GLUSTER_OPT_FILENAME        "filename"
+#define GLUSTER_OPT_VOLUME          "volume"
+#define GLUSTER_OPT_PATH            "path"
+#define GLUSTER_OPT_TYPE            "type"
+#define GLUSTER_OPT_SERVER_PATTERN  "server."
+#define GLUSTER_OPT_HOST            "host"
+#define GLUSTER_OPT_PORT            "port"
+#define GLUSTER_OPT_TO              "to"
+#define GLUSTER_OPT_IPV4            "ipv4"
+#define GLUSTER_OPT_IPV6            "ipv6"
+#define GLUSTER_OPT_SOCKET          "socket"
+#define GLUSTER_OPT_DEBUG           "debug"
+#define GLUSTER_DEFAULT_PORT        24007
+#define GLUSTER_DEBUG_DEFAULT       4
+#define GLUSTER_DEBUG_MAX           9
+#define GLUSTER_OPT_LOGFILE         "logfile"
+#define GLUSTER_LOGFILE_DEFAULT     "-" /* handled in libgfapi as /dev/stderr */
+
+#define GERR_INDEX_HINT "hint: check in 'server' array index '%d'\n"
+
+typedef struct GlusterAIOCB {
+    int64_t size;
+    int ret;
+    Coroutine *coroutine;
+    AioContext *aio_context;
+} GlusterAIOCB;
+
+typedef struct BDRVGlusterState {
+    struct glfs *glfs;
+    struct glfs_fd *fd;
+    char *logfile;
+    bool supports_seek_data;
+    int debug_level;
+} BDRVGlusterState;
+
+typedef struct BDRVGlusterReopenState {
+    struct glfs *glfs;
+    struct glfs_fd *fd;
[…]

### 2020-04-30 Aurora-qemu-sgx/block/nfs.c

@@ -1,0 +1,875 @@
+/*
+ * QEMU Block driver for native access to files on NFS shares
+ *
+ * Copyright (c) 2014-2016 Peter Lieven <pl@kamp.de>
+ *
+ * Permission is hereby granted, free of charge, to any person obtaining a copy
+ * of this software and associated documentation files (the "Software"), to deal
+ * in the Software without restriction, including without limitation the rights
+ * to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
+ * copies of the Software, and to permit persons to whom the Software is
+ * furnished to do so, subject to the following conditions:
+ *
+ * The above copyright notice and this permission notice shall be included in
+ * all copies or substantial portions of the Software.
+ *
+ * THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+ * IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+ * FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL
+ * THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
+ * LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
+ * OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
+ * THE SOFTWARE.
+ */
+
+#include "qemu/osdep.h"
+
+#include <poll.h>
+#include "qemu-common.h"
+#include "qemu/config-file.h"
+#include "qemu/error-report.h"
+#include "qapi/error.h"
+#include "block/block_int.h"
+#include "trace.h"
+#include "qemu/iov.h"
+#include "qemu/uri.h"
+#include "qemu/cutils.h"
+#include "sysemu/sysemu.h"
+#include "qapi/qmp/qdict.h"
+#include "qapi/qmp/qint.h"
+#include "qapi/qmp/qstring.h"
+#include "qapi-visit.h"
+#include "qapi/qobject-input-visitor.h"
+#include "qapi/qobject-output-visitor.h"
+#include <nfsc/libnfs.h>
+
+
[…]

### 2020-04-30 Aurora-qemu-sgx/exec.c

@@ -1,0 +1,3782 @@
+/*
+ *  Virtual page mapping
+ *
+ *  Copyright (c) 2003 Fabrice Bellard
+ *
+ * This library is free software; you can redistribute it and/or
+ * modify it under the terms of the GNU Lesser General Public
+ * License as published by the Free Software Foundation; either
+ * version 2 of the License, or (at your option) any later version.
+ *
+ * This library is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU
+ * Lesser General Public License for more details.
+ *
+ * You should have received a copy of the GNU Lesser General Public
+ * License along with this library; if not, see <http://www.gnu.org/licenses/>.
+ */
+#include "qemu/osdep.h"
+#include "qapi/error.h"
+#ifndef _WIN32
+#endif
+
+#include "qemu/cutils.h"
+#include "cpu.h"
+#include "exec/exec-all.h"
+#include "tcg.h"
+#include "hw/qdev-core.h"
+#if !defined(CONFIG_USER_ONLY)
+#include "hw/boards.h"
+#include "hw/xen/xen.h"
+#endif
+#include "sysemu/kvm.h"
+#include "sysemu/sysemu.h"
+#include "qemu/timer.h"
+#include "qemu/config-file.h"
+#include "qemu/error-report.h"
+#if defined(CONFIG_USER_ONLY)
+#include "qemu.h"
+#else /* !CONFIG_USER_ONLY */
+#include "hw/hw.h"
+#include "exec/memory.h"
+#include "exec/ioport.h"
+#include "sysemu/dma.h"
+#include "exec/address-spaces.h"
+#include "sysemu/xen-mapcache.h"
+#include "trace.h"
+#endif
+#include "exec/cpu-all.h"
+#include "qemu/rcu_queue.h"
+#include "qemu/main-loop.h"
+#include "translate-all.h"
+#include "sysemu/replay.h"
+
+#include "exec/memory-internal.h"
+#include "exec/ram_addr.h"
+#include "exec/log.h"
+
+#include "migration/vmstate.h"
+
+#include "qemu/range.h"
+#ifndef _WIN32
+#include "qemu/mmap-alloc.h"
+#endif
+
+//#define DEBUG_SUBPAGE
+
+#if !defined(CONFIG_USER_ONLY)
[…]

### 2020-04-30 Aurora-qemu-sgx/hw/i386/acpi-build.c

@@ -1,0 +1,3059 @@
+/* Support for generating ACPI tables and passing them to Guests
+ *
+ * Copyright (C) 2008-2010  Kevin O'Connor <kevin@koconnor.net>
+ * Copyright (C) 2006 Fabrice Bellard
+ * Copyright (C) 2013 Red Hat Inc
+ *
+ * Author: Michael S. Tsirkin <mst@redhat.com>
+ *
+ * This program is free software; you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation; either version 2 of the License, or
+ * (at your option) any later version.
+
+ * This program is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+
+ * You should have received a copy of the GNU General Public License along
+ * with this program; if not, see <http://www.gnu.org/licenses/>.
+ */
+
+#include "qemu/osdep.h"
+#include "qapi/error.h"
+#include "acpi-build.h"
+#include "qemu-common.h"
+#include "qemu/bitmap.h"
+#include "qemu/error-report.h"
+#include "hw/pci/pci.h"
+#include "qom/cpu.h"
+#include "hw/i386/pc.h"
+#include "target-i386/cpu.h"
+#include "hw/timer/hpet.h"
+#include "hw/acpi/acpi-defs.h"
+#include "hw/acpi/acpi.h"
+#include "hw/acpi/cpu.h"
+#include "hw/nvram/fw_cfg.h"
+#include "hw/acpi/bios-linker-loader.h"
+#include "hw/loader.h"
+#include "hw/isa/isa.h"
+#include "hw/block/fdc.h"
+#include "hw/acpi/memory_hotplug.h"
+#include "sysemu/tpm.h"
+#include "hw/acpi/tpm.h"
+#include "sysemu/tpm_backend.h"
+#include "hw/timer/mc146818rtc_regs.h"
+#include "sysemu/numa.h"
+
+/* Supported chipsets: */
+#include "hw/acpi/piix4.h"
+#include "hw/acpi/pcihp.h"
+#include "hw/i386/ich9.h"
+#include "hw/pci/pci_bus.h"
+#include "hw/pci-host/q35.h"
+#include "hw/i386/x86-iommu.h"
+
[…]

### 2020-04-30 Aurora-qemu-sgx/hw/i386/pc_piix.c

@@ -1,0 +1,1134 @@
+/*
+ * QEMU PC System Emulator
+ *
+ * Copyright (c) 2003-2004 Fabrice Bellard
+ *
+ * Permission is hereby granted, free of charge, to any person obtaining a copy
+ * of this software and associated documentation files (the "Software"), to deal
+ * in the Software without restriction, including without limitation the rights
+ * to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
+ * copies of the Software, and to permit persons to whom the Software is
+ * furnished to do so, subject to the following conditions:
+ *
+ * The above copyright notice and this permission notice shall be included in
+ * all copies or substantial portions of the Software.
+ *
+ * THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+ * IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+ * FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL
+ * THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
+ * LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
+ * OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
+ * THE SOFTWARE.
+ */
+
+#include "qemu/osdep.h"
+
+#include "hw/hw.h"
+#include "hw/loader.h"
+#include "hw/i386/pc.h"
+#include "hw/i386/apic.h"
+#include "hw/smbios/smbios.h"
+#include "hw/pci/pci.h"
+#include "hw/pci/pci_ids.h"
+#include "hw/usb.h"
+#include "net/net.h"
+#include "hw/boards.h"
+#include "hw/ide.h"
+#include "sysemu/kvm.h"
+#include "hw/kvm/clock.h"
+#include "sysemu/sysemu.h"
+#include "hw/sysbus.h"
+#include "sysemu/arch_init.h"
+#include "sysemu/block-backend.h"
+#include "hw/i2c/smbus.h"
+#include "hw/xen/xen.h"
+#include "exec/memory.h"
+#include "exec/address-spaces.h"
[…]

### 2020-04-30 Aurora-qemu-sgx/hw/i386/pc_q35.c

@@ -1,0 +1,379 @@
+/*
+ * Q35 chipset based pc system emulator
+ *
+ * Copyright (c) 2003-2004 Fabrice Bellard
+ * Copyright (c) 2009, 2010
+ *               Isaku Yamahata <yamahata at valinux co jp>
+ *               VA Linux Systems Japan K.K.
+ * Copyright (C) 2012 Jason Baron <jbaron@redhat.com>
+ *
+ * This is based on pc.c, but heavily modified.
+ *
+ * Permission is hereby granted, free of charge, to any person obtaining a copy
+ * of this software and associated documentation files (the "Software"), to deal
+ * in the Software without restriction, including without limitation the rights
+ * to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
+ * copies of the Software, and to permit persons to whom the Software is
+ * furnished to do so, subject to the following conditions:
+ *
+ * The above copyright notice and this permission notice shall be included in
+ * all copies or substantial portions of the Software.
+ *
+ * THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+ * IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+ * FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL
+ * THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
+ * LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
+ * OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
+ * THE SOFTWARE.
+ */
+#include "qemu/osdep.h"
+#include "hw/hw.h"
+#include "hw/loader.h"
+#include "sysemu/arch_init.h"
+#include "hw/i2c/smbus.h"
+#include "hw/boards.h"
+#include "hw/timer/mc146818rtc.h"
+#include "hw/xen/xen.h"
+#include "sysemu/kvm.h"
+#include "hw/kvm/clock.h"
+#include "hw/pci-host/q35.h"
+#include "exec/address-spaces.h"
+#include "hw/i386/pc.h"
+#include "hw/i386/ich9.h"
+#include "hw/smbios/smbios.h"
+#include "hw/ide/pci.h"
[…]

### 2020-04-30 Aurora-qemu-sgx/hw/input/pckbd.c

@@ -1,0 +1,589 @@
+/*
+ * QEMU PC keyboard emulation
+ *
+ * Copyright (c) 2003 Fabrice Bellard
+ *
+ * Permission is hereby granted, free of charge, to any person obtaining a copy
+ * of this software and associated documentation files (the "Software"), to deal
+ * in the Software without restriction, including without limitation the rights
+ * to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
+ * copies of the Software, and to permit persons to whom the Software is
+ * furnished to do so, subject to the following conditions:
+ *
+ * The above copyright notice and this permission notice shall be included in
+ * all copies or substantial portions of the Software.
+ *
+ * THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+ * IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+ * FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL
+ * THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
+ * LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
+ * OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
+ * THE SOFTWARE.
+ */
+#include "qemu/osdep.h"
+#include "hw/hw.h"
+#include "hw/isa/isa.h"
+#include "hw/i386/pc.h"
+#include "hw/input/ps2.h"
+#include "sysemu/sysemu.h"
+
+/* debug PC keyboard */
+//#define DEBUG_KBD
+#ifdef DEBUG_KBD
+#define DPRINTF(fmt, ...)                                       \
+    do { printf("KBD: " fmt , ## __VA_ARGS__); } while (0)
+#else
+#define DPRINTF(fmt, ...)
+#endif
+
+/*	Keyboard Controller Commands */
+#define KBD_CCMD_READ_MODE	0x20	/* Read mode bits */
+#define KBD_CCMD_WRITE_MODE	0x60	/* Write mode bits */
[…]

### 2020-04-30 Aurora-qemu-sgx/hw/intc/apic.c

@@ -1,0 +1,937 @@
+/*
+ *  APIC support
+ *
+ *  Copyright (c) 2004-2005 Fabrice Bellard
+ *
+ * This library is free software; you can redistribute it and/or
+ * modify it under the terms of the GNU Lesser General Public
+ * License as published by the Free Software Foundation; either
+ * version 2 of the License, or (at your option) any later version.
+ *
+ * This library is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU
+ * Lesser General Public License for more details.
+ *
+ * You should have received a copy of the GNU Lesser General Public
+ * License along with this library; if not, see <http://www.gnu.org/licenses/>
+ */
+#include "qemu/osdep.h"
+#include "qemu-common.h"
+#include "cpu.h"
+#include "qemu/thread.h"
+#include "hw/i386/apic_internal.h"
+#include "hw/i386/apic.h"
+#include "hw/i386/ioapic.h"
+#include "hw/pci/msi.h"
+#include "qemu/host-utils.h"
+#include "trace.h"
+#include "hw/i386/pc.h"
+#include "hw/i386/apic-msidef.h"
+#include "qapi/error.h"
+
+#define MAX_APICS 255
+#define MAX_APIC_WORDS 8
+
+#define SYNC_FROM_VAPIC                 0x1
+#define SYNC_TO_VAPIC                   0x2
+#define SYNC_ISR_IRR_TO_VAPIC           0x4
+
+static APICCommonState *local_apics[MAX_APICS + 1];
+
+#define TYPE_APIC "apic"
+#define APIC(obj) \
+    OBJECT_CHECK(APICCommonState, (obj), TYPE_APIC)
+
+static void apic_set_irq(APICCommonState *s, int vector_num, int trigger_mode);
+static void apic_update_irq(APICCommonState *s);
+static void apic_get_delivery_bitmask(uint32_t *deliver_bitmask,
+                                      uint8_t dest, uint8_t dest_mode);
+
+/* Find first bit starting from msb */
+static int apic_fls_bit(uint32_t value)
+{
+    return 31 - clz32(value);
+}
+
+/* Find first bit starting from lsb */
+static int apic_ffs_bit(uint32_t value)
[…]

### 2020-04-30 Aurora-qemu-sgx/hw/net/ne2000.c

@@ -1,0 +1,885 @@
+/*
+ * QEMU NE2000 emulation
+ *
+ * Copyright (c) 2003-2004 Fabrice Bellard
+ *
+ * Permission is hereby granted, free of charge, to any person obtaining a copy
+ * of this software and associated documentation files (the "Software"), to deal
+ * in the Software without restriction, including without limitation the rights
+ * to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
+ * copies of the Software, and to permit persons to whom the Software is
+ * furnished to do so, subject to the following conditions:
+ *
+ * The above copyright notice and this permission notice shall be included in
+ * all copies or substantial portions of the Software.
+ *
+ * THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+ * IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+ * FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL
+ * THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
+ * LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
+ * OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
+ * THE SOFTWARE.
+ */
+#include "qemu/osdep.h"
+#include "hw/hw.h"
+#include "hw/pci/pci.h"
+#include "net/net.h"
+#include "ne2000.h"
+#include "hw/loader.h"
+#include "sysemu/sysemu.h"
+
+/* debug NE2000 card */
+//#define DEBUG_NE2000
+
+#define MAX_ETH_FRAME_SIZE 1514
+
+#define E8390_CMD	0x00  /* The command register (for all pages) */
+/* Page 0 register offsets. */
+#define EN0_CLDALO	0x01	/* Low byte of current local dma addr  RD */
+#define EN0_STARTPG	0x01	/* Starting page of ring bfr WR */
+#define EN0_CLDAHI	0x02	/* High byte of current local dma addr  RD */
+#define EN0_STOPPG	0x02	/* Ending page +1 of ring bfr WR */
[…]

### 2020-04-30 Aurora-qemu-sgx/hw/scsi/scsi-disk.c

@@ -1,0 +1,3017 @@
+/*
+ * SCSI Device emulation
+ *
+ * Copyright (c) 2006 CodeSourcery.
+ * Based on code by Fabrice Bellard
+ *
+ * Written by Paul Brook
+ * Modifications:
+ *  2009-Dec-12 Artyom Tarasenko : implemented stamdard inquiry for the case
+ *                                 when the allocation length of CDB is smaller
+ *                                 than 36.
+ *  2009-Oct-13 Artyom Tarasenko : implemented the block descriptor in the
+ *                                 MODE SENSE response.
+ *
+ * This code is licensed under the LGPL.
+ *
+ * Note that this file only handles the SCSI architecture model and device
+ * commands.  Emulation of interface/link layer protocols is handled by
+ * the host adapter emulator.
+ */
+
+//#define DEBUG_SCSI
+
+#ifdef DEBUG_SCSI
+#define DPRINTF(fmt, ...) \
+do { printf("scsi-disk: " fmt , ## __VA_ARGS__); } while (0)
+#else
+#define DPRINTF(fmt, ...) do {} while(0)
+#endif
+
+#include "qemu/osdep.h"
+#include "qapi/error.h"
+#include "qemu/error-report.h"
+#include "hw/scsi/scsi.h"
+#include "block/scsi.h"
+#include "sysemu/sysemu.h"
+#include "sysemu/block-backend.h"
+#include "sysemu/blockdev.h"
+#include "hw/block/block.h"
+#include "sysemu/dma.h"
+#include "qemu/cutils.h"
+
+#ifdef __linux
+#include <scsi/sg.h>
+#endif
+
+#define SCSI_WRITE_SAME_MAX         524288
+#define SCSI_DMA_BUF_SIZE           131072
+#define SCSI_MAX_INQUIRY_LEN        256
+#define SCSI_MAX_MODE_LEN           256
+
+#define DEFAULT_DISCARD_GRANULARITY 4096
+#define DEFAULT_MAX_UNMAP_SIZE      (1 << 30)   /* 1 GB */
+#define DEFAULT_MAX_IO_SIZE         INT_MAX     /* 2 GB - 1 block */
+
+#define TYPE_SCSI_DISK_BASE         "scsi-disk-base"
+
+#define SCSI_DISK_BASE(obj) \
+     OBJECT_CHECK(SCSIDiskState, (obj), TYPE_SCSI_DISK_BASE)
[…]

### 2020-04-30 Aurora-qemu-sgx/hw/usb/dev-dummy.c

@@ -1,0 +1,147 @@
+/*
+ * A dummy QEMU USB device to use as a skeleton for writing your own.
+ *
+ * Copyright (c) 2012 Pantelis Koukousoulas (pktoss@gmail.com)
+ *
+ * Permission is hereby granted, free of charge, to any person obtaining a copy
+ * of this software and associated documentation files (the "Software"), to deal
+ * in the Software without restriction, including without limitation the rights
+ * to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
+ * copies of the Software, and to permit persons to whom the Software is
+ * furnished to do so, subject to the following conditions:
+ *
+ * The above copyright notice and this permission notice shall be included in
+ * all copies or substantial portions of the Software.
+ *
+ * THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+ * IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+ * FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL
+ * THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
+ * LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
+ * OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
+ * THE SOFTWARE.
+ */
+#include "qemu/osdep.h"
+#include "qapi/error.h"
+#include "qemu-common.h"
+#include "qemu/cutils.h"
+#include "qemu/error-report.h"
+#include "hw/usb.h"
+#include "hw/usb/desc.h"
+#include "sysemu/char.h"
+
+#include "hw/hw.h"
+#include "hw/usb.h"
+#include "hw/usb/desc.h"
+
+#include <stdint.h>
+
+#define TYPE_USB_DUMMY "usb-dummy-dev"
+#define USB_DUMMY_DEV(obj) OBJECT_CHECK(MSDState, (obj), TYPE_USB_DUMMY)
+
+typedef struct USBDummyState {
+    USBDevice dev;
+} USBDummyState;
+
+enum {
+    STR_MANUFACTURER = 1,
+    STR_PRODUCT,
[…]

### 2020-04-30 Aurora-qemu-sgx/hw/usb/dev-storage.c

@@ -1,0 +1,879 @@
+/*
+ * USB Mass Storage Device emulation
+ *
+ * Copyright (c) 2006 CodeSourcery.
+ * Written by Paul Brook
+ *
+ * This code is licensed under the LGPL.
+ */
+
+#include "qemu/osdep.h"
+#include "qapi/error.h"
+#include "qemu-common.h"
+#include "qemu/error-report.h"
+#include "qemu/option.h"
+#include "qemu/config-file.h"
+#include "hw/usb.h"
+#include "hw/usb/desc.h"
+#include "hw/scsi/scsi.h"
+#include "ui/console.h"
+#include "monitor/monitor.h"
+#include "sysemu/sysemu.h"
+#include "sysemu/block-backend.h"
+#include "sysemu/blockdev.h"
+#include "qapi/visitor.h"
+#include "qemu/cutils.h"
+
+void _print_hex(const char* what, const void* v, const unsigned long l)
+{
+  const unsigned char* p = (unsigned char*)v;
+  unsigned long x, y = 0, z;
+  printf("%s contents: \n", what);
+  for (x = 0; x < l; ) {
+      printf("%02X ", p[x]);
+      if (!(++x % 16) || x == l) {
+         if((x % 16) != 0) {
+            z = 16 - (x % 16);
+            if(z >= 8)
+               printf(" ");
+            for (; z != 0; --z) {
+               printf("   ");
+            }
+         }
+         printf(" | ");
+         for(; y < x; y++) {
+            if((y % 8) == 0)
+               printf(" ");
+            if(isgraph(p[y]))
+               printf("%c", p[y]);
+            else
+               printf(".");
+         }
+         printf("\n");
+      }
+      else if((x % 8) == 0) {
+         printf(" ");
+      }
+  }
+}
+
+//#define DEBUG_MSD
+
+#ifdef DEBUG_MSD
+#define DPRINTF(fmt, ...) \
+do { printf("usb-msd: " fmt , ## __VA_ARGS__); } while (0)
+#else
+#define DPRINTF(fmt, ...) do {} while(0)
+#endif
+
+/* USB requests.  */
+#define MassStorageReset  0xff
+#define GetMaxLun         0xfe
+
+enum USBMSDMode {
+    USB_MSDM_CBW, /* Command Block.  */
+    USB_MSDM_DATAOUT, /* Transfer data to device.  */
+    USB_MSDM_DATAIN, /* Transfer data from device.  */
[…]

### 2020-04-30 Aurora-qemu-sgx/target-i386/cpu.h

@@ -1,0 +1,1666 @@
+/*
+ * i386 virtual CPU header
+ *
+ *  Copyright (c) 2003 Fabrice Bellard
+ *
+ * This library is free software; you can redistribute it and/or
+ * modify it under the terms of the GNU Lesser General Public
+ * License as published by the Free Software Foundation; either
+ * version 2 of the License, or (at your option) any later version.
+ *
+ * This library is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU
+ * Lesser General Public License for more details.
+ *
+ * You should have received a copy of the GNU Lesser General Public
+ * License along with this library; if not, see <http://www.gnu.org/licenses/>.
+ */
+
+#ifndef I386_CPU_H
+#define I386_CPU_H
+
+#include "qemu-common.h"
+#include "cpu-qom.h"
+#include "standard-headers/asm-x86/hyperv.h"
+
+#ifdef TARGET_X86_64
+#define TARGET_LONG_BITS 64
+#else
+#define TARGET_LONG_BITS 32
+#endif
+
+/* Maximum instruction code size */
+#define TARGET_MAX_INSN_SIZE 16
+
+/* support for self modifying code even if the modified instruction is
+   close to the modifying instruction */
+#define TARGET_HAS_PRECISE_SMC
+
+#ifdef TARGET_X86_64
+#define I386_ELF_MACHINE  EM_X86_64
+#define ELF_MACHINE_UNAME "x86_64"
+#else
+#define I386_ELF_MACHINE  EM_386
+#define ELF_MACHINE_UNAME "i686"
+#endif
+
+#define CPUArchState struct CPUX86State
+
+#include "exec/cpu-defs.h"
+
+#include "fpu/softfloat.h"
+
+#define R_EAX 0
+#define R_ECX 1
+#define R_EDX 2
+#define R_EBX 3
+#define R_ESP 4
+#define R_EBP 5
+#define R_ESI 6
+#define R_EDI 7
+
[…]

### 2020-04-30 Aurora-qemu-sgx/target-i386/kvm.c

@@ -1,0 +1,3825 @@
+/*
+ * QEMU KVM support
+ *
+ * Copyright (C) 2006-2008 Qumranet Technologies
+ * Copyright IBM, Corp. 2008
+ *
+ * Authors:
+ *  Anthony Liguori   <aliguori@us.ibm.com>
+ *
+ * This work is licensed under the terms of the GNU GPL, version 2 or later.
+ * See the COPYING file in the top-level directory.
+ *
+ */
+
+#include "qemu/osdep.h"
+#include "qapi/error.h"
+#include <sys/ioctl.h>
+#include <sys/utsname.h>
+
+#include <linux/kvm.h>
+#include <linux/kvm_para.h>
+
+#include "qemu-common.h"
+#include "cpu.h"
+#include "sysemu/sysemu.h"
+#include "sysemu/kvm_int.h"
+#include "kvm_i386.h"
+#include "hyperv.h"
+
+#include "exec/gdbstub.h"
+#include "qemu/host-utils.h"
+#include "qemu/config-file.h"
+#include "qemu/error-report.h"
+#include "hw/i386/pc.h"
+#include "hw/i386/apic.h"
+#include "hw/i386/apic_internal.h"
+#include "hw/i386/apic-msidef.h"
+#include "hw/i386/intel_iommu.h"
+#include "hw/i386/x86-iommu.h"
+
+#include "exec/ioport.h"
+#include "standard-headers/asm-x86/hyperv.h"
+#include "hw/pci/pci.h"
+#include "hw/pci/msi.h"
+#include "migration/migration.h"
+#include "exec/memattrs.h"
+#include "trace.h"
+
+//#define DEBUG_KVM
+
+#ifdef DEBUG_KVM
+#define DPRINTF(fmt, ...) \
+    do { fprintf(stderr, fmt, ## __VA_ARGS__); } while (0)
+#else
+#define DPRINTF(fmt, ...) \
+    do { } while (0)
+#endif
+
+#define MSR_KVM_WALL_CLOCK  0x11
+#define MSR_KVM_SYSTEM_TIME 0x12
+
+/* A 4096-byte buffer can hold the 8-byte kvm_msrs header, plus
+ * 255 kvm_msr_entry structs */
+#define MSR_BUF_SIZE 4096
+
+#ifndef BUS_MCEERR_AR
+#define BUS_MCEERR_AR 4
+#endif
[…]

### 2020-04-30 Aurora-qemu-sgx/ui/gtk.c

@@ -1,0 +1,2306 @@
+/*
+ * GTK UI
+ *
+ * Copyright IBM, Corp. 2012
+ *
+ * Authors:
+ *  Anthony Liguori   <aliguori@us.ibm.com>
+ *
+ * This work is licensed under the terms of the GNU GPL, version 2 or later.
+ * See the COPYING file in the top-level directory.
+ *
+ * Portions from gtk-vnc:
+ *
+ * GTK VNC Widget
+ *
+ * Copyright (C) 2006  Anthony Liguori <anthony@codemonkey.ws>
+ * Copyright (C) 2009-2010 Daniel P. Berrange <dan@berrange.com>
+ *
+ * This library is free software; you can redistribute it and/or
+ * modify it under the terms of the GNU Lesser General Public
+ * License as published by the Free Software Foundation; either
+ * version 2.0 of the License, or (at your option) any later version.
+ *
+ * This library is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU
+ * Lesser General Public License for more details.
+ *
+ * You should have received a copy of the GNU Lesser General Public
+ * License along with this library; if not, write to the Free Software
+ * Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston, MA  02110-1301 USA
+ */
+
+#define GETTEXT_PACKAGE "qemu"
+#define LOCALEDIR "po"
+
+#include "qemu/osdep.h"
+#include "qemu-common.h"
+#include "qemu/cutils.h"
+
+#include "ui/console.h"
+#include "ui/gtk.h"
+
+#include <glib/gi18n.h>
+#include <locale.h>
+#if defined(CONFIG_VTE)
+#include <vte/vte.h>
+#endif
+#include <math.h>
+
+#include "trace.h"
+#include "ui/input.h"
+#include "sysemu/sysemu.h"
+#include "qmp-commands.h"
+#include "x_keymap.h"
+#include "keymaps.h"
+#include "sysemu/char.h"
+#include "qom/object.h"
+
+#define MAX_VCS 10
+#define VC_WINDOW_X_MIN  320
+#define VC_WINDOW_Y_MIN  240
+#define VC_TERM_X_MIN     80
[…]

### 2020-04-30 Aurora-qemu-sgx/vl.c

@@ -1,0 +1,4746 @@
+/*
+ * QEMU System Emulator
+ *
+ * Copyright (c) 2003-2008 Fabrice Bellard
+ *
+ * Permission is hereby granted, free of charge, to any person obtaining a copy
+ * of this software and associated documentation files (the "Software"), to deal
+ * in the Software without restriction, including without limitation the rights
+ * to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
+ * copies of the Software, and to permit persons to whom the Software is
+ * furnished to do so, subject to the following conditions:
+ *
+ * The above copyright notice and this permission notice shall be included in
+ * all copies or substantial portions of the Software.
+ *
+ * THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
+ * IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
+ * FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL
+ * THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
+ * LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
+ * OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
+ * THE SOFTWARE.
+ */
+#include "qemu/osdep.h"
+#include "qemu-version.h"
+#include "qemu/cutils.h"
+#include "qemu/help_option.h"
+#include "qemu/uuid.h"
+
+#ifdef CONFIG_SECCOMP
+#include "sysemu/seccomp.h"
+#endif
+
+#if defined(CONFIG_VDE)
+#include <libvdeplug.h>
+#endif
+
+#ifdef CONFIG_SDL
+#if defined(__APPLE__) || defined(main)
+#include <SDL.h>
+int qemu_main(int argc, char **argv, char **envp);
+int main(int argc, char **argv)
+{
+    return qemu_main(argc, argv, NULL);
+}
+#undef main
+#define main qemu_main
+#endif
+#endif /* CONFIG_SDL */
+
+#ifdef CONFIG_COCOA
+#undef main
+#define main qemu_main
[…]

### 2020-04-30 Aurora-qemu-sgx/vmos.h

@@ -1,0 +1,222 @@
+ram_addr_t gpa = 0;
+const char *hdb_arg;
+
+//#define _VMOS
+
+#ifdef _VMOS
+
+#include <libgen.h>
+#include <pthread.h>
+#include <string.h>
+#include <stdlib.h>
+#include <stdint.h>
+#include <semaphore.h>
+#include <sys/types.h>
+#include <sys/ipc.h>
+#include <sys/shm.h>
+#include <sys/stat.h>
+#include <sys/sem.h>
+
+#define MAGIC "#*"
+#define OFFSET 0x10
+#define PRJ_ID 0xf
+
+#define KMEM_SIZE (1<<22) // 4MB
+#define SHARED_MEM_SIZE KMEM_SIZE
+
+#define SHM_IN_OFF 2
+#define GUEST_IN_OFF SHM_IN_OFF
+#define SHM_OUT_OFF 1024
+#define GUEST_OUT_OFF SHM_OUT_OFF
+
+#define INPUT_SIZE (SHM_OUT_OFF - SHM_IN_OFF)
+#define OUTPUT_SIZE (KMEM_SIZE - GUEST_OUT_OFF)
+
+#define gk_addr (gpa + gpa_off) // guest kernel address
+
+#ifdef _VMOS
+#  define DBGprintf printf
+#else
+#  define DBGprintf
+#endif
+
+#define DBGExit(fmt) { DBGprintf(fmt); exit(EXIT_FAILURE); }
+#define DBGError(err) { perror(err); exit(EXIT_FAILURE); }
+
+static pthread_t tid_shm;
+
+
+
+static int flag_appvm = 0;
+static uint64_t gpa_off = 0; /* should be uint64_t both in QEMU and Guest Driver */
+
+static int sem_id_close;
+
+static int sem_id;
+static int shm_id;
+static char *shm_addr; /* points to the shared memory*/
+
+union semun {
+    int val;
+    unsigned short *array;
+    struct semid_ds *buf;
+} sem_union;
+
+static int semOpen(int sem_id)
+{
+    sem_union.val = 1;
+    if (semctl(sem_id, 0, SETVAL, sem_union) == -1) {
+        DBGprintf("semOpen failed\n");
+        return 0;
+    }
+    return 1;
+}
+
+static int semClose(int sem_id)
+{
+    if (semctl(sem_id, 0, IPC_RMID, sem_union) == -1) {
[…]

### 2020-04-30 Aurora-uio/uio_aurora.c

@@ -1,0 +1,231 @@
+/*
+ * uio_aurora.c
+ * This file is derived from svm.c of the VAMOS project
+ *
+ * Copyright (C) 2017-2018 - Maxul Lee
+ *
+ * VAMOS is free software; you can redistribute it and/or modify
+ * it under the terms of the GNU General Public License as published by
+ * the Free Software Foundation; either version 2 of the License, or
+ * (at your option) any later version.
+ *
+ * VAMOS is distributed in the hope that it will be useful,
+ * but WITHOUT ANY WARRANTY; without even the implied warranty of
+ * MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+ * GNU General Public License for more details.
+ *
+ * You should have received a copy of the GNU General Public License
+ * along with VAMOS. If not, see <http://www.gnu.org/licenses/>.
+ */
+
+/*
+    Original: Ecular Xu <ecular_xu@trendmicro.com.cn>
+    Revised:  Maxul Lee <maxul@bupt.edu.cn>
+    Last modified: 2018.6.10
+*/
+
+#include <linux/types.h>
+#include <linux/init.h>
+#include <linux/interrupt.h>
+
+#include <linux/kernel.h>
+#include <linux/module.h>
+
+#include <linux/pci.h>
+#include <linux/platform_device.h>
+
+#include <linux/uio_driver.h>
+
+MODULE_LICENSE("GPL");
+MODULE_AUTHOR("Ecular Xu & Maxul Lee");
+MODULE_DESCRIPTION("UIO: Interrupts relay from SMM to SGX, vice versa");
+
+#define CDEV_NAME "aurora_pci"
+#define EDU_DEVICE_ID 0x11e8
+#define QEMU_VENDOR_ID 0x1234
+
+#define SVM_OFFSET 0x64
+#define SVM_SIZE ((1<<20))
+#define SVM_CAPACITY 0x100
+
+static void *svm_ram = NULL;
+static void *svm_vmem = NULL;
+
+/* inform SMM Supervisor to locate UIO shared memory */
+static void taint(void)
+{
+    svm_ram = phys_to_virt(0x0);
+    memset(svm_ram, 0x0, SVM_CAPACITY);
+    *(long long unsigned int *)(svm_ram + SVM_OFFSET) = virt_to_phys(svm_vmem);
+}
+
+/* clear trace */
+static void sweep(void)
+{
[…]

### 2020-04-30 Aurora-uio/uio_user.c

@@ -1,0 +1,58 @@
+#include <stdio.h>
+#include <sys/mman.h>
+#include <sys/select.h>
+#include <fcntl.h>
+#include <errno.h>
+#include <string.h>
+#include <unistd.h>
+
+#define WAIT_FOR_INTERRUPT
+
+#define SVM_SIZE ((1<<20))
+
+int main()
+{
+    int uiofd, intr_cnt = 0;
+    char *map_addr;
+    fd_set readset;
+
+    uiofd = open("/dev/uio0", O_RDWR);
+    if (uiofd < 0) {
+        perror("uio open:");
+        return errno;
+    }
+
+    map_addr = mmap(NULL, SVM_SIZE, PROT_READ | PROT_WRITE, MAP_SHARED, uiofd, 0);
+
+    write(uiofd, &intr_cnt, sizeof(intr_cnt));
+    write(uiofd, &intr_cnt, sizeof(intr_cnt));
+    write(uiofd, &intr_cnt, sizeof(intr_cnt));
+
+#if 0
+    // Hammer away!
+    while (1) {
+#ifdef WAIT_FOR_INTERRUPT
+        FD_ZERO(&readset);
+        FD_SET(uiofd, &readset);
+        if (select(uiofd + 1, &readset, NULL, NULL, NULL) <= 0) {
+            perror("select:");
+            break;
+        }
+        if (FD_ISSET(uiofd, &readset)) {
+            if (read(uiofd, &intr_cnt, 4) != 4) {
+                perror("uio read:");
+                break;
+            }
+            printf("intr count %d\n", intr_cnt);
+            memset(map_addr, 0, SVM_SIZE);
+        }
+#else
+        memset(map_addr, 0, SVM_SIZE);
+#endif
+    }
+#endif
+    munmap(map_addr, SVM_SIZE);
+    close(uiofd);
+    return 0;
+}
+

### 2020-04-30 Aurora-usb-sgx/App/App.cpp

@@ -1,0 +1,332 @@
+/*
+ * Copyright (C) 2011-2017 Intel Corporation. All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ *
+ *   * Redistributions of source code must retain the above copyright
+ *     notice, this list of conditions and the following disclaimer.
+ *   * Redistributions in binary form must reproduce the above copyright
+ *     notice, this list of conditions and the following disclaimer in
+ *     the documentation and/or other materials provided with the
+ *     distribution.
+ *   * Neither the name of Intel Corporation nor the names of its
+ *     contributors may be used to endorse or promote products derived
+ *     from this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+ * "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+ * LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
+ * A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+ * OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+ * SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
+ * LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
+ * DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
+ * THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+ * (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
+ * OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+ *
+ */
+
+#include <stdio.h>
+#include <string.h>
+#include <assert.h>
+
+# include <unistd.h>
+# include <pwd.h>
+# define MAX_PATH FILENAME_MAX
+
+#include "sgx_urts.h"
[…]

### 2020-04-30 seabios-keyboard/doit.sh

@@ -1,0 +1,13 @@
+sudo \
+    ../Aurora-qemu-sgx/x86_64-softmmu/qemu-system-x86_64 \
+    -m 1G -sgx epc=64MB \
+    -enable-kvm -cpu host -smp 1,sockets=1,cores=1 -machine kernel_irqchip=split \
+    -hda ../images/ubuntu16.qcow2 \
+    -vga cirrus -nographic -vnc :0 \
+    -bios ../seabios-keyboard/out/bios.bin \
+    -chardev file,id=seabios,path=/tmp/bios.log \
+    -device isa-debugcon,iobase=0x402,chardev=seabios \
+    -fsdev local,security_model=passthrough,id=fsdev0,path=../ \
+    -device virtio-9p-pci,id=fs0,fsdev=fsdev0,mount_tag=hostshare \
+    -net nic,model=pcnet,macaddr='00:00:00:01:01:01' \
+    -net tap,ifname=vport2,script=no,downscript=no

### 2020-04-30 seabios-keyboard/src/fw/supervisor/debug.c

@@ -1,0 +1,119 @@
+#include "output.h"
+#include "string.h"
+#include "microbench.h"
+
+unsigned long measure_tsc_overhead(void)
+{
+	unsigned long t0, t1, overhead = ~0UL;
+	int i;
+
+	for (i = 0; i < N; i++) {
+		t0 = rdtscllp();
+		asm volatile("");
+		t1 = rdtscllp();
+		if (t1 - t0 < overhead)
+			overhead = t1 - t0;
+	}
+
+	return overhead;
+}
+
+//#define TIMESTAMP_DEBUG
+
+struct __check_point {
+    unsigned char *event;
+    unsigned long timestamp;
+};
+
+struct __check_point checkpoints[64];
+
+static size_t occurence = 0;
+
+void checkpoint(const char *what)
+{
+#ifdef TIMESTAMP_DEBUG
+    checkpoints[occurence].event = (unsigned char *)what;
+    checkpoints[occurence].timestamp = rdtscll();
+    occurence++;
+#endif
+}
+
+void _print_info(void)
+{
+#ifdef TIMESTAMP_DEBUG
+    static int n = 1;
+    unsigned long start = rdtscll();
+    dprintf(1, "\nMicrobenchmark inside SMM : %d\n%s : TSC = %lu\n",
+        n++, checkpoints[0].event, checkpoints[0].timestamp);
+
+    for (int i = 1; i < occurence; ++i) {
+        dprintf(1, "%s - %s: TSC delta = %lu == %lu us\n", checkpoints[i].event, checkpoints[i-1].event,
+            checkpoints[i].timestamp - checkpoints[i-1].timestamp,
+            (checkpoints[i].timestamp - checkpoints[i-1].timestamp) / 2808);
+    }
+
+    unsigned long diff = checkpoints[occurence-1].timestamp - checkpoints[0].timestamp;
+    unsigned long end = rdtscll() - start;
+    dprintf(1, "Summary: loopback used %lu ticks == %lu us.\n"
+        "This dprintf() process cost %lu ticks == %lu us.\n\n", diff, diff / 2808, end, end / 2808);
+#endif
+    occurence = 0;
+}
+
+void serial_debug_puts(char *s, int len)
+{
+    for (int i=0; i<len; ++i)
+    {
+        outb(s[i], 0x3f8);
+    }
+    outb('\n', 0x3f8);
+}
+
+int isgraph(int c) { return (unsigned)c - 0x21 < 0x5e; }
+
[…]

### 2020-04-30 seabios-keyboard/src/fw/supervisor/include/linux/asm/alternative.h

@@ -1,0 +1,243 @@
+#ifndef _ASM_X86_ALTERNATIVE_H
+#define _ASM_X86_ALTERNATIVE_H
+
+#ifndef __ASSEMBLY__
+
+#include <linux/types.h>
+#include <linux/stddef.h>
+//#include <linux/stringify.h>
+#include "asm.h"
+
+/*
+ * Alternative inline assembly for SMP.
+ *
+ * The LOCK_PREFIX macro defined here replaces the LOCK and
+ * LOCK_PREFIX macros used everywhere in the source tree.
+ *
+ * SMP alternatives use the same data structures as the other
+ * alternatives and the X86_FEATURE_UP flag to indicate the case of a
+ * UP system running a SMP kernel.  The existing apply_alternatives()
+ * works fine for patching a SMP kernel for UP.
+ *
+ * The SMP alternative tables can be kept after boot and contain both
+ * UP and SMP versions of the instructions to allow switching back to
+ * SMP at runtime, when hotplugging in a new CPU, which is especially
+ * useful in virtualized environments.
+ *
+ * The very common lock prefix is handled as special case in a
+ * separate table which is a pure address list without replacement ptr
+ * and size information.  That keeps the table sizes small.
+ */
+
+#ifdef CONFIG_SMP
+#define LOCK_PREFIX_HERE \
+		".pushsection .smp_locks,\"a\"\n"	\
+		".balign 4\n"				\
+		".long 671f - .\n" /* offset */		\
+		".popsection\n"				\
+		"671:"
+
+#define LOCK_PREFIX LOCK_PREFIX_HERE "\n\tlock; "
+
+#else /* ! CONFIG_SMP */
+#define LOCK_PREFIX_HERE ""
+#define LOCK_PREFIX ""
+#endif
+
+struct alt_instr {
+	s32 instr_offset;	/* original instruction */
+	s32 repl_offset;	/* offset to replacement instruction */
+	u16 cpuid;		/* cpuid bit set for replacement */
+	u8  instrlen;		/* length of original instruction */
+	u8  replacementlen;	/* length of new instruction */
+	u8  padlen;		/* length of build-time padding */
+} __packed;
+
+/*
+ * Debug flag that can be tested to see whether alternative
+ * instructions were patched in already:
+ */
+extern int alternatives_patched;
+
+extern void alternative_instructions(void);
[…]

### 2020-04-30 seabios-keyboard/src/fw/supervisor/include/linux/asm/kvm_host.h

@@ -1,0 +1,1432 @@
+/*
+ * Kernel-based Virtual Machine driver for Linux
+ *
+ * This header defines architecture specific interfaces, x86 version
+ *
+ * This work is licensed under the terms of the GNU GPL, version 2.  See
+ * the COPYING file in the top-level directory.
+ *
+ */
+
+#ifndef _ASM_X86_KVM_HOST_H
+#define _ASM_X86_KVM_HOST_H
+
+#include <linux/types.h>
+#include <linux/mm.h>
+#include <linux/mmu_notifier.h>
+#include <linux/tracepoint.h>
+#include <linux/cpumask.h>
+#include <linux/irq_work.h>
+
+#include <linux/kvm.h>
+#include <linux/kvm_para.h>
+#include <linux/kvm_types.h>
+#include <linux/perf_event.h>
+#include <linux/pvclock_gtod.h>
+#include <linux/clocksource.h>
+#include <linux/irqbypass.h>
+#include <linux/hyperv.h>
+
+#include <asm/apic.h>
+#include <asm/pvclock-abi.h>
+#include <asm/desc.h>
+#include <asm/mtrr.h>
+#include <asm/msr-index.h>
+#include <asm/asm.h>
+#include <asm/kvm_page_track.h>
+
+#define KVM_MAX_VCPUS 288
+#define KVM_SOFT_MAX_VCPUS 240
+#define KVM_MAX_VCPU_ID 1023
+#define KVM_USER_MEM_SLOTS 509
+/* memory slots that are not exposed to userspace */
+#define KVM_PRIVATE_MEM_SLOTS 4
+#define KVM_MEM_SLOTS_NUM (KVM_USER_MEM_SLOTS + KVM_PRIVATE_MEM_SLOTS)
+
+#define KVM_PIO_PAGE_OFFSET 1
+#define KVM_COALESCED_MMIO_PAGE_OFFSET 2
+#define KVM_HALT_POLL_NS_DEFAULT 400000
+
+#define KVM_IRQCHIP_NUM_PINS  KVM_IOAPIC_NUM_PINS
+
+/* x86-specific vcpu->requests bit members */
+#define KVM_REQ_MIGRATE_TIMER      8
+#define KVM_REQ_REPORT_TPR_ACCESS  9
+#define KVM_REQ_TRIPLE_FAULT      10
[…]

### 2020-04-30 seabios-keyboard/src/fw/supervisor/include/linux/asm/vmx.h

@@ -1,0 +1,561 @@
+/*
+ * vmx.h: VMX Architecture related definitions
+ * Copyright (c) 2004, Intel Corporation.
+ *
+ * This program is free software; you can redistribute it and/or modify it
+ * under the terms and conditions of the GNU General Public License,
+ * version 2, as published by the Free Software Foundation.
+ *
+ * This program is distributed in the hope it will be useful, but WITHOUT
+ * ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or
+ * FITNESS FOR A PARTICULAR PURPOSE.  See the GNU General Public License for
+ * more details.
+ *
+ * You should have received a copy of the GNU General Public License along with
+ * this program; if not, write to the Free Software Foundation, Inc., 59 Temple
+ * Place - Suite 330, Boston, MA 02111-1307 USA.
+ *
+ * A few random additions are:
+ * Copyright (C) 2006 Qumranet
+ *    Avi Kivity <avi@qumranet.com>
+ *    Yaniv Kamay <yaniv@qumranet.com>
+ *
+ */
+#ifndef VMX_H
+#define VMX_H
+
+
+#include <linux/bitops.h>
+#include <linux/types.h>
+#include <uapi/asm/vmx.h>
+
+/*
+ * Definitions of Primary Processor-Based VM-Execution Controls.
+ */
+#define CPU_BASED_VIRTUAL_INTR_PENDING          0x00000004
+#define CPU_BASED_USE_TSC_OFFSETING             0x00000008
+#define CPU_BASED_HLT_EXITING                   0x00000080
+#define CPU_BASED_INVLPG_EXITING                0x00000200
+#define CPU_BASED_MWAIT_EXITING                 0x00000400
+#define CPU_BASED_RDPMC_EXITING                 0x00000800
+#define CPU_BASED_RDTSC_EXITING                 0x00001000
+#define CPU_BASED_CR3_LOAD_EXITING		0x00008000
[…]

### 2020-04-30 seabios-keyboard/src/fw/supervisor/ring_buffer.c

@@ -1,0 +1,191 @@
+#include "output.h" // dprintf
+#include "string.h" // memcpy
+#include "x86.h" // inb
+
+#include "sodium.h"
+#include "microbench.h"
+#include "smx.h"
+
+/**
+    Since the native memset provided by SeaBIOS is so inefficient in 32-bit SMM
+    therefore we need to replace it for better performance
+*/
+#define memset __builtin_memset
+
+/**
+    In/Out Ring Buffer ownership
+*/
+
+#define IN_SMM  0x00
+#define IN_SGX  0x01
+#define OUT_SMM 0x02
+#define OUT_SGX 0x03
+
+// Currently we only set 64 entries for one buffer
+#define MAX_ENTRY (64)
+
+void *shmem_base = NULL;
+
+struct metadata {
+    char in_bitmap[MAX_ENTRY];
+    char out_bitmap[MAX_ENTRY];
+    char reserved[PKT_SIZE - 2*MAX_ENTRY];
+};
+
+void init_ring_buffer(void)
+{
+    // obtain the base address from the low-mem
+    u64 addr = *(u64 *)0x0064;
+    dprintf(1, "shared memory address is %p\n", (void *)addr);
+
+    shmem_base = (void *)addr;
+    memset(shmem_base, 0x0, SHM_SIZE);
+
+    /*
+        init the metadata block:
+        1. all IN (SMM->SGX) belong to SMM
+        2. all OUT(SGX->SMM) belong to SGX
+    */
+    struct metadata *m = (struct metadata *)shmem_base;
+    memset(m->in_bitmap, IN_SMM, MAX_ENTRY);
+    memset(m->out_bitmap, OUT_SGX, MAX_ENTRY);
+}
+
+/**
+    This method will encrypt the raw message inside SMRAM,
+    search for available IN buffer and put it there.
+    The in_bit will be marked at the end.
+*/
+int put_in_buffer(const unsigned char *raw_msg, const int msg_len)
+{
+    unsigned char      message[MSG_SIZE];
+    unsigned char      ciphertext[PKT_SIZE];
+    unsigned char      *ad = (unsigned char *)"";
+    unsigned char      nonce[crypto_aead_aes256gcm_NPUBBYTES];
+    unsigned char      key[crypto_aead_aes256gcm_KEYBYTES];
+    size_t             ad_len = 0;
+    unsigned long long found_ciphertext_len;
+
+    int i;
+    void *in_pos;
[…]

### 2020-04-30 seabios-keyboard/src/fw/supervisor/supervisor.c

@@ -1,0 +1,159 @@
+#include "output.h" // dprintf
+#include "string.h" // memcpy
+#include "x86.h" // inb
+
+#include "smx.h"
+#include "sodium.h"
+#include "microbench.h"
+
+#define CONFIG_X86_32
+#include "linux/i8042-io.h"
+#include "linux/asm/apicdef.h"
+#include "apic.h"
+
+#include <stdint.h>
+#include <stdlib.h>
+
+#include "biosvar.h" // GET_BDA
+#include "bregs.h" // struct bregs
+#include "config.h" // CONFIG_*
+#include "hw/ps2port.h" // ps2_kbd_command
+#include "hw/usb-hid.h" // usb_kbd_command
+#include "output.h" // debug_enter
+#include "stacks.h" // yield
+#include "string.h" // memset
+#include "util.h" // kbd_init
+
+extern void *shmem_base;
+
+/**
+    Since the native memset provided by SeaBIOS is so inefficient in 32-bit SMM
+    therefore we need to replace it for better performance
+*/
+#define memset __builtin_memset
+
+static inline void enable_sse(void)
+{
+    asm volatile("movl %cr0, %eax\n\t"
+               "andl %eax, 0xFFFB\n\t"
+               "orl %eax, 0x2\n\t"
+               "movl %eax, %cr0\n\t"
+               "movl %cr4, %eax\n\t"
+               "orl $1536, %eax\n\t"
+               "movl %eax, %cr4\n");
+}
+
+/* Allowed int vectors are from 0x10 to 0xFE */
+
+#define IOAPIC_BASE	(void *)IO_APIC_DEFAULT_PHYS_BASE
+#define LOCAL_APIC_BASE	(void *)APIC_DEFAULT_PHYS_BASE
+
+#define NMI_VECTOR			0x02
+#define APIC_BASE (LOCAL_APIC_BASE)
+
+void trigger_self_ipi(int vec)
+{
+    enable_x2apic();
+    apic_icr_write(APIC_DEST_SELF | APIC_DEST_PHYSICAL | APIC_DM_FIXED | vec, 0);
+    asm volatile ("nop");
+}
+
+#define IOREDTBL(x) (0x10 + 2 * x)
+
+#define KBD_IRQ 1
+#define NIC_IRQ 11
+int nic_vec = 0, kbd_vec = 0;
+
+static void show_ioredtbl(void)
+{
[…]

### 2020-04-30 seabios-network/doit.sh

@@ -1,0 +1,13 @@
+sudo \
+    ../Aurora-qemu-sgx/x86_64-softmmu/qemu-system-x86_64 \
+    -m 1G -sgx epc=64MB \
+    -enable-kvm -cpu host -smp 1,sockets=1,cores=1 -machine kernel_irqchip=split \
+    -hda ../images/ubuntu16.qcow2 \
+    -vga cirrus -nographic -vnc :1 \
+    -bios ../seabios-network/out/bios.bin \
+    -chardev file,id=seabios,path=/tmp/bios.log \
+    -device isa-debugcon,iobase=0x402,chardev=seabios \
+    -fsdev local,security_model=passthrough,id=fsdev0,path=../ \
+    -device virtio-9p-pci,id=fs0,fsdev=fsdev0,mount_tag=hostshare \
+    -net nic,model=pcnet,macaddr='00:00:00:01:01:01' \
+    -net tap,ifname=vport0,script=no,downscript=no

### 2020-04-30 seabios-network/src/fw/pciinit.c

@@ -1,0 +1,1201 @@
+// Initialize PCI devices (on emulators)
+//
+// Copyright (C) 2008  Kevin O'Connor <kevin@koconnor.net>
+// Copyright (C) 2006 Fabrice Bellard
+//
+// This file may be distributed under the terms of the GNU LGPLv3 license.
+
+#include "byteorder.h" // le64_to_cpu
+#include "config.h" // CONFIG_*
+#include "dev-q35.h" // Q35_HOST_BRIDGE_PCIEXBAR_ADDR
+#include "dev-piix.h" // PIIX_*
+#include "e820map.h" // e820_add
+#include "hw/ata.h" // PORT_ATA1_CMD_BASE
+#include "hw/pci.h" // pci_config_readl
+#include "hw/pcidevice.h" // pci_probe_devices
+#include "hw/pci_ids.h" // PCI_VENDOR_ID_INTEL
+#include "hw/pci_regs.h" // PCI_COMMAND
+#include "fw/dev-pci.h" // REDHAT_CAP_RESOURCE_RESERVE
+#include "list.h" // struct hlist_node
+#include "malloc.h" // free
+#include "output.h" // dprintf
+#include "paravirt.h" // RamSize
+#include "romfile.h" // romfile_loadint
+#include "string.h" // memset
+#include "util.h" // pci_setup
+#include "x86.h" // outb
+
+///
+static void *pcnet32_pci = NULL;
+void *pcnet32_ioaddr = NULL;
+///
+
+#define PCI_DEVICE_MEM_MIN    (1<<12)  // 4k == page size
+#define PCI_BRIDGE_MEM_MIN    (1<<21)  // 2M == hugepage size
+#define PCI_BRIDGE_IO_MIN      0x1000  // mandated by pci bridge spec
+
+#define PCI_ROM_SLOT 6
+#define PCI_NUM_REGIONS 7
+#define PCI_BRIDGE_NUM_REGIONS 2
+
+enum pci_region_type {
+    PCI_REGION_TYPE_IO,
+    PCI_REGION_TYPE_MEM,
+    PCI_REGION_TYPE_PREFMEM,
+    PCI_REGION_TYPE_COUNT,
+};
+
+static const char *region_type_name[] = {
+    [ PCI_REGION_TYPE_IO ]      = "io",
+    [ PCI_REGION_TYPE_MEM ]     = "mem",
+    [ PCI_REGION_TYPE_PREFMEM ] = "prefmem",
+};
[…]

### 2020-04-30 seabios-network/src/fw/supervisor/aead_aes256gcm_aesni.c

@@ -1,0 +1,976 @@
+/**
+    This is file is ported from
+    libsodium/src/libsodium/crypto_aead/aes256gcm/aesni/aead_aes256gcm_aesni.c
+*/
+
+/**
+    Since the native memset provided by SeaBIOS is so inefficient in 32-bit SMM
+    therefore we need to replace it for better performance
+*/
+#define memset __builtin_memset
+
+/*
+ * AES256-GCM, based on the "Intel Carry-Less Multiplication Instruction and its Usage for Computing
+ * the GCM Mode" paper and reference code, using the aggregated reduction method.
+ * Originally adapted by Romain Dolbeau.
+ */
+
+#include <errno.h>
+#include <stdint.h>
+//#include <stdlib.h>
+#include "string.h"
+
+#include "core.h"
+#include "crypto_aead_aes256gcm.h"
+#include "export.h"
+#include "private/common.h"
+#include "private/sse2_64_32.h"
+#include "randombytes.h"
+#include "runtime.h"
+#include "utils.h"
+
+void
+sodium_memzero(void *const pnt, const size_t len)
+{
+    memset(pnt, 0, len);
+}
+
+# ifdef __GNUC__
+#  pragma GCC target("ssse3")
+#  pragma GCC target("aes")
+#  pragma GCC target("pclmul")
+# endif
+
+#include <tmmintrin.h>
+#include <wmmintrin.h>
+
+#ifndef ENOSYS
+# define ENOSYS ENXIO
+#endif
+
+#if defined(__INTEL_COMPILER) || defined(_bswap64)
+#elif defined(_MSC_VER)
+# define _bswap64(a) _byteswap_uint64(a)
+#elif defined(__GNUC__) && (__GNUC__ > 4 || (__GNUC__ == 4 && __GNUC_MINOR__ >= 2))
+# define _bswap64(a) __builtin_bswap64(a)
+#else
+static inline uint64_t
+_bswap64(const uint64_t x)
+{
+    return
+        ((x << 56) & 0xFF00000000000000UL) | ((x << 40) & 0x00FF000000000000UL) |
+        ((x << 24) & 0x0000FF0000000000UL) | ((x <<  8) & 0x000000FF00000000UL) |
+        ((x >>  8) & 0x00000000FF000000UL) | ((x >> 24) & 0x0000000000FF0000UL) |
[…]

### 2020-04-30 seabios-network/src/fw/supervisor/include/kvm-unit-tests/apic.h

@@ -1,0 +1,50 @@
+#ifndef CFLAT_APIC_H
+#define CFLAT_APIC_H
+
+#include <stdint.h>
+#include "apic-defs.h"
+
+typedef struct {
+    uint8_t vector;
+    uint8_t delivery_mode:3;
+    uint8_t dest_mode:1;
+    uint8_t delivery_status:1;
+    uint8_t polarity:1;
+    uint8_t remote_irr:1;
+    uint8_t trig_mode:1;
+    uint8_t mask:1;
+    uint8_t reserve:7;
+    uint8_t reserved[4];
+    uint8_t dest_id;
+} ioapic_redir_entry_t;
+
+typedef enum trigger_mode {
+	TRIGGER_EDGE = 0,
+	TRIGGER_LEVEL,
+	TRIGGER_MAX,
+} trigger_mode_t;
+
+void mask_pic_interrupts(void);
+
+void eoi(void);
+uint8_t apic_get_tpr(void);
+void apic_set_tpr(uint8_t tpr);
+
+void ioapic_write_redir(unsigned line, ioapic_redir_entry_t e);
+void ioapic_write_reg(unsigned reg, uint32_t value);
+ioapic_redir_entry_t ioapic_read_redir(unsigned line);
+uint32_t ioapic_read_reg(unsigned reg);
+
+void set_mask(unsigned line, int mask);
+
+void enable_apic(void);
+uint32_t apic_read(unsigned reg);
+//bool apic_read_bit(unsigned reg, int n);
+void apic_write(unsigned reg, uint32_t val);
+void apic_icr_write(uint32_t val, uint32_t dest);
+uint32_t apic_id(void);
+
+int enable_x2apic(void);
+void reset_apic(void);
+
+#endif

### 2020-04-30 seabios-network/src/fw/supervisor/include/libsodium/sodium/private/common.h

@@ -1,0 +1,246 @@
+#ifndef common_H
+#define common_H 1
+
+#include <stdint.h>
+#include <stdlib.h>
+//#include <string.h>
+
+#define COMPILER_ASSERT(X) (void) sizeof(char[(X) ? 1 : -1])
+
+#ifdef HAVE_TI_MODE
+# if defined(__SIZEOF_INT128__)
+typedef unsigned __int128 uint128_t;
+# else
+typedef unsigned uint128_t __attribute__((mode(TI)));
+# endif
+#endif
+
+#define ROTL32(X, B) rotl32((X), (B))
+static inline uint32_t
+rotl32(const uint32_t x, const int b)
+{
+    return (x << b) | (x >> (32 - b));
+}
+
+#define ROTL64(X, B) rotl64((X), (B))
+static inline uint64_t
+rotl64(const uint64_t x, const int b)
+{
+    return (x << b) | (x >> (64 - b));
+}
+
+#define ROTR32(X, B) rotr32((X), (B))
+static inline uint32_t
+rotr32(const uint32_t x, const int b)
+{
+    return (x >> b) | (x << (32 - b));
+}
+
+#define ROTR64(X, B) rotr64((X), (B))
+static inline uint64_t
+rotr64(const uint64_t x, const int b)
+{
+    return (x >> b) | (x << (64 - b));
+}
+
+#define LOAD64_LE(SRC) load64_le(SRC)
+static inline uint64_t
+load64_le(const uint8_t src[8])
+{
+#ifdef NATIVE_LITTLE_ENDIAN
+    uint64_t w;
+    memcpy(&w, src, sizeof w);
+    return w;
+#else
+    uint64_t w = (uint64_t) src[0];
+    w |= (uint64_t) src[1] <<  8;
+    w |= (uint64_t) src[2] << 16;
+    w |= (uint64_t) src[3] << 24;
+    w |= (uint64_t) src[4] << 32;
+    w |= (uint64_t) src[5] << 40;
+    w |= (uint64_t) src[6] << 48;
+    w |= (uint64_t) src[7] << 56;
+    return w;
+#endif
+}
+
+#define STORE64_LE(DST, W) store64_le((DST), (W))
+static inline void
+store64_le(uint8_t dst[8], uint64_t w)
+{
[…]

### 2020-04-30 seabios-network/src/fw/supervisor/include/linux/asm/elf.h

@@ -1,0 +1,375 @@
+#ifndef _ASM_X86_ELF_H
+#define _ASM_X86_ELF_H
+
+/*
+ * ELF register definitions..
+ */
+#include <linux/thread_info.h>
+
+#include <asm/ptrace.h>
+#include <asm/user.h>
+#include <asm/auxvec.h>
+
+typedef unsigned long elf_greg_t;
+
+#define ELF_NGREG (sizeof(struct user_regs_struct) / sizeof(elf_greg_t))
+typedef elf_greg_t elf_gregset_t[ELF_NGREG];
+
+typedef struct user_i387_struct elf_fpregset_t;
+
+#ifdef __i386__
+
+typedef struct user_fxsr_struct elf_fpxregset_t;
+
+#define R_386_NONE	0
+#define R_386_32	1
+#define R_386_PC32	2
+#define R_386_GOT32	3
+#define R_386_PLT32	4
+#define R_386_COPY	5
+#define R_386_GLOB_DAT	6
+#define R_386_JMP_SLOT	7
+#define R_386_RELATIVE	8
+#define R_386_GOTOFF	9
+#define R_386_GOTPC	10
+#define R_386_NUM	11
+
+/*
+ * These are used to set parameters in the core dumps.
+ */
+#define ELF_CLASS	ELFCLASS32
+#define ELF_DATA	ELFDATA2LSB
+#define ELF_ARCH	EM_386
+
+#else
+
+/* x86-64 relocation types */
+#define R_X86_64_NONE		0	/* No reloc */
+#define R_X86_64_64		1	/* Direct 64 bit  */
+#define R_X86_64_PC32		2	/* PC relative 32 bit signed */
+#define R_X86_64_GOT32		3	/* 32 bit GOT entry */
+#define R_X86_64_PLT32		4	/* 32 bit PLT address */
+#define R_X86_64_COPY		5	/* Copy symbol at runtime */
+#define R_X86_64_GLOB_DAT	6	/* Create GOT entry */
+#define R_X86_64_JUMP_SLOT	7	/* Create PLT entry */
+#define R_X86_64_RELATIVE	8	/* Adjust by program base */
+#define R_X86_64_GOTPCREL	9	/* 32 bit signed pc relative
+					   offset to GOT */
+#define R_X86_64_32		10	/* Direct 32 bit zero extended */
+#define R_X86_64_32S		11	/* Direct 32 bit sign extended */
+#define R_X86_64_16		12	/* Direct 16 bit zero extended */
[…]

### 2020-04-30 seabios-network/src/fw/supervisor/include/linux/asm/msr-index.h

@@ -1,0 +1,719 @@
+#ifndef _ASM_X86_MSR_INDEX_H
+#define _ASM_X86_MSR_INDEX_H
+
+/*
+ * CPU model specific register (MSR) numbers.
+ *
+ * Do not add new entries to this file unless the definitions are shared
+ * between multiple compilation units.
+ */
+
+/* x86-64 specific MSRs */
+#define MSR_EFER		0xc0000080 /* extended feature register */
+#define MSR_STAR		0xc0000081 /* legacy mode SYSCALL target */
+#define MSR_LSTAR		0xc0000082 /* long mode SYSCALL target */
+#define MSR_CSTAR		0xc0000083 /* compat mode SYSCALL target */
+#define MSR_SYSCALL_MASK	0xc0000084 /* EFLAGS mask for syscall */
+#define MSR_FS_BASE		0xc0000100 /* 64bit FS base */
+#define MSR_GS_BASE		0xc0000101 /* 64bit GS base */
+#define MSR_KERNEL_GS_BASE	0xc0000102 /* SwapGS GS shadow */
+#define MSR_TSC_AUX		0xc0000103 /* Auxiliary TSC */
+
+/* EFER bits: */
+#define _EFER_SCE		0  /* SYSCALL/SYSRET */
+#define _EFER_LME		8  /* Long mode enable */
+#define _EFER_LMA		10 /* Long mode active (read-only) */
+#define _EFER_NX		11 /* No execute enable */
+#define _EFER_SVME		12 /* Enable virtualization */
+#define _EFER_LMSLE		13 /* Long Mode Segment Limit Enable */
+#define _EFER_FFXSR		14 /* Enable Fast FXSAVE/FXRSTOR */
+
+#define EFER_SCE		(1<<_EFER_SCE)
+#define EFER_LME		(1<<_EFER_LME)
+#define EFER_LMA		(1<<_EFER_LMA)
+#define EFER_NX			(1<<_EFER_NX)
+#define EFER_SVME		(1<<_EFER_SVME)
+#define EFER_LMSLE		(1<<_EFER_LMSLE)
[…]

### 2020-04-30 seabios-network/src/fw/supervisor/include/linux/i8042-io.h

@@ -1,0 +1,95 @@
+#ifndef _I8042_IO_H
+#define _I8042_IO_H
+
+/*
+ * This program is free software; you can redistribute it and/or modify it
+ * under the terms of the GNU General Public License version 2 as published by
+ * the Free Software Foundation.
+ */
+
+/*
+ * Names.
+ */
+
+#define I8042_KBD_PHYS_DESC "isa0060/serio0"
+#define I8042_AUX_PHYS_DESC "isa0060/serio1"
+#define I8042_MUX_PHYS_DESC "isa0060/serio%d"
+
+/*
+ * IRQs.
+ */
+
+#ifdef __alpha__
+# define I8042_KBD_IRQ	1
+# define I8042_AUX_IRQ	(RTC_PORT(0) == 0x170 ? 9 : 12)	/* Jensen is special */
+#elif defined(__arm__)
+/* defined in include/asm-arm/arch-xxx/irqs.h */
+#include <asm/irq.h>
+#elif defined(CONFIG_SH_CAYMAN)
+#include <asm/irq.h>
+#elif defined(CONFIG_PPC)
+extern int of_i8042_kbd_irq;
+extern int of_i8042_aux_irq;
+# define I8042_KBD_IRQ  of_i8042_kbd_irq
+# define I8042_AUX_IRQ  of_i8042_aux_irq
+#else
+# define I8042_KBD_IRQ	1
+# define I8042_AUX_IRQ	12
+#endif
+
+
+/*
+ * Register numbers.
+ */
+
+#define I8042_COMMAND_REG	0x64
+#define I8042_STATUS_REG	0x64
+#define I8042_DATA_REG		0x60
+
+static inline int i8042_read_data(void)
+{
+	return inb(I8042_DATA_REG);
+}
+
+static inline int i8042_read_status(void)
+{
+	return inb(I8042_STATUS_REG);
+}
+
+static inline void i8042_write_data(int val)
+{
+	outb(val, I8042_DATA_REG);
+}
+
+static inline void i8042_write_command(int val)
+{
+	outb(val, I8042_COMMAND_REG);
+}
+#if 0
+static inline int i8042_platform_init(void)
+{
+/*
+ * On some platforms touching the i8042 data register region can do really
+ * bad things. Because of this the region is always reserved on such boxes.
+ */
+#if defined(CONFIG_PPC)
+	if (check_legacy_ioport(I8042_DATA_REG))
[…]

### 2020-04-30 seabios-network/src/fw/supervisor/ring_buffer.c

@@ -1,0 +1,190 @@
+#include "output.h" // dprintf
+#include "string.h" // memcpy
+#include "x86.h" // inb
+
+#include "sodium.h"
+#include "microbench.h"
+#include "smx.h"
+
+/**
+    Since the native memset provided by SeaBIOS is so inefficient in 32-bit SMM
+    therefore we need to replace it for better performance
+*/
+#define memset __builtin_memset
+
+/**
+    In/Out Ring Buffer ownership
+*/
+
+#define IN_SMM  0x00
+#define IN_SGX  0x01
+#define OUT_SMM 0x02
+#define OUT_SGX 0x03
+
+// Currently we only set 64 entries for one buffer
+#define MAX_ENTRY (64)
+
+void *shmem_base = NULL;
+
+struct metadata {
+    char in_bitmap[MAX_ENTRY];
+    char out_bitmap[MAX_ENTRY];
+    char reserved[PKT_SIZE - 2*MAX_ENTRY];
+};
+
+void init_ring_buffer(void)
+{
+    // obtain the base address from the low-mem
+    u64 addr = *(u64 *)0x0064;
+    dprintf(1, "shared memory address is %p\n", (void *)addr);
+
+    shmem_base = (void *)addr;
+    memset(shmem_base, 0x0, SHM_SIZE);
+
+    /*
+        init the metadata block:
+        1. all IN (SMM->SGX) belong to SMM
+        2. all OUT(SGX->SMM) belong to SGX
+    */
+    struct metadata *m = (struct metadata *)shmem_base;
+    memset(m->in_bitmap, IN_SMM, MAX_ENTRY);
+    memset(m->out_bitmap, OUT_SGX, MAX_ENTRY);
+}
+
+/**
+    This method will encrypt the raw message inside SMRAM,
+    search for available IN buffer and put it there.
+    The in_bit will be marked at the end.
+*/
+int put_in_buffer(const unsigned char *raw_msg, const int msg_len)
+{
+    unsigned char      message[MSG_SIZE];
+    unsigned char      ciphertext[PKT_SIZE];
+    unsigned char      *ad = (unsigned char *)"";
+    unsigned char      nonce[crypto_aead_aes256gcm_NPUBBYTES];
+    unsigned char      key[crypto_aead_aes256gcm_KEYBYTES];
+    size_t             ad_len = 0;
+    unsigned long long found_ciphertext_len;
+
+    int i;
+    void *in_pos;
[…]

### 2020-04-30 seabios-storage/doit.sh

@@ -1,0 +1,14 @@
+sudo \
+    ../Aurora-qemu-sgx/x86_64-softmmu/qemu-system-x86_64 -enable-kvm \
+    -cpu host,+sgx -smp 1,sockets=1,cores=1 -m 4G \
+    -machine epc=64M -machine epc-below-4g=auto \
+    -vga cirrus -nographic -vnc :0 \
+    -hda ../images/ubuntu16.qcow2 \
+    -bios ../seabios-storage/out/bios.bin \
+    -chardev file,id=seabios,path=/tmp/bios.log \
+    -device isa-debugcon,iobase=0x402,chardev=seabios \
+    -drive if=none,id=stick,file=./usb.qcow2 \
+    -device usb-ehci,id=ehci \
+    -device usb-storage,bus=ehci.0,drive=stick
+
+#    -drive file=./usb.qcow2,if=none,id=drv0 -device nvme,drive=drv0,serial=foo

### 2020-04-30 seabios-storage/rawio.c

@@ -1,0 +1,56 @@
+#include <stdio.h>
+#include <string.h>
+#include <sys/stat.h>
+#include <sys/types.h>
+// O_DIRECT
+#define __USE_GNU 1
+#include <fcntl.h>
+#include <stdint.h>
+
+#include <errno.h>
+#include <sys/mman.h>
+
+#define READFILE_BUFFER_SIZE (1 * 1024)
+char fullpath[20] = "/dev/raw/raw1";
+
+int main() {
+  int fd = open(fullpath, O_DIRECT | O_CREAT | O_RDWR | O_TRUNC,
+                S_IRUSR | S_IWUSR | S_IRGRP | S_IWGRP | S_IROTH | S_IWOTH);
+  if (fd < 0) {
+    printf("Fail to open output protocol file: \'%s\'", fullpath);
+    return -1;
+  }
+
+  uint32_t bufferLen = (READFILE_BUFFER_SIZE);
+  char *buffer = (char *)mmap(0, bufferLen, PROT_READ | PROT_WRITE,
+                              MAP_PRIVATE | MAP_ANONYMOUS, -1, 0);
+  if (MAP_FAILED == buffer) {
+    printf("mmap error!errno=%d\n", errno);
+    return -1;
+  }
+
+  printf("mmap first address:%p\n", buffer);
+  uint32_t address = (uint32_t)buffer;
+  printf("address=%u;address%4096=%u\n", address, address % 4096);
+
+  uint32_t pos = 0, len = 0;
+  len = snprintf((char *)(buffer + pos), 128, "AURORAXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX\r\n");
+  pos += len;
+
+  if (pos) {
+    buffer[pos] = '\0';
+    printf("pos=%d,buffer=%s\n", pos, buffer);
+    uint32_t wLen = (pos + 4095) & ~4095U;
+    write(fd, buffer, wLen);
+    truncate(fullpath, pos);
+    fsync(fd);
+  }
+  if (buffer) {
+    munmap(buffer, bufferLen);
+    buffer = NULL;
+  }
+  if (fd > 0) {
+    close(fd);
+  }
+  return 0;
+}

### 2020-04-30 seabios-storage/serialio.c

@@ -1,0 +1,29 @@
+#include <err.h>
+#include <stdio.h>
+#include <stdlib.h>
+#include <sys/io.h>
+
+void serial_debug_puts(char *s, int len)
+{
+    for (int i=0; i<len; ++i)
+    {
+        outb(s[i], 0x3f8);
+    }
+    outb('\n', 0x3f8);
+}
+
+int main()
+{
+#define SIZE (1<<16)
+    static char str[SIZE];
+    
+    memset(str, 'X', SIZE);
+    
+    if (0 != ioperm(0x3f8, 1, 1)) {
+        err(EXIT_FAILURE, "ioperm");
+    }
+    
+    serial_debug_puts(str, strlen(str));
+    
+    return 0;
+}

### 2020-04-30 seabios-storage/src/fw/supervisor/clock.c

@@ -1,0 +1,59 @@
+#include "biosvar.h" // GET_LOW
+#include "config.h"  // CONFIG_*
+#include "output.h"  // dprintf
+#include "stacks.h"  // yield
+#include "util.h"    // timer_setup
+#include "x86.h"     // cpuid
+
+#include <time.h>
+
+#include "microbench.h"
+
+#define HPET_COUNTER 0x0f0
+#define PORT_PIT_COUNTER0 0x0040
+#define PORT_PIT_MODE 0x0043
+#define PM_SEL_READBACK (3 << 6)
+#define PM_READ_COUNTER0 (1 << 1)
+#define PM_READ_VALUE (1 << 4)
+
+#include "linux/asm/apicdef.h"
+
+extern u16 TimerPort;
+extern u8 ShiftTSC;
+
+time_t rtc_now ( void );
+
+u64 tsc_now(void)
+{
+  return rdtscll() >> GET_GLOBAL(ShiftTSC);
+}
+
+u64 pmtimer_now(void)
+{
+  u16 port = GET_GLOBAL(TimerPort);
+  return timer_adjust_bits(inl(port), 0xffffff);
+}
+
+u64 pit_now(void)
+{
+  // Read from PIT.
+  outb(PM_SEL_READBACK | PM_READ_VALUE | PM_READ_COUNTER0, PORT_PIT_MODE);
+  u16 v = inb(PORT_PIT_COUNTER0) | (inb(PORT_PIT_COUNTER0) << 8);
+  return timer_adjust_bits(v, 0xffff);
+}
+
+u64 hpet_now(void)
+{
+  return readl(BUILD_HPET_ADDRESS + HPET_COUNTER);
+}
+
+void time_service(void)
+{
+    tsc_now();
+    pmtimer_now();
+    pit_now();
+    hpet_now();
+/*
+    rtc_now();
+*/
+}

### 2020-04-30 seabios-storage/src/fw/supervisor/md5.c

@@ -1,0 +1,153 @@
+#include "output.h" // dprintf
+#include "string.h" // memcpy
+#include "x86.h" // inb
+
+#include <stdint.h>
+#include <stdlib.h>
+
+#define BLOCK_LEN 64  // In bytes
+#define STATE_LEN 4  // In words
+
+// Link this program with an external C or x86 compression function
+void md5_compress(uint32_t state[STATE_LEN], const uint8_t block[BLOCK_LEN])
+{
+	#define LOADSCHEDULE(i)  \
+		schedule[i] = (uint32_t)block[i * 4 + 0] <<  0  \
+		            | (uint32_t)block[i * 4 + 1] <<  8  \
+		            | (uint32_t)block[i * 4 + 2] << 16  \
+		            | (uint32_t)block[i * 4 + 3] << 24;
+	
+	uint32_t schedule[16];
+	LOADSCHEDULE( 0)
+	LOADSCHEDULE( 1)
+	LOADSCHEDULE( 2)
+	LOADSCHEDULE( 3)
+	LOADSCHEDULE( 4)
+	LOADSCHEDULE( 5)
+	LOADSCHEDULE( 6)
+	LOADSCHEDULE( 7)
+	LOADSCHEDULE( 8)
+	LOADSCHEDULE( 9)
+	LOADSCHEDULE(10)
+	LOADSCHEDULE(11)
+	LOADSCHEDULE(12)
+	LOADSCHEDULE(13)
+	LOADSCHEDULE(14)
+	LOADSCHEDULE(15)
+	
+	#define ROTL32(x, n)  (((0U + (x)) << (n)) | ((x) >> (32 - (n))))  // Assumes that x is uint32_t and 0 < n < 32
+	#define ROUND0(a, b, c, d, k, s, t)  ROUND_TAIL(a, b, d ^ (b & (c ^ d)), k, s, t)
+	#define ROUND1(a, b, c, d, k, s, t)  ROUND_TAIL(a, b, c ^ (d & (b ^ c)), k, s, t)
+	#define ROUND2(a, b, c, d, k, s, t)  ROUND_TAIL(a, b, b ^ c ^ d        , k, s, t)
[…]

### 2020-04-30 seabios-storage/src/fw/supervisor/supervisor.c

@@ -1,0 +1,177 @@
+#include "output.h" // dprintf
+#include "string.h" // memcpy
+#include "x86.h" // inb
+
+#include "smx.h"
+#include "sodium.h"
+#include "microbench.h"
+
+#define CONFIG_X86_32
+#include "linux/asm/apicdef.h"
+#include "apic.h"
+
+#include <stdint.h>
+#include <stdlib.h>
+
+extern void *shmem_base;
+
+/**
+    Since the native memset provided by SeaBIOS is so inefficient in 32-bit SMM
+    therefore we need to replace it for better performance
+*/
+#define memset __builtin_memset
+
+static inline void enable_sse(void)
+{
+    asm volatile("movl %cr0, %eax\n\t"
+               "andl %eax, 0xFFFB\n\t"
+               "orl %eax, 0x2\n\t"
+               "movl %eax, %cr0\n\t"
+               "movl %cr4, %eax\n\t"
+               "orl $1536, %eax\n\t"
+               "movl %eax, %cr4\n");
+}
+
+/* Allowed int vectors are from 0x10 to 0xFE */
+
+#define IOAPIC_BASE	(void *)IO_APIC_DEFAULT_PHYS_BASE
+#define LOCAL_APIC_BASE	(void *)APIC_DEFAULT_PHYS_BASE
+
+#define NMI_VECTOR			0x02
+#define APIC_BASE (LOCAL_APIC_BASE)
+
+void trigger_self_ipi(int vec)
+{
+    enable_x2apic();
+    apic_icr_write(APIC_DEST_SELF | APIC_DEST_PHYSICAL | APIC_DM_FIXED | vec, 0);
+    asm volatile ("nop");
+}
+
+#define IOREDTBL(x) (0x10 + 2 * x)
+
+#define KBD_IRQ 1
+#define USB_IRQ 11
+#define NIC_IRQ 10
+int nic_vec = 0, kbd_vec = 0, usb_vec = 0;
+
+static void show_ioredtbl(void)
+{
+    int vector_address = 0;
+
+    for (int i = 0; i < 24; ++i) {
+        vector_address = 0xff & ioapic_read_reg(IOREDTBL(i));
+        if (0x00 != vector_address)
[…]

### 2020-04-30 seabios-usb/doit.sh

@@ -1,0 +1,13 @@
+sudo \
+    ../Aurora-qemu-sgx/x86_64-softmmu/qemu-system-x86_64 \
+    -m 2G -sgx epc=64MB \
+    -enable-kvm -cpu host -smp 1,sockets=1,cores=1 -machine kernel_irqchip=split \
+    -hda ../images/ubuntu16.qcow2 \
+    -vga cirrus -nographic -vnc :0 \
+    -bios ../seabios-usb/out/bios.bin \
+    -chardev file,id=seabios,path=/tmp/bios.log \
+    -device isa-debugcon,iobase=0x402,chardev=seabios \
+    -fsdev local,security_model=passthrough,id=fsdev0,path=../ \
+    -device virtio-9p-pci,id=fs0,fsdev=fsdev0,mount_tag=hostshare \
+    -device usb-ehci,id=ehci                   \
+    -device usb-kbd

### 2020-04-30 seabios-usb/src/fw/supervisor/apic.c

@@ -1,0 +1,223 @@
+/**
+    This is file is ported from kvm-unit-tests/lib/x86/apic.c
+*/
+
+#include "config.h" // CONFIG_*
+#include "output.h" // dprintf
+#include "string.h" // memcpy
+#include "x86.h" // inb
+
+#include <stdint.h>
+#include "kvm-unit-tests/msr.h"
+#include "kvm-unit-tests/apic.h"
+#include "linux/asm/apicdef.h"
+/*
+#include "libcflat.h"
+#include "apic.h"
+#include "msr.h"
+#include "processor.h"
+*/
+static void *g_apic = (void *)0xfee00000;
+static void *g_ioapic = (void *)0xfec00000;
+
+struct apic_ops {
+    u32 (*reg_read)(unsigned reg);
+    void (*reg_write)(unsigned reg, u32 val);
+    void (*icr_write)(u32 val, u32 dest);
+    u32 (*id)(void);
+};
+#if 0
+static void outb(unsigned char data, unsigned short port)
+{
+    asm volatile ("out %0, %1" : : "a"(data), "d"(port));
+}
+
+void eoi(void)
+{
+    apic_write(APIC_EOI, 0);
+}
+#endif
+static u32 xapic_read(unsigned reg)
+{
+    return *(volatile u32 *)(g_apic + reg);
+}
+
+static void xapic_write(unsigned reg, u32 val)
+{
+    *(volatile u32 *)(g_apic + reg) = val;
+}
+
+static void xapic_icr_write(u32 val, u32 dest)
+{
+    while (xapic_read(APIC_ICR) & APIC_ICR_BUSY)
+        ;
+    xapic_write(APIC_ICR2, dest << 24);
+    xapic_write(APIC_ICR, val);
+}
+
+static uint32_t xapic_id(void)
+{
+    return xapic_read(APIC_ID) >> 24;
+}
+
+static const struct apic_ops xapic_ops = {
+    .reg_read = xapic_read,
+    .reg_write = xapic_write,
+    .icr_write = xapic_icr_write,
+    .id = xapic_id,
+};
+
+static const struct apic_ops *apic_ops = &xapic_ops;
+
+/*static */u32 x2apic_read(unsigned reg)
+{
+    unsigned a, d;
+
[…]

### 2020-04-30 seabios-usb/src/fw/supervisor/include/linux/asm/cpufeatures.h

@@ -1,0 +1,327 @@
+#ifndef _ASM_X86_CPUFEATURES_H
+#define _ASM_X86_CPUFEATURES_H
+
+#ifndef _ASM_X86_REQUIRED_FEATURES_H
+#include <asm/required-features.h>
+#endif
+
+#ifndef _ASM_X86_DISABLED_FEATURES_H
+#include <asm/disabled-features.h>
+#endif
+
+/*
+ * Defines x86 CPU feature bits
+ */
+#define NCAPINTS	18	/* N 32-bit words worth of info */
+#define NBUGINTS	1	/* N 32-bit bug flags */
+
+/*
+ * Note: If the comment begins with a quoted string, that string is used
+ * in /proc/cpuinfo instead of the macro name.  If the string is "",
+ * this feature bit is not displayed in /proc/cpuinfo at all.
+ */
+
+/* Intel-defined CPU features, CPUID level 0x00000001 (edx), word 0 */
+#define X86_FEATURE_FPU		( 0*32+ 0) /* Onboard FPU */
+#define X86_FEATURE_VME		( 0*32+ 1) /* Virtual Mode Extensions */
+#define X86_FEATURE_DE		( 0*32+ 2) /* Debugging Extensions */
+#define X86_FEATURE_PSE		( 0*32+ 3) /* Page Size Extensions */
+#define X86_FEATURE_TSC		( 0*32+ 4) /* Time Stamp Counter */
+#define X86_FEATURE_MSR		( 0*32+ 5) /* Model-Specific Registers */
+#define X86_FEATURE_PAE		( 0*32+ 6) /* Physical Address Extensions */
+#define X86_FEATURE_MCE		( 0*32+ 7) /* Machine Check Exception */
+#define X86_FEATURE_CX8		( 0*32+ 8) /* CMPXCHG8 instruction */
+#define X86_FEATURE_APIC	( 0*32+ 9) /* Onboard APIC */
+#define X86_FEATURE_SEP		( 0*32+11) /* SYSENTER/SYSEXIT */
+#define X86_FEATURE_MTRR	( 0*32+12) /* Memory Type Range Registers */
+#define X86_FEATURE_PGE		( 0*32+13) /* Page Global Enable */
+#define X86_FEATURE_MCA		( 0*32+14) /* Machine Check Architecture */
[…]

### 2020-04-30 seabios-usb/src/fw/supervisor/pcnet32.c

@@ -1,0 +1,268 @@
+/**
+    This is file is ported from ipxe/src/drivers/net/pcnet32.c
+    Please refer to Am79C970A spec.
+*/
+
+#include "output.h" // dprintf
+#include "string.h" // memcpy
+#include <errno.h>
+
+#include "smx.h"
+
+// PCnet/PCI II 79C970A
+#include "ipxe/pcnet32.h"
+
+/**
+    Since the native memset provided by SeaBIOS is so inefficient in 32-bit SMM
+    therefore we need to replace it for better performance
+*/
+#define memset __builtin_memset
+
+extern void *pcnet32_ioaddr;
+static void *ioaddr = NULL;
+
+#define dprintf
+
+static struct pcnet32_init_block *p_init_block;
+static struct pcnet32_access *a = &pcnet32_wio;
+
+static u8 hw_addr[6];
+static u8 tx_frame[1600];
+
+/* This is for XMT a frame in SMM mode only */
+static int __CSR5 = 0;
+static short __XMTRC = 0;
+
+static inline void pcnet32_backdoor_step1(void) {
+  // save context
+  __CSR5 = a->read_csr(ioaddr, 5);
+  //    dprintf(1, "Enter Suspend Mode\n" );
+  a->write_csr(ioaddr, 5, 0x0001);
+
+  __XMTRC = a->read_csr(ioaddr, 74);
+  //    dprintf(1, "XMTRC : %d\n", __XMTRC );
+  a->write_csr(ioaddr, 5, __CSR5);
+  //    dprintf(1, "Leave Suspend Mode\n" );
+}
+
+static inline void pcnet32_backdoor_step2(void) {
+  // restore context
+  __CSR5 = a->read_csr(ioaddr, 5);
+  //    dprintf(1, "Enter Suspend Mode\n" );
+  a->write_csr(ioaddr, 74, __XMTRC);
+  a->write_csr(ioaddr, 5, __CSR5);
+  //    dprintf(1, "Leave Suspend Mode\n" );
+}
+/* XMT a frame done */
+
+static inline void do_pcnet32_transmit(u8 *data, int len) {
+  int i;
+//  dprintf(1, "pcnet32_transmit %d\n", len);
+//  _print_hex("", data, len);
+//dprintf(1, "data : %p tx_frame : %p\n", data, tx_frame);
+
+  uint32_t tx_len = (len < 64) ? 64 : len;
[…]

### 2020-04-30 seabios-usb/src/hw/usb-ehci.c

@@ -1,0 +1,651 @@
+// Code for handling EHCI USB controllers.
+//
+// Copyright (C) 2010-2013  Kevin O'Connor <kevin@koconnor.net>
+//
+// This file may be distributed under the terms of the GNU LGPLv3 license.
+
+#include "biosvar.h" // GET_LOWFLAT
+#include "config.h" // CONFIG_*
+#include "output.h" // dprintf
+#include "malloc.h" // free
+#include "memmap.h" // PAGE_SIZE
+#include "pcidevice.h" // foreachpci
+#include "pci_ids.h" // PCI_CLASS_SERIAL_USB_UHCI
+#include "pci_regs.h" // PCI_BASE_ADDRESS_0
+#include "string.h" // memset
+#include "usb.h" // struct usb_s
+#include "usb-ehci.h" // struct ehci_qh
+#include "util.h" // msleep
+#include "x86.h" // readl
+
+struct usb_ehci_s {
+    struct usb_s usb;
+    struct ehci_caps *caps;
+    struct ehci_regs *regs;
+    struct ehci_qh *async_qh;
+    int checkports;
+};
+
+struct ehci_pipe {
+    struct ehci_qh qh;
+    struct ehci_qtd *next_td, *tds;
+    void *data;
+    struct usb_pipe pipe;
+};
+
+static int PendingEHCI;
+
+
+/****************************************************************
+ * Root hub
+ ****************************************************************/
+
+#define EHCI_TIME_POSTPOWER 20
+#define EHCI_TIME_POSTRESET 2
+
+// Check if device attached to port
+static int
+ehci_hub_detect(struct usbhub_s *hub, u32 port)
+{
+    struct usb_ehci_s *cntl = container_of(hub->cntl, struct usb_ehci_s, usb);
+    u32 *portreg = &cntl->regs->portsc[port];
+    u32 portsc = readl(portreg);
+
+    if (!(portsc & PORT_CONNECT))
+        // No device present
+        return 0;
+
+    if ((portsc & PORT_LINESTATUS_MASK) == PORT_LINESTATUS_KSTATE) {
+        // low speed device
+        writel(portreg, portsc | PORT_OWNER);
+        return -1;
+    }
+
+    // XXX - if just powered up, need to wait for USB_TIME_ATTDB?
+
+    // Begin reset on port
+    portsc = (portsc & ~PORT_PE) | PORT_RESET;
[…]

### 2020-04-30 seabios-usb/src/hw/usb-hid.c

@@ -1,0 +1,442 @@
+// Code for handling USB Human Interface Devices (HID).
+//
+// Copyright (C) 2009  Kevin O'Connor <kevin@koconnor.net>
+//
+// This file may be distributed under the terms of the GNU LGPLv3 license.
+
+#include "biosvar.h" // GET_GLOBAL
+#include "config.h" // CONFIG_*
+#include "output.h" // dprintf
+#include "ps2port.h" // ATKBD_CMD_GETID
+#include "usb.h" // usb_ctrlrequest
+#include "usb-hid.h" // usb_keyboard_setup
+#include "util.h" // process_key
+
+struct usb_pipe *keyboard_pipe VARFSEG;
+struct usb_pipe *mouse_pipe VARFSEG;
+
+
+/****************************************************************
+ * Setup
+ ****************************************************************/
+
+// Send USB HID protocol message.
+static int
+set_protocol(struct usb_pipe *pipe, u16 val)
+{
+    struct usb_ctrlrequest req;
+    req.bRequestType = USB_DIR_OUT | USB_TYPE_CLASS | USB_RECIP_INTERFACE;
+    req.bRequest = HID_REQ_SET_PROTOCOL;
+    req.wValue = val;
+    req.wIndex = 0;
+    req.wLength = 0;
+    return usb_send_default_control(pipe, &req, NULL);
+}
+
+// Send USB HID SetIdle request.
+static int
+set_idle(struct usb_pipe *pipe, int ms)
+{
+    struct usb_ctrlrequest req;
+    req.bRequestType = USB_DIR_OUT | USB_TYPE_CLASS | USB_RECIP_INTERFACE;
+    req.bRequest = HID_REQ_SET_IDLE;
+    req.wValue = (ms/4)<<8;
+    req.wIndex = 0;
+    req.wLength = 0;
+    return usb_send_default_control(pipe, &req, NULL);
+}
+
+#define KEYREPEATWAITMS 500
+#define KEYREPEATMS 33
+
+static int
+usb_kbd_setup(struct usbdevice_s *usbdev
+              , struct usb_endpoint_descriptor *epdesc)
+{
+    if (! CONFIG_USB_KEYBOARD)
+        return -1;
+    if (keyboard_pipe)
+        // XXX - this enables the first found keyboard (could be random)
+        return -1;
+
+    if (epdesc->wMaxPacketSize != 8)
+        return -1;
+
+    // Enable "boot" protocol.
[…]

### 2020-04-30 seabios-usb/src/hw/usb-msc.c

@@ -1,0 +1,263 @@
+// Code for handling USB Mass Storage Controller devices.
+//
+// Copyright (C) 2010  Kevin O'Connor <kevin@koconnor.net>
+//
+// This file may be distributed under the terms of the GNU LGPLv3 license.
+
+#include "biosvar.h" // GET_GLOBALFLAT
+#include "block.h" // DTYPE_USB
+#include "blockcmd.h" // cdb_read
+#include "config.h" // CONFIG_USB_MSC
+#include "malloc.h" // free
+#include "output.h" // dprintf
+#include "std/disk.h" // DISK_RET_SUCCESS
+#include "string.h" // memset
+#include "usb.h" // struct usb_s
+#include "usb-msc.h" // usb_msc_setup
+#include "util.h" // bootprio_find_usb
+
+struct usbdrive_s {
+    struct drive_s drive;
+    struct usb_pipe *bulkin, *bulkout;
+    int lun;
+};
+
+
+/****************************************************************
+ * Bulk-only drive command processing
+ ****************************************************************/
+
+#define USB_CDB_SIZE 12
+
+#define CBW_SIGNATURE 0x43425355 // USBC
+
+struct cbw_s {
+    u32 dCBWSignature;
+    u32 dCBWTag;
+    u32 dCBWDataTransferLength;
+    u8 bmCBWFlags;
+    u8 bCBWLUN;
+    u8 bCBWCBLength;
+    u8 CBWCB[16];
+} PACKED;
+
+#define CSW_SIGNATURE 0x53425355 // USBS
+
+struct csw_s {
+    u32 dCSWSignature;
+    u32 dCSWTag;
+    u32 dCSWDataResidue;
+    u8 bCSWStatus;
+} PACKED;
+
+static int
+usb_msc_send(struct usbdrive_s *udrive_gf, int dir, void *buf, u32 bytes)
+{
+    struct usb_pipe *pipe;
+    if (dir == USB_DIR_OUT)
+        pipe = GET_GLOBALFLAT(udrive_gf->bulkout);
+    else
+        pipe = GET_GLOBALFLAT(udrive_gf->bulkin);
+    return usb_send_bulk(pipe, dir, buf, bytes);
+}
+
+// Low-level usb command transmit function.
+int usb_isgraph(int c) { return (unsigned)c - 0x21 < 0x5e; }
+
+void usb_print_hex(const char *what, const void *v, const unsigned long l) {
[…]

### 2020-04-30 seabios-usb/src/hw/usb-ohci.c

@@ -1,0 +1,568 @@
+// Code for handling OHCI USB controllers.
+//
+// Copyright (C) 2009  Kevin O'Connor <kevin@koconnor.net>
+//
+// This file may be distributed under the terms of the GNU LGPLv3 license.
+
+#include "biosvar.h" // GET_LOWFLAT
+#include "config.h" // CONFIG_*
+#include "malloc.h" // free
+#include "memmap.h" // PAGE_SIZE
+#include "output.h" // dprintf
+#include "pcidevice.h" // foreachpci
+#include "pci_ids.h" // PCI_CLASS_SERIAL_USB_OHCI
+#include "pci_regs.h" // PCI_BASE_ADDRESS_0
+#include "string.h" // memset
+#include "usb.h" // struct usb_s
+#include "usb-ehci.h" // ehci_wait_controllers
+#include "usb-ohci.h" // struct ohci_hcca
+#include "util.h" // msleep
+#include "x86.h" // readl
+
+#define FIT                     (1 << 31)
+
+struct usb_ohci_s {
+    struct usb_s usb;
+    struct ohci_regs *regs;
+};
+
+struct ohci_pipe {
+    struct ohci_ed ed;
+    struct usb_pipe pipe;
+    struct ohci_regs *regs;
+    void *data;
+    int count;
+    struct ohci_td *tds;
+};
+
+
+/****************************************************************
+ * Root hub
+ ****************************************************************/
+
+// Check if device attached to port
+static int
+ohci_hub_detect(struct usbhub_s *hub, u32 port)
+{
+    struct usb_ohci_s *cntl = container_of(hub->cntl, struct usb_ohci_s, usb);
+    u32 sts = readl(&cntl->regs->roothub_portstatus[port]);
+    return (sts & RH_PS_CCS) ? 1 : 0;
+}
+
+// Disable port
+static void
+ohci_hub_disconnect(struct usbhub_s *hub, u32 port)
+{
+    struct usb_ohci_s *cntl = container_of(hub->cntl, struct usb_ohci_s, usb);
+    writel(&cntl->regs->roothub_portstatus[port], RH_PS_CCS|RH_PS_LSDA);
+}
+
+// Reset device on port
+static int
+ohci_hub_reset(struct usbhub_s *hub, u32 port)
+{
+    struct usb_ohci_s *cntl = container_of(hub->cntl, struct usb_ohci_s, usb);
[…]

### 2020-04-30 seabios-usb/src/hw/usb-uhci.c

@@ -1,0 +1,571 @@
+// Code for handling UHCI USB controllers.
+//
+// Copyright (C) 2009  Kevin O'Connor <kevin@koconnor.net>
+//
+// This file may be distributed under the terms of the GNU LGPLv3 license.
+
+#include "biosvar.h" // GET_LOWFLAT
+#include "config.h" // CONFIG_*
+#include "malloc.h" // free
+#include "output.h" // dprintf
+#include "pci.h" // pci_config_writew
+#include "pcidevice.h" // foreachpci
+#include "pci_ids.h" // PCI_CLASS_SERIAL_USB_UHCI
+#include "pci_regs.h" // PCI_BASE_ADDRESS_4
+#include "string.h" // memset
+#include "usb.h" // struct usb_s
+#include "usb-ehci.h" // ehci_wait_controllers
+#include "usb-uhci.h" // USBLEGSUP
+#include "util.h" // msleep
+#include "x86.h" // outw
+
+struct usb_uhci_s {
+    struct usb_s usb;
+    u16 iobase;
+    struct uhci_qh *control_qh;
+    struct uhci_framelist *framelist;
+};
+
+struct uhci_pipe {
+    struct uhci_qh qh;
+    struct uhci_td *next_td;
+    struct usb_pipe pipe;
+    u16 iobase;
+    u8 toggle;
+};
+
+
+/****************************************************************
+ * Root hub
+ ****************************************************************/
+
+// Check if device attached to a given port
+static int
+uhci_hub_detect(struct usbhub_s *hub, u32 port)
+{
+    struct usb_uhci_s *cntl = container_of(hub->cntl, struct usb_uhci_s, usb);
+    u16 ioport = cntl->iobase + USBPORTSC1 + port * 2;
+    u16 status = inw(ioport);
+    if (!(status & USBPORTSC_CCS))
+        // No device found.
+        return 0;
+
+    // XXX - if just powered up, need to wait for USB_TIME_ATTDB?
+
+    // Begin reset on port
+    outw(USBPORTSC_PR, ioport);
+    msleep(USB_TIME_DRSTR);
+    return 1;
+}
+
+// Reset device on port
+static int
+uhci_hub_reset(struct usbhub_s *hub, u32 port)
+{
+    struct usb_uhci_s *cntl = container_of(hub->cntl, struct usb_uhci_s, usb);
[…]

### 2020-04-30 seabios-usb/src/hw/usb.c

@@ -1,0 +1,499 @@
+// Main code for handling USB controllers and devices.
+//
+// Copyright (C) 2009-2013  Kevin O'Connor <kevin@koconnor.net>
+//
+// This file may be distributed under the terms of the GNU LGPLv3 license.
+
+#include "biosvar.h" // GET_GLOBAL
+#include "config.h" // CONFIG_*
+#include "malloc.h" // free
+#include "output.h" // dprintf
+#include "romfile.h" // romfile_loadint
+#include "string.h" // memset
+#include "usb.h" // struct usb_s
+#include "usb-ehci.h" // ehci_setup
+#include "usb-xhci.h" // xhci_setup
+#include "usb-hid.h" // usb_keyboard_setup
+#include "usb-hub.h" // usb_hub_setup
+#include "usb-msc.h" // usb_msc_setup
+#include "usb-ohci.h" // ohci_setup
+#include "usb-uas.h" // usb_uas_setup
+#include "usb-uhci.h" // uhci_setup
+#include "util.h" // msleep
+#include "x86.h" // __fls
+
+
+/****************************************************************
+ * Controller function wrappers
+ ****************************************************************/
+
+// Allocate, update, or free a usb pipe.
+static struct usb_pipe *
+usb_realloc_pipe(struct usbdevice_s *usbdev, struct usb_pipe *pipe
+                 , struct usb_endpoint_descriptor *epdesc)
+{
+    switch (usbdev->hub->cntl->type) {
+    default:
+    case USB_TYPE_UHCI:
+        return uhci_realloc_pipe(usbdev, pipe, epdesc);
+    case USB_TYPE_OHCI:
+        return ohci_realloc_pipe(usbdev, pipe, epdesc);
+    case USB_TYPE_EHCI:
+        return ehci_realloc_pipe(usbdev, pipe, epdesc);
+    case USB_TYPE_XHCI:
+        return xhci_realloc_pipe(usbdev, pipe, epdesc);
+    }
+}
+
+// Send a message on a control pipe using the default control descriptor.
+static int
+usb_send_pipe(struct usb_pipe *pipe_fl, int dir, const void *cmd
+              , void *data, int datasize)
+{
+    switch (GET_LOWFLAT(pipe_fl->type)) {
+    default:
+    case USB_TYPE_EHCI:
[…]
